---
title: "Create Observational Measures Codebook"
---

```{r}
# Load necessary packages and functions
library(codebookr)
library(dplyr, warn.conflicts = FALSE)
library(readr)
source("../r/variable_descriptions.R")
```

# Purpose of the program

Using the CodebookR package, we will create a data dictionary for follow-up interview data for the DETECT project pertaining to observational measures.

# Load cleaned data

```{r}
obs <- read_rds("../data/cleaned_rds_files/observational_measures_import.rds")
```

# Set column attributes

```{r}
#Set the source to "DETECT Follow-up Interview Questions Observational Measures" for all the variables
obs_vars <- obs %>% 
  names()

for(i in obs_vars) {
  attr(obs[[i]], "source") <- "DETECT Follow-up Interview Questions Observational Measures"
}
```

```{r}
# Choose variables that will not have summary statistics
no_stats <- obs %>%
  select(
    c(matches("^(x|xc)_"), matches("^(name)"), medstar_id, matches("_comments$"), matches("_why$"), aps_reported_confirmation_number)
  )

no_stats_vars <- colnames(no_stats)
```


```{r}
# Add column attributes to all variables
observational_measures <- obs %>%
    cb_add_col_attributes( 
      x_primary_key, 
      description = "Unique record ID used internally by the database."
    ) %>%
  
    cb_add_col_attributes( 
      x_created_by, 
      description = "Person who created the record."
    ) %>%
  
    cb_add_col_attributes( 
      x_created_timestamp, 
      description = "Timestamp when the record was created.",
      col_type = "Time"
    ) %>%
  
    cb_add_col_attributes( 
      x_modified_by, 
      description = "Person who modified the record."
    ) %>%
  
    cb_add_col_attributes( 
      x_modified_timestamp, 
      description = "Timestamp when the record was modified.",
      col_type = "Time"
    ) %>%
  
    cb_add_col_attributes( 
      x_error_message, 
      description = "Error message entered by research team."
    ) %>%
  
    cb_add_col_attributes( 
      medstar_id, 
      description = "Unique record number in MedStar System."
    ) %>%
  
    cb_add_col_attributes( 
      name_full, 
      description = "Full name of older individual."
    ) %>%
  
    cb_add_col_attributes( 
      x_record_status, 
      description = "Status of the record as determined by research team."
    ) %>%
  
    cb_add_col_attributes( 
      x_record_month, 
      description = "Month record was created.",
      col_type = "Time"
    ) %>%
  
    cb_add_col_attributes( 
      x_record_year, 
      description = "Year record was created.",
      col_type = "Time"
    ) %>%
  
    cb_add_col_attributes( 
      x_record_comment, 
      description = "Comments by interviewer."
    ) %>%
  
     cb_add_col_attributes( 
      xc_case_id, 
      description = "Identifier derived by the database from the last 5 characters of the MedstarID."
    ) %>%
  
     cb_add_col_attributes( 
      xc_lead_panel_summary_count, 
      description = "Calculated total count of positive abuse instances across self report, ApsInvestigations, and observational measures."
     ) %>%
  
     cb_add_col_attributes( 
       xc_lead_panel_summary_comment_count, 
       description = "Calculated count of comments provided by the medic, excluding for phrases such as 'No', 'Nothing to report.', etc."
     ) %>%
    
     cb_add_col_attributes( 
       xc_lead_panel_summary, 
       description = "Summary of positive abuse instances across self report, ApsInvestigations, and observational measures."
     ) %>%
  
    cb_add_col_attributes( 
      neglect_comments, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Additional comments. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      exploitation_comments, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Additional comments. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      abandonment_comments, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abandonment Indicators: Additional comments. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      summary_comments, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale - Environment status of subject: Summary - Additional comments. Question from earlier version of follow-up interview."
    ) %>%
   
    cb_add_col_attributes( 
      general_assessment_comments, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale - General Assessment: Additional Comments. Question from earlier version of follow-up interview."
    ) %>%

      cb_add_col_attributes( 
      abuse_indicators_comments, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale - Possible Abuse Indicators: Additional Comments. Question from earlier version of follow-up interview."
    ) %>%
 
     cb_add_col_attributes( 
      at_phys_why, 
      description = "AT_1a. Why do you believe physical abuse has or has not occurred?"
    ) %>%
  
    cb_add_col_attributes( 
      at_sex_why, 
      description = "AT_2a. Why do you believe sexual abuse has or has not occurred?"
    ) %>%
  
    cb_add_col_attributes( 
      at_emot_why, 
      description = "AT_3a. Why do you believe emotional or psychological abuse has or has not occurred?"
    ) %>%

    cb_add_col_attributes( 
      at_neg_why, 
      description = "AT_4a. Why do you believe neglect has or has not occurred?"
    ) %>%
  
    cb_add_col_attributes( 
      at_aban_why, 
      description = "AT_5a. Why do you believe abandonment has or has not occurred?"
    ) %>%

    cb_add_col_attributes( 
      at_fina_why, 
      description = "AT_6a. Why do you believe financial or material exploitation has or hasn’t occurred?"
    ) %>%

    cb_add_col_attributes( 
      at_self_why, 
      description = "AT_7a. Why do you believe self-neglect has or has not occurred?"
    ) %>%
  
    cb_add_col_attributes( 
      clothes_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale General Assessment: Clothes. Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - Clean/neat"  = 0,
        "1"               = 1,
        "2"               = 2,
        "3"               = 3,
        "4 - Very soiled" = 4
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      clothes_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale General Assessment: Clothes. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      hair_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale General Assessment: Hair. Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - Clean/combed" = 0,
        "1"                = 1,
        "2"                = 2,
        "3"                = 3,
        "4 - Matted/dirty" = 4
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      hair_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale General Assessment: Hair. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      nails_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale General Assessment: Nails. Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - Clean/trimmed"        = 0,
        "1"                        = 1,
        "2"                        = 2,
        "3"                        = 3,
        "4 - Long/untrimmed/dirty" = 4
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      nails_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale General Assessment: Nails. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      bruising_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Bruising. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      lacerations_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Lacerations. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      fractures_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Fractures. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      stages_healing_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Various stages of healing of any bruises or fractures/ Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      sexual_abuse_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Evidence of sexual abuse. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      abuse_statement_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Statement by older adult related to abuse. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      contracture_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Contractures. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      decubitus_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Decubitii Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      dehydration_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Dehydration. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      diarrhea_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Diarrhea. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      depression_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Depression. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      impaction_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Impaction. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      malnutrition_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Malnutrition. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      urine_burn_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Urine burns. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      poor_hygiene_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Poor hygiene. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      obvious_disease_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators:  Failure to respond to warning of obvious disease. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      inappropriate_medication_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Inappropirate medications (over/under). Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      repetitive_hosp_admission_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Repetitive hospital admissions due to probable failure of health care surveillance. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      neglect_statement_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Statement by older adult related to neglect. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      money_misuse_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Misuse of money. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      evidence_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Evidence. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      goods_for_services_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Reports of demands for goods in exchange for service. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      inability_account_money_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Inability to account for money/property. Question from earlier version of follow-up interview."
    ) %>%

    cb_add_col_attributes( 
      exploitation_statement_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Statement by older adult related to exploitation. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      caretaker_withdrawn_care_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abandonment Indicators: Evidence that a caretaker has withdrawn care precipitously without alternate arrangements. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      left_alone_unsafe_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abandonment Indicators: Evidence that older adult is left alone in an unsafe environment for extended periods of time without adequate support. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      abandonment_statement_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abandonment Indicators: Statement by older adults regarding abandonment. Question from earlier version of follow-up interview."
    ) %>%
 
    cb_add_col_attributes( 
      exterior_condition_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Exterior condition. Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - Neat/well kept/no trash, debris"       = 0,
        "1"                                         = 1,
        "2"                                         = 2,
        "3"                                         = 3,
        "4 - Poorly maintained/trash, other debris" = 4
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      exterior_condition_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Exterior condition. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      yard_sidewalk_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Yard/Sidewalk. Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - Neat/well kept/no trash, debris" = 0,
        "1"                                   = 1,
        "2"                                   = 2,
        "3"                                   = 3,
        "4 - Poorly maintained/trash, debris" = 4
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      yard_sidewalk_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Yard/Sidewalk. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      roof_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Roof. Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - Intact/no structural damage"          = 0,
        "1"                                        = 1,
        "2"                                        = 2,
        "3"                                        = 3,
        "4 - Dilapidated/poorly maintained, holes" = 4
      ), 
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      roof_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Roof. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      walls_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Walls Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - Intact/no structural damage"          = 0,
        "1"                                        = 1,
        "2"                                        = 2,
        "3"                                        = 3,
        "4 - Dilapidated/poorly maintained, holes" = 4
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      walls_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Walls Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      windows_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Windows. Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - Intact/not broken or missing"     = 0,
        "1"                                    = 1,
        "2"                                    = 2,
        "3"                                    = 3,
        "4 - Multiple sections broken/missing" = 4
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      windows_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Windows. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      interior_condition_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Interior condition. Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - Intact/not broken or missing"     = 0,
        "1"                                    = 1,
        "2"                                    = 2,
        "3"                                    = 3,
        "4 - Multiple sections broken/missing" = 4
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      interior_condition_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Interior condition. Question from earlier version of follow-up interview."
    ) %>%
    
    cb_add_col_attributes( 
      odor_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Odor. Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - Normal household odor"                                              = 0,
        "1"                                                                      = 1,
        "2"                                                                      = 2,
        "3"                                                                      = 3,
        "4 - Pungent, unpleasant odor (may be human/animal waste, rotting food)" = 4
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      odor_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Odor. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      kitchen_cleanliness_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Cleanliness - Kitchen. Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - Clean, no evidence of unsanitary conditions" = 0,
        "1"                                               = 1,
        "2"                                               = 2,
        "3"                                               = 3,
        "4 - Very dirty, unwashed dishes, trash litter"   = 4
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      kitchen_cleanliness_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Cleanliness - Kitchen. Question from earlier version of follow-up interview."
    ) %>%
   
    cb_add_col_attributes( 
      bathroom_cleanliness_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Cleanliness - Bathroom. Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - Clean, no evidence of unsanitary conditions"  = 0,
        "1"                                                = 1,
        "2"                                                = 2,
        "3"                                                = 3,
        "4 - Very dirty, unwashed dishes, trash litter"    = 4
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      bathroom_cleanliness_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Cleanliness - Bathroom. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      bedroom_cleanliness_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Cleanliness - Bedroom. Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - Clean, no evidence of unsanitary conditions" = 0,
        "1"                                               = 1,
        "2"                                               = 2,
        "3"                                               = 3,
        "4 - Very dirty, unwashed dishes, trash litter"   = 4
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      bedroom_cleanliness_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Cleanliness - Bedroom. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      living_room_cleanliness_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Cleanliness - Living room.  Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - Clean, no evidence of unsanitary conditions" = 0,
        "1"                                               = 1,
        "2"                                               = 2,
        "3"                                               = 3,
        "4 - Very dirty, unwashed dishes, trash litter"   = 4
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      living_room_cleanliness_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Cleanliness - Living room.  Question from earlier version of follow-up interview."
    ) %>%
    
    cb_add_col_attributes( 
      clutter_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Clutter. Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - Neat/orderly"                                             = 0,
        "1"                                                            = 1,
        "2"                                                            = 2,
        "3"                                                            = 3,
        "4 - Very cluttered/difficult to move around or find things"   = 4
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      clutter_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Clutter. Question from earlier version of follow-up interview."
    ) %>%
   
    cb_add_col_attributes( 
      structural_problems_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Structural problems. Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - No structural problems"                                                     = 0,
        "1"                                                                              = 1,
        "2"                                                                              = 2,
        "3"                                                                              = 3,
        "4 - Severe structural damage (e.g., holes in sheetrock, floor leaking, ceiling" = 4
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      structural_problems_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Structural problems. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      pets_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Pets. Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - All animals cared for"    = 0,
        "1 or 2 - Uncared animals"     = 1,
        "3 or 4 - Uncared animals"     = 2,
        "5 or 6 - Uncared animals"     = 3,
        "6 or more -  Uncared animals" = 4
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      pets_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Pets. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      utilities_5cat, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Utilities. Question from earlier version of follow-up interview.",
      value_labels = c(
        "0 - All utilities work"             = 0,
        "1 - No phone"                       = 1,
        "2 - No gas/electricity"             = 2,
        "3 - No water"                       = 3,
        "4 - Multiple utilities do not work" = 4
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      utilities_5cat_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Utilities. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      summary_evidence_abuse_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Summary - Evidence of abuse. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      summary_evidence_neglect_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Summary - Evidence of neglect. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      summary_evidence_exploitation_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Summary - Evidence of exploitation. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      summary_evidence_abandonment_f, 
      description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Summary - Evidence of abandonment. Question from earlier version of follow-up interview."
    ) %>%
  
    cb_add_col_attributes( 
      at_physical_4cat, 
      description = "AT_1. Do you believe physical abuse has occurred?",
      value_labels = c(
        "Yes"        = 1,
        "No"         = 2,
        "Don't know" = 7,
        "Refused"    = 9
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      at_sexual_4cat, 
      description = "AT_2. Do you believe sexual abuse has occurred?",
      value_labels = c(
        "Yes"        = 1,
        "No"         = 2,
        "Don't know" = 7,
        "Refused"    = 9
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      at_emotional_4cat, 
      description = "AT_3. Do you believe emotional or psychological abuse has occurred?",
      value_labels = c(
        "Yes"        = 1,
        "No"         = 2,
        "Don't know" = 7,
        "Refused"    = 9
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      at_neglect_4cat, 
      description = "AT_4. Do you believe neglect has occurred?",
      value_labels = c(
        "Yes"        = 1,
        "No"         = 2,
        "Don't know" = 7,
        "Refused"    = 9
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      at_abandon_4cat, 
      description = "AT_5. Do you believe abandonment has occurred?",
      value_labels = c(
        "Yes"        = 1,
        "No"         = 2,
        "Don't know" = 7,
        "Refused"    = 9
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      at_financial_4cat, 
      description = "AT_6. Do you believe financial or material exploitation has occurred?",
      value_labels = c(
        "Yes"        = 1,
        "No"         = 2,
        "Don't know" = 7,
        "Refused"    = 9
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      at_self_4cat, 
      description = "AT_7. Do you believe self-neglect has occurred?",
      value_labels = c(
        "Yes"        = 1,
        "No"         = 2,
        "Don't know" = 7,
        "Refused"    = 9
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      at_physical_4cat_f, 
      description = "AT_1. Do you believe physical abuse has occurred?",
      value_labels = c(
        "Yes"        = 1,
        "No"         = 2,
        "Don't know" = 7,
        "Refused"    = 9
      ),
      col_type = "Categorical"
    ) %>%
  
    cb_add_col_attributes( 
      at_sexual_4cat_f, 
      description = "AT_2. Do you believe sexual abuse has occurred?"
    ) %>%
  
    cb_add_col_attributes( 
      at_emotional_4cat_f, 
      description = "AT_3. Do you believe emotional or psychological abuse has occurred?"
    ) %>%
  
    cb_add_col_attributes( 
      at_neglect_4cat_f, 
      description = "AT_4. Do you believe neglect has occurred?"
    ) %>%
  
    cb_add_col_attributes( 
      at_abandon_4cat_f, 
      description = "AT_5. Do you believe abandonment has occurred?"
    ) %>%
  
    cb_add_col_attributes( 
      at_financial_4cat_f, 
      description = "AT_6. Do you believe financial or material exploitation has occurred?"
    ) %>%
  
    cb_add_col_attributes( 
      at_self_4cat_f, 
      description = "AT_7. Do you believe self-neglect has occurred?"
    ) %>%
  
    cb_add_col_attributes( 
      aps_reported_f, 
      description = "No longer used - In the original observational measures, it would indicate if the medic submitted an APS report."
    ) %>%
  
    cb_add_col_attributes( 
      aps_reported_method_f, 
      description = "No longer used - In the original observational measures, it would indicate the method through which the medic submitted the APS report (Phone, Online, Other)."
    )%>%
  
    cb_add_col_attributes( 
      aps_reported_confirmation_number, 
      description = ""
    ) %>%
    cb_add_col_attributes( 
      c_detect_status_f, 
      description = "Calculation indicating if the DETECT screener was positive or negative."
    )
  
```
# Create a data frame containing the column names and their descriptions using the df_descriptions function

```{r}
obs_meas_desc <- var_descriptions(observational_measures)
```

## Save as rds file
```{r}
write_rds(obs_meas_desc, "../codebooks/variable_descriptions/observational_measures_var_desc.rds")
```

# Pass data frame to the codebook() function

```{r}
# Add title and description to codebook
obs_meas_codebook <- codebook(
  df = observational_measures,
  title = "Observational Measures Dataset",
  description = "Data collected during DETECT follow-up interviews on  Observational Measures of Elder Abuse, Neglect, and Exploitation",
  no_summary_stats = no_stats_vars) 
```

```{r}
print(obs_meas_codebook, "../codebooks/observational_measures_codebook.docx")
```
