---
title: "Create APS Investigations Codebook"
---

# Load the necessary packages and functions
```{r}
#| warning: false
library(codebookr)
library(dplyr, warn.conflicts = FALSE)
library(haven)
library(here)
library(readr)
source("../r/variable_descriptions.R")
```

# Purpose of the program

Using the CodebookR package, we will create a data dictionary for follow-up interview data for the DETECT project pertaining to APS.

# Load cleaned data
```{r}
aps_inv_path <- here::here("data", "cleaned_rds_files", "aps_investigations_import.rds")
```

```{r}
aps_inv <- readr::read_rds(aps_inv_path)
```

# Set column attributes

```{r}
# Set the source to "DETECT Follow-up Interview APS Investigations" for all the variables
aps_vars <- aps_inv %>%
  names()

for (i in aps_vars) {
  attr(aps_inv[[i]], "source") <- "DETECT Follow-up Interview APS Investigations"
}
```

```{r}
# Add column attributes to all variables
aps_inv <- aps_inv %>%
  cb_add_col_attributes(
    x_primary_key,
    description = "Unique record ID used internally by the database"
  ) %>%
  cb_add_col_attributes(
    x_created_by,
    description = "Person who created the record"
  ) %>%
  cb_add_col_attributes(
    x_created_timestamp,
    description = "Timestamp when the record was created",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_modified_by,
    description = "Person who modified the record"
  ) %>%
  cb_add_col_attributes(
    x_modified_timestamp,
    description = "Timestamp when the record was modified",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_error_message,
    description = "Error message entered by research team"
  ) %>%
  cb_add_col_attributes(
    x_record_month,
    description = "Month record was created",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_record_year,
    description = "Year record was created",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_record_status,
    description = "Status of the record as determined by research team"
  ) %>%
  cb_add_col_attributes(
    x_record_comment,
    description = "Comments by interviewer"
  ) %>%
  cb_add_col_attributes(
    xc_case_id,
    description = "Calculated by the database from the last 5 characters of the MedstarID"
  ) %>%
  cb_add_col_attributes(
    xc_lead_panel_summary_count,
    description = "Calculated count of positive abuse instances across SelfReport, ApsInvestigations, and ObservationalMeasures"
  ) %>%
  cb_add_col_attributes(
    medstar_id,
    description = "Unique record number in MedStar System"
  ) %>%
  cb_add_col_attributes(
    name_full,
    description = "Full name of older individual"
  ) %>%
  cb_add_col_attributes(
    aps_report,
    description = "AI_1. Has anyone from Adult Protective Services ever attempted to investigate whether or not you were living with elder abuse or neglect?",
    skip_pattern = "Skip to section 6 if any answer is given but Yes"
  ) %>%
  cb_add_col_attributes(
    aps_report_2cat,
    description = "AI_1. Has anyone from Adult Protective Services ever attempted to investigate whether or not you were living with elder abuse or neglect?",
    skip_pattern = "Skip to section 6 if any answer is given but Yes",
    value_labels = c(
      "No"        = 0,
      "Yes"       = 1
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    aps_report_2cat_f,
    description = "AI_1. Has anyone from Adult Protective Services ever attempted to investigate whether or not you were living with elder abuse or neglect?",
    skip_pattern = "Skip to section 6 if any answer is given but Yes"
  ) %>%
  cb_add_col_attributes(
    aps_times,
    description = "AI_2. How many times has this happened in your life?",
    skip_pattern = "If answer is 0 or Refused, go to Section 6. If answer is 1 go to AI_4."
  ) %>%
  cb_add_col_attributes(
    aps_times_3cat,
    description = "AI_2. How many times has this happened in your life?",
    skip_pattern = "If answer is 0 or Refused, go to Section 6. If answer is 1 go to AI_4.",
    value_labels = c(
      "0"          = 0,
      "1"          = 1,
      "2+"         = 2
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    aps_times_3cat_f,
    description = "AI_2. How many times has this happened in your life?",
    skip_pattern = "If answer is 0 or Refused, go to Section 6. If answer is 1 go to AI_4."
  ) %>%
  cb_add_col_attributes(
    aps_first,
    description = "AI_3. When was the first time APS attempted to do an investigation?",
    skip_pattern = "If answer is Refused, go to Section 6. If answer is 1 to 7, go to AI_4."
  ) %>%
  cb_add_col_attributes(
    aps_first_6cat,
    description = "AI_3. When was the first time APS attempted to do an investigation?",
    skip_pattern = "If answer is Refused, go to Section 6. If answer is 1 to 7, go to AI_4.",
    value_labels = c(
      "10 or more years ago"                       = 1,
      "5-10 years ago"                             = 2,
      "1-5 years ago"                              = 3,
      "In the past year but more than a month ago" = 4,
      "In the past month"                          = 5,
      "In the past week"                           = 6
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    aps_first_6cat_f,
    description = "AI_3. When was the first time APS attempted to do an investigation?",
    skip_pattern = "If answer is Refused, go to Section 6. If answer is 1 to 7, go to AI_4."
  ) %>%
  cb_add_col_attributes(
    aps_recent,
    description = "AI_4. When was the most recent time APS attempted to do an investigation?"
  ) %>%
  cb_add_col_attributes(
    aps_recent_6cat,
    description = "AI_4. When was the most recent time APS attempted to do an investigation?",
    value_labels = c(
      "In the past week"                           = 1,
      "In the past month"                          = 2,
      "In the past year but more than a month ago" = 3,
      "1-5 years ago"                              = 4,
      "5-10 years ago"                             = 5,
      "10 or more years ago"                       = 6
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    aps_recent_6cat_f,
    description = "AI_4. When was the most recent time APS attempted to do an investigation?"
  )
```

# Exclude summary stats for certain variables in word doc

```{r}
# Create a vector of variables to exclude summary statistics from
no_stats <- aps_inv %>%
  select(
    c(matches("^(x|xc)_"), name_full, medstar_id)
  )

no_stats_vars <- colnames(no_stats)
```

# Create a data frame containing the column names and their descriptions using the df_descriptions function

```{r}
aps_inv_desc <- var_descriptions(aps_inv)
```


## Save as rds file

```{r}
aps_inv_desc_path <- here::here("codebooks", "variable_descriptions", "aps_investigations_var_desc.rds")
```

```{r}
readr::write_rds(aps_inv, aps_inv_desc_path)
```

# Pass data frame to the codebook function
```{r}
# Add title, subtitle and description while excluding summary statistics for the specified variables
aps_codebook <- codebook(
  df = aps_inv,
  title = "APS Investigation Dataset",
  description = "Data collected during DETECT follow-up interviews regarding visits the patient may have had from Adult Protective Services",
  no_summary_stats = no_stats_vars
)
```

```{r}
aps_codebook_path <- here::here("codebooks", "aps_investigations_codebook.docx")
```

```{r}
print(aps_codebook, aps_codebook_path)
```
