---
title: "Create Participant Codebook"
---

```{r}
# Load necessary packages
library(codebookr)
library(dplyr, warn.conflicts = FALSE)
library(readr)
```


# Purpose of the program

Using the CodebookR package, we will create a data dictionary for follow-up interview data for the DETECT project.


# Load cleaned data

```{r}
#| warning: false
participant <- read_rds(here::here("data", "cleaned_rds_files", 
                                  "participant_import.rds"))
```


# Load custom functions

```{r}
source(here::here("r", "variable_descriptions.R"))
source(here::here("r", "identify_codebook_variables_to_update.R"))
```


# Data variables check

```{r}
# Compare variables in this data frame to the variables in the most recent 
# version of the cleaned data 

vars_to_update(participant, "participant_var_desc.rds")
```


# Set column attributes

```{r}
# Set the source to "Participant data" for all the variables
participant_vars <- participant %>%
  names()

for (i in participant_vars) {
  attr(participant[[i]], "source") <- "Participant data"
}
```

```{r}
# Add column attributes to all variables
participant <- participant %>%
  cb_add_col_attributes(
    x_primary_key,
    description = "Unique record ID used internally by the database."
  ) %>%
  cb_add_col_attributes(
    x_created_by,
    description = "User who created the record."
  ) %>%
  cb_add_col_attributes(
    x_created_timestamp,
    description = "Timestamp when the record was created.",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_modified_by,
    description = "User who last modified the record."
  ) %>%
  cb_add_col_attributes(
    x_modified_timestamp,
    description = "Timestamp when the record was last modified.",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_error_message,
    description = "Any database error messages."
  ) %>%
  cb_add_col_attributes(
    x_record_month,
    description = "Related month of the record.",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_record_year,
    description = "Related year of the record.",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_record_status,
    description = "The records status."
  ) %>%
  cb_add_col_attributes(
    medstar_id,
    description = "Record ID of the participant."
  ) %>%
  cb_add_col_attributes(
    name_full,
    description = "Full name of the participant."
  ) %>%
  cb_add_col_attributes(
    name_first,
    description = "First name of the participant."
  ) %>%
  cb_add_col_attributes(
    name_middle_initial,
    description = "Initial of the middle name of the participant."
  ) %>%
  cb_add_col_attributes(
    name_last,
    description = "Last name of the participant."
  ) %>%
  cb_add_col_attributes(
    name_suffix,
    description = "Name suffix of the participant."
  ) %>%
  cb_add_col_attributes(
    xc_case_id,
    description = "Last 5 characters of the MedstarID."
  ) %>%
  cb_add_col_attributes(
    x_address_original,
    description = "Participant's street address."
  ) %>%
  cb_add_col_attributes(
    city,
    description = "Participant's city of residence."
  ) %>%
  cb_add_col_attributes(
    state,
    description = "Participant's state of residence."
  ) %>%
  cb_add_col_attributes(
    zip_code,
    description = "Participant's zip_code."
  ) %>%
  cb_add_col_attributes(
    dob,
    description = "Participant's date of birth."
  ) %>%
  cb_add_col_attributes(
    x_randomizer,
    description = "Internal system variable used to randomize records."
  ) %>%
  cb_add_col_attributes(
    phone,
    description = "Participant phone number."
  ) %>%
  cb_add_col_attributes(
    x_call_order,
    description = "System variable used to track the order that participants should be called."
  ) %>%
  cb_add_col_attributes(
    incident_timestamp,
    description = "Coming from Medstar; Timestamp of when EMS was notified of the incident."
  ) %>%
  cb_add_col_attributes(
    unit_arrived_timestamp,
    description = "Coming from Medstar; Timestamp of when EMS arrived at the incident."
  ) %>%
  cb_add_col_attributes(
    medstar_internal_id,
    description = "Coming from Medstar; Internal ID number for the incident."
  ) %>%
  cb_add_col_attributes(
    ems_response_number,
    description = "Coming from Medstar; EMS response number."
  ) %>%
  cb_add_col_attributes(
    complaint_reported,
    description = "Coming from Medstar; Compliants reported by dispatch for patient."
  ) %>%
  cb_add_col_attributes(
    age,
    description = "Participant's age in years."
  ) %>%
  cb_add_col_attributes(
    incident_result,
    description = "Coming from Medstar; Result of the incident."
  ) %>%
  cb_add_col_attributes(
    ems_crew_member,
    description = "Coming from Medstar; Name of the EMS crew member that completed the report."
  ) %>%
  cb_add_col_attributes(
    symptom_list,
    description = "Coming from Medstar; participant list of symptoms."
  ) %>%
  cb_add_col_attributes(
    race,
    description = "Participant's racial identity."
  ) %>%
  cb_add_col_attributes(
    race_8cat,
    description = "Participant's racial identity.",
    value_labels = c(
      "American Indian or Alaskan Native"         = 1, 
      "Asian"                                     = 2, 
      "Black or African American"                 = 3,
      "Native Hawaiian or Other Pacific Islander" = 4,
      "White"                                     = 5, 
      "Other race or multiple races"              = 6, 
      "Not Applicable"                            = 7, 
      "Not Recorded"                              = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    race_6cat,
    description = "Participant's racial identity.",
    value_labels = c(
      "American Indian or Alaskan Native"         = 1, 
      "Asian"                                     = 2, 
      "Black or African American"                 = 3,
      "Native Hawaiian or Other Pacific Islander" = 4,
      "White"                                     = 5, 
      "Other race or multiple races"              = 6
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    race_6cat_f,
    description = "Participant's racial identity."
  ) %>%
  cb_add_col_attributes(
    race_eth_4cat,
    description = "Participant's racial identity.",
    value_labels = c(
        "Hispanic, any race"                         = 1, 
        "Black, non-Hispanic"                        = 2, 
        "White, non-Hispanic"                        = 3, 
        "Other race or multiple races, non-Hispanic" = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    race_eth_4cat_f,
    description = "Participant's racial identity."
  ) %>%
  cb_add_col_attributes(
    xc_incident_day_name,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    xc_incident_month_name,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    xc_incident_day,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    xc_incident_year,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    xc_record_month_year_abbr,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    x_is_archived,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    apt,
    description = "Participant's apartment number."
  ) %>%
  cb_add_col_attributes(
    address,
    description = "Participant's street address (reformatted)."
  ) %>%
  cb_add_col_attributes(
    x_usps_address_result,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    x_address_verified,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    x_call_order_initial,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    x_exclusion_reason,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    xc_call_order_even_odd,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    xc_participant_list_found_count,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    x_aps_reported_confirmation_number,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    x_aps_reported_2cat,
    description = "Indicates if the medic submitted an APS report. It is no longer in use.",
    value_labels = c(
       "Yes" = 1, 
       "No"  = 0
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_aps_reported_2cat_f,
    description = "Indicates if the medic submitted an APS report. It is no longer in use."
  ) %>%
  cb_add_col_attributes(
    incident_timestamp,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    xc_name_title,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    address_valid,
    description = ""
  ) %>%
  cb_add_col_attributes(
    address_updated,
    description = "Participant's address."
  ) %>%
  cb_add_col_attributes(
    apt_updated,
    description = "Participant's apartment number."
  ) %>%
  cb_add_col_attributes(
    city_updated,
    description = "Participant's city."
  ) %>%
  cb_add_col_attributes(
    zip_code_updated,
    description = "Participant's ZIP code."
  ) %>%
  cb_add_col_attributes(
    xc_address,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    xc_incident_date,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    xc_detect_positive_summary_count,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    x_do_not_call_2cat,
    description = "Internal system variable.",
    value_labels = c(
       "Yes" = 1, 
       "No"  = 0
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_do_not_call_2cat_f,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    x_unusual_odor,
    description = "Are there unusual odors (e.g. urine, feces) that are unrelated to current medical conditions and/or are more extreme than expected given current medical conditions?",
    value_labels = c(
       "Yes"                          = 1, 
       "No"                           = 0, 
       "No caregiver present"         = 2, 
       "Did not enter patient's home" = 3,
       "Unable to assess"             = 8
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_unusual_odor_4cat,
    description = "Are there unusual odors (e.g. urine, feces) that are unrelated to current medical conditions and/or are more extreme than expected given current medical conditions?",
    value_labels = c(
       "Yes"                          = 1, 
       "No"                           = 0, 
       "No caregiver present"         = 2, 
       "Did not enter patient's home" = 3
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_unusual_odor_4cat_f,
    description = "Are there unusual odors (e.g. urine, feces) that are unrelated to current medical conditions and/or are more extreme than expected given current medical conditions?"
  ) %>%
  cb_add_col_attributes(
    x_unmet_needs_4cat,
    description = "Is/Does the patient/older adult have unmet needs for assistance with eating, toileting, transferring, dressing, or bathing?",
    value_labels = c(
       "Yes"                          = 1, 
       "No"                           = 0, 
       "No caregiver present"         = 2, 
       "Did not enter patient's home" = 3
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_unmet_needs_4cat_f,
    description = "Is/Does the patient/older adult have unmet needs for assistance with eating, toileting, transferring, dressing, or bathing?"
  ) %>%
  cb_add_col_attributes(
    x_hoarding_medications,
    description = "Does the older adult appear to be hoarding/saving old medications?",
    value_labels = c(
       "Yes"                          = 1, 
       "No"                           = 0, 
       "No caregiver present"         = 2, 
       "Did not enter patient's home" = 3,
       "Unable to assess"             = 8
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_hoarding_medications_4cat,
    description = "Does the older adult appear to be hoarding/saving old medications?",
    value_labels = c(
       "Yes"                          = 1, 
       "No"                           = 0, 
       "No caregiver present"         = 2, 
       "Did not enter patient's home" = 3
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_hoarding_medications_4cat_f,
    description = "Does the older adult appear to be hoarding/saving old medications?"
  ) %>%
  cb_add_col_attributes(
    x_difficulty_medications_4cat,
    description = "Does the older adult have difficulties taking their prescribed medications as directed?",
    value_labels = c(
       "Yes"                          = 1, 
       "No"                           = 0, 
       "No caregiver present"         = 2, 
       "Did not enter patient's home" = 3
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_difficulty_medications_4cat_f,
    description = "Does the older adult have difficulties taking their prescribed medications as directed?"
  ) %>%
  cb_add_col_attributes(
    x_disarray_hoarding_4cat,
    description = "Is inside of home in extreme disarray/hoarding?",
    value_labels = c(
       "Yes"                          = 1, 
       "No"                           = 0, 
       "No caregiver present"         = 2, 
       "Did not enter patient's home" = 3
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_disarray_hoarding_4cat_f,
    description = "Is inside of home in extreme disarray/hoarding?"
  ) %>%
  cb_add_col_attributes(
    x_health_safety_concern,
    description = "Does the living environment pose a health or safety concern (e.g., fire hazard, insect or rodent infestation, urine or feces present)?",
    value_labels = c(
       "Yes"                          = 1, 
       "No"                           = 0, 
       "No caregiver present"         = 2, 
       "Did not enter patient's home" = 3,
       "Unable to assess"             = 8
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_health_safety_concern_4cat,
    description = "Does the living environment pose a health or safety concern (e.g., fire hazard, insect or rodent infestation, urine or feces present)?",
    value_labels = c(
       "Yes"                          = 1, 
       "No"                           = 0, 
       "No caregiver present"         = 2, 
       "Did not enter patient's home" = 3
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_health_safety_concern_4cat_f,
    description = "Does the living environment pose a health or safety concern (e.g., fire hazard, insect or rodent infestation, urine or feces present)?"
  ) %>%
  cb_add_col_attributes(
    x_caregiver_lack_knowledge_4cat,
    description = "If caregiver present, do they appear to lack knowledge of the patient/older adult’s medical needs?",
    value_labels = c(
       "Yes"                          = 1, 
       "No"                           = 0, 
       "No caregiver present"         = 2, 
       "Did not enter patient's home" = 3
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_caregiver_lack_knowledge_4cat_f,
    description = "If caregiver present, do they appear to lack knowledge of the patient/older adult’s medical needs?"
  ) %>%
  cb_add_col_attributes(
    x_caregiver_unengaged_4cat,
    description = "If caregiver(s) present, do they appear unengaged an inattentive in caring for the patient/older adult?",
    value_labels = c(
       "Yes"                          = 1, 
       "No"                           = 0, 
       "No caregiver present"         = 2, 
       "Did not enter patient's home" = 3
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_caregiver_unengaged_4cat_f,
    description = "If caregiver(s) present, do they appear unengaged an inattentive in caring for the patient/older adult?"
  ) %>%
  cb_add_col_attributes(
    x_caregiver_frustrated_4cat,
    description = "If caregiver(s) present, do they appear frustrated, tired, angry or burdened by the patient/older adult?",
    value_labels = c(
       "Yes"                          = 1, 
       "No"                           = 0, 
       "No caregiver present"         = 2, 
       "Did not enter patient's home" = 3
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_caregiver_frustrated_4cat_f,
    description = "If caregiver(s) present, do they appear frustrated, tired, angry or burdened by the patient/older adult?"
  ) %>%
  cb_add_col_attributes(
    x_caregiver_anxious_4cat,
    description = "If caregiver(s) present, do they appear overly concerned (e.g., anxious, hovering)?",
    value_labels = c(
       "Yes"                          = 1, 
       "No"                           = 0, 
       "No caregiver present"         = 2, 
       "Did not enter patient's home" = 3
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_caregiver_anxious_4cat_f,
    description = "If caregiver(s) present, do they appear overly concerned (e.g., anxious, hovering)?"
  ) %>%
  cb_add_col_attributes(
    x_isolated_home_4cat,
    description = "Is the older adult isolated in the home and/or cut-off from needed social networks or supports?",
    value_labels = c(
       "Yes"                          = 1, 
       "No"                           = 0, 
       "No caregiver present"         = 2, 
       "Did not enter patient's home" = 3
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_isolated_home_4cat_f,
    description = "Is the older adult isolated in the home and/or cut-off from needed social networks or supports?"
  ) %>%
  cb_add_col_attributes(
    x_depressed_4cat,
    description = "Does the older adult appear depressed, anxious, or emotionally distressed for reasons other than their immediate medical condition?",
    value_labels = c(
       "Yes"                          = 1, 
       "No"                           = 0, 
       "No caregiver present"         = 2, 
       "Did not enter patient's home" = 3
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_depressed_4cat_f,
    description = "Does the older adult appear depressed, anxious, or emotionally distressed for reasons other than their immediate medical condition?"
  ) %>%
  cb_add_col_attributes(
    x_poor_personal_hygiene_4cat,
    description = "Does the older adult have poor personal hygiene (including soiled in urine or feces)?",
    value_labels = c(
       "Yes"                          = 1, 
       "No"                           = 0, 
       "No caregiver present"         = 2, 
       "Did not enter patient's home" = 3
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_poor_personal_hygiene_4cat_f,
    description = "Does the older adult have poor personal hygiene (including soiled in urine or feces)?"
  ) %>%
  cb_add_col_attributes(
    x_inadequately_clothed_4cat,
    description = "Is the older adult inadequately clothed or wearing dirty, torn, or soiled clothing?",
    value_labels = c(
       "Yes"                          = 1, 
       "No"                           = 0, 
       "No caregiver present"         = 2, 
       "Did not enter patient's home" = 3
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    x_inadequately_clothed_4cat_f,
    description = "Is the older adult inadequately clothed or wearing dirty, torn, or soiled clothing?"
  ) %>%
  cb_add_col_attributes(
    xc_detect_status_2cat,
    description = "Internal system variable.",
    value_labels = c(
       "Positive" = 1, 
       "Negative" = 0
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    xc_detect_status_2cat_f,
    description = "Internal system variable."
  ) %>%
  cb_add_col_attributes(
    sex,
    description = "Participant's sex.",
    value_labels = c(
       "Male"                          = 1, 
       "Female"                        = 2, 
       "Unknown (Unable To Determine)" = 7
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sex_2cat,
    description = "Participant's sex.",
    value_labels = c(
       "Male"                          = 1, 
       "Female"                        = 2
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sex_2cat_f,
    description = "Participant's sex.",
    col_type = "Categorical"
  )
```


# Choose variables that will not have summary statistics

```{r}
vars <- c(
  "x_created_by", "x_created_timestamp", "name_first", "name_middle_initial", 
  "name_last", "medstar_id", "name_full", "x_address_original", "city", "state", 
  "zip_code", "name_suffix", "x_primary_key", "x_modified_by", 
  "x_modified_timestamp", "x_record_status", "phone", "x_record_month", 
  "x_record_year", "x_error_message", "dob", "x_randomizer", 
  "x_call_order", "incident_timestamp", "unit_arrived_timestamp", 
  "ems_response_number", "medstar_internal_id", "complaint_reported", 
  "incident_result", "ems_crew_member", "symptom_list", "xc_incident_day_name", 
  "xc_incident_month_name", "xc_incident_day", "xc_incident_year", 
  "xc_record_month_year_abbr", "x_is_archived", "apt", "address", 
  "x_usps_address_result", "x_address_verified", "x_call_order_initial", 
  "x_exclusion_reason", "xc_case_id", "xc_call_order_even_odd", 
  "xc_participant_list_found_count", "x_aps_reported_confirmation_number", 
  "xc_name_title", "address_valid", "address_updated", "apt_updated", 
  "city_updated", "zip_code_updated", "xc_address", "xc_incident_date"
)
no_stats_vars <- participant %>% select(all_of(vars)) %>% names()
```

# Create a data frame containing the column names and their descriptions using the df_descriptions function

```{r}
par_desc <- var_descriptions(participant)
```

## Save as rds file

```{r}
write_rds(par_desc, here::here("codebooks", "variable_descriptions", "participant_var_desc.rds"))
```

# Pass data frame to the codebook() function

```{r}
# Add title and description to codebook
participant_codebook <- codebook(
  df = participant,
  title = "Participant Dataset",
  description = "",
  no_summary_stats = no_stats_vars
)
```

```{r}
print(participant_codebook, here::here("codebooks", "participant_codebook.docx"))
```
