---
title: "Sociodemographic Information Codebook"
---

```{r}
# Load necessary packages and functions
library(codebookr)
library(dplyr, warn.conflicts = FALSE)
library(readr)
```


# Purpose of the program

Using the CodebookR package, we will create a data dictionary for follow-up interview data for the DETECT project.


# Load cleaned data

```{r}
socdem_path <- here::here("data", "cleaned_rds_files", 
                          "sociodemographic_information_import.rds")
```

```{r}
socdem <- readr::read_rds(socdem_path)
```


# Load custom functions

```{r}
source(here::here("r", "variable_descriptions.R"))
source(here::here("r", "identify_codebook_variables_to_update.R"))
```


# Data variables check

```{r}
# Compare variables in this data frame to the variables in the most recent 
# version of the cleaned data 

socdem_desc_path <- "sociodemographic_information_var_desc.rds"
vars_to_update(socdem, socdem_desc_path)
```


# Set column attributes

```{r}
# Set the source to "DETECT Follow-up Interview Questions - Sociodemographic Information" for all the variables
socdem_vars <- socdem %>%
  names()

for (i in socdem_vars) {
  attr(socdem[[i]], "source") <- "DETECT Follow-up Interview Questions - Sociodemographic Information"
}
```

```{r}
# Add column attributes to all variables
sociodemographic_information <- socdem %>%
  cb_add_col_attributes(
    x_primary_key,
    description = "Unique record ID used internally by the database"
  ) %>%
  cb_add_col_attributes(
    x_created_by,
    description = "Person who created the record"
  ) %>%
  cb_add_col_attributes(
    x_created_timestamp,
    description = "Timestamp when the record was created",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_modified_by,
    description = "Person who modified the record"
  ) %>%
  cb_add_col_attributes(
    x_modified_timestamp,
    description = "Timestamp when the record was modified",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_error_message,
    description = "Error message entered by research team"
  ) %>%
  cb_add_col_attributes(
    x_record_month,
    description = "Month record was created",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_record_year,
    description = "Year record was created",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_record_status,
    description = "Status of the record as determined by research team"
  ) %>%
  cb_add_col_attributes(
    x_record_comment,
    description = "Comments by interviewer"
  ) %>%
  cb_add_col_attributes(
    medstar_id,
    description = "Unique record number in MedStar System"
  ) %>%
  cb_add_col_attributes(
    name_full,
    description = "Full name of older individual"
  ) %>%
  cb_add_col_attributes(
    xc_case_id,
    description = "Calculated by the database from the last 5 characters of the MedstarID"
  ) %>%
  cb_add_col_attributes(
    sode_people,
    description = "SI_1. Including you how many people live in this household?"
  ) %>%
  cb_add_col_attributes(
    sode_marital,
    description = "Recoded variable sode_marital to match levels in follow-up interview protocol",
    value_labels = c(
      "Married"                                     = 1,
      "Living as an unmarried or common law couple" = 2,
      "Separated"                                   = 3,
      "Divorced"                                    = 4,
      "Widowed"                                     = 5,
      "Single, or never married"                    = 6,
      "Don't know"                                  = 7,
      "Refused"                                     = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_marital_6cat,
    description = "Recoded variable sode_marital to match levels in follow-up interview protocol",
    value_labels = c(
      "Married"                                     = 1,
      "Living as an unmarried or common law couple" = 2,
      "Separated"                                   = 3,
      "Divorced"                                    = 4,
      "Widowed"                                     = 5,
      "Single, or never married"                    = 6
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_marital_6cat_f,
    description = "SI_2. What is your marital status? Would you say you are…"
  ) %>%
  cb_add_col_attributes(
    sogi_identity,
    description = "SOGI_1. What is your gender identity?",
    value_labels = c(
      "Male"       = 1,
      "Female"     = 2,
      "Other"      = 3,
      "Don't know" = 7,
      "Refused"    = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sogi_identity_3cat,
    description = "SOGI_1. What is your gender identity?",
    value_labels = c(
      "Male"       = 1,
      "Female"     = 2,
      "Other"      = 3
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sogi_identity_3cat_f,
    description = "SOGI_1. What is your gender identity?"
  ) %>%
  cb_add_col_attributes(
    sogi_orientation,
    description = "SOGI_2. What best describes your sexual orientation?",
    value_labels = c(
      "Straight/heterosexual" = 1,
      "Gay man"               = 2,
      "Lesbian/gay woman"     = 3,
      "Bisexual"              = 4,
      "Queer"                 = 5,
      "Other"                 = 6,
      "Don't know"            = 7,
      "Refused"               = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sogi_orientation_6cat,
    description = "SOGI_2. What best describes your sexual orientation?",
    value_labels = c(
      "Straight/heterosexual" = 1,
      "Gay man"               = 2,
      "Lesbian/gay woman"     = 3,
      "Bisexual"              = 4,
      "Queer"                 = 5,
      "Other"                 = 6
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sogi_orientation_6cat_f,
    description = "SOGI_2. What best describes your sexual orientation?"
  ) %>%
  cb_add_col_attributes(
    sode_age,
    description = "SI_3. How old are you?",
    value_labels = c(
      "Age 65 to 100+" = 1,
      "Don't know"     = 7,
      "Refused"        = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_age_1cat,
    description = "SI_3. How old are you?",
    value_labels = c(
      "Age 65 to 100+" = 1
    )
  ) %>%
  cb_add_col_attributes(
    sode_age_1cat_f,
    description = "SI_3. How old are you?"
  ) %>%
  cb_add_col_attributes(
    sode_age_years,
    description = "Reported age of older individual - Question used in older version of protocol"
  ) %>%
  cb_add_col_attributes(
    sode_hispanic,
    description = "SI_4. Are you of Hispanic or Latino origin?",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0,
      "Don't know" = 7,
      "Refused"    = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_hispanic_2cat,
    description = "SI_4. Are you of Hispanic or Latino origin?",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_hispanic_2cat_f,
    description = "SI_4. Are you of Hispanic or Latino origin?"
  ) %>%
  cb_add_col_attributes(
    sode_school,
    description = "SI_6. What is the highest level of schooling you completed",
    value_labels = c(
      "Did not complete high school or GED"                            = 1, 
      "High school graduate or GED"                                    = 2,
      "Some college (no degree)"                                       = 3, 
      "Associate's degree"                                             = 4,  
      "Bachelor's degree (BA, AB, BS, etc.)"                           = 5, 
      "Some graduate or professional school (no degree)"               = 6,
      "Graduate or professional school degree (MS, MA, MD, PhD, etc.)" = 7,
      "Don't know"                                                     = 77, 
      "Refused"                                                        = 99
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_school_7cat,
    description = "SI_6. What is the highest level of schooling you completed",
    value_labels = c(
      "Did not complete high school or GED"                            = 1, 
      "High school graduate or GED"                                    = 2,
      "Some college (no degree)"                                       = 3, 
      "Associate's degree"                                             = 4,  
      "Bachelor's degree (BA, AB, BS, etc.)"                           = 5, 
      "Some graduate or professional school (no degree)"               = 6,
      "Graduate or professional school degree (MS, MA, MD, PhD, etc.)" = 7
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_school_7cat_f,
    description = "SI_6. What is the highest level of schooling you completed"
  ) %>%
  cb_add_col_attributes(
    sode_employed,
    description = "SI_7. What is your employment status? Would you say you are…",
    value_labels = c(
      "Employed full time"         = 1,
      "Employed part time"         = 2,
      "In the military"            = 3,
      "Unemployed"                 = 4,
      "Retired"                    = 5,
      "A student"                  = 6,
      "A homemaker"                = 7,
      "Disabled or unable to work" = 8,
      "Something else"             = 9,
      "Don't know"                 = 77,
      "Refused"                    = 99
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_employed_9cat,
    description = "SI_7. What is your employment status? Would you say you are…",
    value_labels = c(
      "Employed full time"         = 1,
      "Employed part time"         = 2,
      "In the military"            = 3,
      "Unemployed"                 = 4,
      "Retired"                    = 5,
      "A student"                  = 6,
      "A homemaker"                = 7,
      "Disabled or unable to work" = 8,
      "Something else"             = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_employed_9cat_f,
    description = "SI_7. What is your employment status? Would you say you are…"
  ) %>%
  cb_add_col_attributes(
    sode_income,
    description = "SI_8. Including everyone else in your household, which of the following categories best describes your total household income before taxes? Is it..",
    value_labels = c(
      "$10,000 or less"              = 1,
      "Between $10,001 and $20,000"  = 2,
      "Between $20,001 and $35,000"  = 3,
      "Between $35,001 and $50,000"  = 4,
      "Between $50,001 and $75,000"  = 5,
      "Between $75,001 and $100,000" = 6,
      "More than $100,000"           = 7,
      "Don't know"                   = 77,
      "Refused"                      = 99
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_income_7cat,
    description = "SI_8. Including everyone else in your household, which of the following categories best describes your total household income before taxes? Is it..",
    value_labels = c(
      "$10,000 or less"              = 1,
      "Between $10,001 and $20,000"  = 2,
      "Between $20,001 and $35,000"  = 3,
      "Between $35,001 and $50,000"  = 4,
      "Between $50,001 and $75,000"  = 5,
      "Between $75,001 and $100,000" = 6,
      "More than $100,000"           = 7
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_income_7cat_f,
    description = "SI_8. Including everyone else in your household, which of the following categories best describes your total household income before taxes? Is it.."
  ) %>%
  cb_add_col_attributes(
    sode_military_2cat,
    description = "SI_9. Have you ever served in the military (e.g., on active duty in the U.S. Armed Forces, Reserves, or National Guard)?",
    skip_pattern = "If answer is yes, go to SI_10. For all other answers, go to SI_11",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_military_2cat_f,
    description = "SI_9. Have you ever served in the military (e.g., on active duty in the U.S. Armed Forces, Reserves, or National Guard)?",
    skip_pattern = "If answer is yes, go to SI_10. For all other answers, go to SI_11"
  ) %>%
  cb_add_col_attributes(
    sode_unwanted,
    description = "When you were in the military: SI_10.  Did you ever receive unwanted, threatening or repeated sexual attention (for example, touching, cornering, pressure for sexual favors, or inappropriate verbal remarks, etc.?)",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0,
      "Don't know" = 7,
      "Refused"    = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_unwanted_2cat,
    description = "When you were in the military: SI_10.  Did you ever receive unwanted, threatening or repeated sexual attention (for example, touching, cornering, pressure for sexual favors, or inappropriate verbal remarks, etc.?)",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_unwanted_2cat_f,
    description = "When you were in the military: SI_10.  Did you ever receive unwanted, threatening or repeated sexual attention (for example, touching, cornering, pressure for sexual favors, or inappropriate verbal remarks, etc.?)"
  ) %>%
  cb_add_col_attributes(
    sode_sexual,
    description = "SI_11. Did you have sexual contact against your will or when you were unable to say no (for example, after being forced or threatened or to avoid other consequences?)",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0,
      "Don't know" = 7,
      "Refused"    = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_sexual_2cat,
    description = "SI_11. Did you have sexual contact against your will or when you were unable to say no (for example, after being forced or threatened or to avoid other consequences?)",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_sexual_2cat_f,
    description = "SI_11. Did you have sexual contact against your will or when you were unable to say no (for example, after being forced or threatened or to avoid other consequences?)"
  ) %>%
  cb_add_col_attributes(
    hsi_contact,
    description = "HS_1. Would it be alright if we contact you again in the future?",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0,
      "Don't know" = 7,
      "Refused"    = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    hsi_contact_2cat,
    description = "HS_1. Would it be alright if we contact you again in the future?",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    hsi_contact_2cat_f,
    description = "HS_1. Would it be alright if we contact you again in the future?"
  ) %>%
  cb_add_col_attributes(
    sode_people,
    description = "SI_1. Including you how many people live in this household?",
    value_labels = c(
      "1"          = 1, 
      "2"          = 2, 
      "3"          = 3, 
      "4"          = 4, 
      "5"          = 5, 
      "6"          = 6, 
      "7"          = 7, 
      "8"          = 8, 
      "9+"         = 9, 
      "Don't know" = 77, 
      "Refused"    = 99
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_people_9cat,
    description = "SI_1. Including you how many people live in this household?",
    value_labels = c(
      "1"          = 1, 
      "2"          = 2, 
      "3"          = 3, 
      "4"          = 4, 
      "5"          = 5, 
      "6"          = 6, 
      "7"          = 7, 
      "8"          = 8, 
      "9+"         = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_people_9cat_f,
    description = "SI_1. Including you how many people live in this household?"
  ) %>%
  cb_add_col_attributes(
    sode_race,
    description = "SI_5. Which of the following racial categories describes you? You may select more than one."
  ) %>%
  cb_add_col_attributes(
    sode_race_8cat,
    description = "SI_5. Which of the following racial categories describes you? You may select more than one.",
    value_labels = c(
      "American Indian or Alaskan Native"         = 1,
      "Asian"                                     = 2,
      "Black or African American"                 = 3,
      "Native Hawaiian or Other Pacific Islander" = 4,
      "White"                                     = 5,
      "Other race or multiple races"              = 6,
      "Don't know"                                = 7,
      "Refused"                                   = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_race_6cat,
    description = "SI_5. Which of the following racial categories describes you? You may select more than one.",
    value_labels = c(
      "American Indian or Alaskan Native"         = 1,
      "Asian"                                     = 2,
      "Black or African American"                 = 3,
      "Native Hawaiian or Other Pacific Islander" = 4,
      "White"                                     = 5,
      "Other race or multiple races"              = 6
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_race_6cat_f,
    description = "SI_5. Which of the following racial categories describes you? You may select more than one."
  ) %>%
  cb_add_col_attributes(
    sode_race_eth_4cat,
    description = "Ethnicity the participant self-identifies with. Derived from sode_race and sode_hispanic variables.",
    value_labels = c(
      "Hispanic, any race"                         = 1,
      "Black, non-Hispanic"                        = 2,
      "White, non-Hispanic"                        = 3,
      "Other race or multiple races, non-Hispanic" = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sode_race_eth_4cat_f,
    description = "Ethnicity the participant self-identifies with. Derived from sode_race and sode_hispanic variables."
  )

table(socdem$sode_race_eth_4cat_f)
test <- socdem %>% select(starts_with("sode_sexual"))
```


# Choose variables that will not have summary statistics

```{r}
vars <- c(
  "x_primary_key", "x_created_by", "x_created_timestamp", "x_modified_by", 
  "x_modified_timestamp", "x_record_status", "x_error_message", 
  "x_record_month", "x_record_year", "x_record_comment", "xc_case_id", 
  "name_full", "medstar_id" 
)
no_stats_vars <- sociodemographic_information %>% select(all_of(vars)) %>% names()
```


# Create a data frame containing the column names and their descriptions using the var_descriptions function

```{r}
soc_desc <- var_descriptions(sociodemographic_information)
```

## Save as rds file

```{r}
write_rds(soc_desc, here::here("codebooks", "variable_descriptions",
                               "sociodemographic_information_var_desc.rds"))
```

# Pass data frame to the codebook() function

```{r}
# Add title and description to codebook
socdem_codebook <- codebook(
  df = sociodemographic_information,
  title = "Sociodemographic Information Dataset",
  description = "Data collected during DETECT follow-up interviews about sociodemographic information",
  no_summary_stats = no_stats_vars
)
```

```{r}
print(socdem_codebook, here::here("codebooks", "sociodemographic_information_codebook.docx"))
```
