---
title: "Create Observational Measures Codebook"
---

```{r}
# Load necessary packages and functions
library(codebookr)
library(dplyr, warn.conflicts = FALSE)
library(readr)
library(here)
```


# Purpose of the program

Using the CodebookR package, we will create a data dictionary for follow-up interview data for the DETECT project pertaining to observational measures.


# Load cleaned data

```{r}
obs <- read_rds(here::here("data", "cleaned_rds_files", "observational_measures_import.rds"))
```


# Data variables check

```{r}
# Compare variables in this data frame to the variables in the most recent 
# version of the cleaned data 

obs_desc_path <- "observational_measures_var_desc.rds"
vars_to_update(observational_measures, obs_desc_path)
```


# Load custom functions

```{r}
source(here::here("r", "variable_descriptions.R"))
source(here::here("r", "identify_codebook_variables_to_update.R"))
```


# Set column attributes

```{r}
# Set the source to "DETECT Follow-up Interview Questions Observational Measures" for all the variables
obs_vars <- obs %>%
  names()

for (i in obs_vars) {
  attr(obs[[i]], "source") <- "DETECT Follow-up Interview Questions Observational Measures"
}
```


# Choose variables that will not have summary statistics

```{r}
no_stats_vars <- c(
  "x_primary_key", "x_created_by", "x_created_timestamp", "x_modified_by", 
  "x_modified_timestamp", "x_error_message", "x_record_status", 
  "x_record_month", "x_record_year", "x_record_comment", "xc_case_id", 
  "xc_lead_panel_summary_count", "xc_lead_panel_summary_comment_count", 
  "xc_lead_panel_summary", "name_full", "medstar_id", "neglect_comments", 
  "exploitation_comments", "abandonment_comments", "summary_comments", 
  "general_assessment_comments", "abuse_indicators_comments", "at_phys_why", 
  "at_sex_why", "at_emot_why", "at_neg_why", "at_aban_why", "at_fina_why",
  "at_self_why", "aps_reported_confirmation_number")

no_stats_vars <- sr %>% select(all_of(vars)) %>% names()
```

```{r}
# Add column attributes to all variables
observational_measures <- obs %>%
  cb_add_col_attributes(
    x_primary_key,
    description = "Unique record ID used internally by the database."
  ) %>%
  cb_add_col_attributes(
    x_created_by,
    description = "Person who created the record."
  ) %>%
  cb_add_col_attributes(
    x_created_timestamp,
    description = "Timestamp when the record was created.",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_modified_by,
    description = "Person who modified the record."
  ) %>%
  cb_add_col_attributes(
    x_modified_timestamp,
    description = "Timestamp when the record was modified.",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_error_message,
    description = "Error message entered by research team."
  ) %>%
  cb_add_col_attributes(
    medstar_id,
    description = "Unique record number in MedStar System."
  ) %>%
  cb_add_col_attributes(
    name_full,
    description = "Full name of older individual."
  ) %>%
  cb_add_col_attributes(
    x_record_status,
    description = "Status of the record as determined by research team."
  ) %>%
  cb_add_col_attributes(
    x_record_month,
    description = "Month record was created.",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_record_year,
    description = "Year record was created.",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_record_comment,
    description = "Comments by interviewer."
  ) %>%
  cb_add_col_attributes(
    xc_case_id,
    description = "Identifier derived by the database from the last 5 characters of the MedstarID."
  ) %>%
  cb_add_col_attributes(
    xc_lead_panel_summary_count,
    description = "Calculated total count of positive abuse instances across self report, ApsInvestigations, and observational measures."
  ) %>%
  cb_add_col_attributes(
    xc_lead_panel_summary_comment_count,
    description = "Calculated count of comments provided by the medic, excluding for phrases such as 'No', 'Nothing to report.', etc."
  ) %>%
  cb_add_col_attributes(
    xc_lead_panel_summary,
    description = "Summary of positive abuse instances across self report, ApsInvestigations, and observational measures."
  ) %>%
  cb_add_col_attributes(
    neglect_comments,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Additional comments. (Question used in older version of the follow-up interview until 9/24/2020.)"
  ) %>%
  cb_add_col_attributes(
    exploitation_comments,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Additional comments. (Question used in older version of the follow-up interview until 9/24/2020.)"
  ) %>%
  cb_add_col_attributes(
    abandonment_comments,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abandonment Indicators: Additional comments. (Question used in older version of the follow-up interview until 9/24/2020.)"
  ) %>%
  cb_add_col_attributes(
    summary_comments,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale - Environment status of subject: Summary - Additional comments. (Question used in older version of the follow-up interview until 9/24/2020.)"
  ) %>%
  cb_add_col_attributes(
    general_assessment_comments,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale - General Assessment: Additional comments. (Question used in older version of the follow-up interview until 9/24/2020.)"
  ) %>%
  cb_add_col_attributes(
    abuse_indicators_comments,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale - Possible Abuse Indicators: Additional comments. (Question used in older version of the follow-up interview until 9/24/2020.)"
  ) %>%
  cb_add_col_attributes(
    at_phys_why,
    description = "AT_1a. Why do you believe physical abuse has or has not occurred?"
  ) %>%
  cb_add_col_attributes(
    at_sex_why,
    description = "AT_2a. Why do you believe sexual abuse has or has not occurred?"
  ) %>%
  cb_add_col_attributes(
    at_emot_why,
    description = "AT_3a. Why do you believe emotional or psychological abuse has or has not occurred?"
  ) %>%
  cb_add_col_attributes(
    at_neg_why,
    description = "AT_4a. Why do you believe neglect has or has not occurred?"
  ) %>%
  cb_add_col_attributes(
    at_aban_why,
    description = "AT_5a. Why do you believe abandonment has or has not occurred?"
  ) %>%
  cb_add_col_attributes(
    at_fina_why,
    description = "AT_6a. Why do you believe financial or material exploitation has or hasn’t occurred?"
  ) %>%
  cb_add_col_attributes(
    at_self_why,
    description = "AT_7a. Why do you believe self-neglect has or has not occurred?"
  ) %>%
  cb_add_col_attributes(
    clothes_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale General Assessment: Clothes. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "0 - Clean/neat"  = 0,
      "1"               = 1,
      "2"               = 2,
      "3"               = 3,
      "4 - Very soiled" = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    unusual_odor,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Unusual odors (e.g. urine, feces) that are unrelated to current medical conditions and/or are more extreme than expected given current medical conditions.",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3,
    "Unable to assess"             = 8
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    unusual_odor_4cat,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Unusual odors (e.g. urine, feces) that are unrelated to current medical conditions and/or are more extreme than expected given current medical conditions.",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    unusual_odor_4cat_f,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Unusual odors (e.g. urine, feces) that are unrelated to current medical conditions and/or are more extreme than expected given current medical conditions."
  ) %>%
  cb_add_col_attributes(
    disarray_hoarding,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Inside of home is in extreme disarray/hoarding.",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3,
    "Unable to assess"             = 8
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    disarray_hoarding_4cat,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Inside of home is in extreme disarray/hoarding.",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    disarray_hoarding_4cat_f,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Inside of home is in extreme disarray/hoarding."
  ) %>%
  cb_add_col_attributes(
    health_safety_concern,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Living environment poses a health or safety concern (e.g., fire hazard, insect or rodent infestation, urine or feces present).",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3,
    "Unable to assess"             = 8
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    health_safety_concern_4cat,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Living environment poses a health or safety concern (e.g., fire hazard, insect or rodent infestation, urine or feces present).",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    health_safety_concern_4cat_f,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Living environment poses a health or safety concern (e.g., fire hazard, insect or rodent infestation, urine or feces present)."
  ) %>%
  cb_add_col_attributes(
    caregiver_lack_knowledge_4cat,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: If caregiver present, they appear to lack knowledge of the patient/older adult’s medical needs.",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    caregiver_lack_knowledge_4cat_f,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: If caregiver present, they appear to lack knowledge of the patient/older adult’s medical needs."
  ) %>%
  cb_add_col_attributes(
    caregiver_unengaged_4cat,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: If caregiver(s) present, they appear unengaged an inattentive in caring for the patient/older adult.",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3
),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    caregiver_unengaged_4cat_f,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: If caregiver(s) present, they appear unengaged an inattentive in caring for the patient/older adult."
  ) %>%
  cb_add_col_attributes(
    caregiver_frustrated_4cat,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: If caregiver(s) present, they appear frustrated, tired, angry or burdened by the patient/older adult.",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3
),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    caregiver_frustrated_4cat_f,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: If caregiver(s) present, they appear frustrated, tired, angry or burdened by the patient/older adult."
  ) %>%
  cb_add_col_attributes(
    caregiver_anxious_4cat,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: If caregiver(s) present, they appear overly concerned (e.g., anxious, hovering).",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3
),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    caregiver_anxious_4cat_f,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: If caregiver(s) present, they appear overly concerned (e.g., anxious, hovering)."
  ) %>%
  cb_add_col_attributes(
    isolated_home,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Is the older adult isolated in the home and/or cut-off from needed social networks or supports?",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3,
    "Unable to assess"             = 8
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    isolated_home_4cat,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Is the older adult isolated in the home and/or cut-off from needed social networks or supports?",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    isolated_home_4cat_f,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Is the older adult isolated in the home and/or cut-off from needed social networks or supports?"
  ) %>%
  cb_add_col_attributes(
    depressed,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Does the older adult appear depressed, anxious, or emotionally distressed for reasons other than their immediate medical condition?",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3,
    "Unable to assess"             = 8
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depressed_4cat,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Does the older adult appear depressed, anxious, or emotionally distressed for reasons other than their immediate medical condition?",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depressed_4cat_f,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Does the older adult appear depressed, anxious, or emotionally distressed for reasons other than their immediate medical condition?"
  ) %>%
  cb_add_col_attributes(
    poor_personal_hygiene,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Does the older adult have poor personal hygiene (including soiled in urine or feces)?",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3,
    "Unable to assess"             = 8
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    poor_personal_hygiene_4cat_f,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Does the older adult have poor personal hygiene (including soiled in urine or feces)?",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    poor_personal_hygiene_4cat_f,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Does the older adult have poor personal hygiene (including soiled in urine or feces)?"
  ) %>%
  cb_add_col_attributes(
    inadequately_clothed,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Is the older adult inadequately clothed or wearing dirty, torn, or soiled clothing?",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3,
    "Unable to assess"             = 8
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    inadequately_clothed_4cat,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Is the older adult inadequately clothed or wearing dirty, torn, or soiled clothing?",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3,
    "Unable to assess"             = 8
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    inadequately_clothed_4cat_f,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Is the older adult inadequately clothed or wearing dirty, torn, or soiled clothing?"
  ) %>%
  cb_add_col_attributes(
    difficulty_medications,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Does the older adult have difficulties taking their prescribed medications as directed?",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3,
    "Unable to assess"             = 8
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    difficulty_medications_4cat,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Does the older adult have difficulties taking their prescribed medications as directed?",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    difficulty_medications_4cat_f,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Does the older adult have difficulties taking their prescribed medications as directed?"
  ) %>%
  cb_add_col_attributes(
    hoarding_medications,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Does the older adult appear to be hoarding/saving old medications?",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3,
    "Unable to assess"             = 8
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    hoarding_medications_4cat,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Does the older adult appear to be hoarding/saving old medications?",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    hoarding_medications_4cat_f,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Does the older adult appear to be hoarding/saving old medications?"
  ) %>%
  cb_add_col_attributes(
    unmet_needs,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Is/Does the patient/older adult have unmet needs for assistance with eating, toileting, transferring, dressing, or bathing?",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3,
    "Unable to assess"             = 8
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    unmet_needs_4cat,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Is/Does the patient/older adult have unmet needs for assistance with eating, toileting, transferring, dressing, or bathing?",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    unmet_needs_4cat_f,
    description = "Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Items: Is/Does the patient/older adult have unmet needs for assistance with eating, toileting, transferring, dressing, or bathing?"
  ) %>%
  cb_add_col_attributes(
    report_elder_abuse,
    description = "Did you report elder abuse/neglect to APS, or, do you plan to based on what you just observed?",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3,
    "Unable to assess"             = 8
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    report_elder_abuse_4cat,
    description = "Did you report elder abuse/neglect to APS, or, do you plan to based on what you just observed?",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    report_elder_abuse_4cat_f,
    description = "Did you report elder abuse/neglect to APS, or, do you plan to based on what you just observed?"
  ) %>%
  cb_add_col_attributes(
    hygiene_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Hygiene. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "Very good"        = 1, 
      "Good"             = 2, 
      "Poor"             = 3, 
      "Very poor"        = 4
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    hygiene_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Hygiene. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    nutrition,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Nutrition. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "Very good"        = 1, 
      "Good"             = 2, 
      "Poor"             = 3, 
      "Very poor"        = 4,
      "Unable to assess" = 8
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    nutrition_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Nutrition. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "Very good"        = 1, 
      "Good"             = 2, 
      "Poor"             = 3, 
      "Very poor"        = 4
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    nutrition_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Nutrition. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    skin_integrity_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Skin integrity. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "Very good"        = 1, 
      "Good"             = 2, 
      "Poor"             = 3, 
      "Very poor"        = 4
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    skin_integrity_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Skin integrity. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    clothes_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale General Assessment: Clothes. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    hair_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale General Assessment: Hair. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "0 - Clean/combed" = 0,
      "1"                = 1,
      "2"                = 2,
      "3"                = 3,
      "4 - Matted/dirty" = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    hair_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale General Assessment: Hair. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    nails_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale General Assessment: Nails. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "0 - Clean/trimmed"        = 0,
      "1"                        = 1,
      "2"                        = 2,
      "3"                        = 3,
      "4 - Long/untrimmed/dirty" = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    nails_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale General Assessment: Nails. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    bruising,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Bruising. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    bruising_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Bruising. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    bruising_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Bruising. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
   lacerations,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Lacerations. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
   lacerations_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Lacerations. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    lacerations_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Lacerations. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    fractures,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Fractures. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    fractures_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Fractures. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    fractures_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Fractures. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    stages_healing,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Various stages of healing of any bruises or fractures/ (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    stages_healing_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Various stages of healing of any bruises or fractures/ (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    stages_healing_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Various stages of healing of any bruises or fractures/ (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    sexual_abuse,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Evidence of sexual abuse. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sexual_abuse_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Evidence of sexual abuse. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    sexual_abuse_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Evidence of sexual abuse. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    abuse_statement,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Statement by older adult related to abuse. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    abuse_statement_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Statement by older adult related to abuse. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    abuse_statement_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abuse Indicators: Statement by older adult related to abuse. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    contracture,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Contractures. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2,
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    contracture_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Contractures. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2,
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    contracture_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Contractures. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    decubitus,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Decubitii (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2,
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    decubitus_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Decubitii (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2,
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    decubitus_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Decubitii (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    dehydration,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Dehydration. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2,
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    dehydration_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Dehydration. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2,
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    dehydration_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Dehydration. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    diarrhea,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Diarrhea. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    diarrhea_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Diarrhea. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    diarrhea_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Diarrhea. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    depression,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Depression. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depression_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Depression. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depression_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Depression. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    impaction,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Impaction. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    impaction_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Impaction. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    impaction_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Impaction. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    malnutrition,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Malnutrition. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2,
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    malnutrition_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Malnutrition. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2,
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    malnutrition_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Malnutrition. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    urine_burn,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Urine burns. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    urine_burn_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Urine burns. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    urine_burn_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Urine burns. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    poor_hygiene,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Poor hygiene. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    poor_hygiene_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Poor hygiene. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    poor_hygiene_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Poor hygiene. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    obvious_disease,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators:  Failure to respond to warning of obvious disease. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    obvious_disease_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators:  Failure to respond to warning of obvious disease. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    obvious_disease_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators:  Failure to respond to warning of obvious disease. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    inappropriate_medication,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Inappropirate medications (over/under). (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2,
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    inappropriate_medication_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Inappropirate medications (over/under). (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2,
      "Definite evidence" = 3 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    inappropriate_medication_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Inappropirate medications (over/under). (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    repetitive_hosp_admission,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Repetitive hospital admissions due to probable failure of health care surveillance. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    repetitive_hosp_admission_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Repetitive hospital admissions due to probable failure of health care surveillance. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    repetitive_hosp_admission_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Repetitive hospital admissions due to probable failure of health care surveillance. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    neglect_statement,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Statement by older adult related to neglect. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2,
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    neglect_statement_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Statement by older adult related to neglect. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2,
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    neglect_statement_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Neglect Indicators: Statement by older adult related to neglect. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    money_misuse,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Misuse of money. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2,
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    money_misuse_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Misuse of money. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2,
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    money_misuse_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Misuse of money. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    evidence,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Evidence. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    evidence_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Evidence. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    evidence_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Evidence. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    goods_for_services,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Reports of demands for goods in exchange for service. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    goods_for_services_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Reports of demands for goods in exchange for service. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    goods_for_services_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Reports of demands for goods in exchange for service. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    inability_account_money,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Inability to account for money/property. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    inability_account_money_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Inability to account for money/property. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    inability_account_money_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Inability to account for money/property. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    exploitation_statement,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Statement by older adult related to exploitation. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    exploitation_statement_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Statement by older adult related to exploitation. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    exploitation_statement_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Exploitation Indicators: Statement by older adult related to exploitation. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    caretaker_withdrawn_care,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abandonment Indicators: Evidence that a caretaker has withdrawn care precipitously without alternate arrangements. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2,
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    caretaker_withdrawn_care_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abandonment Indicators: Evidence that a caretaker has withdrawn care precipitously without alternate arrangements. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2,
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    caretaker_withdrawn_care_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abandonment Indicators: Evidence that a caretaker has withdrawn care precipitously without alternate arrangements. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    left_alone_unsafe,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abandonment Indicators: Evidence that older adult is left alone in an unsafe environment for extended periods of time without adequate support. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3,
    "Unable to assess"             = 8
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    left_alone_unsafe_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abandonment Indicators: Evidence that older adult is left alone in an unsafe environment for extended periods of time without adequate support. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
    "Yes"                          = 1, 
    "No"                           = 0, 
    "No caregiver present"         = 2, 
    "Did not enter patient's home" = 3
    
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    left_alone_unsafe_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abandonment Indicators: Evidence that older adult is left alone in an unsafe environment for extended periods of time without adequate support. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    abandonment_statement,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abandonment Indicators: Statement by older adults regarding abandonment. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3, 
      "Unable to assess"  = 8 
),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    abandonment_statement_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abandonment Indicators: Statement by older adults regarding abandonment. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    abandonment_statement_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Scale Possible Abandonment Indicators: Statement by older adults regarding abandonment. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    exterior_condition_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Exterior condition. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "0 - Neat/well kept/no trash, debris"       = 0,
      "1"                                         = 1,
      "2"                                         = 2,
      "3"                                         = 3,
      "4 - Poorly maintained/trash, other debris" = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    exterior_condition_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Exterior condition. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    yard_sidewalk_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Yard/Sidewalk. (Question used in older version of the follow-up interview until 9/24/2020.)",
    value_labels = c(
      "0 - Neat/well kept/no trash, debris" = 0,
      "1"                                   = 1,
      "2"                                   = 2,
      "3"                                   = 3,
      "4 - Poorly maintained/trash, debris" = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    yard_sidewalk_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Yard/Sidewalk. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    roof_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Roof. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "0 - Intact/no structural damage"          = 0,
      "1"                                        = 1,
      "2"                                        = 2,
      "3"                                        = 3,
      "4 - Dilapidated/poorly maintained, holes" = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    roof_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Roof. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    walls_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Walls (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "0 - Intact/no structural damage"          = 0,
      "1"                                        = 1,
      "2"                                        = 2,
      "3"                                        = 3,
      "4 - Dilapidated/poorly maintained, holes" = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    walls_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Walls (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    windows_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Windows. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "0 - Intact/not broken or missing"     = 0,
      "1"                                    = 1,
      "2"                                    = 2,
      "3"                                    = 3,
      "4 - Multiple sections broken/missing" = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    windows_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Windows. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    interior_condition_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Interior condition. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "0 - Intact/not broken or missing"     = 0,
      "1"                                    = 1,
      "2"                                    = 2,
      "3"                                    = 3,
      "4 - Multiple sections broken/missing" = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    interior_condition_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Interior condition. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    odor_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Odor. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "0 - Normal household odor"                                              = 0,
      "1"                                                                      = 1,
      "2"                                                                      = 2,
      "3"                                                                      = 3,
      "4 - Pungent, unpleasant odor (may be human/animal waste, rotting food)" = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    odor_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Odor. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    kitchen_cleanliness_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Cleanliness - Kitchen. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "0 - Clean, no evidence of unsanitary conditions" = 0,
      "1"                                               = 1,
      "2"                                               = 2,
      "3"                                               = 3,
      "4 - Very dirty, unwashed dishes, trash litter"   = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    kitchen_cleanliness_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Cleanliness - Kitchen. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    bathroom_cleanliness_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Cleanliness - Bathroom. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "0 - Clean, no evidence of unsanitary conditions"  = 0,
      "1"                                                = 1,
      "2"                                                = 2,
      "3"                                                = 3,
      "4 - Very dirty, unwashed dishes, trash litter"    = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    bathroom_cleanliness_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Cleanliness - Bathroom. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    bedroom_cleanliness_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Cleanliness - Bedroom. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "0 - Clean, no evidence of unsanitary conditions" = 0,
      "1"                                               = 1,
      "2"                                               = 2,
      "3"                                               = 3,
      "4 - Very dirty, unwashed dishes, trash litter"   = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    bedroom_cleanliness_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Cleanliness - Bedroom. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    living_room_cleanliness_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Cleanliness - Living room.  (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "0 - Clean, no evidence of unsanitary conditions" = 0,
      "1"                                               = 1,
      "2"                                               = 2,
      "3"                                               = 3,
      "4 - Very dirty, unwashed dishes, trash litter"   = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    living_room_cleanliness_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Cleanliness - Living room.  (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    clutter_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Clutter. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "0 - Neat/orderly"                                             = 0,
      "1"                                                            = 1,
      "2"                                                            = 2,
      "3"                                                            = 3,
      "4 - Very cluttered/difficult to move around or find things"   = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    clutter_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Clutter. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    structural_problems_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Structural problems. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "0 - No structural problems"                                                     = 0,
      "1"                                                                              = 1,
      "2"                                                                              = 2,
      "3"                                                                              = 3,
      "4 - Severe structural damage (e.g., holes in sheetrock, floor leaking, ceiling" = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    structural_problems_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Structural problems. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    pets_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Pets. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "0 - All animals cared for"    = 0,
      "1 or 2 - Uncared animals"     = 1,
      "3 or 4 - Uncared animals"     = 2,
      "5 or 6 - Uncared animals"     = 3,
      "6 or more -  Uncared animals" = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    pets_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Pets. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    utilities_5cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Utilities. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "0 - All utilities work"             = 0,
      "1 - No phone"                       = 1,
      "2 - No gas/electricity"             = 2,
      "3 - No water"                       = 3,
      "4 - Multiple utilities do not work" = 4
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    utilities_5cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Utilities. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    summary_evidence_abuse_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Summary - Evidence of abuse. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    summary_evidence_abuse_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Summary - Evidence of abuse. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    summary_evidence_neglect_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Summary - Evidence of neglect. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    summary_evidence_neglect_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Summary - Evidence of neglect. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    summary_evidence_exploitation_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Summary - Evidence of exploitation. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    summary_evidence_exploitation_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Summary - Evidence of exploitation. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    summary_evidence_abandonment_4cat,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Summary - Evidence of abandonment. (Question used in older version of the follow-up interview until 08/25/2020.)",
    value_labels = c(
      "No evidence"       = 0, 
      "Possible evidence" = 1, 
      "Probable evidence" = 2, 
      "Definite evidence" = 3
      ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    summary_evidence_abandonment_4cat_f,
    description = "Elder Assessment Instrument (EAI) / Self-neglect Severity Environment status of subject: Summary - Evidence of abandonment. (Question used in older version of the follow-up interview until 08/25/2020.)"
  ) %>%
  cb_add_col_attributes(
    at_physical,
    description = "AT_1. Do you believe physical abuse has occurred?",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0,
      "Don't know" = 7,
      "Refused"    = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    at_physical_2cat,
    description = "AT_1. Do you believe physical abuse has occurred?",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    at_physical_2cat_f,
    description = "AT_1. Do you believe physical abuse has occurred?"
  ) %>%
  cb_add_col_attributes(
    at_sexual,
    description = "AT_2. Do you believe sexual abuse has occurred?",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0,
      "Don't know" = 7,
      "Refused"    = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    at_sexual_2cat,
    description = "AT_2. Do you believe sexual abuse has occurred?",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    at_sexual_2cat_f,
    description = "AT_2. Do you believe sexual abuse has occurred?"
  ) %>%
  cb_add_col_attributes(
    at_emotional,
    description = "AT_3. Do you believe emotional or psychological abuse has occurred?",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0,
      "Don't know" = 7,
      "Refused"    = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    at_emotional_2cat,
    description = "AT_3. Do you believe emotional or psychological abuse has occurred?",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    at_emotional_2cat_f,
    description = "AT_3. Do you believe emotional or psychological abuse has occurred?"
  ) %>%
  cb_add_col_attributes(
    at_neglect,
    description = "AT_4. Do you believe neglect has occurred?",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0,
      "Don't know" = 7,
      "Refused"    = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    at_neglect_2cat,
    description = "AT_4. Do you believe neglect has occurred?",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    at_neglect_2cat_f,
    description = "AT_4. Do you believe neglect has occurred?"
  ) %>%
  cb_add_col_attributes(
    at_abandon_2cat,
    description = "AT_5. Do you believe abandonment has occurred?",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    at_abandon_2cat_f,
    description = "AT_5. Do you believe abandonment has occurred?"
  ) %>%
  cb_add_col_attributes(
    at_financial,
    description = "AT_6. Do you believe financial or material exploitation has occurred?",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0,
      "Don't know" = 7,
      "Refused"    = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    at_financial_2cat,
    description = "AT_6. Do you believe financial or material exploitation has occurred?",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    at_financial_2cat_f,
    description = "AT_6. Do you believe financial or material exploitation has occurred?"
  ) %>%
  cb_add_col_attributes(
    at_self,
    description = "AT_7. Do you believe self-neglect has occurred?",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0,
      "Don't know" = 7,
      "Refused"    = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    at_self_2cat,
    description = "AT_7. Do you believe self-neglect has occurred?",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    at_self_2cat_f,
    description = "AT_7. Do you believe self-neglect has occurred?"
  ) %>%
  cb_add_col_attributes(
    aps_reported_2cat,
    description = "No longer used - In the original observational measures, it would indicate if the medic submitted an APS report.",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 0
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    aps_reported_2cat_f,
    description = "No longer used - In the original observational measures, it would indicate if the medic submitted an APS report."
  ) %>%
  cb_add_col_attributes(
    aps_reported_method_3cat,
    description = "No longer used - In the original observational measures, it would indicate the method through which the medic submitted the APS report (Phone, Online, Other).",
    value_labels = c(
      "Phone"       = 1,
      "Online"      = 2,
      "Other"       = 3
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    aps_reported_method_3cat_f,
    description = "No longer used - In the original observational measures, it would indicate the method through which the medic submitted the APS report (Phone, Online, Other)."
  ) %>%
  cb_add_col_attributes(
    aps_reported_confirmation_number,
    description = ""
  ) %>%
  cb_add_col_attributes(
    c_detect_status_2cat,
    description = "Calculation indicating if the DETECT screener was positive or negative.",
    value_labels = c(
      "Positive" = 1, 
      "Negative" = 0
      ),
    col_type = "Categorical"
    ) %>%
  cb_add_col_attributes(
    c_detect_status_2cat_f,
    description = "Calculation indicating if the DETECT screener was positive or negative."
  )
```


# Create a data frame containing the column names and their descriptions using the df_descriptions function

```{r}
obs_meas_desc <- var_descriptions(observational_measures)
```

## Save as rds file

```{r}
write_rds(obs_meas_desc, 
          here::here("codebooks", "variable_descriptions", "observational_measures_var_desc.rds"))
```


# Pass data frame to the codebook() function

```{r}
# Add title and description to codebook
obs_meas_codebook <- codebook(
  df = observational_measures,
  title = "Observational Measures Dataset",
  description = "Data collected during DETECT follow-up interviews on  Observational Measures of Elder Abuse, Neglect, and Exploitation",
  no_summary_stats = no_stats_vars
)
```

```{r}
print(obs_meas_codebook, here::here("codebooks", "observational_measures_codebook.docx"))
```
