---
title: "Create Clutter Scale Codebook"
---

```{r}
# Load needed packages and functions
library(codebookr)
library(dplyr, warn.conflicts = FALSE)
library(haven)
library(readr)
source("../r/variable_descriptions.R")
```

# Purpose of the program

Using the CodebookR package, we will create a data dictionary for follow-up interview data for the DETECT project pertaining to home inspection and the clutter image rating scale

# Load cleaned data
```{r}
#| warning: false
clutter_scale <- read_rds("../data/cleaned_rds_files/clutter_scale_import.rds")
```

# Set column attributes

```{r}
# Set the source to "DETECT Follow-up Interview home inspection and the clutter image rating scale data" for all the variables
clutter_scale_vars <- clutter_scale %>%
  names()

for (i in clutter_scale_vars) {
  attr(clutter_scale[[i]], "source") <- "DETECT Follow-up Interview Clutter Scale"
}
```

```{r}
# Add column attributes to all variables
clutter_scale <- clutter_scale %>%
  cb_add_col_attributes(
    x_primary_key,
    description = "Unique record ID used internally by the database"
  ) %>%
  cb_add_col_attributes(
    x_created_by,
    description = "Person who created the record"
  ) %>%
  cb_add_col_attributes(
    x_created_timestamp,
    description = "Timestamp when the record was created",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_modified_by,
    description = "Person who modified the record"
  ) %>%
  cb_add_col_attributes(
    x_modified_timestamp,
    description = "Timestamp when the record was modified",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_error_message,
    description = "Error message entered by research team"
  ) %>%
  cb_add_col_attributes(
    medstar_id,
    description = "Unique record number in MedStar System"
  ) %>%
  cb_add_col_attributes(
    name_full,
    description = "Full name of older individual"
  ) %>%
  cb_add_col_attributes(
    x_record_status,
    description = "Status of the record as determined by research team"
  ) %>%
  cb_add_col_attributes(
    name_last,
    description = "Last name of older individual"
  ) %>%
  cb_add_col_attributes(
    x_record_month,
    description = "Month record was created",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_record_year,
    description = "Year record was created",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_record_comment,
    description = "Comments by interviewer"
  ) %>%
  cb_add_col_attributes(
    xc_case_id,
    description = "Calculated by the database from the last 5 characters of the MedstarID"
  ) %>%
  cb_add_col_attributes(
    look_living_3cat,
    description = "CL_1a. May I take a look at your living room?",
    skip_pattern = "If answer is No, go to CL_2a.",
    value_labels = c(
      "Yes"            = 1,
      "No"             = 0,
      "No living room" = 7
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    look_living_3cat_f,
    description = "CL_1a. May I take a look at your living room?",
    skip_pattern = "If answer is No, go to CL_2a."
  ) %>%
  cb_add_col_attributes(
    clutter_living_f,
    description = "Clutter Image Rating Scale: Living Room. Please select the photo that most accurately reflects the amount of clutter in the room"
  ) %>%
  cb_add_col_attributes(
    clutter_living_photo_3cat,
    description = "CL_1b. May I take a picture of your living room?",
    skip_pattern = "If answer is No, go to CL_2a.",
    value_labels = c(
      "Yes"            = 1,
      "No"             = 0,
      "No living room" = 7
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    clutter_living_photo_3cat_f,
    description = "CL_1b. May I take a picture of your living room?",
    skip_pattern = "If answer is No, go to CL_2a."
  ) %>%
  cb_add_col_attributes(
    look_kitchen_3cat,
    description = "CL_2a. May I take a look at your kitchen?",
    skip_pattern = "If answer is No, go to CL_3a.",
    value_labels = c(
      "Yes"            = 1,
      "No"             = 0,
      "No kitchen"     = 7
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    look_kitchen_3cat_f,
    description = "CL_2a. May I take a look at your kitchen?",
    skip_pattern = "If answer is No, go to CL_3a."
  ) %>%
  cb_add_col_attributes(
    clutter_kitchen_f,
    description = "Clutter Image Rating Scale: Kitchen. Please select the photo that most accurately reflects the amount of clutter in the room"
  ) %>%
  cb_add_col_attributes(
    clutter_kitchen_photo_3cat,
    description = "CL_2b. May I take a picture of your kitchen?",
    skip_pattern = "If answer is No, go to CL_3a.",
    value_labels = c(
      "Yes"            = 1,
      "No"             = 0,
      "No kitchen"     = 7
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    clutter_kitchen_photo_3cat_f,
    description = "CL_2b. May I take a picture of your kitchen?",
    skip_pattern = "If answer is No, go to CL_3a."
  ) %>%
  cb_add_col_attributes(
    look_bedroom_3cat,
    description = "CL_3a. May I take a look at the bedroom where you sleep most regularly?",
    skip_pattern = "If answer is No, go to section 4.",
    value_labels = c(
      "Yes"            = 1,
      "No"             = 0,
      "No bedroom"     = 7
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    look_bedroom_3cat_f,
    description = "CL_3a. May I take a look at the bedroom where you sleep most regularly?",
    skip_pattern = "If answer is No, go to section 4."
  ) %>%
  cb_add_col_attributes(
    clutter_bedroom_f,
    description = "Clutter Image Rating Scale: Bedroom. Please select the photo that most accurately reflects the amount of clutter in the room"
  ) %>%
  cb_add_col_attributes(
    clutter_bedroom_photo_3cat,
    description = "CL_3b. May I take a picture of your bedroom?",
    skip_pattern = "If answer is No, go to section 4.",
    value_labels = c(
      "Yes"            = 1,
      "No"             = 0,
      "No bedroom"     = 7
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    clutter_bedroom_photo_3cat_f,
    description = "CL_3b. May I take a picture of your bedroom?",
    skip_pattern = "If answer is No, go to section 4."
  )
```

# Create a data frame containing the column names and their descriptions using the df_descriptions function

```{r}
cls_desc <- var_descriptions(clutter_scale)
```

## Save as rds file
```{r}
write_rds(cls_desc, "../codebooks/variable_descriptions/clutter_scale_var_desc.rds")
```


# Exclude summary stats for certain variables in word doc

```{r}
# Create a vector of variables to exclude summary statistics from
no_stats <- clutter_scale %>%
  select(
    c(matches("^(x|xc)_"), matches("^(name)"), medstar_id)
  )

no_stats_vars <- colnames(no_stats)
```

# Pass data frame to the codebook function
```{r}
# Add title, subtitle and description while excluding summary statistics for the specified variables
clutter_scale_codebook <- codebook(
  df = clutter_scale,
  title = "Clutter Scale Dataset",
  description = "Data collected during DETECT follow-up interviews regarding the patient's home inspection and clutter image rating scale",
  no_summary_stats = no_stats_vars
)
```

```{r}
print(clutter_scale_codebook, "../codebooks/clutter_scale_codebook.docx")
```
