---
title: "Create General Health Codebook"
---
```{r}
# Load needed packages and functions
library(codebookr)
library(dplyr, warn.conflicts = FALSE)
library(readr)
source("../r/variable_descriptions.R")
```

# Purpose of the program

Using the CodebookR package, we will create a data dictionary for follow-up interview data for the DETECT project pertaining to general health

# Load cleaned data

```{r}
#| warning: false
general_health <- read_rds("../data/cleaned_rds_files/general_health_import.rds")
```

# Set column attributes

```{r}
# Set the source to "DETECT Follow-up Interview General Health" for all the variables
general_health_vars <- general_health %>%
  names()

for (i in general_health_vars) {
  attr(general_health[[i]], "source") <- "DETECT Follow-up Interview General Health"
}
```


```{r}
# Add column attributes to all variables
general_health <- general_health %>%
  cb_add_col_attributes(
    x_primary_key,
    description = "Unique record ID used internally by the database."
  ) %>%
  cb_add_col_attributes(
    x_created_by,
    description = "Person who created the record."
  ) %>%
  cb_add_col_attributes(
    x_created_timestamp,
    description = "Timestamp when the record was created.",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_modified_by,
    description = "Person who modified the record."
  ) %>%
  cb_add_col_attributes(
    x_modified_timestamp,
    description = "Timestamp when the record was modified.",
    col_type = "Time"
  ) %>%
  cb_add_col_attributes(
    x_error_message,
    description = "Error message entered by research team."
  ) %>%
  cb_add_col_attributes(
    medstar_id,
    description = "Unique record number in MedStar System."
  ) %>%
  cb_add_col_attributes(
    name_full,
    description = "Full name of older individual."
  ) %>%
  cb_add_col_attributes(
    xc_case_id,
    description = "Calculated by the database from the last 5 characters of the MedstarID"
  ) %>%
  cb_add_col_attributes(
    peg_pain_12cat,
    description = "PEG_1. What number best describes your pain on average in the past week?",
    value_labels = c(
      "No Pain"                        = 0,
      "1"                              = 1,
      "2"                              = 2,
      "3"                              = 3,
      "4"                              = 4,
      "5"                              = 5,
      "6"                              = 6,
      "7"                              = 7,
      "8"                              = 8,
      "9"                              = 9,
      "Pain as bad as you can imagine" = 10,
      "Refused"                        = 99
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    peg_enjoyment_12cat,
    description = "PEG_2. What number best describes how, during the past week, pain has interfered with your enjoyment of life?",
    value_labels = c(
      "No Pain"                        = 0,
      "1"                              = 1,
      "2"                              = 2,
      "3"                              = 3,
      "4"                              = 4,
      "5"                              = 5,
      "6"                              = 6,
      "7"                              = 7,
      "8"                              = 8,
      "9"                              = 9,
      "Pain as bad as you can imagine" = 10,
      "Refused"                        = 99
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    peg_activity_12cat,
    description = "PEG_3. What number best describes how, during the past week, pain has interfered with your general activity?",
    value_labels = c(
      "0 - No Pain" = 0,
      "1" = 1,
      "2" = 2,
      "3" = 3,
      "4" = 4,
      "5" = 5,
      "6" = 6,
      "7" = 7,
      "8" = 8,
      "9" = 9,
      "10 - Pain as bad as you can imagine" = 10,
      "Refused" = 99
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    peg_pain_12cat_f,
    description = "PEG_1. What number best describes your pain on average in the past week?"
  ) %>%
  cb_add_col_attributes(
    peg_enjoyment_12cat_f,
    description = "PEG_2. What number best describes how, during the past week, pain has interfered with your enjoyment of life?"
  ) %>%
  cb_add_col_attributes(
    peg_activity_12cat_f,
    description = "PEG_3. What number best describes how, during the past week, pain has interfered with your general activity?"
  ) %>%
  cb_add_col_attributes(
    outcomes_health_general_7cat,
    description = "MO_2. In general, would you say your health is...",
    value_labels = c(
      "Excellent"  = 1,
      "Very good"  = 2,
      "Good"       = 3,
      "Fair"       = 4,
      "Poor"       = 5,
      "Don't know" = 7,
      "Refused"    = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_health_general_7cat_f,
    description = "MO_2. In general, would you say your health is..."
  ) %>%
  cb_add_col_attributes(
    outcomes_health_vigorous_5cat,
    description = "MO_3. The kinds or amounts of vigorous activities you can do, like lifting heavy objects, running or participating in strenuous sports",
    value_labels = c(
      "Yes, limited for more than 3 months" = 1,
      "Yes, limited for 3 months or less"   = 2,
      "Not limited at all"                  = 3,
      "Don’t know"                          = 7,
      "Refused"                             = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_health_moderate_5cat,
    description = "MO_4. The kinds or amounts of moderate activities you can do, like moving a table, carrying groceries, or bowling",
    value_labels = c(
      "Yes, limited for more than 3 months" = 1,
      "Yes, limited for 3 months or less"   = 2,
      "Not limited at all"                  = 3,
      "Don’t know"                          = 7,
      "Refused"                             = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_health_uphill_5cat,
    description = "MO_5. Walking uphill or climbing a few flights of stairs",
    value_labels = c(
      "Yes, limited for more than 3 months" = 1,
      "Yes, limited for 3 months or less"   = 2,
      "Not limited at all"                  = 3,
      "Don’t know"                          = 7,
      "Refused"                             = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_health_bend_5cat,
    description = "MO_6. Bending, lifting, or stooping",
    value_labels = c(
      "Yes, limited for more than 3 months" = 1,
      "Yes, limited for 3 months or less"   = 2,
      "Not limited at all"                  = 3,
      "Don’t know"                          = 7,
      "Refused"                             = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_health_block_5cat,
    description = "MO_7. Walking one block",
    value_labels = c(
      "Yes, limited for more than 3 months" = 1,
      "Yes, limited for 3 months or less"   = 2,
      "Not limited at all"                  = 3,
      "Don’t know"                          = 7,
      "Refused"                             = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_health_bathe_5cat,
    description = "MO_8. Eating, dressing, bathing or using the toilet",
    value_labels = c(
      "Yes, limited for more than 3 months" = 1,
      "Yes, limited for 3 months or less"   = 2,
      "Not limited at all"                  = 3,
      "Don’t know"                          = 7,
      "Refused"                             = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_health_vigorous_5cat_f,
    description = "MO_3. The kinds or amounts of vigorous activities you can do, like lifting heavy objects, running or participating in strenuous sports"
  ) %>%
  cb_add_col_attributes(
    outcomes_health_moderate_5cat_f,
    description = "MO_4. The kinds or amounts of moderate activities you can do, like moving a table, carrying groceries, or bowling"
  ) %>%
  cb_add_col_attributes(
    outcomes_health_uphill_5cat_f,
    description = "MO_5. Walking uphill or climbing a few flights of stairs"
  ) %>%
  cb_add_col_attributes(
    outcomes_health_bend_5cat_f,
    description = "MO_6. Bending, lifting, or stooping"
  ) %>%
  cb_add_col_attributes(
    outcomes_health_block_5cat_f,
    description = "MO_7. Walking one block"
  ) %>%
  cb_add_col_attributes(
    outcomes_health_bathe_5cat_f,
    description = "MO_8. Eating, dressing, bathing or using the toilet"
  ) %>%
  cb_add_col_attributes(
    outcomes_4weeks_pain_8cat,
    description = "MO_1. How much bodily pain have you had during the past 4 weeks?",
    value_labels = c(
      "None"        = 0,
      "Very mild"   = 1,
      "Mild"        = 2,
      "Moderate"    = 3,
      "Severe"      = 4,
      "Very Severe" = 5,
      "Don't know"  = 7,
      "Refused"     = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_4weeks_pain_8cat_f,
    description = "MO_1. How much bodily pain have you had during the past 4 weeks?"
  ) %>%
  cb_add_col_attributes(
    outcomes_health_keep_5cat,
    description = "MO_9. Does your health keep you from working at a job, doing work around the house, or going to school?",
    value_labels = c(
      "Yes, for more than 3 months" = 1,
      "Yes, for 3 months or less"   = 2,
      "No"                          = 3,
      "Don’t know"                  = 7,
      "Refused"                     = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_health_unable_5cat,
    description = "MO_10. Have you been unable to do certain kinds or amounts of work, housework, or schoolwork because of your health?",
    value_labels = c(
      "Yes, for more than 3 months" = 1,
      "Yes, for 3 months or less"   = 2,
      "No"                          = 3,
      "Don’t know"                  = 7,
      "Refused"                     = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_health_keep_5cat_f,
    description = "MO_9. Does your health keep you from working at a job, doing work around the house, or going to school?"
  ) %>%
  cb_add_col_attributes(
    outcomes_health_unable_5cat_f,
    description = "MO_10. Have you been unable to do certain kinds or amounts of work, housework, or schoolwork because of your health?"
  ) %>%
  cb_add_col_attributes(
    outcomes_month_social_7cat,
    description = "MO_11. How much of the time during the past month has your health limited your social activities (like visiting with friends or close relatives)?",
    value_labels = c(
      "All of the time"      = 1,
      "Most of the time"     = 2,
      "Some of the time"     = 3,
      "A little of the time" = 4,
      "None of the time"     = 5,
      "Don’t know"           = 7,
      "Refused"              = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_month_nervous_7cat,
    description = "MO_12. How much of the time, during the past month, have you been a very nervous person?",
    value_labels = c(
      "All of the time"      = 1,
      "Most of the time"     = 2,
      "Some of the time"     = 3,
      "A little of the time" = 4,
      "None of the time"     = 5,
      "Don’t know"           = 7,
      "Refused"              = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_month_calm_7cat,
    description = "MO_13. During the past month, how much of the time have you felt calm and peaceful?",
    value_labels = c(
      "All of the time"      = 1,
      "Most of the time"     = 2,
      "Some of the time"     = 3,
      "A little of the time" = 4,
      "None of the time"     = 5,
      "Don’t know"           = 7,
      "Refused"              = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_month_blue_7cat,
    description = "MO_14. How much of the time, during the past month, have you felt downhearted and blue?",
    value_labels = c(
      "All of the time"      = 1,
      "Most of the time"     = 2,
      "Some of the time"     = 3,
      "A little of the time" = 4,
      "None of the time"     = 5,
      "Don’t know"           = 7,
      "Refused"              = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_month_happy_7cat,
    description = "MO_15. During the past month, how much of the time have you been a happy person?",
    value_labels = c(
      "All of the time"      = 1,
      "Most of the time"     = 2,
      "Some of the time"     = 3,
      "A little of the time" = 4,
      "None of the time"     = 5,
      "Don’t know"           = 7,
      "Refused"              = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_month_dumps_7cat,
    description = "MO_16. How often, during the past month, have you felt so down in the dumps that nothing could cheer you up?",
    value_labels = c(
      "All of the time"      = 1,
      "Most of the time"     = 2,
      "Some of the time"     = 3,
      "A little of the time" = 4,
      "None of the time"     = 5,
      "Don’t know"           = 7,
      "Refused"              = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_month_social_7cat_f,
    description = "MO_11. How much of the time during the past month has your health limited your social activities (like visiting with friends or close relatives)?"
  ) %>%
  cb_add_col_attributes(
    outcomes_month_nervous_7cat_f,
    description = "MO_12. How much of the time, during the past month, have you been a very nervous person?"
  ) %>%
  cb_add_col_attributes(
    outcomes_month_calm_7cat_f,
    description = "MO_13. During the past month, how much of the time have you felt calm and peaceful?"
  ) %>%
  cb_add_col_attributes(
    outcomes_month_blue_7cat_f,
    description = "MO_14. How much of the time, during the past month, have you felt downhearted and blue?"
  ) %>%
  cb_add_col_attributes(
    outcomes_month_happy_7cat_f,
    description = "MO_15. During the past month, how much of the time have you been a happy person?"
  ) %>%
  cb_add_col_attributes(
    outcomes_month_dumps_7cat_f,
    description = "MO_16. How often, during the past month, have you felt so down in the dumps that nothing could cheer you up?"
  ) %>%
  cb_add_col_attributes(
    outcomes_tf_ill_6cat,
    description = "MO_17. I am somewhat ill.",
    value_labels = c(
      "Definitely true"  = 1,
      "Mostly true"      = 2,
      "Don't know"       = 3,
      "Mostly false"     = 4,
      "Definitely false" = 5,
      "Refused"          = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_tf_anybody_6cat,
    description = "MO_18. I am as healthy as anybody I know.",
    value_labels = c(
      "Definitely true"  = 1,
      "Mostly true"      = 2,
      "Don't know"       = 3,
      "Mostly false"     = 4,
      "Definitely false" = 5,
      "Refused"          = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_tf_health_6cat,
    description = "MO_19. My health is excellent.",
    value_labels = c(
      "Definitely true"  = 1,
      "Mostly true"      = 2,
      "Don't know"       = 3,
      "Mostly false"     = 4,
      "Definitely false" = 5,
      "Refused"          = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_tf_bad_6cat,
    description = "MO_20. I have been feeling bad lately",
    value_labels = c(
      "Definitely true"  = 1,
      "Mostly true"      = 2,
      "Don't know"       = 3,
      "Mostly false"     = 4,
      "Definitely false" = 5,
      "Refused"          = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    outcomes_tf_ill_6cat_f,
    description = "MO_17. I am somewhat ill"
  ) %>%
  cb_add_col_attributes(
    outcomes_tf_anybody_6cat_f,
    description = "MO_18. I am as healthy as anybody I know"
  ) %>%
  cb_add_col_attributes(
    outcomes_tf_health_6cat_f,
    description = "MO_19. My health is excellent"
  ) %>%
  cb_add_col_attributes(
    outcomes_tf_bad_6cat_f,
    description = "MO_20. I have been feeling bad lately"
  ) %>%
  cb_add_col_attributes(
    depres_satisfied_2cat,
    description = "GD_1. Are you basically satisfied with your life?",
    value_labels = c(
      "Yes"  = 0,
      "No"   = 1
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depres_satisfied_2cat_f,
    description = "GD_1. Are you basically satisfied with your life?"
  ) %>%
  cb_add_col_attributes(
    depres_hopeless_2cat,
    description = "GD_2. Do you feel that your situation is hopeless?",
    value_labels = c(
      "No"  = 0,
      "Yes" = 1
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depres_hopeless_2cat_f,
    description = "GD_2. Do you feel that your situation is hopeless?"
  ) %>%
  cb_add_col_attributes(
    depres_better_2cat,
    description = "GD_3. Do you think that most people are better off than you are?",
    value_labels = c(
      "No"  = 0,
      "Yes" = 1
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depres_better_2cat_f,
    description = "GD_3. Do you think that most people are better off than you are?"
  ) %>%
  cb_add_col_attributes(
    depres_activities_2cat,
    description = "GD_4. Have you dropped many of your activities and interests",
    value_labels = c(
      "No"  = 0,
      "Yes" = 1
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depres_activities_2cat_f,
    description = "GD_4. Have you dropped many of your activities and interests"
  ) %>%
  cb_add_col_attributes(
    depres_empty_2cat,
    description = "GD_5. Do you feel that your life is empty?",
    value_labels = c(
      "No"  = 0,
      "Yes" = 1
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depres_empty_2cat_f,
    description = "GD_5. Do you feel that your life is empty?"
  ) %>%
  cb_add_col_attributes(
    depres_bored_2cat,
    description = "GD_6. Do you often get bored?",
    value_labels = c(
      "No"  = 0,
      "Yes" = 1
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depres_bored_2cat_f,
    description = "GD_6. Do you often get bored?"
  ) %>%
  cb_add_col_attributes(
    depres_spirits_2cat,
    description = "GD_7. Are you in good spirits most of the time?",
    value_labels = c(
      "Yes"  = 0,
      "No"   = 1
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depres_spirits_2cat_f,
    description = "GD_7. Are you in good spirits most of the time?"
  ) %>%
  cb_add_col_attributes(
    depres_afraid_2cat,
    description = "GD_8. Are you afraid that something bad is going to happen to you?",
    value_labels = c(
      "No"  = 0,
      "Yes" = 1
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depres_afraid_2cat_f,
    description = "GD_8. Are you afraid that something bad is going to happen to you?"
  ) %>%
  cb_add_col_attributes(
    depres_happy_2cat,
    description = "GD_9. Do you feel happy most of the time?",
    value_labels = c(
      "Yes"  = 0,
      "No"   = 1
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depres_happy_2cat_f,
    description = "GD_9. Do you feel happy most of the time?"
  ) %>%
  cb_add_col_attributes(
    depres_helpless_2cat,
    description = "GD_10. Do you often feel helpless?",
    value_labels = c(
      "No"  = 0,
      "Yes" = 1
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depres_helpless_2cat_f,
    description = "GD_10. Do you often feel helpless?"
  ) %>%
  cb_add_col_attributes(
    depres_home_2cat,
    description = "GD_11. Do you prefer to stay at home, rather than going out and doing things?",
    value_labels = c(
      "No"  = 0,
      "Yes" = 1
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depres_home_2cat_f,
    description = "GD_11. Do you prefer to stay at home, rather than going out and doing things?"
  ) %>%
  cb_add_col_attributes(
    depres_memory_2cat,
    description = "GD_12. Do you feel that you have more problems with your memory than most?",
    value_labels = c(
      "No"  = 0,
      "Yes" = 1
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depres_memory_2cat_f,
    description = "GD_12. Do you feel that you have more problems with your memory than most?"
  ) %>%
  cb_add_col_attributes(
    depres_alive_2cat,
    description = "GD_13. Do you think it is wonderful to be alive now?",
    value_labels = c(
      "Yes"  = 0,
      "No"   = 1
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depres_alive_2cat_f,
    description = "GD_13. Do you think it is wonderful to be alive now?"
  ) %>%
  cb_add_col_attributes(
    depres_worthless_2cat,
    description = "GD_14. Do you feel worthless the way you are now?",
    value_labels = c(
      "No"  = 0,
      "Yes" = 1
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depres_worthless_2cat_f,
    description = "GD_14. Do you feel worthless the way you are now?"
  ) %>%
  cb_add_col_attributes(
    depres_energy_2cat,
    description = "GD_15. Do you feel full of energy?",
    value_labels = c(
      "Yes"  = 0,
      "No"   = 1
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    depres_energy_2cat_f,
    description = "GD_15. Do you feel full of energy?"
  ) %>%
  cb_add_col_attributes(
    ls_lack_companionship_4cat,
    description = "LS_1. First, how often do you feel that you lack companionship?",
    value_labels = c(
      "Hardly ever"      = 1,
      "Some of the time" = 2,
      "Often"            = 3,
      "Refused"          = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    ls_feel_left_out_4cat,
    description = "LS_2. How often do you feel left out?",
    value_labels = c(
      "Hardly ever"      = 1,
      "Some of the time" = 2,
      "Often"            = 3,
      "Refused"          = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    ls_feel_isolated_4cat,
    description = "LS_3. How often do you feel isolated from others?",
    value_labels = c(
      "Hardly ever"      = 1,
      "Some of the time" = 2,
      "Often"            = 3,
      "Refused"          = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    ls_lack_companionship_4cat_f,
    description = "LS_1. First, how often do you feel that you lack companionship?"
  ) %>%
  cb_add_col_attributes(
    ls_feel_left_out_4cat_f,
    description = "LS_2. How often do you feel left out?"
  ) %>%
  cb_add_col_attributes(
    ls_feel_isolated_4cat_f,
    description = "LS_3. How often do you feel isolated from others?"
  ) %>%
  cb_add_col_attributes(
    nesarc_drink_4cat,
    description = "NC_1. In your entire life, have you had at least 1 drink of any kind of alcohol, not counting small tastes or sips?",
    skip_pattern = "If 'Yes', go to Section 3. All other answers, go to NC_2",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 2,
      "Don't know" = 3,
      "Refused"    = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    nesarc_months_4cat,
    description = "NC_2. During the last 12 months, did you have at least 1 drink of any kind of alcohol?",
    skip_pattern = "If 'Yes', go to Section 3. All other answers, go to AC_1",
    value_labels = c(
      "Yes"        = 1,
      "No"         = 2,
      "Don't know" = 3,
      "Refused"    = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    nesarc_drink_4cat_f,
    description = "NC_1. In your entire life, have you had at least 1 drink of any kind of alcohol, not counting small tastes or sips?",
    skip_pattern = "If 'Yes', go to Section 3. All other answers, go to NC_2"
  ) %>%
  cb_add_col_attributes(
    nesarc_months_4cat_f,
    description = "NC_2. During the last 12 months, did you have at least 1 drink of any kind of alcohol?",
    skip_pattern = "If 'Yes', go to Section 3. All other answers, go to AC_1"
  ) %>%
  cb_add_col_attributes(
    auditc_drink_7cat,
    description = "AC_1. How often do you have a drink containing alcohol?",
    skip_pattern = "If 'Never', go to Section 3. All other answers, go to AC_2",
    value_labels = c(
      "Never"                  = 0,
      "Monthly or less"        = 1,
      "2-4 times a month"      = 2,
      "2-3 times a week"       = 3,
      "4 or more times a week" = 4,
      "Don't know"             = 7,
      "Refused"                = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    auditc_drink_7cat_f,
    description = "AC_1. How often do you have a drink containing alcohol?",
    skip_pattern = "If 'Never', go to Section 3. All other answers, go to AC_2"
  ) %>%
  cb_add_col_attributes(
    auditc_day_7cat,
    description = "AC_2. How many standard drinks containing alcohol do you have on a typical day?",
    value_labels = c(
      "1 or 2"     = 1,
      "3 or 4"     = 2,
      "5 or 6"     = 3,
      "7 to 9"     = 4,
      "10 or more" = 5,
      "Don't know" = 7,
      "Refused"    = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    auditc_day_7cat_f,
    description = "AC_2. How many standard drinks containing alcohol do you have on a typical day?"
  ) %>%
  cb_add_col_attributes(
    auditc_five_7cat,
    description = "AC_3. How often do you have five or more drinks on one occasion?",
    value_labels = c(
      "Never"                 = 0,
      "Less than monthly"     = 1,
      "Monthly"               = 2,
      "Weekly"                = 3,
      "Daily or almost daily" = 4,
      "Don't know"            = 7,
      "Refused"               = 9
    ),
    col_type = "Categorical"
  ) %>%
  cb_add_col_attributes(
    auditc_five_7cat_f,
    description = "AC_5. How often do you have five or more drinks on one occasion?"
  ) %>%
  cb_add_col_attributes(
    x_record_month,
    description = "Month record was created."
  ) %>%
  cb_add_col_attributes(
    x_record_year,
    description = "Year record was created."
  ) %>%
  cb_add_col_attributes(
    x_record_status,
    description = "Status of the record as determined by research team."
  ) %>%
  cb_add_col_attributes(
    x_record_comment,
    description = "Comments by interviewer."
  )
```

# Create a data frame containing the column names and their descriptions using the df_descriptions function

```{r}
gh_desc <- var_descriptions(general_health)
```

## Save as rds file
```{r}
write_rds(gh_desc, "../codebooks/variable_descriptions/general_health_var_desc.rds")
```

# Exclude summary stats for certain variables in word doc

```{r}
# Create a vector of variables to exclude summary statistics from
no_stats <- general_health %>%
  select(
    c(matches("^(x|xc)_"), matches("^(name)"), medstar_id)
  )

no_stats_vars <- colnames(no_stats)
```

# Pass data frame to the codebook() function

```{r}
# Add title and description to codebook
general_health_codebook <- codebook(
  df = general_health,
  title = "General Health Dataset",
  description = "Data collected during DETECT follow-up interviews regarding the patient's general health and safety",
  no_summary_stats = no_stats_vars
)
```

```{r}
print(general_health_codebook, "../codebooks/general_health_codebook.docx")
```
