---
title: "Remove duplicate rows (by MedStar ID) from EPCR Data"
date: "2020-10-14"
---

# Background

For some reason, the patient data we were initially downloading from [MedStar's FTP Server](https://sftp.medstar911.org/login.html) did not include the initial DETECT screenings. We weren't doing anything with the initial DETECT screenings at first, so it took a little while to figure out that the initial screenings weren't there. 

We requested that the initial DETECT screenings be included in the data going forward. MedStar also uploaded the initial DETECT screenings for all records on the FTP server going back to 2019-07-01. 

On 2020-09-10 Sunil tried to import the initial DETECT screenings into FM Pro, but ran into an error. The error was caused by duplicated MedStar IDs (Incident_Patient_Care_Report_Number). Further, he noticed that the initial DETECT screening responses by row within MedStar ID.

On 2020-10-05 MedStar uploaded an updated data set to the FTP Server. There are still multiple MedStar IDs in some cases, however. After several conversations with MedStar, here is what we figured out about the multiple IDs.

From Desiree:

"Some more feedback on this…
 
I reached out to both crews for these two incidents in September.
 
The crew for the record ending in 51c91 emphasized that they had ran the patient twice. The first worksheet at 0724 was initially created by the paramedic during the preliminary encounter, however, the second worksheet at 0820 was created by his partner as she was the one who ultimately assessed, treated and transferred the patient over to hospital staff so she had the most accurate encounter. She also reported that she put the APS report information in that worksheet.
 
Regarding the record ending in 9c294, I spoke to the crew member who ran the patient. She stated that the worksheet was started at the end of the call and she thinks that the computer timed out which prompted her to do another worksheet. She also emphasized that the APS report information was included in her worksheet and therefore that one should be the most accurate.
 
To Ricky’s point, it appears as though there are a couple of reasons as to why 2 worksheets are created. From what I gather from these two incidents, the second form is the accurate one."

**Update 2020-12-11:**
* Nitin started adding "worksheet_instance_crew_member" and "worksheet_date_time" to the regular data uploads that MedStar sends to the FTP server. Duplicates by MedStar ID instantly went up from 1 or 2 per month to 562 in December. I don't think this reflects changing conditions on the ground. This is primarily due to differences in worksheet timestamp only. Not differences to substantive values. 

# Decision

After further discussion we decided that it seem like a reasonable assumption to make that the medics typically only create a second worksheet in order to make it more accurate (or complete it). Therefore, whenever there are two worksheets with conflicting information, we should keep the second one. The exception is when only the first row contains an APS report number. In that case, we will keep the row with the APS report number because 1.) We can use later in data quality checks (i.e., to merge with APS data), and 2.) it is the presumably the screening responses that prompted the medic to report to APS.

# Load packages

```{r message=FALSE}
library(dplyr)
library(readxl)
library(readr)
library(stringr)
library(readr)
library(lubridate)
```

# Load data

Convert csv file to excel file outside of R.

```{r}
df_w_dups <- read_excel(
  "/Users/bradcannell/Desktop/Detect Report-2021_07_01_134023.xlsx",
  na = c("", " ", "NULL")
)
```

Take an initial look to see how many duplicate MedStar ID's there are.

```{r}
df_w_dups %>% 
  count(Incident_Patient_Care_Report_Number) %>% 
  filter(n > 1)
```

# Initial data cleaning

Convert variable names to lowercase
Also, fill in spaces with underscores

```{r}
names(df_w_dups) <- str_to_lower(names(df_w_dups))
names(df_w_dups) <- str_replace_all(names(df_w_dups), " ", "_")
```

# Add within group row number

```{r}
df_w_dups <- df_w_dups %>%
  group_by(incident_patient_care_report_number) %>% 
  arrange(worksheet_date_time) %>% 
  mutate(
    row = row_number(),
    n_rows = max(row)
  ) %>% 
  ungroup()
```

# Check for duplicate MedStar IDs

```{r}
dups_by_year_month <- df_w_dups %>% 
  mutate(
    year = year(incident_date_time),
    month = month(incident_date_time)
  ) %>% 
  # Only keep MedStar ID's with more than one row
  filter(n_rows > 1) %>% 
  # Only keep one row per MedStar ID. We want a count of ID's with at 
  # least one duplicate row. Not a count of rows that are duplicates.
  filter(row == 1) %>% 
  count(year, month)
```

# Save number of duplicates for record keeping

Created a csv file to store various quality control metrics over time. In this case, I want to keep a count of the duplicate MedStar IDs by year and month. We will update this each month before adding the MedStar patient data to FM Pro.

Actually, once this is all in FM Pro, the process may change. Oh well, do it this way for now.

```{r}
qc <- read_csv(
  "data/dup_medstar_ids.csv",
  col_types = "ddd"
)
```

```{r}
qc <- qc %>% 
  bind_rows(
    dups_by_year_month %>% 
      rename(count = n)
  )
```

If there are no dups, then set to zero. Just do this manually for now.

```{r}
write_csv(qc, "data/dup_medstar_ids.csv")
```

# Remove duplicate rows

After further discussion we decided that it seem like a reasonable assumption to make that the medics typically only create a second worksheet in order to make it more accurate (or complete it). Therefore, whenever there are two worksheets with conflicting information, we should keep the second one. The exception is when only the first row contains an APS report number. In that case, we will keep the row with the APS report number because 1.) We can use later in data quality checks (i.e., to merge with APS data), and 2.) it is the presumably the screening responses that prompted the medic to report to APS.

First, if only one row has an APS report number, keep that row. 
1. We can use later in data quality checks.
2. It is the presumably the screening responses that prompted the medic to report to APS.

Then keep the second row, if applicable.

```{r rows.print=11}
# # For testing
# # 1 = no aps report number. Keep second row.
# # 2 = one aps report number. Keep row with aps report number.
# # 3 = Both aps report number. Keep second row.
# # 4 = Mix. Keep last row with aps report number.
# # 5 = PCR with only one row and no aps report number
# # 6 = PCR with only one row and an aps report number
# tibble(
#   incident_patient_care_report_number = c(1, 1, 2, 2, 3, 3, 4, 4, 4, 5, 6),
#   x = c(1, 0, 0, 0, 1, 0, 1, 0, 1, 1, 1),
#   aps_report_number = c(NA, NA, 1001, NA, 1002, 1002, NA, 1003, 1003, NA, 1004),
#   worksheet_date_time = c(1, 2, 1, 2, 1, 2, 2, 1, 3, 1, 1),
#   row = c(1, 2, 1, 2, 1, 2, 1, 2, 3, 1, 1),
#   n_rows = c(2, 2, 2, 2, 2, 2, 3, 3, 3, 1, 1)
# ) %>% 
#   # Identify set of PCR numbers with none, one, and multiple APS report numbers.
#   # Also identify the latest worksheet date for each PCR set.
#   group_by(incident_patient_care_report_number) %>% 
#   mutate(
#     max_date = worksheet_date_time == max(worksheet_date_time),
#     aps_report_rows = case_when(
#       # Identify PCR numbers with one row and don't consider them further.
#       # All cases considered below have at least two rows.
#       n_rows == 1 ~ "ignore",
#       # Identify sets of PCR numbers with no APS reports
#       all(is.na(aps_report_number)) ~ "none",
#       # Identify sets of PCR numbers with multiple rows with an APS report
#       sum(!is.na(aps_report_number)) > 1 ~ "multiple",
#       # Finally identify rows with one NA and one APS report number
#       sum(!is.na(aps_report_number)) == 1 ~ "one"
#     )
#   ) %>% 
#   filter(
#     # Keep all non-duplicated rows
#     n_rows == 1 |
#     # If there's only one row in the set with an APS number, keep that row.
#     (aps_report_rows == "one" & !is.na(aps_report_number)) |
#     # Otherwise, keep the last row by worksheet date time
#     (aps_report_rows %in% c("none", "multiple") & max_date == TRUE)
#   ) %>% 
#   ungroup()
```

```{r}
df <- df_w_dups %>%
  # Identify set of PCR numbers with none, one, and multiple APS report numbers.
  # Also identify the latest worksheet date for each PCR set.
  group_by(incident_patient_care_report_number) %>% 
  mutate(
    max_date = worksheet_date_time == max(worksheet_date_time),
    aps_report_rows = case_when(
      # Identify PCR numbers with one row and don't consider them further.
      # All cases considered below have at least two rows.
      n_rows == 1 ~ "ignore",
      # Identify sets of PCR numbers with no APS reports
      all(is.na(aps_report_number)) ~ "none",
      # Identify sets of PCR numbers with multiple rows with an APS report
      sum(!is.na(aps_report_number)) > 1 ~ "multiple",
      # Finally identify rows with one NA and one APS report number
      sum(!is.na(aps_report_number)) == 1 ~ "one"
    )
  ) %>% 
  filter(
    # Keep all non-duplicated rows
    n_rows == 1 |
    # If there's only one row in the set with an APS number, keep that row.
    (aps_report_rows == "one" & !is.na(aps_report_number)) |
    # Otherwise, keep the last row by worksheet date time
    (aps_report_rows %in% c("none", "multiple") & max_date == TRUE)
  ) %>% 
  ungroup()
```

# Keep variables of interest (for import into FM Pro)

```{r}
df <- df %>%
  select(-row:-aps_report_rows) # 39 columns
```

2021-02-02, From Sunil:
One minor thing, in the file you sent me to upload. In your coding to process this file, can you drop the last two columns (worksheet_instance_crew_member and worksheet_date_time)?

```{r}
df <- df %>% 
  select(-worksheet_instance_crew_member, -worksheet_date_time) # 37 columns
```

# Reformat the date

So that it can be imported into FM Pro.

2021-01-07, from Sunil: Main reason the database refused the import is that timestamps have been reformatted to “2019-12-01T00:02:18Z” when it is expecting “12/1/2019  12:02:18 AM”.

```{r}
# For data checks
# df %>% 
#   select(where(is.POSIXct))
```

```{r}
df <- df %>% 
  mutate(
    across(
      c(incident_date_time, unit_arrived_on_scene_date_time),
      ~ format(.x, "%m/%d/%Y %I:%M:%S %p") 
    ),
    patient_date_of_birth = format(patient_date_of_birth, "%m/%d/%Y")
  )
```

# Export for FM Pro

```{r}
write_csv(
  df, 
  paste0("/Users/bradcannell/Desktop/medstar_data_", Sys.Date() %>% format("%Y_%m_%d"), ".csv"),
  na = ""
)
```






































