---
title: "Checking for missing observational data - Currently in development"
date: "2021-02-08"
---

Data collected on the observational measures layout in FM Pro during the F/U interviews. 

2021-02-08: Downloaded this to check for incomplete. If this is still useful/necessary then we will want to add this code back to the larger dashboarding process.

```{r}
library(dplyr)
library(DBI)
library(odbc)
library(keyring)
```

# Import the observational measures data

```{r}
con <- dbConnect(
  odbc(),
  driver   = "/Library/ODBC/FileMaker ODBC.bundle/Contents/MacOS/FileMaker ODBC",
  server   = "spsqlapwv003.sph.uthouston.edu",
  database = "DETECT",
  uid      = key_list("detect_fm_db_readonly")[1,2],
  pwd      = key_get("detect_fm_db_readonly")
)
```

```{r}
walk(
  # List of tables to import
  c("ObservationalMeasures"),
  
  # Import and add data frames to the global environment
  function(x) {
    df <- dbReadTable(con, x)
    # Convert camel case to snake case for df name
    nm <- str_replace_all(x, "(\\B)([A-Z])", "_\\2")
    nm <- str_to_lower(nm)
    assign(nm, df, envir = .GlobalEnv)
  }
)
```

```{r}
dbDisconnect(con)
rm(con)
```

I think we can just acknowledge that the completion of this section was a big problem prior to changing up the format.

For now, I just want to start by looking at missingness in the new format. According to the Google important dates sheet (https://docs.google.com/spreadsheets/d/1U9ZvrRVrIPd6RY3Mry5YczTwO-RhHd3E8-afLudwSjY/edit#gid=0), we started using the new version of the observtional measures layout on 2020-08-17.

```{r}
date_new_layout <- as.POSIXct("2020-08-17 00:00:00")
om_new <- observational_measures %>% 
  filter(xCreatedTimestamp >= date_new_layout) %>% 
  # Keep only the columns of interest. Drop columns from previous version of
  # the layout.
  select(
    xCreatedBy, xCreatedTimestamp, MedstarID, UnusualOdor:HoardingMedications, 
    AtPhysical:AtSelfWhy
  )
```

# Count the number of incomplete detect items

```{r}
om_new %>% 
  select(UnusualOdor:HoardingMedications) %>% 
  rowwise() %>%
  mutate(n_miss = sum(is.na(c_across(UnusualOdor:HoardingMedications)))) %>% 
  ungroup() %>% 
  filter(n_miss > 0)
```

There doesn't appear to be a big problem with missing data in the DETECT items (7 out of 134 rows as of 2021-02-08).

# Count the number of incomplete medic EM assessment items

```{r}
om_new %>% 
  select(starts_with("AT") & !ends_with("Why")) %>% 
  rowwise() %>%
  mutate(n_miss = sum(is.na(c_across()))) %>% 
  ungroup() %>% 
  filter(n_miss > 0)
```

Count the number of incomplete medic EM assessment comments

```{r}
om_new %>% 
  select(ends_with("Why")) %>% 
  rowwise() %>%
  mutate(n_miss = sum(is.na(c_across()))) %>% 
  ungroup() %>% 
  filter(n_miss > 0)
```

There are comments missing in some cases, but that is to be expected. Except when there is a yes. Let's see if there are any yes's and if there are comments for those yes's

```{r}
purrr::map2_df(
  .x = select(om_new, starts_with("AT") & !ends_with("Why")) %>% names() %>% syms(),
  .y = select(om_new, ends_with("Why")) %>% names() %>% syms(),
  .f = function(x, y) {
    om_new %>% 
      filter({{ x }} == "Yes") %>% 
      select(MedstarID, {{ x }}, {{ y }}) %>% 
      mutate({{ x }} := names(.)[2]) %>% 
      rename(yes_column = 2, comment = 3)
  }
)
```


```{r}
# om_new %>% 
#   filter(MedstarID == "7d6ff06abd134660b4eea67931aa0155")
```

2021-02-08: There aren't any "Yes's" without a comment. There is one "Yes" with a comment of "No evidence". It looks like a typo.




