---
title: "geheal_recode_factor"
author: "Marissa Gough"
date: "June 29, 2022"
---

```{r, message= FALSE}
# Load all necessary libraries
library(readr)
library(purrr)
library(stringr)
library(dplyr, warn.conflicts = FALSE)
```


## Load data

Load the data tables into the global environment as data frames. We will create categorical variables with numerical values that match the codebook and also create a factor variable for each categorical variable in the data frame to be used for analysis.

```{r load data, messages = FALSE}
geheal <- read_csv("../data/raw/General Health.csv")
```

# Data cleaning

Here we will convert all variable names to snake case so that everything is uniform.

```{r}
# Convert all variable names to snake case
walk(
  # Grab the names of all data frames in the global environment
  .x = ls()[map_lgl(ls(), ~ is.data.frame(get(.)))],
  .f = function(x) {
    # Grab individual df from environment
    df <- get(x)
    # Grab the variables names
    var_names <- names(df)
    # Convert variable names to snake case
    var_names <- str_replace_all(var_names, '(\\B)([A-Z])', '_\\2')
    # Convert variable names to lower case
    var_names <- str_to_lower(var_names)
    # Fix medstar_id
    var_names[var_names == "medstar_i_d"] <- "medstar_id"
    # assign back to the dataframe
    names(df) <- var_names
    # Replace df with new names in global environment
    assign(x, df, envir = .GlobalEnv)
  }
)
```


## Change the encoding of columns that contain unrecognized characters where there is an apostrophe. Substitute an apostrophe for the special characters so that the value is "Don't know"

```{r}
Encoding(geheal$outcomes_health_general) <- "ASCII"
Encoding(geheal$outcomes_health_unable) <- "ASCII"
Encoding(geheal$outcomes_health_keep) <- "ASCII"
Encoding(geheal$auditc_drink) <- "ASCII"
Encoding(geheal$auditc_day) <- "ASCII"
Encoding(geheal$auditc_five) <- "ASCII"

geheal <- geheal %>%
  mutate(
    outcomes_health_general =
      iconv(outcomes_health_general, "ASCII", "latin1", "'"),
    outcomes_health_keep = 
      iconv(outcomes_health_keep, "ASCII", "latin1", "'"),
    outcomes_health_unable = 
      iconv(outcomes_health_unable, "ASCII", "latin1", "'"),
    auditc_drink = 
      iconv(auditc_drink, "ASCII", "latin1", "'"),
    auditc_day = 
      iconv(auditc_day, "ASCII", "latin1", "'"),
    auditc_five = 
      iconv(auditc_five, "ASCII", "latin1", "'")
)
```

## Change all instances of "Very severe" to "Very Severe" to match codebook.

```{r}
geheal <- geheal %>% 
  mutate_all(str_replace_all, "Very severe", "Very Severe")
```

Remove unwanted characters and replace with "Don't know"

```{r}
geheal[geheal == "Dont know"] <- "Don't know"
```

### PEG: A Three-Item Scale Assessing Pain Intensity and Interference

```{r}
geheal <- geheal %>%
  mutate(
    across(
      .cols = starts_with("peg"),
      .fns  = ~case_when(
        .x == "0 - No pain"                         ~ 0,
        .x == "1"                                   ~ 1,
        .x == "2"                                   ~ 2,
        .x == "3"                                   ~ 3,
        .x == "4"                                   ~ 4,
        .x == "5"                                   ~ 5,
        .x == "6"                                   ~ 6,
        .x == "7"                                   ~ 7,
        .x == "8"                                   ~ 8,
        .x == "9"                                   ~ 9,
        .x == "10 - Pain as bad as you can imagine" ~ 10,
        .x == "Refused"                             ~ 99
        ),
      .names = "{col}_12cat"
      ),
       across(
      .cols  = ends_with("12cat"),
      .fns   = ~ factor(.x, labels = c(
        "0 - No pain", "1", "2", "3", "4", "5", "6", "7", 
        "8", "9", "10 - Pain as bad as you can imagine", "Refused"
      )
      ),
      .names = "{col}_f"
    )
  )
```

### Medical Outcomes Study

```{r}
geheal <- geheal %>%
  mutate (
    outcomes_health_general_7cat = factor(
      outcomes_health_general,
      levels = c(
        "Excellent", "Very good", "Good", "Fair", 
        "Poor", "Don't know", "Refused"
      )
    )
  )
```


```{r}
geheal <- geheal %>%
  mutate(
    across(
      .col = c(22:27),
      .fn = ~ factor(.x, levels = c(
        "Yes, limited for more than 3 months", "Yes, limited for 3 months or less", 
        "Not limited at all", "Don't know", "Refused"
      )
      ),
      .names = "{col}_5cat"
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    outcomes4_weeks_pain_8cat = factor(
      outcomes4_weeks_pain,
      levels = c("None", "Very mild", "Mild", "Moderate", "Severe", "Very Severe", "Don't know", "Refused")
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    across(
      .col = c(29:30),
      .fn = ~ factor(.x, levels = c(
        "Yes, for more than 3 months", "Yes, for 3 months or less", 
        "No", "Don't know", "Refused"
      )
      ),
      .names = "{col}_5cat"
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    across(
      .col = (31:36),
      .fn = ~ factor(.x, levels = c(
        "All of the time", "Most of the time", "Some of the time", 
        "A little of the time", "None of the time", "Don't know", "Refused"
      )
      ),
      .names = "{col}_7cat"
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    across(
      .col = (37:40),
      .fn = ~ factor(.x, levels = c(
        "Definitely true", "Mostly true", "Don't know", 
        "Mostly false", "Definitely false", "Refused"
      )
      ),
      .names = "{col}_6cat"
    )
  )
```

## Geriatric Depression Scale Variables

These had to be coded individually, since some variables are coded 0 for "Yes" and 1 for "No" and others are coded the opposite

```{r}
geheal <- geheal %>%
  mutate(
    depres_satisfied_2cat = factor(
      depres_satisfied,
      levels = c("Yes", "No")
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    depres_hopeless_2cat = factor(
    depres_hopeless,
    levels = c("No", "Yes")
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    depres_better_2cat = factor(
    depres_better,
    levels = c("No", "Yes")
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    depres_activities_2cat = factor(
    depres_activities,
    levels = c("No", "Yes")
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    depres_empty_2cat = factor(
    depres_empty,
    levels = c("No", "Yes")
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    depres_bored_2cat = factor(
    depres_bored,
    levels = c("No", "Yes")
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    depres_spirits_2cat = factor(
    depres_spirits,
    levels = c("Yes", "No")
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    depres_afraid_2cat = factor(
    depres_afraid,
    levels = c("No", "Yes")
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    depres_happy_2cat = factor(
    depres_happy,
    levels = c("Yes", "No")
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    depres_helpless_2cat = factor(
    depres_helpless,
    levels = c("No", "Yes")
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    depres_home_2cat = factor(
    depres_home,
    levels = c("No", "Yes")
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    depres_memory_2cat = factor(
    depres_memory,
    levels = c("No", "Yes")
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    depres_alive_2cat = factor(
    depres_alive,
    levels = c("Yes", "No")
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    depres_worthless_2cat = factor(
    depres_worthless,
    levels = c("No", "Yes")
    ),
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    depres_energy_2cat = factor(
    depres_energy,
    levels = c("Yes", "No")
    ),
  )
```

## UCLA 3-Item Loneliness Scale variables

```{r}
geheal <- geheal %>%
  mutate(
    across(
      .col = (56:58),
      .fn = ~ factor(.x, levels = c("Hardly ever", "Some of the time", "Often", "Refused")
      ),
      .names = "{col}_4cat"
    )
  )
```

## National Epidemiological Survey on Alcohol and Related Conditions-III (NESARC-III) variables

```{r}
geheal <- geheal %>%
  mutate(
    across(
      .col = (59:60),
      .fn = ~ factor(.x, levels = c("Yes", "No", "Don't know", "Refused")
      ),
      .names = "{col}_4cat"
    )
  )
```


## Alcohol Use Disorders Test, Consumption Questions (AUDIT-C) variables

```{r}
geheal <- geheal %>%
  mutate(
    auditc_drink_7cat = factor(
      auditc_drink,
      levels = c(
        "Never", "Monthly or less", "2-4 times a month", 
        "2-3 times a week", "4 or more times a week", "Don't know", "Refused"
      )
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    auditc_day_7cat = factor(
      auditc_day,
      levels = c("1 or 2", "3 or 4", "5 or 6", "7 to 9", "10 or more", "Don't know", "Refused")
    )
  )
```

```{r}
geheal <- geheal %>%
  mutate(
    auditc_five_7cat = factor(
      auditc_five,
      levels = c("Never", "Less than monthly", "Monthly", "Weekly", "Daily or almost daily", "Don't know", "Refused")
    )
  )
```

# Write file to csv

```{r}
write_csv(geheal, "geheal_factor.csv")
```

