---
title: "Self Report Variables - Recode Categorical Variables as Factors"
author: "Marissa Gough"
---
```{r, message= FALSE}
# Load all necessary libraries
library(readr)
library(purrr)
library(stringr)
library(dplyr, warn.conflicts = FALSE)
```

# Load data

Load the data tables into the global environment as data frames. We will create categorical variables with numerical values that match the codebook and also create a factor variable for each categorical variable in the data frame to be used for analysis.

```{r load data, messages = FALSE}
# I changed the encoding to remove unrecognized characters "Donít know" for don't know

sr <- read_csv("../data/raw/Self Report.csv", show_col_types = FALSE, locale = locale(encoding = "latin1", asciify = TRUE)) # 598 203
```

# Data cleaning

Here we will convert all variable names to snake case so that everything is uniform.

```{r}
# Convert all variable names to snake case
walk(
  # Grab the names of all data frames in the global environment
  .x = ls()[map_lgl(ls(), ~ is.data.frame(get(.)))],
  .f = function(x) {
    # Grab individual df from environment
    df <- get(x)
    # Grab the variables names
    var_names <- names(df)
    # Convert variable names to snake case
    var_names <- str_replace_all(var_names, '(\\B)([A-Z])', '_\\2')
    # Convert variable names to lower case
    var_names <- str_to_lower(var_names)
    # Fix medstar_id
    var_names[var_names == "medstar_i_d"] <- "medstar_id"
    # assign back to the dataframe
    names(df) <- var_names
    # Replace df with new names in global environment
    assign(x, df, envir = .GlobalEnv)
  }
)
```

Remove unwanted characters and replace with "Don't know"

```{r}
sr[sr == "Dont know"] <- "Don't know"
```

## Self-report injury, violence, neglect, and exploitation

Set levels to be used throughout this program

```{r}

# Set levels for factors for different types of questions
levels_yes_no   <- c("Yes", "No", "Don't know", "Refused")
levels_help     <- c("Yes, one person", "Yes, more than one person", "No",
                     "Don't know", "Refused")
levels_reliable <- c("Not at all reliable", "Somewhat reliable", 
                     "Very reliable", "Completely reliable", "Don’t know",
                     "Refused")
levels_person   <- c("A spouse or partner", "An ex spouse or partner", 
                     "A parent or step-parent", "A brother or sister", 
                     "A son or daughter", "Another relative", "A coworker", 
                     "A neighbor", "A friend", "Some other non-relative",
                     "Don't know", "Refused")
```

### Neglect variables

```{r}
sr <- sr %>%
  mutate(
    across(
      #Selects variables that have yes/no levels
      .cols = starts_with("neglect") & !ends_with("help") &
        !ends_with("reliable") & !ends_with("person"),
      .fns  = ~ case_when(
        .x == "Yes"        ~ 1,
        .x == "No"         ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused"    ~ 9 
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("neglect") & !ends_with("help") &
        !ends_with("reliable") & !ends_with("person") & !ends_with("4cat"),
      .fn    = ~ factor(.x, levels = levels_yes_no),
      .names = "{col}_4cat_f"
    )
  )
```    

```{r}
sr <- sr %>%
  mutate(
    across(
      .cols  = starts_with("neglect") & ends_with("help"),
      .fns   = ~ case_when(
        .x == "Yes, one person"           ~ 1, 
        .x == "Yes, more than one person" ~ 2, 
        .x == "No"                        ~ 3,
        .x == "Don't know"                ~ 7, 
        .x == "Refused"                   ~ 9
      ),
      .names = "{col}_5cat" 
    ),
    across(
      .cols  = starts_with("neglect") & ends_with("help"),
      .fns   = ~ factor(.x, levels = levels_help),
      .names = "{col}_5cat_f"
    )
  )
```
   
```{r}
sr <- sr %>%
  mutate(
    across(
      .cols  = starts_with("neglect") & ends_with("reliable"),
      .fns   = ~ case_when(
        .x == "Not at all reliable" ~ 1, 
        .x == "Somewhat reliable"   ~ 2, 
        .x == "Very reliable"       ~ 3, 
        .x == "Completely reliable" ~ 4, 
        .x == "Don't know"          ~ 7,
        .x == "Refused"             ~ 9
      ),
      .names = "{col}_6cat" 
    ),
    across(
      .cols  = starts_with("neglect") & ends_with("reliable"),
      .fns   = ~ factor(.x, levels = levels_reliable),
      .names = "{col}_6cat_f"
    )
  )
```

Participants were allowed to choose more than one person during the interview. Since some people chose more than one person for these questions, a dummy variable was created. 

```{r}
#Create dummy variables for race categories 1 = TRUE 0 = FALSE
sr <- sr %>% 
  mutate(
    neglect_spouse         = as.numeric(str_detect(neglect_person, "A spouse or partner")),
    neglect_ex_partner     = as.numeric(str_detect(neglect_person, "An ex-spouse or parner")),
    neglect_parent         = as.numeric(str_detect(neglect_person, "A parent or step-parent")),
    neglect_sibling        = as.numeric(str_detect(neglect_person, "A brother or sister")),
    neglect_child          = as.numeric(str_detect(neglect_person, "A son or daughter")),
    neglect_other_relative = as.numeric(str_detect(neglect_person, "Another relative")),
    neglect_coworker       = as.numeric(str_detect(neglect_person, "A coworker")),
    neglect_neighbor       = as.numeric(str_detect(neglect_person, "A neighbor")),
    neglect_friend         = as.numeric(str_detect(neglect_person, "A friend")),
    neglect_non_relative   = as.numeric(str_detect(neglect_person, "Some other non-relative")),
    neglect_dont_know      = as.numeric(str_detect(neglect_person, "Don't know")),
    neglect_refused        = as.numeric(str_detect(neglect_person, "Refused"))
  )
```
  
### Financial Exploitation Variables

Set levels for factors used in these variables

```{r}
levels_last_time <- c("Less than 1 month ago", 
                      "Between 1 month and less than 3 months ago",
                      "Between 3 months and less than 6 months ago",
                      "Between 6 months and less than 1 year ago",
                      "Between 1 year and less than 3 years ago",
                      "3 or more years ago", "Don't know", "Refused")
```

Recode categorical variables to factor variables

```{r}
sr <- sr %>%
  mutate(
    across(
      #Select variables that have yes/no levels
      .cols = starts_with("finance") & !ends_with("years") &
        !ends_with("times") &  !ends_with("age") & !ends_with("person") &
        !ends_with("last_time"),
      .fns  = ~ case_when(
        .x == "Yes"        ~ 1,
        .x == "No"         ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused"    ~ 9 
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("finance") & !ends_with("years") &
        !ends_with("times") &  !ends_with("age") & !ends_with("person") &
        !ends_with("last_time") & !ends_with("4cat"),
      .fns  = ~ factor(.x, levels = levels_yes_no),
    .names = "{col}_4cat_f"
    )
  )
```    

Participants were allowed to choose more than one person during the interview. Since some people chose more than one person for these questions, a dummy variable was created. 

```{r}
#Create dummy variables for race categories 1 = TRUE 0 = FALSE
sr <- sr %>% 
  mutate(
    finance_spouse         = as.numeric(str_detect(finance_person, "A spouse or partner")),
    finance_ex_partner     = as.numeric(str_detect(finance_person, "An ex-spouse or parner")),
    finance_parent         = as.numeric(str_detect(finance_person, "A parent or step-parent")),
    finance_sibling        = as.numeric(str_detect(finance_person, "A brother or sister")),
    finance_child          = as.numeric(str_detect(finance_person, "A son or daughter")),
    finance_other_relative = as.numeric(str_detect(finance_person, "Another relative")),
    finance_coworker       = as.numeric(str_detect(finance_person, "A coworker")),
    finance_neighbor       = as.numeric(str_detect(finance_person, "A neighbor")),
    finance_friend         = as.numeric(str_detect(finance_person, "A friend")),
    finance_non_relative   = as.numeric(str_detect(finance_person, "Some other non-relative")),
    finance_dont_know      = as.numeric(str_detect(finance_person, "Don't know")),
    finance_refused        = as.numeric(str_detect(finance_person, "Refused"))
  )
```

```{r}
sr <- sr %>%
  mutate(
    across(
      .cols = starts_with("finance") & ends_with("last_time"),
      .fns  = ~ case_when(
        .x == "Less than 1 month ago"                       ~ 1,
        .x == "Between 1 month and less than 3 months ago"  ~ 2,
        .x == "Between 3 months and less than 6 months ago" ~ 3,
        .x == "Between 6 months and less than 1 year ago"   ~ 4,
        .x == "Between 1 year and less than 3 years ago"    ~ 5,
        .x == "3 or more years ago"                         ~ 6, 
        .x == "Don't know"                                  ~ 7,
        .x == "Refused"                                     ~ 9
      ),
    .names = "{col}_8cat"
    ),
    across(
      .cols  = starts_with("finance") & ends_with("last_time"),
      .fns   = ~ factor(.x, levels = levels_last_time),
      .names =  "{col}_8cat_f"
    )
  )
```
    
### Emotional Mistreatment Variables

Set levels to be used with these variables

```{r}
levels_times     <- c("1 or 2 times", "Between 3 and less than 5 times",
                      "Between 5 and less than 10 times", 
                      "Between 10 and less than 20 times", "20 or more times",
                      "Don't know", "Refused")

levels_friends   <- c("None", "Very few (1-3)", "Some (4-6)", "A lot (7+)",
                      "Don't know", "Refused")

#These levels are different than Levels_person as they start with "A Stranger"
# v2 variables were used in later versions of the follow-up interview
levels_person_v2 <- c("A stranger", "A spouse or partner", "An ex spouse or partner", 
                      "A parent or step-parent", "A brother or sister",
                      "A son or daughter", "Another relative", "A coworker", 
                      "A neighbor", "A friend", "Some other non-relative",
                      "Don't know", "Refused")
```
 
Recode categorical variables to factor variables

```{r}
sr <- sr %>%
  mutate(
    across(
      #Select variables with yes/no levels
      .cols = starts_with("emotional") & !ends_with("years") &
        !ends_with("times") &  !ends_with("age") & !ends_with("person") &
        !ends_with("last_time") & !ends_with("friends") &
        !ends_with("person_v2"),
      .fns  = ~ case_when(
        .x == "Yes"        ~ 1,
        .x == "No"         ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused"    ~ 9 
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("emotional") & !ends_with("years") &
        !ends_with("times") &  !ends_with("age") & !ends_with("person") &
        !ends_with("last_time") & !ends_with("friends") & !ends_with("4cat") &
        !ends_with("person_v2"),
      .fns  = ~ factor(.x, levels = levels_yes_no),
      .names = "{col}_4cat_f"
    )
  )
```
  
Participants were allowed to choose more than one person during the interview. Since some people chose more than one person for these questions, a dummy variable was created. 

```{r}
#Create dummy variables for race categories 1 = TRUE 0 = FALSE
sr <- sr %>% 
  mutate(
    emotional_stranger       = as.numeric(str_detect(emotional_incident_person, "A stranger")),
    emotional_spouse         = as.numeric(str_detect(emotional_incident_person, "A spouse or partner")),
    emotional_ex_partner     = as.numeric(str_detect(emotional_incident_person, "An ex-spouse or parner")),
    emotional_parent         = as.numeric(str_detect(emotional_incident_person, "A parent or step-parent")),
    emotional_sibling        = as.numeric(str_detect(emotional_incident_person, "A brother or sister")),
    emotional_child          = as.numeric(str_detect(emotional_incident_person, "A son or daughter")),
    emotional_other_relative = as.numeric(str_detect(emotional_incident_person, "Another relative")),
    emotional_coworker       = as.numeric(str_detect(emotional_incident_person, "A coworker")),
    emotional_neighbor       = as.numeric(str_detect(emotional_incident_person, "A neighbor")),
    emotional_friend         = as.numeric(str_detect(emotional_incident_person, "A friend")),
    emotional_non_relative   = as.numeric(str_detect(emotional_incident_person, "Some other non-relative")),
    emotional_dont_know      = as.numeric(str_detect(emotional_incident_person, "Don't know")),
    emotional_refused        = as.numeric(str_detect(emotional_incident_person, "Refused"))
  )
```
    
```{r}
sr <- sr %>%
  mutate(
    across(
      .cols = starts_with("emotional") & ends_with("last_time"),
      .fns  = ~ case_when(
        .x == "Less than 1 month ago"                       ~ 1,
        .x == "Between 1 month and less than 3 months ago"  ~ 2,
        .x == "Between 3 months and less than 6 months ago" ~ 3,
        .x == "Between 6 months and less than 1 year ago"   ~ 4,
        .x == "Between 1 year and less than 3 years ago"    ~ 5,
        .x == "3 or more years ago"                         ~ 6, 
        .x == "Don't know"                                  ~ 7,
        .x == "Refused"                                     ~ 9
      ),
      .names = "{col}_8cat"
    ),
    across(
      .cols  = starts_with("emotional") & ends_with("last_time"),
      .fns   = ~ factor(.x, levels = levels_last_time),
      .names =  "{col}_8cat_f"
    )
  )
```

```{r}
sr <- sr %>%
  mutate(
    across(
      .cols = starts_with("emotional") & ends_with("times") & 
              !ends_with("times_times"),
      .fns = ~ case_when(
        .x == "1 or 2 times"                      ~ 1, 
        .x == "Between 3 and less than 5 times"   ~ 2,
        .x == "Between 5 and less than 10 times"  ~ 3, 
        .x == "Between 10 and less than 20 times" ~ 4, 
        .x == "20 or more times"                  ~ 5,
        .x == "Don't know"                        ~ 7, 
        .x == "Refused"                           ~ 9
      ),
      .names = "{col}_7cat"
    ),
    across(
      .cols  = starts_with("emotional") & ends_with("times") & 
              !ends_with("times_times"),
      .fns   = ~ factor(.x, levels = levels_times),
      .names = "{col}_7cat_f"
    )
  )
```
  
```{r}
sr <- sr %>%
  mutate(
    emotional_person_friends_6cat = case_when(
      emotional_person_friends == "None"           ~ 0, 
      emotional_person_friends == "Very few (1-3)" ~ 1, 
      emotional_person_friends == "Some (4-6)"     ~ 2, 
      emotional_person_friends == "A lot (7+)"     ~ 3,
      emotional_person_friends == "Don't know"     ~ 7, 
      emotional_person_friends == "Refused"        ~ 9
    ),
    emotional_person_friends_6cat_f = factor(
      emotional_person_friends,
      levels = levels_friends
    )
  )
```
  
Participants were allowed to choose more than one person during the interview. Since some people chose more than one person for these questions, a dummy variable was created. 

```{r}
#Create dummy variables for race categories 1 = TRUE 0 = FALSE
sr <- sr %>% 
  mutate(
    emotional_stranger_v2       = as.numeric(str_detect(emotional_incident_person_v2, "A stranger")),
    emotional_spouse_v2         = as.numeric(str_detect(emotional_incident_person_v2, "A spouse or partner")),
    emotional_ex_partner_v2     = as.numeric(str_detect(emotional_incident_person_v2, "An ex-spouse or parner")),
    emotional_parent_v2         = as.numeric(str_detect(emotional_incident_person_v2, "A parent or step-parent")),
    emotional_sibling_v2        = as.numeric(str_detect(emotional_incident_person_v2, "A brother or sister")),
    emotional_child_v2          = as.numeric(str_detect(emotional_incident_person_v2, "A son or daughter")),
    emotional_other_relative_v2 = as.numeric(str_detect(emotional_incident_person_v2, "Another relative")),
    emotional_coworker_v2       = as.numeric(str_detect(emotional_incident_person_v2, "A coworker")),
    emotional_neighbor_v2       = as.numeric(str_detect(emotional_incident_person_v2, "A neighbor")),
    emotional_friend_v2         = as.numeric(str_detect(emotional_incident_person_v2, "A friend")),
    emotional_non_relative_v2   = as.numeric(str_detect(emotional_incident_person_v2, "Some other non-relative")),
    emotional_dont_know_v2      = as.numeric(str_detect(emotional_incident_person_v2, "Don't know")),
    emotional_refused_v2        = as.numeric(str_detect(emotional_incident_person_v2, "Refused"))
  )
```
  
### Physical Mistreatment Variables

Recode categorical variables to factor variables

```{r}
sr <- sr %>%
  mutate(
    across(
      #Select variables with yes/no levels
      .cols = starts_with("physical") & !ends_with("years") &
        !ends_with("times") &  !ends_with("age") &
        !ends_with("last_time") & !ends_with("friends") &
        !ends_with("person_v2"),
      .fns  = ~ case_when(
        .x == "Yes"        ~ 1,
        .x == "No"         ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused"    ~ 9 
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("physical") & !ends_with("years") &
        !ends_with("times") &  !ends_with("age")  &
        !ends_with("last_time") & !ends_with("friends") & !ends_with("4cat") &
        !ends_with("person_v2"),
      .fns  = ~ factor(.x, levels = levels_yes_no),
    .names = "{col}_4cat_f"
    )
  )
```

```{r}
sr <- sr %>%
  mutate(
    across(
      .cols = starts_with("physical") & ends_with("last_time"),
      .fns  = ~ case_when(
        .x == "Less than 1 month ago"                       ~ 1,
        .x == "Between 1 month and less than 3 months ago"  ~ 2,
        .x == "Between 3 months and less than 6 months ago" ~ 3,
        .x == "Between 6 months and less than 1 year ago"   ~ 4,
        .x == "Between 1 year and less than 3 years ago"    ~ 5,
        .x == "3 or more years ago"                         ~ 6, 
        .x == "Don't know"                                  ~ 7,
        .x == "Refused"                                     ~ 9
      ),
      .names = "{col}_8cat"
    ),
    across(
      .cols  = starts_with("physical") & ends_with("last_time"),
      .fns   = ~ factor(.x, levels = levels_last_time),
      .names =  "{col}_8cat_f"
    )
  )
```

```{r}
sr <- sr %>%
  mutate(
    across(
      .cols = starts_with("physical") & ends_with("times") & 
              !ends_with("times_times"),
      .fns = ~ case_when(
        .x == "1 or 2 times"                      ~ 1, 
        .x == "Between 3 and less than 5 times"   ~ 2,
        .x == "Between 5 and less than 10 times"  ~ 3, 
        .x == "Between 10 and less than 20 times" ~ 4, 
        .x == "20 or more times"                  ~ 5,
        .x == "Don't know"                        ~ 7, 
        .x == "Refused"                           ~ 9),
      .names = "{col}_7cat"
    ),
    across(
      .cols  = starts_with("physical") & ends_with("times") & 
              !ends_with("times_times"),
      .fns   = ~ factor(.x, levels = levels_times),
      .names = "{col}_7cat_f"
    )
  )
```
  
```{r}
sr <- sr %>%
  mutate(
    physical_person_friends_6cat = case_when(
      physical_person_friends == "None"           ~ 0, 
      physical_person_friends == "Very few (1-3)" ~ 1, 
      physical_person_friends == "Some (4-6)"     ~ 2, 
      physical_person_friends == "A lot (7+)"     ~ 3,
      physical_person_friends == "Don't know"     ~ 7, 
      physical_person_friends == "Refused"        ~ 9
    ),
    physical_person_friends_6cat_f = factor(
      physical_person_friends,
      levels = levels_friends
    )
  )
```
  

Participants were allowed to choose more than one person during the interview. Since some people chose more than one person for these questions, a dummy variable was created. 

```{r}
#Create dummy variables for race categories 1 = TRUE 0 = FALSE
sr <- sr %>% 
  mutate(
    physical_stranger_v2       = as.numeric(str_detect(physical_incident_person_v2, "A stranger")),
    physical_spouse_v2         = as.numeric(str_detect(physical_incident_person_v2, "A spouse or partner")),
    physical_ex_partner_v2     = as.numeric(str_detect(physical_incident_person_v2, "An ex-spouse or parner")),
    physical_parent_v2         = as.numeric(str_detect(physical_incident_person_v2, "A parent or step-parent")),
    physical_sibling_v2        = as.numeric(str_detect(physical_incident_person_v2, "A brother or sister")),
    physical_child_v2          = as.numeric(str_detect(physical_incident_person_v2, "A son or daughter")),
    physical_other_relative_v2 = as.numeric(str_detect(physical_incident_person_v2, "Another relative")),
    physical_coworker_v2       = as.numeric(str_detect(physical_incident_person_v2, "A coworker")),
    physical_neighbor_v2       = as.numeric(str_detect(physical_incident_person_v2, "A neighbor")),
    physical_friend_v2         = as.numeric(str_detect(physical_incident_person_v2, "A friend")),
    physical_non_relative_v2   = as.numeric(str_detect(physical_incident_person_v2, "Some other non-relative")),
    physical_dont_know_v2      = as.numeric(str_detect(physical_incident_person_v2, "Don't know")),
    physical_refused_v2        = as.numeric(str_detect(physical_incident_person_v2, "Refused"))
  )
```
Participants were allowed to choose more than one person during the interview. Since some people chose more than one person for these questions, a dummy variable was created. 

```{r}
#Create dummy variables for race categories 1 = TRUE 0 = FALSE
sr <- sr %>% 
  mutate(
    physical_stranger       = as.numeric(str_detect(physical_incident_person, "A stranger")),
    physical_spouse         = as.numeric(str_detect(physical_incident_person, "A spouse or partner")),
    physical_ex_partner     = as.numeric(str_detect(physical_incident_person, "An ex-spouse or parner")),
    physical_parent         = as.numeric(str_detect(physical_incident_person, "A parent or step-parent")),
    physical_sibling        = as.numeric(str_detect(physical_incident_person, "A brother or sister")),
    physical_child          = as.numeric(str_detect(physical_incident_person, "A son or daughter")),
    physical_other_relative = as.numeric(str_detect(physical_incident_person, "Another relative")),
    physical_coworker       = as.numeric(str_detect(physical_incident_person, "A coworker")),
    physical_neighbor       = as.numeric(str_detect(physical_incident_person, "A neighbor")),
    physical_friend         = as.numeric(str_detect(physical_incident_person, "A friend")),
    physical_non_relative   = as.numeric(str_detect(physical_incident_person, "Some other non-relative")),
    physical_dont_know      = as.numeric(str_detect(physical_incident_person, "Don't know")),
    physical_refused        = as.numeric(str_detect(physical_incident_person, "Refused"))
  )
```
  
### Sexual mistreatment variables

Recode categorical variables to factor variables

```{r}
sr <- sr %>%
  mutate(
    across(
      .cols = starts_with("sexual") & !ends_with("years") &
        !ends_with("times") &  !ends_with("age") &
        !ends_with("last_time") & !ends_with("friends") &
        !ends_with("person_v2"),
      .fns  = ~ case_when(
        .x == "Yes"        ~ 1,
        .x == "No"         ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused"    ~ 9 
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("sexual") & !ends_with("years") &
        !ends_with("times") &  !ends_with("age") &
        !ends_with("last_time") & !ends_with("friends") & !ends_with("4cat") &
        !ends_with("person_v2"),
      .fns  = ~ factor(.x, levels = levels_yes_no),
      .names = "{col}_4cat_f"
    )
  )
```
  
```{r}
sr <- sr %>%
  mutate(
    across(
      .cols = starts_with("sexual") & ends_with("last_time"),
      .fns  = ~ case_when(
        .x == "Less than 1 month ago"                       ~ 1,
        .x == "Between 1 month and less than 3 months ago"  ~ 2,
        .x == "Between 3 months and less than 6 months ago" ~ 3,
        .x == "Between 6 months and less than 1 year ago"   ~ 4,
        .x == "Between 1 year and less than 3 years ago"    ~ 5,
        .x == "3 or more years ago"                         ~ 6, 
        .x == "Don't know"                                  ~ 7,
        .x == "Refused"                                     ~ 9
      ),
      .names = "{col}_8cat"
    ),
    across(
      .cols  = starts_with("sexual") & ends_with("last_time"),
      .fns   = ~ factor(.x, levels = levels_last_time),
      .names =  "{col}_8cat_f"
    )
  )
```
  
```{r}
sr <- sr %>%
  mutate(
    across(
      .cols = starts_with("sexual") & ends_with("times") & 
              !ends_with("times_times"),
      .fns = ~ case_when(
        .x == "1 or 2 times"                      ~ 1, 
        .x == "Between 3 and less than 5 times"   ~ 2,
        .x == "Between 5 and less than 10 times"  ~ 3, 
        .x == "Between 10 and less than 20 times" ~ 4, 
        .x == "20 or more times"                  ~ 5,
        .x == "Don't know"                        ~ 7, 
        .x == "Refused"                           ~ 9
      ),
      .names = "{col}_7cat"
    ),
    across(
      .cols  = starts_with("sexual") & ends_with("times") & 
              !ends_with("times_times"),
      .fns   = ~ factor(.x, levels = levels_times),
      .names = "{col}_7cat_f"
    )
  )
```
  
```{r}
sr <- sr %>%
  mutate(
    sexual_person_friends_6cat = case_when(
      sexual_person_friends == "None"           ~ 0, 
      sexual_person_friends == "Very few (1-3)" ~ 1, 
      sexual_person_friends == "Some (4-6)"     ~ 2, 
      sexual_person_friends == "A lot (7+)"     ~ 3,
      sexual_person_friends == "Don't know"     ~ 7, 
      sexual_person_friends == "Refused"        ~ 9
    ),
    sexual_person_friends_6cat_f = factor(
      sexual_person_friends,
      levels = levels_friends
    )
  )
```
  
Participants were allowed to choose more than one person during the interview. Since some people chose more than one person for these questions, a dummy variable was created. 

```{r}
#Create dummy variables for race categories 1 = TRUE 0 = FALSE
sr <- sr %>% 
  mutate(
    sexual_stranger_v2       = as.numeric(str_detect(sexual_incident_person_v2, "A stranger")),
    sexual_spouse_v2         = as.numeric(str_detect(sexual_incident_person_v2, "A spouse or partner")),
    sexual_ex_partner_v2     = as.numeric(str_detect(sexual_incident_person_v2, "An ex-spouse or parner")),
    sexual_parent_v2         = as.numeric(str_detect(sexual_incident_person_v2, "A parent or step-parent")),
    sexual_sibling_v2        = as.numeric(str_detect(sexual_incident_person_v2, "A brother or sister")),
    sexual_child_v2          = as.numeric(str_detect(sexual_incident_person_v2, "A son or daughter")),
    sexual_other_relative_v2 = as.numeric(str_detect(sexual_incident_person_v2, "Another relative")),
    sexual_coworker_v2       = as.numeric(str_detect(sexual_incident_person_v2, "A coworker")),
    sexual_neighbor_v2       = as.numeric(str_detect(sexual_incident_person_v2, "A neighbor")),
    sexual_friend_v2         = as.numeric(str_detect(sexual_incident_person_v2, "A friend")),
    sexual_non_relative_v2   = as.numeric(str_detect(sexual_incident_person_v2, "Some other non-relative")),
    sexual_dont_know_v2      = as.numeric(str_detect(sexual_incident_person_v2, "Don't know")),
    sexual_refused_v2        = as.numeric(str_detect(sexual_incident_person_v2, "Refused"))
  )
```
Participants were allowed to choose more than one person during the interview. Since some people chose more than one person for these questions, a dummy variable was created. 

```{r}
#Create dummy variables for race categories 1 = TRUE 0 = FALSE
sr <- sr %>% 
  mutate(
    sexual_stranger       = as.numeric(str_detect(sexual_incident_person, "A stranger")),
    sexual_spouse         = as.numeric(str_detect(sexual_incident_person, "A spouse or partner")),
    sexual_ex_partner     = as.numeric(str_detect(sexual_incident_person, "An ex-spouse or parner")),
    sexual_parent         = as.numeric(str_detect(sexual_incident_person, "A parent or step-parent")),
    sexual_sibling        = as.numeric(str_detect(sexual_incident_person, "A brother or sister")),
    sexual_child          = as.numeric(str_detect(sexual_incident_person, "A son or daughter")),
    sexual_other_relative = as.numeric(str_detect(sexual_incident_person, "Another relative")),
    sexual_coworker       = as.numeric(str_detect(sexual_incident_person, "A coworker")),
    sexual_neighbor       = as.numeric(str_detect(sexual_incident_person, "A neighbor")),
    sexual_friend         = as.numeric(str_detect(sexual_incident_person, "A friend")),
    sexual_non_relative   = as.numeric(str_detect(sexual_incident_person, "Some other non-relative")),
    sexual_dont_know      = as.numeric(str_detect(sexual_incident_person, "Don't know")),
    sexual_refused        = as.numeric(str_detect(sexual_incident_person, "Refused"))
  )
```

## Fears, wants, needs variables

Recode categorical variables to factor variables

```{r}
sr <- sr %>%
  mutate(
    across(
      .cols = starts_with("fear") & !ends_with("response"),
      .fns  = ~ case_when(
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_2cat"
    ),
    across(
      .cols  = starts_with("fear") & !ends_with("response") &
        !ends_with("2cat"),
      .fns   = ~ factor(.x, levels = c("Don't know", "Refused")),
      .names = "{col}_2cat_f"
    )
  )
```


## Environment Variables

Recode categorical variables to factor variables

```{r}
sr <- sr %>%
  mutate(
    report_private_5cat = case_when(
      report_private == "Yes, for the entire time"                     ~ 1,
      report_private == "Yes, for part of the time"                    ~ 2,
      report_private == "No, but they were still close enough to hear" ~ 3,
      report_private == "No"                                           ~ 4,
      report_private == "Don't know"                                   ~ 7
    ),
    report_private_5cat_f = factor(
      report_private,
      levels = c("Yes, for the entire time", "Yes, for part of the time",
                "No, but they were still close enough to hear", "No",
                "Don't know")),
    report_influence_4cat = case_when(
      report_influence == "Yes"        ~ 1,
      report_influence == "No"         ~ 2,
      report_influence == "Don't know" ~ 7,
      report_influence == "Refused"    ~ 9
    ),
    report_influence_4cat_f = factor(
      report_influence,
      levels = levels_yes_no
    )
  )
```


```{r}
dim(sr) # 598 491
```



# Write data frame to files

Write data frame to CSV

```{r}
write_csv(sr, "sr_factor.csv") #598 491
```

Write data frame to RDS to preserve metadata

```{r}
write_rds(sr, "sr_factor.rds") #598 491
```

