---
title: "Create data sets of variable labels."
---

```{r}
# Load necessary packages and functions
library(dplyr, warn.conflicts = FALSE)
library(readr)
library(here)
library(expss, warn.conflicts = FALSE)
source(here::here("r", "variable_descriptions.R"))
```

# Purpose of the program

RDS files containing descriptions for each variable have been created. Variable labels similar to what is seen in SAS data sets will be created for each variable. These will be added manually. 

# APS Investigations

## Load cleaned data

```{r}
# APS Investigations data set
aps_path <- here::here("data", "cleaned_rds_files", "aps_investigations_import.rds")
aps <- readr::read_rds(aps_path)

# APS Investigations variable descriptions
aps_var_desc_path <- here::here("codebooks", "variable_descriptions", "aps_investigations_var_desc.rds")
aps_var_desc <- readr::read_rds(aps_var_desc_path)
```

## Create CSV file for variable descriptions

A label column will be created manually in Microsoft Excel

```{r}
aps_var_desc_path <- here::here("codebooks", "variable_labels", "aps_investigations_var_lab.csv")
readr::write_csv(aps_var_desc, aps_var_desc_path)
```

## Load CSV file with added label column

```{r, include = FALSE}
aps_var_labs <- readr::read_csv(aps_var_desc_path)
```

## Add the labels to the data frame

```{r}
add_labs <- function(label_df, df){
  labels_named_vec <- setNames(label_df[["label"]], label_df[["name"]]) %>% as.list() 
  result <- apply_labels(df, labels_named_vec)
}
```

```{r}
aps_lab <- add_labs(aps_var_labs, aps)
```


# Self Report

## Load cleaned data

```{r}
# Self report data set
sr_path <- here::here("data", "cleaned_rds_files", "self_report_import.rds")
sr <- readr::read_rds(sr_path)

# Self report variable descriptions
sr_var_desc_path <- here::here("codebooks", "variable_descriptions", "self_report_var_desc.rds")
sr_var_desc <- readr::read_rds(sr_var_desc_path)
```

## Create CSV file for variable descriptions

A label column will be created manually in Microsoft Excel

```{r}
sr_var_desc_path <- here::here("codebooks", "variable_labels", "self_report_var_lab.csv")
readr::write_csv(sr_var_desc, sr_var_desc_path)
```

## Load CSV file with added label column

```{r, include = FALSE}
aps_var_labs <- readr::read_csv(aps_var_desc_path)
```

## Add the labels to the data frame

```{r}
add_labs <- function(label_df, df){
  labels_named_vec <- setNames(label_df[["label"]], label_df[["name"]]) %>% as.list() 
  result <- apply_labels(df, labels_named_vec)
}
```

```{r}
aps_lab <- add_labs(aps_var_labs, aps)
```
