---
title: "Import Data from FileMaker Pro: Self Report"
---

# Overview

In this file, we import and do some initial cleaning of the EM self-report data collected and stored in FileMaker Pro.


# Load packages

```{r, message= FALSE}
# Load all necessary libraries
library(readr)
library(dplyr, warn.conflicts = FALSE)
library(janitor, warn.conflicts = FALSE)
library(stringr)
```


# Load custom functions

```{r}
source(here::here("R", "recoding_factoring_relocating.R"))
```


# Load data

Load the data table into the global environment as a data frame using the raw csv file. See this Wiki page for more information about the location of the data: https://github.com/brad-cannell/detect_fu_interviews_public/wiki. 

```{r}
self_rep_path <- here::here("data", "filemaker_pro_exports", "self_report_import.csv")
```

```{r}
self_rep <- read_csv(self_rep_path)
```

```{r}
# Data check
dim(self_rep) # 956 209
```


# Data cleaning

Here we will convert all variable names to snake case so that everything is uniform.

```{r}
self_rep <- clean_names(self_rep,
  replace = c(
    "60" = "_60",
    "65" = "_65"
  )
)
```

## Filter rows

There is one row that is missing a MedStar ID and almost all other variables. My best guess is that this was a record Sunil was experimenting with. We will drop the row.

```{r}
self_rep <- self_rep |> 
  filter(!is.na(medstar_id))
```

```{r}
# Data check
dim(self_rep) # 955 209
```

## Create factor variables to match levels in follow-up interview protocol

NOTE: We considered recoding all "Don't Know" and "Refused" responses to missing in this file, but chose not to. In this file, we will keep the responses consistent with those that were selected during data collection. The "Don't Know" and "Refused" responses can be converted to missing when cleaning the data for specific analyses. That way, the reasons for missing data can still be evaluated.

### Neglect variables

Columns with Yes/No responses

```{r}
# Columns of interest
cols <- c(
  "neglect_go", "neglect_food", "neglect_house", "neglect_clean", "neglect_ready", 
  "neglect_bills"
)

# labels for factors
labs_no_yes <- c("No" = 0, "Yes" = 1, "Don't know" = 7, "Refused" = 9)

self_rep <- self_rep |>
  chars_to_nums(cols, labs_no_yes) |> 
  factors(cols, labs_no_yes) |> 
  relocate_factors(cols)
```

Columns with number of people responses

```{r}
# Columns of interest
cols <- c(
  "neglect_go_help", "neglect_food_help", "neglect_house_help", "neglect_clean_help", 
  "neglect_ready_help", "neglect_bills_help"
)

# labels for factors
labs_help <- c(
  "Yes, one person" = 1, "Yes, more than one person" = 2, "No" = 0,
  "Don’t know" = 7, "Refused" = 9
)

self_rep <- self_rep |> 
  chars_to_nums(cols, labs_help) |> 
  factors(cols, labs_help) |> 
  relocate_factors(cols)
```

Columns with reliability responses

```{r}
# Columns of interest
cols <- c(
  "neglect_go_reliable", "neglect_food_reliable", "neglect_house_reliable", 
  "neglect_clean_reliable", "neglect_ready_reliable", "neglect_bills_reliable"
)

# labels for factors
labs_reliable <- c(
  "Not at all reliable" = 1, "Somewhat reliable" = 2,
  "Very reliable" = 3, "Completely reliable" = 4, "Don’t know" = 7,
  "Refused" = 9
)

self_rep <- self_rep |> 
  chars_to_nums(cols, labs_reliable) |> 
  factors(cols, labs_reliable) |> 
  relocate_factors(cols)
```

Participants were allowed to choose more than one person during the interview. Since some people chose more than one person for these questions, a dummy variable was created. 

```{r}
#Create dummy variables for race categories 1 = TRUE 0 = FALSE
self_rep <- self_rep %>%
  mutate(
    neglect_person_spouse         = str_detect(neglect_person, "A spouse or partner"),
    neglect_person_ex_partner     = str_detect(neglect_person, "An ex-spouse or parner"),
    neglect_person_parent         = str_detect(neglect_person, "A parent or step-parent"),
    neglect_person_sibling        = str_detect(neglect_person, "A brother or sister"),
    neglect_person_child          = str_detect(neglect_person, "A son or daughter"),
    neglect_person_other_relative = str_detect(neglect_person, "Another relative"),
    neglect_person_coworker       = str_detect(neglect_person, "A coworker"),
    neglect_person_neighbor       = str_detect(neglect_person, "A neighbor"),
    neglect_person_friend         = str_detect(neglect_person, "A friend"),
    neglect_person_non_relative   = str_detect(neglect_person, "Some other non-relative"),
    neglect_person_dont_know      = str_detect(neglect_person, "Don’t know"),
    neglect_person_refused        = str_detect(neglect_person, "Refused")
  ) |> 
  # Coerce True and False to 1 and 0
  mutate(across(neglect_person_spouse:neglect_person_refused, ~ as.numeric(.x)))
```

### Financial Exploitation Variables

#### Set levels for factors used in these variables

# 🔴 Delete

Delete the code chunk below when no longer needed.

```{r}
# Not needed, this variable is not used in this CSV
levels_last_time <- c(
  "Less than 1 month ago",
  "Between 1 month and less than 3 months ago",
  "Between 3 months and less than 6 months ago",
  "Between 6 months and less than 1 year ago",
  "Between 1 year and less than 3 years ago",
  "3 or more years ago", "Don't know", "Refused"
)

levels_times <- c(
  "1 or 2 times", "Between 3 and less than 5 times",
  "Between 5 and less than 10 times",
  "Between 10 and less than 20 times", "20 or more times",
  "Don't know", "Refused"
)
```

#### Recode categorical variables to factor variables

```{r}
# 🔴 I'm just using this code to help me figure out the name of the columns that the original code was manipulating. Again, all these tidyselectors make it difficult to figure out which columns we are mutating.
# This code chunk should be deleted after we get rid of the tidyselectors in the mutate code.
self_rep |> 
  select(
    starts_with("neglect") & ends_with("reliable")
  ) |> 
  names() |> 
  cat(sep = ', ')
```


```{r}
self_rep <- self_rep %>%
  mutate(
    across(
      .cols = starts_with("finance") & !ends_with("years") &
        !ends_with("times") & !ends_with("age") & !ends_with("person") &
        !ends_with("last_time"),
      .fns = ~ case_when(
        .x == "Yes" ~ 1,
        .x == "No" ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("finance") & !ends_with("years") &
        !ends_with("times") & !ends_with("age") & !ends_with("person") &
        !ends_with("last_time") & !ends_with("4cat"),
      .fns = ~ factor(.x, levels = levels_yes_no),
      .names = "{col}_4cat_f"
    ),
    finance_person_12cat = case_when(
      finance_person == "A spouse or partner" ~ 1,
      finance_person == "An ex spouse or partner" ~ 2,
      finance_person == "A parent or step-parent" ~ 3,
      finance_person == "A brother or sister" ~ 4,
      finance_person == "A son or daughter" ~ 5,
      finance_person == "Another relative" ~ 6,
      finance_person == "A coworker" ~ 7,
      finance_person == "A neighbor" ~ 8,
      finance_person == "A friend" ~ 9,
      finance_person == "Some other non-relative" ~ 10,
      finance_person == "Don't know" ~ 77,
      finance_person == "Refused" ~ 99
    ),
    finance_person_12cat_f = factor(
      finance_person,
      levels = levels_person
    ),
    across(
      .cols = starts_with("finance") & ends_with("last_time"),
      .fns = ~ case_when(
        .x == "Less than 1 month ago" ~ 1,
        .x == "Between 1 month and less than 3 months ago" ~ 2,
        .x == "Between 3 months and less than 6 months ago" ~ 3,
        .x == "Between 6 months and less than 1 year ago" ~ 4,
        .x == "Between 1 year and less than 3 years ago" ~ 5,
        .x == "3 or more years ago" ~ 6,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_8cat"
    ),
    across(
      .cols  = starts_with("finance") & ends_with("last_time"),
      .fns   = ~ factor(.x, levels = levels_last_time),
      .names =  "{col}_8cat_f"
    ),
    across(
      .cols = starts_with("finance") & ends_with("times") &
        !ends_with("times_times"),
      .fns = ~ case_when(
        .x == "1 or 2 times" ~ 1,
        .x == "Between 3 and less than 5 times" ~ 2,
        .x == "Between 5 and less than 10 times" ~ 3,
        .x == "Between 10 and less than 20 times" ~ 4,
        .x == "20 or more times" ~ 5,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_7cat"
    ),
    across(
      .cols  = starts_with("finance") & ends_with("times") &
        !ends_with("times_times"),
      .fns   = ~ factor(.x, levels = levels_times),
      .names =  "{col}_7cat_f"
    )
  )
```

### Emotional Mistreatment Variables

#### Set levels to be used with these variables

```{r}
levels_times <- c(
  "1 or 2 times", "Between 3 and less than 5 times",
  "Between 5 and less than 10 times",
  "Between 10 and less than 20 times", "20 or more times",
  "Don't know", "Refused"
)

levels_friends <- c(
  "None", "Very few (1-3)", "Some (4-6)", "A lot (7+)",
  "Don't know", "Refused"
)

levels_person_v2 <- c(
  "A stranger", "A spouse or partner", "An ex spouse or partner",
  "A parent or step-parent", "A brother or sister",
  "A son or daughter", "Another relative", "A coworker",
  "A neighbor", "A friend", "Some other non-relative",
  "Don't know", "Refused"
)
```

#### Recode categorical variables to factor variables

```{r}
self_rep <- self_rep %>%
  mutate(
    across(
      .cols = starts_with("emotional") & !ends_with("years") &
        !ends_with("times") & !ends_with("age") & !ends_with("person") &
        !ends_with("last_time") & !ends_with("friends") &
        !ends_with("person_v2"),
      .fns = ~ case_when(
        .x == "Yes" ~ 1,
        .x == "No" ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("emotional") & !ends_with("years") &
        !ends_with("times") & !ends_with("age") & !ends_with("person") &
        !ends_with("last_time") & !ends_with("friends") & !ends_with("4cat") &
        !ends_with("person_v2"),
      .fns = ~ factor(.x, levels = levels_yes_no),
      .names = "{col}_4cat_f"
    ),
    emotional_incident_person_12cat = case_when(
      emotional_incident_person == "A stranger" ~ 1,
      emotional_incident_person == "A spouse or partner" ~ 2,
      emotional_incident_person == "An ex spouse or partner" ~ 3,
      emotional_incident_person == "A parent or step-parent" ~ 4,
      emotional_incident_person == "A brother or sister" ~ 5,
      emotional_incident_person == "A son or daughter" ~ 6,
      emotional_incident_person == "Another relative" ~ 7,
      emotional_incident_person == "A coworker" ~ 8,
      emotional_incident_person == "A neighbor" ~ 9,
      emotional_incident_person == "A friend" ~ 10,
      emotional_incident_person == "Some other non-relative" ~ 11,
      emotional_incident_person == "Don't know" ~ 77,
      emotional_incident_person == "Refused" ~ 99
    ),
    emotional_incident_person_12cat_f = factor(
      emotional_incident_person,
      levels = levels_person_v2
    ),
    across(
      .cols = starts_with("emotional") & ends_with("last_time"),
      .fns = ~ case_when(
        .x == "Less than 1 month ago" ~ 1,
        .x == "Between 1 month and less than 3 months ago" ~ 2,
        .x == "Between 3 months and less than 6 months ago" ~ 3,
        .x == "Between 6 months and less than 1 year ago" ~ 4,
        .x == "Between 1 year and less than 3 years ago" ~ 5,
        .x == "3 or more years ago" ~ 6,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_8cat"
    ),
    across(
      .cols  = starts_with("emotional") & ends_with("last_time"),
      .fns   = ~ factor(.x, levels = levels_last_time),
      .names =  "{col}_8cat_f"
    ),
    across(
      .cols = starts_with("emotional") & ends_with("times") &
        !ends_with("times_times"),
      .fns = ~ case_when(
        .x == "1 or 2 times" ~ 1,
        .x == "Between 3 and less than 5 times" ~ 2,
        .x == "Between 5 and less than 10 times" ~ 3,
        .x == "Between 10 and less than 20 times" ~ 4,
        .x == "20 or more times" ~ 5,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_7cat"
    ),
    across(
      .cols = starts_with("emotional") & ends_with("times") &
        !ends_with("times_times"),
      .fns = ~ factor(.x, levels = levels_times),
      .names = "{col}_7cat_f"
    ),
    emotional_person_friends_6cat = case_when(
      emotional_person_friends == "None" ~ 0,
      emotional_person_friends == "Very few (1-3)" ~ 1,
      emotional_person_friends == "Some (4-6)" ~ 2,
      emotional_person_friends == "A lot (7+)" ~ 3,
      emotional_person_friends == "Don't know" ~ 7,
      emotional_person_friends == "Refused" ~ 9
    ),
    emotional_person_friends_6cat_f = factor(
      emotional_person_friends,
      levels = levels_friends
    ),
    # Are the levels the same for v2 and v1?
    emotional_incident_person_v2_12cat = case_when(
      emotional_incident_person_v2 == "A stranger" ~ 1,
      emotional_incident_person_v2 == "A spouse or partner" ~ 2,
      emotional_incident_person_v2 == "An ex spouse or partner" ~ 3,
      emotional_incident_person_v2 == "A parent or step-parent" ~ 4,
      emotional_incident_person_v2 == "A brother or sister" ~ 5,
      emotional_incident_person_v2 == "A son or daughter" ~ 6,
      emotional_incident_person_v2 == "Another relative" ~ 7,
      emotional_incident_person_v2 == "A coworker" ~ 8,
      emotional_incident_person_v2 == "A neighbor" ~ 9,
      emotional_incident_person_v2 == "A friend" ~ 10,
      emotional_incident_person_v2 == "Some other non-relative" ~ 11,
      emotional_incident_person_v2 == "Don't know" ~ 77,
      emotional_incident_person_v2 == "Refused" ~ 99
    ),
    emotional_incident_person_v2_12cat_f = factor(
      emotional_incident_person_v2,
      levels = levels_person_v2
    ),
  )
```
 
### Physical Mistreatment Variables

#### Recode categorical variables to factor variables

```{r}
self_rep <- self_rep %>%
  mutate(
    across(
      .cols = starts_with("physical") & !ends_with("years") &
        !ends_with("times") & !ends_with("age") &
        !ends_with("last_time") & !ends_with("friends") &
        !ends_with("person_v2"),
      .fns = ~ case_when(
        .x == "Yes" ~ 1,
        .x == "No" ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("physical") & !ends_with("years") &
        !ends_with("times") & !ends_with("age") &
        !ends_with("last_time") & !ends_with("friends") & !ends_with("4cat") &
        !ends_with("person_v2"),
      .fns = ~ factor(.x, levels = levels_yes_no),
      .names = "{col}_4cat_f"
    ),
    across(
      .cols = starts_with("physical") & ends_with("last_time"),
      .fns = ~ case_when(
        .x == "Less than 1 month ago" ~ 1,
        .x == "Between 1 month and less than 3 months ago" ~ 2,
        .x == "Between 3 months and less than 6 months ago" ~ 3,
        .x == "Between 6 months and less than 1 year ago" ~ 4,
        .x == "Between 1 year and less than 3 years ago" ~ 5,
        .x == "3 or more years ago" ~ 6,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_8cat"
    ),
    across(
      .cols  = starts_with("physical") & ends_with("last_time"),
      .fns   = ~ factor(.x, levels = levels_last_time),
      .names =  "{col}_8cat_f"
    ),
    across(
      .cols = starts_with("physical") & ends_with("times") &
        !ends_with("times_times"),
      .fns = ~ case_when(
        .x == "1 or 2 times" ~ 1,
        .x == "Between 3 and less than 5 times" ~ 2,
        .x == "Between 5 and less than 10 times" ~ 3,
        .x == "Between 10 and less than 20 times" ~ 4,
        .x == "20 or more times" ~ 5,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_7cat"
    ),
    across(
      .cols = starts_with("physical") & ends_with("times") &
        !ends_with("times_times"),
      .fns = ~ factor(.x, levels = levels_times),
      .names = "{col}_7cat_f"
    ),
    physical_person_friends_6cat = case_when(
      physical_person_friends == "None" ~ 0,
      physical_person_friends == "Very few (1-3)" ~ 1,
      physical_person_friends == "Some (4-6)" ~ 2,
      physical_person_friends == "A lot (7+)" ~ 3,
      physical_person_friends == "Don't know" ~ 7,
      physical_person_friends == "Refused" ~ 9
    ),
    physical_person_friends_6cat_f = factor(
      physical_person_friends,
      levels = levels_friends
    ),
    physical_incident_person_v2_12cat = case_when(
      physical_incident_person_v2 == "A stranger" ~ 1,
      physical_incident_person_v2 == "A spouse or partner" ~ 2,
      physical_incident_person_v2 == "An ex spouse or partner" ~ 3,
      physical_incident_person_v2 == "A parent or step-parent" ~ 4,
      physical_incident_person_v2 == "A brother or sister" ~ 5,
      physical_incident_person_v2 == "A son or daughter" ~ 6,
      physical_incident_person_v2 == "Another relative" ~ 7,
      physical_incident_person_v2 == "A coworker" ~ 8,
      physical_incident_person_v2 == "A neighbor" ~ 9,
      physical_incident_person_v2 == "A friend" ~ 10,
      physical_incident_person_v2 == "Some other non-relative" ~ 11,
      physical_incident_person_v2 == "Don't know" ~ 77,
      physical_incident_person_v2 == "Refused" ~ 99
    ),
    physical_incident_person_v2_12cat_f = factor(
      physical_incident_person_v2,
      levels = levels_person_v2
    ),
    physical_person_12cat = case_when(
      physical_person == "A stranger" ~ 1,
      physical_person == "A spouse or partner" ~ 2,
      physical_person == "An ex spouse or partner" ~ 3,
      physical_person == "A parent or step-parent" ~ 4,
      physical_person == "A brother or sister" ~ 5,
      physical_person == "A son or daughter" ~ 6,
      physical_person == "Another relative" ~ 7,
      physical_person == "A coworker" ~ 8,
      physical_person == "A neighbor" ~ 9,
      physical_person == "A friend" ~ 10,
      physical_person == "Some other non-relative" ~ 11,
      physical_person == "Don't know" ~ 77,
      physical_person == "Refused" ~ 99
    ),
    physical_person_12cat_f = factor(
      physical_person,
      levels = levels_person_v2
    )
  )
```

### Sexual mistreatment variables

#### Recode categorical variables to factor variables

```{r}
self_rep <- self_rep %>%
  mutate(
    across(
      .cols = starts_with("sexual") & !ends_with("years") &
        !ends_with("times") & !ends_with("age") &
        !ends_with("last_time") & !ends_with("friends") &
        !ends_with("person_v2") & !ends_with("sexual_person"),
      .fns = ~ case_when(
        .x == "Yes" ~ 1,
        .x == "No" ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("sexual") & !ends_with("years") &
        !ends_with("times") & !ends_with("age") &
        !ends_with("last_time") & !ends_with("friends") & !ends_with("4cat") &
        !ends_with("person_v2") & !ends_with("sexual_person"),
      .fns = ~ factor(.x, levels = levels_yes_no),
      .names = "{col}_4cat_f"
    ),
    across(
      .cols = starts_with("sexual") & ends_with("last_time"),
      .fns = ~ case_when(
        .x == "Less than 1 month ago" ~ 1,
        .x == "Between 1 month and less than 3 months ago" ~ 2,
        .x == "Between 3 months and less than 6 months ago" ~ 3,
        .x == "Between 6 months and less than 1 year ago" ~ 4,
        .x == "Between 1 year and less than 3 years ago" ~ 5,
        .x == "3 or more years ago" ~ 6,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_8cat"
    ),
    across(
      .cols  = starts_with("sexual") & ends_with("last_time"),
      .fns   = ~ factor(.x, levels = levels_last_time),
      .names =  "{col}_8cat_f"
    ),
    across(
      .cols = starts_with("sexual") & ends_with("times") &
        !ends_with("times_times"),
      .fns = ~ case_when(
        .x == "1 or 2 times" ~ 1,
        .x == "Between 3 and less than 5 times" ~ 2,
        .x == "Between 5 and less than 10 times" ~ 3,
        .x == "Between 10 and less than 20 times" ~ 4,
        .x == "20 or more times" ~ 5,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_7cat"
    ),
    across(
      .cols = starts_with("sexual") & ends_with("times") &
        !ends_with("times_times"),
      .fns = ~ factor(.x, levels = levels_times),
      .names = "{col}_7cat_f"
    ),
    sexual_person_friends_6cat = case_when(
      sexual_person_friends == "None" ~ 0,
      sexual_person_friends == "Very few (1-3)" ~ 1,
      sexual_person_friends == "Some (4-6)" ~ 2,
      sexual_person_friends == "A lot (7+)" ~ 3,
      sexual_person_friends == "Don't know" ~ 7,
      sexual_person_friends == "Refused" ~ 9
    ),
    sexual_person_friends_6cat_f = factor(
      sexual_person_friends,
      levels = levels_friends
    ),
    sexual_incident_person_v2_12cat = case_when(
      sexual_incident_person_v2 == "A stranger" ~ 1,
      sexual_incident_person_v2 == "A spouse or partner" ~ 2,
      sexual_incident_person_v2 == "An ex spouse or partner" ~ 3,
      sexual_incident_person_v2 == "A parent or step-parent" ~ 4,
      sexual_incident_person_v2 == "A brother or sister" ~ 5,
      sexual_incident_person_v2 == "A son or daughter" ~ 6,
      sexual_incident_person_v2 == "Another relative" ~ 7,
      sexual_incident_person_v2 == "A coworker" ~ 8,
      sexual_incident_person_v2 == "A neighbor" ~ 9,
      sexual_incident_person_v2 == "A friend" ~ 10,
      sexual_incident_person_v2 == "Some other non-relative" ~ 11,
      sexual_incident_person_v2 == "Don't know" ~ 77,
      sexual_incident_person_v2 == "Refused" ~ 99
    ),
    sexual_incident_person_v2_12cat_f = factor(
      sexual_incident_person_v2,
      levels = levels_person_v2
    ),
    sexual_person_13cat = case_when(
      sexual_person == "A stranger" ~ 1,
      sexual_person == "A spouse or partner" ~ 2,
      sexual_person == "An ex spouse or partner" ~ 3,
      sexual_person == "A parent or step-parent" ~ 4,
      sexual_person == "A brother or sister" ~ 5,
      sexual_person == "A son or daughter" ~ 6,
      sexual_person == "Another relative" ~ 7,
      sexual_person == "A coworker" ~ 8,
      sexual_person == "A neighbor" ~ 9,
      sexual_person == "A friend" ~ 10,
      sexual_person == "Some other non-relative" ~ 11,
      sexual_person == "Don't know" ~ 77,
      sexual_person == "Refused" ~ 99
    ),
    sexual_person_13cat_f = factor(
      sexual_person,
      levels = levels_person_v2
    )
  )
```

### Fears, wants, needs variables

#### Recode categorical variables to factor variables

```{r}
self_rep <- self_rep %>%
  mutate(
    across(
      .cols = starts_with("fear") & !ends_with("response"),
      .fns = ~ case_when(
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_2cat"
    ),
    across(
      .cols = starts_with("fear") & !ends_with("response") &
        !ends_with("2cat"),
      .fns = ~ factor(.x, levels = c("Don't know", "Refused")),
      .names = "{col}_2cat_f"
    )
  )
```

### Environment Variables

#### Recode categorical variables to factor variables

```{r}
self_rep <- self_rep %>%
  mutate(
    report_private_5cat = case_when(
      report_private == "Yes, for the entire time" ~ 1,
      report_private == "Yes, for part of the time" ~ 2,
      report_private == "No, but they were still close enough to hear" ~ 3,
      report_private == "No" ~ 4,
      report_private == "Don't know" ~ 7
    ),
    report_private_5cat_f = factor(
      report_private,
      levels = c(
        "Yes, for the entire time", "Yes, for part of the time",
        "No, but they were still close enough to hear", "No",
        "Don't know"
      )
    ),
    report_influence_4cat = case_when(
      report_influence == "Yes" ~ 1,
      report_influence == "No" ~ 2,
      report_influence == "Don't know" ~ 7,
      report_influence == "Refused" ~ 9
    ),
    report_influence_4cat_f = factor(
      report_influence,
      levels = levels_yes_no
    )
  )
```

## Remove raw character variables that have recoded forms

```{r}
self_rep <- self_rep %>% select(
  -c(
    (starts_with("emotional") & (!matches("[0-9]cat") & !matches("_age") & !matches("_times_times"))),
    (starts_with("fear") & (!matches("[0-9]cat") & !matches("_response$"))),
    (starts_with("finance") & (!matches("[0-9]cat") & !matches("_age") & !matches("_times_times"))),
    (starts_with("neglect") & (!matches("[0-9]cat") & !matches("_age") & !matches("_times_times"))),
    (starts_with("physical") & (!matches("[0-9]cat") & !matches("_age") & !matches("_times_times"))),
    (starts_with("report") & !matches("[0-9]cat")),
    (starts_with("sexual") & (!matches("[0-9]cat") & !matches("_age") & !matches("_times_times")))
  )
)
```

```{r}
# Data check
dim(self_rep) # 955 351
```


# Save as rds file

```{r}
self_rep_path <- here::here("data", "cleaned_rds_files", "self_report_import.rds")
```

```{r}
write_rds(self_rep, self_rep_path)
```


# Clean up

```{r}
rm(list = ls())
```
