---
title: "Import Data from FileMaker Pro: Clutter Rating Scale"
---

# Overview

In this file, we import and do some initial cleaning of the Clutter Rating Scale data collected and stored in FileMaker Pro.


# Load packages

```{r}
library(dplyr, warn.conflicts = FALSE)
library(readr)
library(janitor)
```


# Load data

Load the data table into the global environment as a data frame using the raw csv file. See this Wiki page for more information about the location of the data: https://github.com/brad-cannell/detect_fu_interviews_public/wiki/Using-this-repository. 

```{r}
clutter_scale <- read_csv("../data/filemaker_pro_exports/clutter_scale_import.csv")
```

```{r}
# Data check
dim(clutter_scale) # 893  23
```


# Data cleaning

We will create categorical variables with numerical values that match the codebook and also create a factor variable for each categorical variable in the data frame to be used for analysis.

## Convert all variable names to snake case

```{r}
clutter_scale <- clean_names(clutter_scale)
```

## Create recoded variables and factor variables to match levels in follow-up interview protocol

```{r}
# Create recoded variable for look_living
clutter_scale <- clutter_scale %>%
  mutate(
    look_living_3cat = case_when(
      look_living == "No" ~ 0,
      look_living == "Yes" ~ 1,
      look_living == "No living room" ~ 7
    ),
    # Create factor variable for look_living
    look_living_3cat_f = factor(
      look_living,
      levels = c("No", "Yes", "No living room")
    )
  )
```

```{r}
# Create factor variable for clutter_living
clutter_scale <- clutter_scale %>%
  mutate(
    clutter_living_f = factor(
      clutter_living
    ),
    # Create recoded variable for clutter_living_photo
    clutter_living_photo_3cat = case_when(
      clutter_living_photo == "No" ~ 0,
      clutter_living_photo == "Yes" ~ 1,
      clutter_living_photo == "No living room" ~ 7
    ),
    # Create factor variable for clutter_living_photo
    clutter_living_photo_3cat_f = factor(
      clutter_living_photo,
      levels = c("No", "Yes", "No living room")
    )
  )
```

```{r}
# Create recoded variable for look_kitchen
clutter_scale <- clutter_scale %>%
  mutate(
    look_kitchen_3cat = case_when(
      look_kitchen == "No" ~ 0,
      look_kitchen == "Yes" ~ 1,
      look_kitchen == "No kitchen" ~ 7
    ),
    # Create factor variable for look_kitchen
    look_kitchen_3cat_f = factor(
      look_kitchen,
      levels = c("No", "Yes", "No kitchen")
    )
  )
```

```{r}
# Create factor variable for clutter_kitchen
clutter_scale <- clutter_scale %>%
  mutate(
    clutter_kitchen_f = factor(
      clutter_kitchen
    ),
    # Create recoded variable for clutter_kitchen_photo
    clutter_kitchen_photo_3cat = case_when(
      clutter_kitchen_photo == "No" ~ 0,
      clutter_kitchen_photo == "Yes" ~ 1,
      clutter_kitchen_photo == "No kitchen" ~ 7
    ),
    # Create factor variable for clutter_kitchen_photo
    clutter_kitchen_photo_3cat_f = factor(
      clutter_kitchen_photo,
      levels = c("No", "Yes", "No living room")
    )
  )
```

```{r}
# Create recoded variable for look_bedroom
clutter_scale <- clutter_scale %>%
  mutate(
    look_bedroom_3cat = case_when(
      look_bedroom == "No" ~ 0,
      look_bedroom == "Yes" ~ 1,
      look_bedroom == "No bedroom" ~ 7
    ),
    # Create factor variable for look_bedroom
    look_bedroom_3cat_f = factor(
      look_bedroom,
      levels = c("No", "Yes", "No bedroom")
    )
  )
```

```{r}
# Create factor variable for clutter_bedroom
clutter_scale <- clutter_scale %>%
  mutate(
    clutter_bedroom_f = factor(
      clutter_bedroom
    ),
    # Create recoded variable for clutter_bedroom_photo
    clutter_bedroom_photo_3cat = case_when(
      clutter_bedroom_photo == "No" ~ 0,
      clutter_bedroom_photo == "Yes" ~ 1,
      clutter_bedroom_photo == "No bedroom" ~ 7
    ),
    # Create factor variable for clutter_bedroom_photo
    clutter_bedroom_photo_3cat_f = factor(
      clutter_bedroom_photo,
      levels = c("No", "Yes", "No bedroom")
    )
  )
```

## Remove raw variables that have recoded forms

```{r}
clutter_scale <- clutter_scale %>%
  select(-c(
    look_living, clutter_living, clutter_living_photo, look_kitchen, clutter_kitchen,
    clutter_kitchen_photo, look_bedroom, clutter_bedroom, clutter_bedroom_photo
  ))
```

```{r}
# Data check
dim(clutter_scale) # 893  29
```


# Save as rds file

```{r}
write_rds(clutter_scale, "../data/cleaned_rds_files/clutter_scale_import.rds")
```
