---
title: "Import Data from FileMaker Pro: Self Report"
---

# Overview

In this file, we import and do some initial cleaning of the EM self-report data collected and stored in FileMaker Pro.

```{r, message= FALSE}
# Load all necessary libraries
library(readr)
library(dplyr, warn.conflicts = FALSE)
library(janitor, warn.conflicts = FALSE)
```


# Load data

Load the data table into the global environment as a data frame using the raw csv file. See this Wiki page for more information about the location of the data: https://github.com/brad-cannell/detect_fu_interviews_public/wiki. 

```{r}
self_rep_path <- here::here("data", "filemaker_pro_exports", "self_report_import.csv")
```

```{r}
self_rep <- read_csv(self_rep_path)
```

```{r}
# Data check
dim(self_rep) # 956 209
```


# Data cleaning

Here we will convert all variable names to snake case so that everything is uniform.

```{r}
self_rep <- clean_names(self_rep,
  replace = c(
    "60" = "_60",
    "65" = "_65"
  )
)
```

## Filter rows

There is one row that is missing a MedStar ID and almost all other variables. My best guess is that this was a record Sunil was experimenting with. We will drop the row.

```{r}
self_rep <- self_rep |> 
  filter(!is.na(medstar_id))
```

```{r}
# Data check
dim(self_rep) # 955 209
```

## Create factor variables to match levels in follow-up interview protocol

### Self-report injury, violence, neglect, and exploitation

```{r}
# Set levels for factors for different types of questions
levels_yes_no <- c("Yes", "No", "Don't know", "Refused")

levels_help <- c(
  "Yes, one person", "Yes, more than one person", "No",
  "Don't know", "Refused"
)

levels_reliable <- c(
  "Not at all reliable", "Somewhat reliable",
  "Very reliable", "Completely reliable", "Don’t know",
  "Refused"
)

levels_person <- c(
  "A spouse or partner", "An ex spouse or partner",
  "A parent or step-parent", "A brother or sister",
  "A son or daughter", "Another relative", "A coworker",
  "A neighbor", "A friend", "Some other non-relative",
  "Don't know", "Refused"
)
```

### Neglect variables

# 🔴 Experimental code below ---

- I want to use explicit column names with across(). It makes the code easier to reason about.
- I want to create a function that will take a column as an input, create a factor version that uses the "_f" naming convention, groups the new columns next to each other in the data, then deletes the character version of the column. I think I created something like this for L2C.

```{r}
# I'm just using this code to help me figure out the name of the columns that the original code was manipulating. Again, all these tidyselectors make it difficult to figure out which columns we are mutating.
#  This code chunk should be deleted after we get rid of the tidyselectors in the mutate code.
self_rep |> 
  select(
    starts_with("neglect") & !ends_with("help") & !ends_with("reliable") & !ends_with("person")
  ) |> 
  names() |> 
  cat(sep = ', ')
```

Columns with Yes/No levels

```{r}
# For testing
# Eventually move this to an R script.
mtcars_test <- mtcars |> 
  # Create character variables, because that's what we are working with in the
  # DETECT data.
  mutate(
    # Two dichotomous variables so we can test the function inside of across()
    vs = if_else(vs == 0, "No", "Yes"),
    am = if_else(am == 0, "No", "Yes"),
    # One variable with more than 2 levels
    cyl = case_when(
      cyl == 4 ~ "Four",
      cyl == 6 ~ "Six",
      cyl == 8 ~ "Eight"
    )
  )
```

Break this up into multiple functions

```{r}
char_to_num <- function(.data, .col, .recode) {
  # Extract names from the named list
  char_vals = names(.recode)
  # Recode character values to numeric values
  for (i in seq_along(char_vals)) {
    .data[[.col]][.data[[.col]] == char_vals[i]] <- .recode[i]
  }
  # Return data
  .data
}

# I want this to work on one variable at a time. We will work on multiple
# variables with across.
char_to_num(mtcars_test, "vs", c("No" = 0, "Yes" = 1))
```

```{r}
recode_factor_relocate <- function(.data, .col, .recode) {
  # Create character version of column name
  col_nm <- rlang::enquo(.col) |> rlang::as_name()
  # Recode character values to numeric values 
  df_num <- .data |> 
    char_to_num(col_nm, .recode)
  # Return data frame
  df_num
  
  # This works. now I need to create a factor version and then relocate the column.
}

# I want this to work on one variable at a time. We will work on multiple
# variables with across.
recode_factor_relocate(mtcars_test, "vs", c("No" = 0, "Yes" = 1))
```



```{r}
# self_rep <- 
self_rep %>%
  mutate(
    across(
      .cols = c(
        neglect_go, neglect_food, neglect_house, neglect_clean, neglect_ready, 
        neglect_bills
      ),
      .fns = ~ case_when(
        .x == "Yes" ~ 1,
        .x == "No" ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = c(
        neglect_go, neglect_food, neglect_house, neglect_clean, neglect_ready, 
        neglect_bills
      ),
      .fn = ~ factor(.x, levels = levels_yes_no),
      .names = "{col}_4cat_f"
    )
  ) |> 
  select(starts_with("neglect_go"))
```

# 🔴 Experimental code above ---

```{r}
self_rep <- self_rep %>%
  mutate(
    across(
      .cols = ,
      .fns = ~ case_when(
        .x == "Yes" ~ 1,
        .x == "No" ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("neglect") & !ends_with("help") &
        !ends_with("reliable") & !ends_with("person") & !ends_with("4cat"),
      .fn = ~ factor(.x, levels = levels_yes_no),
      .names = "{col}_4cat_f"
    ),
    across(
      .cols = starts_with("neglect") & ends_with("help"),
      .fns = ~ case_when(
        .x == "Yes, one person" ~ 1,
        .x == "Yes, more than one person" ~ 2,
        .x == "No" ~ 3,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_5cat"
    ),
    across(
      .cols  = starts_with("neglect") & ends_with("help"),
      .fns   = ~ factor(.x, levels = levels_help),
      .names = "{col}_5cat_f"
    ),
    across(
      .cols = starts_with("neglect") & ends_with("reliable"),
      .fns = ~ case_when(
        .x == "Not at all reliable" ~ 1,
        .x == "Somewhat reliable" ~ 2,
        .x == "Very reliable" ~ 3,
        .x == "Completely reliable" ~ 4,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_6cat"
    ),
    across(
      .cols  = starts_with("neglect") & ends_with("reliable"),
      .fns   = ~ factor(.x, levels = levels_reliable),
      .names = "{col}_6cat_f"
    ),
    neglect_person_12cat = case_when(
      neglect_person == "A spouse or partner" ~ 1,
      neglect_person == "An ex spouse or partner" ~ 2,
      neglect_person == "A parent or step-parent" ~ 3,
      neglect_person == "A brother or sister" ~ 4,
      neglect_person == "A son or daughter" ~ 5,
      neglect_person == "Another relative" ~ 6,
      neglect_person == "A coworker" ~ 7,
      neglect_person == "A neighbor" ~ 8,
      neglect_person == "A friend" ~ 9,
      neglect_person == "Some other non-relative" ~ 10,
      neglect_person == "Don't know" ~ 77,
      neglect_person == "Refused" ~ 99
    ),
    neglect_person_12cat_f = factor(
      neglect_person,
      levels = levels_person
    )
  )
```
  
### Financial Exploitation Variables

#### Set levels for factors used in these variables

```{r}
# Not needed, this variable is not used in this CSV
levels_last_time <- c(
  "Less than 1 month ago",
  "Between 1 month and less than 3 months ago",
  "Between 3 months and less than 6 months ago",
  "Between 6 months and less than 1 year ago",
  "Between 1 year and less than 3 years ago",
  "3 or more years ago", "Don't know", "Refused"
)
```

#### Recode categorical variables to factor variables

```{r}
self_rep <- self_rep %>%
  mutate(
    across(
      .cols = starts_with("finance") & !ends_with("years") &
        !ends_with("times") & !ends_with("age") & !ends_with("person") &
        !ends_with("last_time"),
      .fns = ~ case_when(
        .x == "Yes" ~ 1,
        .x == "No" ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("finance") & !ends_with("years") &
        !ends_with("times") & !ends_with("age") & !ends_with("person") &
        !ends_with("last_time") & !ends_with("4cat"),
      .fns = ~ factor(.x, levels = levels_yes_no),
      .names = "{col}_4cat_f"
    ),
    finance_person_12cat = case_when(
      finance_person == "A spouse or partner" ~ 1,
      finance_person == "An ex spouse or partner" ~ 2,
      finance_person == "A parent or step-parent" ~ 3,
      finance_person == "A brother or sister" ~ 4,
      finance_person == "A son or daughter" ~ 5,
      finance_person == "Another relative" ~ 6,
      finance_person == "A coworker" ~ 7,
      finance_person == "A neighbor" ~ 8,
      finance_person == "A friend" ~ 9,
      finance_person == "Some other non-relative" ~ 10,
      finance_person == "Don't know" ~ 77,
      finance_person == "Refused" ~ 99
    ),
    finance_person_12cat_f = factor(
      finance_person,
      levels = levels_person
    ),
    across(
      .cols = starts_with("finance") & ends_with("last_time"),
      .fns = ~ case_when(
        .x == "Less than 1 month ago" ~ 1,
        .x == "Between 1 month and less than 3 months ago" ~ 2,
        .x == "Between 3 months and less than 6 months ago" ~ 3,
        .x == "Between 6 months and less than 1 year ago" ~ 4,
        .x == "Between 1 year and less than 3 years ago" ~ 5,
        .x == "3 or more years ago" ~ 6,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_8cat"
    ),
    across(
      .cols  = starts_with("finance") & ends_with("last_time"),
      .fns   = ~ factor(.x, levels = levels_last_time),
      .names =  "{col}_8cat_f"
    )
  )
```

### Emotional Mistreatment Variables

#### Set levels to be used with these variables

```{r}
levels_times <- c(
  "1 or 2 times", "Between 3 and less than 5 times",
  "Between 5 and less than 10 times",
  "Between 10 and less than 20 times", "20 or more times",
  "Don't know", "Refused"
)

levels_friends <- c(
  "None", "Very few (1-3)", "Some (4-6)", "A lot (7+)",
  "Don't know", "Refused"
)

levels_person_v2 <- c(
  "A stranger", "A spouse or partner", "An ex spouse or partner",
  "A parent or step-parent", "A brother or sister",
  "A son or daughter", "Another relative", "A coworker",
  "A neighbor", "A friend", "Some other non-relative",
  "Don't know", "Refused"
)
```

#### Recode categorical variables to factor variables

```{r}
self_rep <- self_rep %>%
  mutate(
    across(
      .cols = starts_with("emotional") & !ends_with("years") &
        !ends_with("times") & !ends_with("age") & !ends_with("person") &
        !ends_with("last_time") & !ends_with("friends") &
        !ends_with("person_v2"),
      .fns = ~ case_when(
        .x == "Yes" ~ 1,
        .x == "No" ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("emotional") & !ends_with("years") &
        !ends_with("times") & !ends_with("age") & !ends_with("person") &
        !ends_with("last_time") & !ends_with("friends") & !ends_with("4cat") &
        !ends_with("person_v2"),
      .fns = ~ factor(.x, levels = levels_yes_no),
      .names = "{col}_4cat_f"
    ),
    emotional_incident_person_12cat = case_when(
      emotional_incident_person == "A stranger" ~ 1,
      emotional_incident_person == "A spouse or partner" ~ 2,
      emotional_incident_person == "An ex spouse or partner" ~ 3,
      emotional_incident_person == "A parent or step-parent" ~ 4,
      emotional_incident_person == "A brother or sister" ~ 5,
      emotional_incident_person == "A son or daughter" ~ 6,
      emotional_incident_person == "Another relative" ~ 7,
      emotional_incident_person == "A coworker" ~ 8,
      emotional_incident_person == "A neighbor" ~ 9,
      emotional_incident_person == "A friend" ~ 10,
      emotional_incident_person == "Some other non-relative" ~ 11,
      emotional_incident_person == "Don't know" ~ 77,
      emotional_incident_person == "Refused" ~ 99
    ),
    emotional_incident_person_12cat_f = factor(
      emotional_incident_person,
      levels = levels_person_v2
    ),
    across(
      .cols = starts_with("emotional") & ends_with("last_time"),
      .fns = ~ case_when(
        .x == "Less than 1 month ago" ~ 1,
        .x == "Between 1 month and less than 3 months ago" ~ 2,
        .x == "Between 3 months and less than 6 months ago" ~ 3,
        .x == "Between 6 months and less than 1 year ago" ~ 4,
        .x == "Between 1 year and less than 3 years ago" ~ 5,
        .x == "3 or more years ago" ~ 6,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_8cat"
    ),
    across(
      .cols  = starts_with("emotional") & ends_with("last_time"),
      .fns   = ~ factor(.x, levels = levels_last_time),
      .names =  "{col}_8cat_f"
    ),
    across(
      .cols = starts_with("emotional") & ends_with("times") &
        !ends_with("times_times"),
      .fns = ~ case_when(
        .x == "1 or 2 times" ~ 1,
        .x == "Between 3 and less than 5 times" ~ 2,
        .x == "Between 5 and less than 10 times" ~ 3,
        .x == "Between 10 and less than 20 times" ~ 4,
        .x == "20 or more times" ~ 5,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_7cat"
    ),
    across(
      .cols = starts_with("emotional") & ends_with("times") &
        !ends_with("times_times"),
      .fns = ~ factor(.x, levels = levels_times),
      .names = "{col}_7cat_f"
    ),
    emotional_person_friends_6cat = case_when(
      emotional_person_friends == "None" ~ 0,
      emotional_person_friends == "Very few (1-3)" ~ 1,
      emotional_person_friends == "Some (4-6)" ~ 2,
      emotional_person_friends == "A lot (7+)" ~ 3,
      emotional_person_friends == "Don't know" ~ 7,
      emotional_person_friends == "Refused" ~ 9
    ),
    emotional_person_friends_6cat_f = factor(
      emotional_person_friends,
      levels = levels_friends
    ),
    # Are the levels the same for v2 and v1?
    emotional_incident_person_v2_12cat = case_when(
      emotional_incident_person_v2 == "A stranger" ~ 1,
      emotional_incident_person_v2 == "A spouse or partner" ~ 2,
      emotional_incident_person_v2 == "An ex spouse or partner" ~ 3,
      emotional_incident_person_v2 == "A parent or step-parent" ~ 4,
      emotional_incident_person_v2 == "A brother or sister" ~ 5,
      emotional_incident_person_v2 == "A son or daughter" ~ 6,
      emotional_incident_person_v2 == "Another relative" ~ 7,
      emotional_incident_person_v2 == "A coworker" ~ 8,
      emotional_incident_person_v2 == "A neighbor" ~ 9,
      emotional_incident_person_v2 == "A friend" ~ 10,
      emotional_incident_person_v2 == "Some other non-relative" ~ 11,
      emotional_incident_person_v2 == "Don't know" ~ 77,
      emotional_incident_person_v2 == "Refused" ~ 99
    ),
    emotional_incident_person_v2_12cat_f = factor(
      emotional_incident_person_v2,
      levels = levels_person_v2
    ),
  )
```
 
### Physical Mistreatment Variables

#### Recode categorical variables to factor variables

```{r}
self_rep <- self_rep %>%
  mutate(
    across(
      .cols = starts_with("physical") & !ends_with("years") &
        !ends_with("times") & !ends_with("age") &
        !ends_with("last_time") & !ends_with("friends") &
        !ends_with("person_v2"),
      .fns = ~ case_when(
        .x == "Yes" ~ 1,
        .x == "No" ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("physical") & !ends_with("years") &
        !ends_with("times") & !ends_with("age") &
        !ends_with("last_time") & !ends_with("friends") & !ends_with("4cat") &
        !ends_with("person_v2"),
      .fns = ~ factor(.x, levels = levels_yes_no),
      .names = "{col}_4cat_f"
    ),
    across(
      .cols = starts_with("physical") & ends_with("last_time"),
      .fns = ~ case_when(
        .x == "Less than 1 month ago" ~ 1,
        .x == "Between 1 month and less than 3 months ago" ~ 2,
        .x == "Between 3 months and less than 6 months ago" ~ 3,
        .x == "Between 6 months and less than 1 year ago" ~ 4,
        .x == "Between 1 year and less than 3 years ago" ~ 5,
        .x == "3 or more years ago" ~ 6,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_8cat"
    ),
    across(
      .cols  = starts_with("physical") & ends_with("last_time"),
      .fns   = ~ factor(.x, levels = levels_last_time),
      .names =  "{col}_8cat_f"
    ),
    across(
      .cols = starts_with("physical") & ends_with("times") &
        !ends_with("times_times"),
      .fns = ~ case_when(
        .x == "1 or 2 times" ~ 1,
        .x == "Between 3 and less than 5 times" ~ 2,
        .x == "Between 5 and less than 10 times" ~ 3,
        .x == "Between 10 and less than 20 times" ~ 4,
        .x == "20 or more times" ~ 5,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_7cat"
    ),
    across(
      .cols = starts_with("physical") & ends_with("times") &
        !ends_with("times_times"),
      .fns = ~ factor(.x, levels = levels_times),
      .names = "{col}_7cat_f"
    ),
    physical_person_friends_6cat = case_when(
      physical_person_friends == "None" ~ 0,
      physical_person_friends == "Very few (1-3)" ~ 1,
      physical_person_friends == "Some (4-6)" ~ 2,
      physical_person_friends == "A lot (7+)" ~ 3,
      physical_person_friends == "Don't know" ~ 7,
      physical_person_friends == "Refused" ~ 9
    ),
    physical_person_friends_6cat_f = factor(
      physical_person_friends,
      levels = levels_friends
    ),
    physical_incident_person_v2_12cat = case_when(
      physical_incident_person_v2 == "A stranger" ~ 1,
      physical_incident_person_v2 == "A spouse or partner" ~ 2,
      physical_incident_person_v2 == "An ex spouse or partner" ~ 3,
      physical_incident_person_v2 == "A parent or step-parent" ~ 4,
      physical_incident_person_v2 == "A brother or sister" ~ 5,
      physical_incident_person_v2 == "A son or daughter" ~ 6,
      physical_incident_person_v2 == "Another relative" ~ 7,
      physical_incident_person_v2 == "A coworker" ~ 8,
      physical_incident_person_v2 == "A neighbor" ~ 9,
      physical_incident_person_v2 == "A friend" ~ 10,
      physical_incident_person_v2 == "Some other non-relative" ~ 11,
      physical_incident_person_v2 == "Don't know" ~ 77,
      physical_incident_person_v2 == "Refused" ~ 99
    ),
    physical_incident_person_v2_12cat_f = factor(
      physical_incident_person_v2,
      levels = levels_person_v2
    ),
    physical_person_12cat = case_when(
      physical_person == "A stranger" ~ 1,
      physical_person == "A spouse or partner" ~ 2,
      physical_person == "An ex spouse or partner" ~ 3,
      physical_person == "A parent or step-parent" ~ 4,
      physical_person == "A brother or sister" ~ 5,
      physical_person == "A son or daughter" ~ 6,
      physical_person == "Another relative" ~ 7,
      physical_person == "A coworker" ~ 8,
      physical_person == "A neighbor" ~ 9,
      physical_person == "A friend" ~ 10,
      physical_person == "Some other non-relative" ~ 11,
      physical_person == "Don't know" ~ 77,
      physical_person == "Refused" ~ 99
    ),
    physical_person_12cat_f = factor(
      physical_person,
      levels = levels_person_v2
    )
  )
```

### Sexual mistreatment variables

#### Recode categorical variables to factor variables

```{r}
self_rep <- self_rep %>%
  mutate(
    across(
      .cols = starts_with("sexual") & !ends_with("years") &
        !ends_with("times") & !ends_with("age") &
        !ends_with("last_time") & !ends_with("friends") &
        !ends_with("person_v2") & !ends_with("sexual_person"),
      .fns = ~ case_when(
        .x == "Yes" ~ 1,
        .x == "No" ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("sexual") & !ends_with("years") &
        !ends_with("times") & !ends_with("age") &
        !ends_with("last_time") & !ends_with("friends") & !ends_with("4cat") &
        !ends_with("person_v2") & !ends_with("sexual_person"),
      .fns = ~ factor(.x, levels = levels_yes_no),
      .names = "{col}_4cat_f"
    ),
    across(
      .cols = starts_with("sexual") & ends_with("last_time"),
      .fns = ~ case_when(
        .x == "Less than 1 month ago" ~ 1,
        .x == "Between 1 month and less than 3 months ago" ~ 2,
        .x == "Between 3 months and less than 6 months ago" ~ 3,
        .x == "Between 6 months and less than 1 year ago" ~ 4,
        .x == "Between 1 year and less than 3 years ago" ~ 5,
        .x == "3 or more years ago" ~ 6,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_8cat"
    ),
    across(
      .cols  = starts_with("sexual") & ends_with("last_time"),
      .fns   = ~ factor(.x, levels = levels_last_time),
      .names =  "{col}_8cat_f"
    ),
    across(
      .cols = starts_with("sexual") & ends_with("times") &
        !ends_with("times_times"),
      .fns = ~ case_when(
        .x == "1 or 2 times" ~ 1,
        .x == "Between 3 and less than 5 times" ~ 2,
        .x == "Between 5 and less than 10 times" ~ 3,
        .x == "Between 10 and less than 20 times" ~ 4,
        .x == "20 or more times" ~ 5,
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_7cat"
    ),
    across(
      .cols = starts_with("sexual") & ends_with("times") &
        !ends_with("times_times"),
      .fns = ~ factor(.x, levels = levels_times),
      .names = "{col}_7cat_f"
    ),
    sexual_person_friends_6cat = case_when(
      sexual_person_friends == "None" ~ 0,
      sexual_person_friends == "Very few (1-3)" ~ 1,
      sexual_person_friends == "Some (4-6)" ~ 2,
      sexual_person_friends == "A lot (7+)" ~ 3,
      sexual_person_friends == "Don't know" ~ 7,
      sexual_person_friends == "Refused" ~ 9
    ),
    sexual_person_friends_6cat_f = factor(
      sexual_person_friends,
      levels = levels_friends
    ),
    sexual_incident_person_v2_12cat = case_when(
      sexual_incident_person_v2 == "A stranger" ~ 1,
      sexual_incident_person_v2 == "A spouse or partner" ~ 2,
      sexual_incident_person_v2 == "An ex spouse or partner" ~ 3,
      sexual_incident_person_v2 == "A parent or step-parent" ~ 4,
      sexual_incident_person_v2 == "A brother or sister" ~ 5,
      sexual_incident_person_v2 == "A son or daughter" ~ 6,
      sexual_incident_person_v2 == "Another relative" ~ 7,
      sexual_incident_person_v2 == "A coworker" ~ 8,
      sexual_incident_person_v2 == "A neighbor" ~ 9,
      sexual_incident_person_v2 == "A friend" ~ 10,
      sexual_incident_person_v2 == "Some other non-relative" ~ 11,
      sexual_incident_person_v2 == "Don't know" ~ 77,
      sexual_incident_person_v2 == "Refused" ~ 99
    ),
    sexual_incident_person_v2_12cat_f = factor(
      sexual_incident_person_v2,
      levels = levels_person_v2
    ),
    sexual_person_13cat = case_when(
      sexual_person == "A stranger" ~ 1,
      sexual_person == "A spouse or partner" ~ 2,
      sexual_person == "An ex spouse or partner" ~ 3,
      sexual_person == "A parent or step-parent" ~ 4,
      sexual_person == "A brother or sister" ~ 5,
      sexual_person == "A son or daughter" ~ 6,
      sexual_person == "Another relative" ~ 7,
      sexual_person == "A coworker" ~ 8,
      sexual_person == "A neighbor" ~ 9,
      sexual_person == "A friend" ~ 10,
      sexual_person == "Some other non-relative" ~ 11,
      sexual_person == "Don't know" ~ 77,
      sexual_person == "Refused" ~ 99
    ),
    sexual_person_13cat_f = factor(
      sexual_person,
      levels = levels_person_v2
    )
  )
```

### Fears, wants, needs variables

#### Recode categorical variables to factor variables

```{r}
self_rep <- self_rep %>%
  mutate(
    across(
      .cols = starts_with("fear") & !ends_with("response"),
      .fns = ~ case_when(
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_2cat"
    ),
    across(
      .cols = starts_with("fear") & !ends_with("response") &
        !ends_with("2cat"),
      .fns = ~ factor(.x, levels = c("Don't know", "Refused")),
      .names = "{col}_2cat_f"
    )
  )
```

### Environment Variables

#### Recode categorical variables to factor variables

```{r}
self_rep <- self_rep %>%
  mutate(
    report_private_5cat = case_when(
      report_private == "Yes, for the entire time" ~ 1,
      report_private == "Yes, for part of the time" ~ 2,
      report_private == "No, but they were still close enough to hear" ~ 3,
      report_private == "No" ~ 4,
      report_private == "Don't know" ~ 7
    ),
    report_private_5cat_f = factor(
      report_private,
      levels = c(
        "Yes, for the entire time", "Yes, for part of the time",
        "No, but they were still close enough to hear", "No",
        "Don't know"
      )
    ),
    report_influence_4cat = case_when(
      report_influence == "Yes" ~ 1,
      report_influence == "No" ~ 2,
      report_influence == "Don't know" ~ 7,
      report_influence == "Refused" ~ 9
    ),
    report_influence_4cat_f = factor(
      report_influence,
      levels = levels_yes_no
    )
  )
```

## Remove raw character variables that have recoded forms

```{r}
self_rep <- self_rep %>% select(
  -c(
    (starts_with("emotional") & (!matches("[0-9]cat") & !matches("_age") & !matches("_times_times"))),
    (starts_with("fear") & (!matches("[0-9]cat") & !matches("_response$"))),
    (starts_with("finance") & (!matches("[0-9]cat") & !matches("_age") & !matches("_times_times") & !matches("_stranger_forged_times"))),
    (starts_with("neglect") & (!matches("[0-9]cat") & !matches("_age") & !matches("_times_times"))),
    (starts_with("physical") & (!matches("[0-9]cat") & !matches("_age") & !matches("_times_times"))),
    (starts_with("report") & !matches("[0-9]cat")),
    (starts_with("sexual") & (!matches("[0-9]cat") & !matches("_age") & !matches("_times_times")))
  )
)
```

```{r}
# Data check
dim(self_rep) # 955 351
```


# Save as rds file

```{r}
self_rep_path <- here::here("data", "cleaned_rds_files", "self_report_import.rds")
```

```{r}
write_rds(self_rep, self_rep_path)
```


# Clean up

```{r}
rm(list = ls())
```
