---
title: "Import Data from FileMaker Pro: Sociodemographic Information"
---

```{r, message= FALSE}
library(dplyr)
library(readr)
library(purrr)
library(stringr)
library(expss)
library(janitor)
```

# Load the data

Load the data table into the global environment as a data frame using the raw csv file. We will create categorical variables with numerical values that match the codebook and also create a factor variable for each categorical variable in the data frame to be used for analysis.

```{r}
sociodemographic_information <- read_csv("../data/filemaker_pro_exports/sociodemographic_information_import.csv")
``` 

# Clean the data

Here we will convert all variable names to snake case so that everything is uniform.

```{r}
# Convert all variable names to snake case

sociodemographic_information <- clean_names(sociodemographic_information)
```

```{r}
# Data check
dim(sociodemographic_information) # 963  28
```

## Remove rows

For MedStar IDs ...92912, ...83082, ...281fa, ...9b0f2, ...3a6e2, and ...4419d, no consent was given. There was no follow-up interview scheduled. There aren't any values in FM Pro. We will delete these records. For more details, see `check_consenting_participants.qmd`.

```{r}
sociodemographic_information <- sociodemographic_information |>
  filter(!stringr::str_detect(medstar_id, "92912")) |>
  filter(!stringr::str_detect(medstar_id, "83082")) |>
  filter(!stringr::str_detect(medstar_id, "281fa")) |>
  filter(!stringr::str_detect(medstar_id, "9b0f2")) |>
  filter(!stringr::str_detect(medstar_id, "3a6e2")) |>
  filter(!stringr::str_detect(medstar_id, "4419d"))
```

```{r}
# Data check
dim(sociodemographic_information) # 957  28
```

## Coerce categorical variables to factor variables

### Sociodemographic Information

#### Create factor variables for all categorical variables.

```{r}
soc_dem <- sociodemographic_information %>%
  mutate(
    sode_marital_8cat = case_when(
      sode_marital == "Married" ~ 1,
      sode_marital == "Living as an unmarried or common law couple" ~ 2,
      sode_marital == "Separated" ~ 3,
      sode_marital == "Divorced" ~ 4,
      sode_marital == "Widowed" ~ 5,
      sode_marital == "Single, or never married" ~ 6,
      sode_marital == "Don't know" ~ 7,
      sode_marital == "Refused" ~ 9
    ),
    sode_marital_8cat_f = factor(
      sode_marital,
      levels = c(
        "Married", "Living as an unmarried or common law couple",
        "Separated", "Divorced", "Widowed", "Single, or never married",
        "Don’t know", "Refused"
      )
    )
  )

soc_dem <- soc_dem %>%
  mutate(
    sogi_identity_5cat = case_when(
      sogi_identity == "Male" ~ 1,
      sogi_identity == "Female" ~ 2,
      sogi_identity == "Other" ~ 3,
      sogi_identity == "Don't Know" ~ 7,
      sogi_identity == "Refused" ~ 9
    ),
    sogi_identity_5cat_f = factor(
      sogi_identity,
      levels = c("Male", "Female", "Other", "Don't know", "Refused")
    )
  )


soc_dem <- soc_dem %>%
  mutate(
    sogi_orientation_8cat = case_when(
      sogi_orientation == "Straight/heterosexual" ~ 1,
      sogi_orientation == "Gay man" ~ 2,
      sogi_orientation == "Lesbian/gay woman" ~ 3,
      sogi_orientation == "Bisexual" ~ 4,
      sogi_orientation == "Queer" ~ 5,
      sogi_orientation == "Don't know" ~ 7,
      sogi_orientation == "Refused" ~ 9
    ),
    sogi_orientation_8cat_f = factor(
      sogi_orientation,
      levels = c(
        "Straight/heterosexual", "Gay man", "Lesbian/gay woman",
        "Bisexual", "Queer", "Other", "Don't know", "Refused"
      )
    )
  )


soc_dem <- soc_dem %>%
  mutate(
    sode_age_4cat = case_when(
      sode_age == "Age 65 to 100+" ~ 1,
      sode_age == "Don't know" ~ 7,
      sode_age == "Refused" ~ 9
    ),
    sode_age_4cat_f = factor(
      sode_age,
      levels = c("Age 65 to 100+", "Don't know", "Refused")
    )
  )

soc_dem <- soc_dem %>%
  mutate(
    sode_hispanic_4cat = case_when(
      sode_hispanic == "Yes" ~ 1,
      sode_hispanic == "No" ~ 2,
      sode_hispanic == "Don't know" ~ 7,
      sode_hispanic == "Refused" ~ 9
    ),
    sode_hispanic_4cat_f = factor(
      sode_hispanic,
      levels = c("Yes", "No", "Don't know", "Refused")
    )
  )


soc_dem <- soc_dem %>%
  mutate(
    sode_school_9cat = case_when(
      sode_school == "Did not complete high school or GED" ~ 1,
      sode_school == "High school graduate or GED" ~ 2,
      sode_school == "Some college (no degree)" ~ 3,
      sode_school == "Associate's degree" ~ 4,
      sode_school == "Bachelor's degree (BA, AB, BS, etc.)" ~ 5,
      sode_school == "Some graduate or professional school (no degree)" ~ 6,
      sode_school ==
        "Graduate or professional school degree (MS, MA, MD, PhD, etc.)" ~ 7,
      sode_school == "Don't know" ~ 77,
      sode_school == "Refused" ~ 99
    ),
    sode_school_9cat_f = factor(
      sode_school,
      levels = c(
        "Did not complete high school or GED",
        "High school graduate or GED",
        "Some college (no degree)",
        "Associate's degree",
        "Bachelor's degree (BA, AB, BS, etc.)",
        "Some graduate or professional school (no degree)",
        "Graduate or professional school degree (MS, MA, MD, PhD, etc.)",
        "Don't know", "Refused"
      )
    )
  )


soc_dem <- soc_dem %>%
  mutate(
    sode_employed_11cat = case_when(
      sode_employed == "Employed full time" ~ 1,
      sode_employed == "Employed part time" ~ 2,
      sode_employed == "In the military" ~ 3,
      sode_employed == "Unemployed" ~ 4,
      sode_employed == "Retired" ~ 5,
      sode_employed == "A student" ~ 6,
      sode_employed == "A homemaker" ~ 7,
      sode_employed == "Disabled or unable to work" ~ 8,
      sode_employed == "Something else" ~ 9,
      sode_employed == "Don't know" ~ 77,
      sode_employed == "Refused" ~ 99
    ),
    sode_employed_11cat_f = factor(
      sode_employed,
      levels = c(
        "Employed full time", "Employed part time", "In the military",
        "Unemployed", "Retired", "A student", "A homemaker",
        "Disabled or unable to work", "Something else", "Don't know",
        "Refused"
      )
    )
  )

soc_dem <- soc_dem %>%
  mutate(
    sode_income_9cat = case_when(
      sode_income == "$10,000 or less" ~ 1,
      sode_income == "Between $10,001 and $20,000" ~ 2,
      sode_income == "Between $20,001 and $35,000" ~ 3,
      sode_income == "Between $35,001 and $50,000" ~ 4,
      sode_income == "Between $50,001 and $75,000" ~ 5,
      sode_income == "Between $75,001 and $100,000" ~ 6,
      sode_income == "More than $100,000" ~ 7,
      sode_income == "Don't know" ~ 77,
      sode_income == "Refused" ~ 99
    ),
    sode_income_9cat_f = factor(
      sode_income,
      levels = c(
        "$10,000 or less", "Between $10,001 and $20,000",
        "Between $20,001 and $35,000", "Between $35,001 and $50,000",
        "Between $50,001 and $75,000", "Between $75,001 and $100,000",
        "More than $100,000", "Don't know", "Refused"
      )
    )
  )

soc_dem <- soc_dem %>%
  mutate(
    sode_military_4cat = case_when(
      sode_military == "Yes" ~ 1,
      sode_military == "No" ~ 2,
      sode_military == "Don't know" ~ 7,
      sode_military == "Refused" ~ 9
    ),
    sode_military_4cat_f = factor(
      sode_military,
      levels = c("Yes", "No", "Don't know", "Refused")
    )
  )

soc_dem <- soc_dem %>%
  mutate(
    sode_unwanted_4cat = case_when(
      sode_unwanted == "Yes" ~ 1,
      sode_unwanted == "No" ~ 2,
      sode_unwanted == "Don't know" ~ 7,
      sode_unwanted == "Refused" ~ 9
    ),
    sode_unwanted_4cat_f = factor(
      sode_unwanted,
      levels = c("Yes", "No", "Don't know", "Refused")
    )
  )

soc_dem <- soc_dem %>%
  mutate(
    sode_sexual_4cat = case_when(
      sode_sexual == "Yes" ~ 1,
      sode_sexual == "No" ~ 2,
      sode_sexual == "Don't know" ~ 7,
      sode_sexual == "Refused" ~ 9
    ),
    sode_sexual_4cat_f = factor(
      sode_sexual,
      levels = c("Yes", "No", "Don't know", "Refused")
    )
  )

soc_dem <- soc_dem %>%
  mutate(
    hsi_contact_4cat = case_when(
      hsi_contact == "Yes" ~ 1,
      hsi_contact == "No" ~ 2,
      hsi_contact == "Don't know" ~ 7,
      hsi_contact == "Refused" ~ 9
    ),
    hsi_contact_4cat_f = factor(
      hsi_contact,
      levels = c("Yes", "No", "Don't know", "Refused")
    )
  )

soc_dem <- soc_dem %>%
  mutate(
    sode_people_def = case_when(
      grepl("0|1|2|3|4|5|6|7|8|9", sode_people) ~ "Number 1 to 9+",
      sode_people == "Don't know" ~ "Don't know",
      sode_people == "Refused" ~ "Refused",
    ),
    sode_people_3cat = case_when(
      sode_people_def == "Number 1 to 9+" ~ "1-9",
      sode_people_def == "Don't know" ~ "77",
      sode_people_def == "Refused" ~ "99",
    ),
    sode_people_3cat_f = factor(
      sode_people_def,
      levels = c("Number 1 to 9+", "Don't know", "Refused")
    )
  )

soc_dem <- soc_dem %>%
  mutate(
    sode_race_8cat = case_when(
      is.na(sode_race) ~ NA_integer_,
      sode_race == "American Indian or Alaskan Native" ~ 1,
      sode_race == "Asian" ~ 2,
      sode_race == "Black or African American" ~ 3,
      sode_race == "Native Hawaiian or Other Pacific Islander" ~ 4,
      sode_race == "White" ~ 5,
      sode_race == "Don't know" ~ 7,
      sode_race == "Refused" ~ 8,
      TRUE ~ 6 # "Other race or multiple races",
    ),
    sode_race_8cat_f = factor(
      sode_race_8cat,
      levels = c(1, 2, 3, 4, 5, 6, 7, 8),
      labels = c(
        "American Indian or Alaskan Native", "Asian", "Black or African American", "Native Hawaiian or Other Pacific Islander",
        "White", "Other race or multiple races", "Don't know", "Refused"
      )
    ),
    sode_race_eth_6cat = case_when(
      is.na(sode_hispanic_4cat_f) ~ NA_integer_,
      sode_hispanic_4cat_f == "Yes" ~ 1, # "Hispanic, any race"
      sode_race == "Black or African American" ~ 2, # "Black, non-Hispanic"
      sode_race == "White" ~ 3, # "White, non-Hispanic"
      sode_hispanic_4cat_f == "Don't know" ~ 5,
      sode_hispanic_4cat_f == "Refused" ~ 6,
      TRUE ~ 4, # "Other race or multiple races, non-Hispanic"
    ),
    sode_race_eth_6cat_f = factor(
      sode_race_eth_6cat,
      levels = c(1, 2, 3, 4, 5, 6),
      labels = c("Hispanic, any race", "Black, non-Hispanic", "White, non-Hispanic", "Other race or multiple races, non-Hispanic", "Don't know", "Refused")
    )
  )

# Create a numerical continuous variable for sode_people
soc_dem <- soc_dem %>%
  mutate(
    sode_people_cont = case_when(
      sode_people == "Don't know" |
        is.na(sode_people) ~ NA_integer_,
      TRUE ~ as.numeric(sode_people)
    )
  )
```
#### Create dummy variables for the sode_race variable

```{r}
soc_dem <- soc_dem %>%
  mutate(
    american_indian_or_alaska_native          = ifelse(grepl("American Indian or Alaska Native", sode_race), 1, 0),
    asian                                     = ifelse(grepl("Asian", sode_race), 1, 0),
    black_or_african_american                 = ifelse(grepl("Black or African American", sode_race), 1, 0),
    native_hawaiian_or_other_pacific_islander = ifelse(grepl("Native Hawaiian or Other Pacific Islander", sode_race), 1, 0),
    white                                     = ifelse(grepl("White", sode_race), 1, 0),
    other                                     = ifelse(grepl("Other", sode_race), 1, 0)
  )

# Create factor variables and set labels
soc_dem <- soc_dem %>%
  mutate(
    across(
      .cols = american_indian_or_alaska_native:other,
      .fns = ~ factor(
        .x,
        levels = c(0, 1),
        labels = c("No", "Yes")
      ),
      .names = "{col}"
    )
  )
```

### Remove variables that have recoded forms

```{r}
soc_dem <- soc_dem %>%
  select(-c(
    "sode_people_def", "sode_marital", "sode_age", "sode_hispanic", "sode_race", "sode_school", "sode_employed", "sode_income", "sode_military",
    "sode_unwanted", "sode_sexual", "hsi_contact", "sogi_identity", "sogi_orientation"
  ))
```

### Re-order columns

```{r}
soc_dem <- soc_dem %>% relocate(c("american_indian_or_alaska_native":"other", contains("sode_race_")), .after = sode_race_8cat_f)
```

```{r}
# Data check
dim(soc_dem) # 963 52
```

# Save as rds file

```{r}
write_rds(soc_dem, "../data/cleaned_rds_files/sociodemographic_information_import.rds")
```
