---
title: "Import Data from FileMaker Pro: Consent"
---

# Overview

In this file, we import and do some initial cleaning of the consent form data collected and stored in FileMaker Pro.


# Load packages

```{r, message= FALSE}
library(readr)
library(dplyr, warn.conflicts = FALSE)
library(janitor, warn.conflicts = FALSE)
```


# Load the data

Load the data table into the global environment as a data frame using the raw csv file. See this Wiki page for more information about the location of the data: https://github.com/brad-cannell/detect_fu_interviews_public/wiki. 

```{r}
consent_path <- here::here("data", "filemaker_pro_exports", "consent_import.csv")
```

```{r}
consent <- read_csv(consent_path)
```

```{r}
# Data check
dim(consent) # 1013 16
```


# Data cleaning

We will create categorical variables with numerical values that match the codebook and also create a factor variable for each categorical variable in the data frame to be used for analysis.

## Convert all variable names to snake case

```{r}
consent <- clean_names(consent)
```

## Coerce categorical variables to factor variables

```{r}
consent <- consent %>%
  mutate(
    consent_given = case_when(
      x_record_status == "Consent received/Participating" ~ 1,
      TRUE ~ 0
    )
  )
```

```{r}
# Data check
dim(consent) # 1013 17
```


# Save as rds file

```{r}
consent_path <- here::here("data", "cleaned_rds_files", "consent_import.rds")
```

```{r}
write_rds(consent, consent_path)
```


# Clean up

```{r}
rm(list = ls())
```