---
title: "Import Data from FileMaker Pro: Observational Measures"
---

# Overview

In this file, we import and do some initial cleaning of the Observational Measures data collected and stored in FileMaker Pro.

```{r, message= FALSE}
# Load all necessary libraries
library(readr)
library(purrr)
library(stringr)
library(dplyr)
library(janitor)
```


# Load data

Load the data table into the global environment as a data frame using the raw csv file. We will create categorical variables with numerical values that match the codebook and also create a factor variable for each categorical variable in the data frame to be used for analysis.

```{r}
obs_meas <- read_csv("../data/filemaker_pro_exports/observational_measures_import.csv")
```
```{r}
# Data check
dim(obs_meas) # 935 107
```

# Clean data

Here we will convert all variable names to snake case so that everything is uniform.

```{r}
# Convert all variable names to snake case
obs_meas <- clean_names(obs_meas)

```

## Create factor variables to match levels in follow-up interview protocol

### Detection of Elder abuse Through Emergency Care Technicians (DETECT) Screening Item

```{r}
obs_meas <- obs_meas %>%
  mutate(
    across(
      .cols  = c(unusual_odor, disarray_hoarding, health_safety_concern, caregiver_lack_knowledge, caregiver_unengaged, caregiver_frustrated,
                 caregiver_anxious, isolated_home, depressed, poor_personal_hygiene, inadequately_clothed, difficulty_medications, unmet_needs,
                 report_elder_abuse, hoarding_medications),
      .fns   = ~ factor(.x, levels= c("Yes", "No", "No caregiver present", "Unable to assess", "Did not enter patient’s home")),
      .names = "{col}_f"
    )
  )
```

### Elder Assessment Instrument (EAI) / Self-neglect Severity Scale

#### General Assessment
```{r}
# Hygiene to skin integrity
obs_meas <- obs_meas %>%
  mutate(
    across(
      .cols  = c(hygiene, nutrition, skin_integrity),
      .fns   = ~ factor(.x, levels = c("Very good", "Good", "Poor", "Very poor", 
      "Unable to assess")),
      .names = "{col}_f"
    )
  )

```

```{r}
# Clothes
obs_meas <- obs_meas %>%
  mutate(
    clothes_5cat = case_when(
      clothes == "0 - Clean/neat"  ~ 0,
      clothes == "1"               ~ 1,
      clothes == "2"               ~ 2,
      clothes == "3"               ~ 3,
      clothes == "4 - Very soiled" ~ 4
    ),
    clothes_5cat_f = factor(
      clothes,
      levels = c("0 - Clean/neat", 1, 2, 3, "4 - Very soiled")),
# Hair
    hair_5cat = case_when(
      hair == "0 - Clean/combed" ~ 0,
      hair == "1"                ~ 1,
      hair == "2"                ~ 2,
      hair == "3"                ~ 3,
      hair == "4 - Matted/dirty" ~ 4
    ),
    hair_5cat_f = factor(
      hair,
      levels = c("0 - Clean/combed", 1, 2, 3, "4 - Matted/dirty")),
# Nails
    nails_5cat = case_when(
      nails == "0 - Clean/trimmed"        ~ 0,
      nails == "1"                        ~ 1,
      nails == "2"                        ~ 2,
      nails == "3"                        ~ 3,
      nails == "4 - Long/untrimmed/dirty" ~ 4
    ),
    nails_5cat_f = factor(
      nails,
      levels = c("0 - Clean/trimmed", 1, 2, 3, "4 - Long/untrimmed/dirty")),
    )
```


#### Possible Abuse, Neglect, Exploitation and Abandonment Indicators

```{r}
obs_meas <- obs_meas %>%
  mutate(
    across(
      .cols  = c(bruising, fractures, stages_healing, abuse_statement, lacerations, sexual_abuse, contracture, decubitus, dehydration, diarrhea, depression,
                 impaction, malnutrition, urine_burn, poor_hygiene, obvious_disease, inappropriate_medication, repetitive_hosp_admission, neglect_statement,
                 money_misuse, evidence, goods_for_services, inability_account_money, exploitation_statement, caretaker_withdrawn_care, left_alone_unsafe,
                 abandonment_statement),
      .fns   = ~ factor(.x, levels = c("No evidence", "Possible Evidence", "Probable evidence", "Definite evidence", "Unable to assess")),
      .names = "{col}_f"
    )
  )
```

### Environmental Status of Subject
```{r}
# Exterior Condition
obs_meas <- obs_meas %>%
  mutate(
    exterior_condition_5cat = case_when(
      exterior_condition == "0 - Neat/well kept/no trash, debris"       ~ 0,
      exterior_condition == "1"                                         ~ 1,
      exterior_condition == "2"                                         ~ 2,
      exterior_condition == "3"                                         ~ 3,
      exterior_condition == "4 - Poorly maintained/trash, other debris" ~ 4
    ),
    exterior_condition_5cat_f = factor(
      exterior_condition,
      levels = c("0 - Neat/well kept/no trash, debris", 1, 2, 3, 
                 "4 - Poorly maintained/trash, other debris")),
# Yard/ Sidewalk
    yard_sidewalk_5cat = case_when(
      yard_sidewalk == "0 - Neat/well kept/no trash, debris" ~ 0,
      yard_sidewalk == "1"                                   ~ 1,
      yard_sidewalk == "2"                                   ~ 2,
      yard_sidewalk == "3"                                   ~ 3,
      yard_sidewalk == "4 - Poorly maintained/trash, debris" ~ 4
    ),
    yard_sidewalk_5cat_f = factor(
      yard_sidewalk,
      levels = c("0 - Neat/well kept/no trash, debris", 1, 2, 3, 
                 "4 - Poorly maintained/trash, debris")),
# Roof
    roof_5cat = case_when(
      roof == "0 - Intact/no structural damage"          ~ 0,
      roof == "1"                                        ~ 1,
      roof == "2"                                        ~ 2,
      roof == "3"                                        ~ 3,
      roof == "4 - Dilapidated/poorly maintained, holes" ~ 4
    ),
    roof_5cat_f = factor(
      roof,
      levels = c("0 - Intact/no structural damage", 1, 2, 3, 
                 "4 - Dilapidated/poorly maintained, holes")),
# Walls
    walls_5cat = case_when(
      walls == "0 - Intact/no structural damage"          ~ 0,
      walls == "1"                                        ~ 1,
      walls == "2"                                        ~ 2,
      walls == "3"                                        ~ 3,
      walls == "4 - Dilapidated/poorly maintained, holes" ~ 4
    ),
    walls_5cat_f = factor(
      walls,
      levels = c("0 - Intact/no structural damage", 1, 2, 3, 
                 "4 - Dilapidated/poorly maintained, holes")),
# Windows
    windows_5cat = case_when(
      windows == "0 - Intact/not broken or missing"     ~ 0,
      windows == "1"                                    ~ 1,
      windows == "2"                                   ~ 2,
      windows == "3"                                    ~ 3,
      windows == "4 - Multiple sections broken/missing" ~ 4
    ),
    windows_5cat_f = factor(
      windows,
      levels = c("0 - Intact/not broken or missing", 1, 2, 3, 
                 "4 - Multiple sections broken/missing")),
# Interior condition
      interior_condition_5cat = case_when(
      interior_condition == "0 - Intact/not broken or missing"     ~ 0,
      interior_condition == "1"                                    ~ 1,
      interior_condition == "2"                                    ~ 2,
      interior_condition == "3"                                    ~ 3,
      interior_condition == "4 - Multiple sections broken/missing" ~ 4
    ),
    interior_condition_5cat_f = factor(
      interior_condition,
      levels = c("0 - Intact/not broken or missing", 1, 2, 3, 
                 "4 - Multiple sections broken/missing")),
# Odor
      odor_5cat = case_when(
      windows == "0 - Normal household odor"                                              ~ 0,
      windows == "1"                                                                      ~ 1,
      windows == "2"                                                                      ~ 2,
      windows == "3"                                                                      ~ 3,
      windows == "4 - Pungent, unpleasant odor (may be human/animal waste, rotting food)" ~ 4
    ),
    odor_5cat_f = factor(
      odor,
      levels = c("0 - Normal household odor", 1, 2, 3, 
                 "4 - Pungent, unpleasant odor (may be human/animal waste, rotting food)")),
# Cleanliness
## Kitchen
    kitchen_cleanliness_5cat = case_when(
      kitchen_cleanliness == "0 - Clean, no evidence of unsanitary conditions" ~ 0,
      kitchen_cleanliness == "1"                                               ~ 1,
      kitchen_cleanliness == "2"                                               ~ 2,
      kitchen_cleanliness == "3"                                               ~ 3,
      kitchen_cleanliness == "4 - Very dirty, unwashed dishes, trash litter"   ~ 4
    ),
    kitchen_cleanliness_5cat_f = factor(
      kitchen_cleanliness,
      levels = c("0 - Clean, no evidence of unsanitary conditions", 1, 2, 3, 
                 "4 - Very dirty, unwashed dishes, trash litter")),
## Bathroom
    bathroom_cleanliness_5cat = case_when(
      bathroom_cleanliness == "0 - Clean, no evidence of unsanitary conditions"  ~ 0,
      bathroom_cleanliness == "1"                                                ~ 1,
      bathroom_cleanliness == "2"                                                ~ 2,
      bathroom_cleanliness == "3"                                                ~ 3,
      bathroom_cleanliness == "4 - Very dirty, unwashed dishes, trash litter"    ~ 4
    ),
    bathroom_cleanliness_5cat_f = factor(
      bathroom_cleanliness,
      levels = c("0 - Clean, no evidence of unsanitary conditions", 1, 2, 3, 
                 "4 - Very dirty, unwashed dishes, trash litter")),
## Bedroom
    bedroom_cleanliness_5cat = case_when(
      bedroom_cleanliness == "0 - Clean, no evidence of unsanitary conditions" ~ 0,
      bedroom_cleanliness == "1"                                               ~ 1,
      bedroom_cleanliness == "2"                                               ~ 2,
      bedroom_cleanliness == "3"                                               ~ 3,
      bedroom_cleanliness == "4 - Very dirty, unwashed dishes, trash litter"   ~ 4
    ),
    bedroom_cleanliness_5cat_f = factor(
      bedroom_cleanliness,
      levels = c("0 - Clean, no evidence of unsanitary conditions", 1, 2, 3, 
                 "4 - Very dirty, unwashed dishes, trash litter")),
## Living room
    living_room_cleanliness_5cat = case_when(
      living_room_cleanliness == "0 - Clean, no evidence of unsanitary conditions" ~ 0,
      living_room_cleanliness == "1"                                               ~ 1,
      living_room_cleanliness == "2"                                               ~ 2,
      living_room_cleanliness == "3"                                               ~ 3,
      living_room_cleanliness == "4 - Very dirty, unwashed dishes, trash litter"   ~ 4
    ),
    living_room_cleanliness_5cat_f = factor(
      living_room_cleanliness,
      levels = c("0 - Clean, no evidence of unsanitary conditions", 1, 2, 3, 
                 "4 - Very dirty, unwashed dishes, trash litter")),
# Clutter
    clutter_5cat = case_when(
      clutter == "0 - Neat/orderly"                                             ~ 0,
      clutter == "1"                                                            ~ 1,
      clutter == "2"                                                            ~ 2,
      clutter == "3"                                                            ~ 3,
      clutter == "4 - Very cluttered/difficult to move around or find things"   ~ 4
    ),
    clutter_5cat_f = factor(
      clutter,
      levels = c("0 - Neat/orderly", 1, 2, 3, 
                 "4 - Very cluttered/difficult to move around or find things")),
# Structural problems
    structural_problems_5cat = case_when(
      structural_problems == "0 - No structural problems" ~ 0,
      structural_problems == "1"                          ~ 1,
      structural_problems == "2"                          ~ 2,
      structural_problems == "3"                          ~ 3,
      structural_problems == "4 - Severe structural damage (e.g., holes in sheetrock, floor leaking, ceiling"                                         ~ 4
    ),
    structural_problems_5cat_f = factor(
      structural_problems,
      levels = c("0 - No structural problems", 1, 2, 3, 
                 "4 - Severe structural damage (e.g., holes in sheetrock, floor leaking, ceiling")),
# Pets
      pets_5cat = case_when(
      pets == "0 - All animals cared for"    ~ 0,
      pets == "1 or 2 - Uncared animals"     ~ 1,
      pets == "3 or 4 - Uncared animals"     ~ 2,
      pets == "5 or 6 - Uncared animals"     ~ 3,
      pets == "6 or more -  Uncared animals" ~ 4
    ),
    pets_5cat_f = factor(
      pets,
      levels = c("0 - All animals cared for", "1 or 2 - Uncared animals", 
                 "3 or 4 - Uncared animals", "5 or 6 - Uncared animals", 
                 "6 or more - Uncared animals")),
# Utilities
    utilities_5cat = case_when(
      utilities == "0 - All utilities work"             ~ 0,
      utilities == "1 - No phone"                       ~ 1,
      utilities == "2 - No gas/electricity"             ~ 2,
      utilities == "3 - No water"                       ~ 3,
      utilities == "4 - Multiple utilities do not work" ~ 4
    ),
    utilities_5cat_f = factor(
      utilities,
      levels = c("0 - All utilities work", "1 - No phone", "2 - No gas/electricity",
                 "3 - No water", "4 - Multiple utilities do not work"))
    
    
  )


```

### Summary

```{r}
obs_meas <- obs_meas %>%
  mutate(
    across(
      .cols  = ("summary_evidence_abuse": "summary_evidence_abandonment"),
      .fns   = ~ factor(.x, levels = c("No evidence", "Possible Evidence", "Probable evidence", "Definite evidence", "Unable to assess")),
      .names = "{col}_f"
    )
  )
```

### Medic EM Assessment Variables

```{r}
obs_meas <- obs_meas %>%
  mutate(
    across(
      .cols = starts_with("at") & !ends_with("why"),
      .fns  = ~ case_when(
        .x == "Yes"        ~ 1,
        .x == "No"         ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused"    ~ 9
      ),
      .names =  "{col}_4cat"
    ),
    across(
      .cols  = starts_with("at") & !ends_with("why") & !ends_with("cat"),
      .fns   =  ~ factor(.x, levels = c("Yes", "No", "Don't know", "Refused")),
      .names = "{col}_4cat_f" 
    )
    
  )
```

### APS report and C Detect Status

```{r}
obs_meas <- obs_meas %>%
  mutate(
    aps_reported_f = factor(
    aps_reported
    ),
    aps_reported_method_f = factor(
      aps_reported_method
      ),
    c_detect_status_f = factor(
      c_detect_status
    )    
  )
```

## Remove raw variables that have recoded forms and move a column

```{r}
obs_meas<-obs_meas %>% 
  select(
    -c(
      ends_with("_statement"), ends_with("reported"), ends_with("reported_method"), (starts_with("at_") & !(ends_with("why") | contains("_4cat"))),
      (contains("_cleanliness") & !matches("_[0-9]cat")), bruising, c_detect_status, (starts_with("care") & !ends_with("_f")), clothes, clutter,
      contracture, decubitus, dehydration, depressed, depression, diarrhea, difficulty_medications, disarray_hoarding, evidence, exterior_condition, 
      fractures, goods_for_services, hair, health_safety_concern, hoarding_medications, (contains("hygiene") & !ends_with("_f")), impaction,
      inability_account_money, inadequately_clothed, inappropriate_medication, interior_condition, isolated_home, lacerations, left_alone_unsafe,
      malnutrition, money_misuse, nails, nutrition, obvious_disease, odor, pets, repetitive_hosp_admission, report_elder_abuse, roof, sexual_abuse,
      skin_integrity, stages_healing, structural_problems, (starts_with("summary_evidence") & !ends_with("_f")), unmet_needs, unusual_odor, urine_burn, 
      utilities, walls, windows, yard_sidewalk
      )
  )

```

```{r}
# Data check
dim(obs_meas) # 935 132
```

# Save as rds file

```{r}
write_rds(obs_meas, "../data/cleaned_rds_files/observational_measures_import.rds")

```