---
title: "Import Data from FileMaker Pro: APS Investigations"
---

# Overview

In this file, we import and do some initial cleaning of the APS Investigations data collected and stored in FileMaker Pro.


# Load packages

```{r}
library(dplyr, warn.conflicts = FALSE)
library(readr)
library(purrr)
library(stringr)
library(janitor)
```


# Load data

Load the data table into the global environment as a data frame using the raw csv file. See this Wiki page for more information about the location of the data: https://github.com/brad-cannell/detect_fu_interviews_public/wiki/Using-this-repository. 

```{r}
aps_inv <- read_csv("../data/filemaker_pro_exports/aps_investigations_import.csv")
```

```{r}
# Data check
dim(aps_inv) # 951  18
```
# Data cleaning

We will create categorical variables with numerical values that match the codebook and also create a factor variable for each categorical variable in the data frame to be used for analysis.

## Convert all variable names to snake case

```{r}
aps_inv <- clean_names(aps_inv)
```

## Create recoded variables to match levels in follow-up interview protocol

```{r}
# Create recoded variables for aps_report
aps_inv <- aps_inv %>%
  mutate(
    aps_report_4cat = case_when(
      aps_report == "Yes"        ~ 1,
      aps_report == "No"         ~ 2,
      aps_report == "Don't know" ~ 7,
      aps_report == "Refused"    ~ 9
    ),
    aps_report_4cat_f = factor(
      aps_report,
      levels = c("Yes", "No", "Don't know", "Refused")
      )
  )
```

```{r}
# Create recoded variables for aps_times
aps_inv <- aps_inv %>%
  mutate(
    aps_times_5cat = case_when(
      aps_times == "0"          ~ 0,
      aps_times == "1"          ~ 1,
      aps_times == "2+"         ~ 2,
      aps_times == "Don't know" ~ 7,
      aps_times == "Refused"    ~ 9
    ),
    aps_times_5cat_f = factor(
      aps_times,
      levels = c("0", "1", "2+", "Don't know", "Refused")
      )
  )
```

```{r}
# Create recoded variables for aps_first
aps_inv <- aps_inv %>%
  mutate(
    aps_first_8cat = case_when(
      aps_first == "10 or more years ago"                       ~ 1,
      aps_first == "5-10 years ago"                             ~ 2,
      aps_first == "1-5 years ago"                              ~ 3,
      aps_first == "In the past year but more than a month ago" ~ 4,
      aps_first == "In the past month"                          ~ 5,
      aps_first == "In the past week"                           ~ 6,
      aps_first == "Don't know"                                 ~ 7,
      aps_first == "Refused"                                    ~ 9
    ),
    aps_first_8cat_f = factor(
      aps_first,
      levels = c(
        "10 or more years ago", "5-10 years ago", "1-5 years ago", 
        "In the past year but more than a month ago", "In the past month" , 
        "In the past week", "Don't know", "Refused"
      )
    )
  )
```

```{r}
# Create recoded variables for aps_recent
aps_inv <- aps_inv %>%
  mutate(
    aps_recent_8cat = case_when(
      aps_recent == "In the past week"                           ~ 1,
      aps_recent == "In the past month"                          ~ 2,
      aps_recent == "In the past year but more than a month ago" ~ 3,
      aps_recent == "1-5 years ago"                              ~ 4,
      aps_recent == "5-10 years ago"                             ~ 5, 
      aps_recent == "10 or more years ago"                       ~ 6,
      aps_recent == "Don’t know"                                 ~ 7,
      aps_recent == "Refused"                                    ~ 9
    ),
    aps_recent_8cat_f = factor(
      aps_recent,
      levels = c(
        "In the past week", "In the past month", 
        "In the past year but more than a month ago", "1-5 years ago", 
        "5-10 years ago", "10 or more years ago", "Don’t know", "Refused"
      )
    )
  )
```

## Remove raw variables that have recoded forms

```{r}
aps_inv <- aps_inv %>% 
  select(-c(aps_report, aps_times, aps_first, aps_recent))
```

```{r}
# Data check
dim(aps_inv) # 951  22
```

# Save as rds file

```{r}
write_rds(aps_inv, "../data/cleaned_rds_files/aps_investigations_import.rds")
```
