---
title: "clusca_recode_factor"
author: "Marissa Gough"
date : "May 11, 2022"
---


```{r, message= FALSE}
# Load all necessary libraries
library(readr)
library(purrr)
library(stringr)
library(dplyr, warn.conflicts = FALSE)
library(expss)
```


## Load data

Load the data tables into the global environment as data frames. We will create categorical variables with numerical values that match the codebook and also create a factor variable for each categorical variable in the data frame to be used for analysis.

```{r load data, messages = FALSE}
clusca <- read_csv("Clutter Scale.csv")
```

# Data cleaning.

Here we will convert all variable names to snake case so that everything is uniform.

```{r}
# Convert all variable names to snake case
walk(
  # Grab the names of all data frames in the global environment
  .x = ls()[map_lgl(ls(), ~ is.data.frame(get(.)))],
  .f = function(x) {
    # Grab individual df from environment
    df <- get(x)
    # Grab the variables names
    var_names <- names(df)
    # Convert variable names to snake case
    var_names <- str_replace_all(var_names, '(\\B)([A-Z])', '_\\2')
    # Convert variable names to lower case
    var_names <- str_to_lower(var_names)
    # Fix medstar_id
    var_names[var_names == "medstar_i_d"] <- "medstar_id"
    # assign back to the dataframe
    names(df) <- var_names
    # Replace df with new names in global environment
    assign(x, df, envir = .GlobalEnv)
  }
)
```


## Clutter Scale Variables

```{r}
clusca <- clusca%>%
  mutate(
    look_living_3cat = factor(
      look_living,
      levels = c("Yes", "No", "No living room")
    )
  )
```

```{r}
clusca <- clusca%>%
  mutate(
    clutter_living_f = factor(
      clutter_living
    ),
    clutter_living_photo_3cat = factor(
      clutter_living_photo,
      levels = c("Yes", "No", "No living room")
    )
  )
```

```{r}
clusca <- clusca%>%
  mutate(
    look_kitchen_3cat = factor(
      look_kitchen,
      levels = c("Yes", "No", "No kitchen")
    )
  )
```

```{r}
clusca <- clusca%>%
  mutate(
    clutter_kitchen_f = factor(
      clutter_kitchen
    ),
    clutter_kitchen_photo_3cat = factor(
      clutter_kitchen_photo,
      levels = c("Yes", "No", "No living room")
    )
  )
```

```{r}
clusca <- clusca%>%
  mutate(
    look_bedroom_3cat = factor(
      look_bedroom,
      levels = c("Yes", "No", "No bedroom")
    )
  )
```

```{r}
clusca <- clusca%>%
  mutate(
    clutter_bedroom_f = factor(
      clutter_bedroom
    ),
    clutter_bedroom_photo_3cat = factor(
      clutter_bedroom_photo,
      levels = c("Yes", "No", "No bedroom")
    )
  )
```

# Write file to csv

```{r}
write_csv(clusca, "clusca_factor.csv")
```
