---
title: "APS Investigations Recode"
author: "Marissa Gough"
---

```{r, message= FALSE}
# Load all necessary libraries
library(readr)
library(purrr)
library(stringr)
library(dplyr, warn.conflicts = FALSE)
```

## Load data

Load the data tables into the global environment as data frames. We will create categorical variables with numerical values that match the codebook and also create a factor variable for each categorical variable in the data frame to be used for analysis.

```{r load data, messages = FALSE}
apinve <- read_csv("../data/raw/APS Investigations.csv")
```

# Data cleaning.

Here we will convert all variable names to snake case so that everything is uniform.

```{r}
# Convert all variable names to snake case
walk(
  # Grab the names of all data frames in the global environment
  .x = ls()[map_lgl(ls(), ~ is.data.frame(get(.)))],
  .f = function(x) {
    # Grab individual df from environment
    df <- get(x)
    # Grab the variables names
    var_names <- names(df)
    # Convert variable names to snake case
    var_names <- str_replace_all(var_names, '(\\B)([A-Z])', '_\\2')
    # Convert variable names to lower case
    var_names <- str_to_lower(var_names)
    # Fix medstar_id
    var_names[var_names == "medstar_i_d"] <- "medstar_id"
    # assign back to the dataframe
    names(df) <- var_names
    # Replace df with new names in global environment
    assign(x, df, envir = .GlobalEnv)
  }
)
```

## Change the encoding of columns that contain unrecognized characters where there is an apostrophe. Substitute an apostrophe for the special characters so that the value is "Don't know"

```{r}
Encoding(apinve$aps_first) <- "ASCII"

apinve <- apinve %>%
  mutate(
    aps_first = 
      iconv(aps_first, "ASCII", "latin1", "'")
)
```

```{r}
apinve <- apinve %>%
  mutate(
    aps_report_4cat = factor(
      aps_report,
      levels = c("Yes", "No", "Don't know", "Refused")
    )
  )
```

```{r}
apinve <- apinve %>%
  mutate(
    aps_times_5cat = case_when(
      aps_times == "0"          ~ 0,
      aps_times == "1"          ~ 1,
      aps_times == "2+"         ~ 2,
      aps_times == "Don't know" ~ 7,
      aps_times == "Refused"    ~ 9
    ),
    aps_times_5cat_f = factor(
      aps_times,
      levels = c("0", "1", "2+", "Don't know", "Refused")
    )
  )
```

```{r}
apinve <- apinve %>%
  mutate(
    aps_first_8cat = factor(
      aps_first,
      levels = c(
        "10 or more years ago", "5-10 years ago", "1-5 years ago", 
        "In the past year but more than a month ago", "In the past month", 
        "In the past week", "Don't know", "Refused"
      )
    )
  )
```

```{r}
apinve <- apinve %>%
  mutate(
    aps_recent_8cat = factor(
      aps_recent,
      levels = c("In the past week", "In the past month",
                 "In the past year but more than a month ago",
                 "1-5 years ago", "5-10 years ago", "10 or more years ago",
                 "Don’t know", "Refused")
    )
  )
```

# Write file to csv

```{r}
write_csv(apinve, "apinve_factor.csv")
```

