---
title: "self_report_recode_factor"
output: html_notebook
author: "Marissa Gough"
---
```{r, message= FALSE}
# Load all necessary libraries
library(readr)
library(purrr)
library(stringr)
library(dplyr)

```


# Load data

Load the data tables into the global environment as data frames. We will create categorical variables with numerical values that match the codebook and also create a factor variable for each categorical variable in the data frame to be used for analysis.

```{r load data, messages = FALSE}
# I changed the encoding to remove unrecognized characters "Donít know" for don't know

self_report <- read_csv("../data/raw/Self Report.csv", show_col_types = FALSE, locale = locale(encoding = "latin1", asciify = TRUE)) # 598 203
```

# Data cleaning.

Here we will convert all variable names to snake case so that everything is uniform.

```{r}
# Convert all variable names to snake case
walk(
  # Grab the names of all data frames in the global environment
  .x = ls()[map_lgl(ls(), ~ is.data.frame(get(.)))],
  .f = function(x) {
    # Grab individual df from environment
    df <- get(x)
    # Grab the variables names
    var_names <- names(df)
    # Convert variable names to snake case
    var_names <- str_replace_all(var_names, '(\\B)([A-Z])', '_\\2')
    # Convert variable names to lower case
    var_names <- str_to_lower(var_names)
    # Fix medstar_id
    var_names[var_names == "medstar_i_d"] <- "medstar_id"
    # assign back to the dataframe
    names(df) <- var_names
    # Replace df with new names in global environment
    assign(x, df, envir = .GlobalEnv)
  }
)

```

Remove unwanted characters and replace with "Don't know"
```{r}
self_report[self_report == "Dont know"] <- "Don't know"
```

# Self-report injury, violence, neglect, and exploitation

Set levels to be used throughout this program

```{r}

# Set levels for factors for different types of questions
levels_yes_no   <- c("Yes", "No", "Don't know", "Refused")
levels_help     <- c("Yes, one person", "Yes, more than one person", "No",
                     "Don't know", "Refused")
levels_reliable <- c("Not at all reliable", "Somewhat reliable", 
                     "Very reliable", "Completely reliable", "Don’t know",
                     "Refused")
levels_person   <- c("A spouse or partner", "An ex spouse or partner", 
                     "A parent or step-parent", "A brother or sister", 
                     "A son or daughter", "Another relative", "A coworker", 
                     "A neighbor", "A friend", "Some other non-relative",
                     "Don't know", "Refused")
```


### Neglect variables

```{r}
self_report <- self_report %>%
  mutate(
    across(
      .cols = starts_with("neglect") & !ends_with("help") &
        !ends_with("reliable") & !ends_with("person"),
      .fns  = ~ case_when(
        .x == "Yes"        ~ 1,
        .x == "No"         ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused"    ~ 9 
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("neglect") & !ends_with("help") &
        !ends_with("reliable") & !ends_with("person") & !ends_with("4cat"),
      .fn    = ~ factor(.x, levels = levels_yes_no),
      .names = "{col}_4cat_f"
    )
  )
```    

```{r}
self_report <- self_report %>%
  mutate(
    across(
      .cols  = starts_with("neglect") & ends_with("help"),
      .fns   = ~ case_when(
        .x == "Yes, one person"           ~ 1, 
        .x == "Yes, more than one person" ~ 2, 
        .x == "No"                        ~ 3,
        .x == "Don't know"                ~ 7, 
        .x == "Refused"                   ~ 9
      ),
      .names = "{col}_5cat" 
    ),
    across(
      .cols  = starts_with("neglect") & ends_with("help"),
      .fns   = ~ factor(.x, levels = levels_help),
      .names = "{col}_5cat_f"
    )
  )
```
   
```{r}
self_report <- self_report %>%
  mutate(
    across(
      .cols  = starts_with("neglect") & ends_with("reliable"),
      .fns   = ~ case_when(
        .x == "Not at all reliable" ~ 1, 
        .x == "Somewhat reliable"   ~ 2, 
        .x == "Very reliable"       ~ 3, 
        .x == "Completely reliable" ~ 4, 
        .x == "Don't know"          ~ 7,
        .x == "Refused"             ~ 9
      ),
      .names = "{col}_6cat" 
    ),
    across(
      .cols  = starts_with("neglect") & ends_with("reliable"),
      .fns   = ~ factor(.x, levels = levels_reliable),
      .names = "{col}_6cat_f"
    )
  )
```

```{r}
self_report <- self_report %>%
  mutate(
    neglect_person_12cat = case_when(
        neglect_person == "A spouse or partner"     ~ 1, 
        neglect_person == "An ex spouse or partner" ~ 2, 
        neglect_person == "A parent or step-parent" ~ 3, 
        neglect_person == "A brother or sister"     ~ 4, 
        neglect_person == "A son or daughter"       ~ 5, 
        neglect_person == "Another relative"        ~ 6, 
        neglect_person == "A coworker"              ~ 7, 
        neglect_person == "A neighbor"              ~ 8, 
        neglect_person == "A friend"                ~ 9, 
        neglect_person == "Some other non-relative" ~ 10,
        neglect_person == "Don't know"              ~ 77, 
        neglect_person == "Refused"                 ~ 99
    ),
    neglect_person_12cat_f = factor(
        neglect_person,
        levels = levels_person
    )
  )
```
  
# Financial Exploitation Variables

Set levels for factors used in these variables

```{r}
levels_last_time <- c("Less than 1 month ago", 
                      "Between 1 month and less than 3 months ago",
                      "Between 3 months and less than 6 months ago",
                      "Between 6 months and less than 1 year ago",
                      "Between 1 year and less than 3 years ago",
                      "3 or more years ago", "Don't know", "Refused")
```

Recode categorical variables to factor variables

```{r}
self_report <- self_report %>%
  mutate(
    across(
      .cols = starts_with("finance") & !ends_with("years") &
        !ends_with("times") &  !ends_with("age") & !ends_with("person") &
        !ends_with("last_time"),
      .fns  = ~ case_when(
        .x == "Yes"        ~ 1,
        .x == "No"         ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused"    ~ 9 
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("finance") & !ends_with("years") &
        !ends_with("times") &  !ends_with("age") & !ends_with("person") &
        !ends_with("last_time") & !ends_with("4cat"),
      .fns  = ~ factor(.x, levels = levels_yes_no),
    .names = "{col}_4cat_f"
    )
  )
```    

```{r}
self_report <- self_report %>%
  mutate(
    finance_person_12cat = case_when(
      finance_person == "A spouse or partner"     ~ 1, 
      finance_person == "An ex spouse or partner" ~ 2, 
      finance_person == "A parent or step-parent" ~ 3, 
      finance_person == "A brother or sister"     ~ 4, 
      finance_person == "A son or daughter"       ~ 5, 
      finance_person == "Another relative"        ~ 6, 
      finance_person == "A coworker"              ~ 7, 
      finance_person == "A neighbor"              ~ 8, 
      finance_person == "A friend"                ~ 9, 
      finance_person == "Some other non-relative" ~ 10,
      finance_person == "Don't know"              ~ 77, 
      finance_person == "Refused"                 ~ 99
    ),
    finance_person_12cat_f = factor(
      finance_person,
      levels = levels_person
    )
  )
```

```{r}
self_report <- self_report %>%
  mutate(
    across(
      .cols = starts_with("finance") & ends_with("last_time"),
      .fns  = ~ case_when(
        .x == "Less than 1 month ago"                       ~ 1,
        .x == "Between 1 month and less than 3 months ago"  ~ 2,
        .x == "Between 3 months and less than 6 months ago" ~ 3,
        .x == "Between 6 months and less than 1 year ago"   ~ 4,
        .x == "Between 1 year and less than 3 years ago"    ~ 5,
        .x == "3 or more years ago"                         ~ 6, 
        .x == "Don't know"                                  ~ 7,
        .x == "Refused"                                     ~ 9
      ),
    .names = "{col}_8cat"
    ),
    across(
      .cols  = starts_with("finance") & ends_with("last_time"),
      .fns   = ~ factor(.x, levels = levels_last_time),
      .names =  "{col}_8cat_f"
    )
  )
```
    

# Emotional Mistreatment Variables

Set levels to be used with these variables

```{r}
levels_times     <- c("1 or 2 times", "Between 3 and less than 5 times",
                      "Between 5 and less than 10 times", 
                      "Between 10 and less than 20 times", "20 or more times",
                      "Don't know", "Refused")

levels_friends   <- c("None", "Very few (1-3)", "Some (4-6)", "A lot (7+)",
                      "Don't know", "Refused")

levels_person_v2 <- c("A stranger", "A spouse or partner", "An ex spouse or partner", 
                      "A parent or step-parent", "A brother or sister",
                      "A son or daughter", "Another relative", "A coworker", 
                      "A neighbor", "A friend", "Some other non-relative",
                      "Don't know", "Refused")
```
 

Recode categorical variables to factor variables

```{r}
self_report <- self_report %>%
  mutate(
    across(
      .cols = starts_with("emotional") & !ends_with("years") &
        !ends_with("times") &  !ends_with("age") & !ends_with("person") &
        !ends_with("last_time") & !ends_with("friends") &
        !ends_with("person_v2"),
      .fns  = ~ case_when(
        .x == "Yes"        ~ 1,
        .x == "No"         ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused"    ~ 9 
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("emotional") & !ends_with("years") &
        !ends_with("times") &  !ends_with("age") & !ends_with("person") &
        !ends_with("last_time") & !ends_with("friends") & !ends_with("4cat") &
        !ends_with("person_v2"),
      .fns  = ~ factor(.x, levels = levels_yes_no),
      .names = "{col}_4cat_f"
    )
  )
```
  
```{r}
self_report <- self_report %>%
  mutate(
    emotional_incident_person_12cat = case_when(
      emotional_incident_person == "A stranger"              ~ 1,
      emotional_incident_person == "A spouse or partner"     ~ 2, 
      emotional_incident_person == "An ex spouse or partner" ~ 3, 
      emotional_incident_person == "A parent or step-parent" ~ 4, 
      emotional_incident_person == "A brother or sister"     ~ 5, 
      emotional_incident_person == "A son or daughter"       ~ 6, 
      emotional_incident_person == "Another relative"        ~ 7, 
      emotional_incident_person == "A coworker"              ~ 8, 
      emotional_incident_person == "A neighbor"              ~ 9, 
      emotional_incident_person == "A friend"                ~ 10, 
      emotional_incident_person == "Some other non-relative" ~ 11,
      emotional_incident_person == "Don't know"              ~ 77, 
      emotional_incident_person == "Refused"                 ~ 99
    ),
    emotional_incident_person_12cat_f = factor(
      emotional_incident_person,
      levels = levels_person_v2
    )
  )
  
```
    
```{r}
self_report <- self_report %>%
  mutate(
    across(
      .cols = starts_with("emotional") & ends_with("last_time"),
      .fns  = ~ case_when(
        .x == "Less than 1 month ago"                       ~ 1,
        .x == "Between 1 month and less than 3 months ago"  ~ 2,
        .x == "Between 3 months and less than 6 months ago" ~ 3,
        .x == "Between 6 months and less than 1 year ago"   ~ 4,
        .x == "Between 1 year and less than 3 years ago"    ~ 5,
        .x == "3 or more years ago"                         ~ 6, 
        .x == "Don't know"                                  ~ 7,
        .x == "Refused"                                     ~ 9
      ),
      .names = "{col}_8cat"
    ),
    across(
      .cols  = starts_with("emotional") & ends_with("last_time"),
      .fns   = ~ factor(.x, levels = levels_last_time),
      .names =  "{col}_8cat_f"
    )
  )

  
```

```{r}
self_report <- self_report %>%
  mutate(
    across(
      .cols = starts_with("emotional") & ends_with("times") & 
              !ends_with("times_times"),
      .fns = ~ case_when(
        .x == "1 or 2 times"                      ~ 1, 
        .x == "Between 3 and less than 5 times"   ~ 2,
        .x == "Between 5 and less than 10 times"  ~ 3, 
        .x == "Between 10 and less than 20 times" ~ 4, 
        .x == "20 or more times"                  ~ 5,
        .x == "Don't know"                        ~ 7, 
        .x == "Refused"                           ~ 9
      ),
      .names = "{col}_7cat"
    ),
    across(
      .cols  = starts_with("emotional") & ends_with("times") & 
              !ends_with("times_times"),
      .fns   = ~ factor(.x, levels = levels_times),
      .names = "{col}_7cat_f"
    )
  )
```
  
```{r}
self_report <- self_report %>%
  mutate(
    emotional_person_friends_6cat = case_when(
      emotional_person_friends == "None"           ~ 0, 
      emotional_person_friends == "Very few (1-3)" ~ 1, 
      emotional_person_friends == "Some (4-6)"     ~ 2, 
      emotional_person_friends == "A lot (7+)"     ~ 3,
      emotional_person_friends == "Don't know"     ~ 7, 
      emotional_person_friends == "Refused"        ~ 9
    ),
    emotional_person_friends_6cat_f = factor(
      emotional_person_friends,
      levels = levels_friends
    )
  )
```
  
```{r}
self_report <- self_report %>%
  mutate(
    emotional_incident_person_v2_12cat = case_when(
      emotional_incident_person_v2 == "A stranger"              ~ 1,
      emotional_incident_person_v2 == "A spouse or partner"     ~ 2, 
      emotional_incident_person_v2 == "An ex spouse or partner" ~ 3, 
      emotional_incident_person_v2 == "A parent or step-parent" ~ 4, 
      emotional_incident_person_v2 == "A brother or sister"     ~ 5, 
      emotional_incident_person_v2 == "A son or daughter"       ~ 6, 
      emotional_incident_person_v2 == "Another relative"        ~ 7, 
      emotional_incident_person_v2 == "A coworker"              ~ 8, 
      emotional_incident_person_v2 == "A neighbor"              ~ 9, 
      emotional_incident_person_v2 == "A friend"                ~ 10, 
      emotional_incident_person_v2 == "Some other non-relative" ~ 11,
      emotional_incident_person_v2 == "Don't know"              ~ 77, 
      emotional_incident_person_v2 == "Refused"                 ~ 99
    ),
    emotional_incident_person_v2_12cat_f = factor(
      emotional_incident_person_v2,
      levels = levels_person_v2
    )
  )
```
  
# Physical Mistreatment Variables

Recode categorical variables to factor variables

```{r}
self_report <- self_report %>%
  mutate(
    across(
      .cols = starts_with("physical") & !ends_with("years") &
        !ends_with("times") &  !ends_with("age") &
        !ends_with("last_time") & !ends_with("friends") &
        !ends_with("person_v2"),
      .fns  = ~ case_when(
        .x == "Yes"        ~ 1,
        .x == "No"         ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused"    ~ 9 
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("physical") & !ends_with("years") &
        !ends_with("times") &  !ends_with("age")  &
        !ends_with("last_time") & !ends_with("friends") & !ends_with("4cat") &
        !ends_with("person_v2"),
      .fns  = ~ factor(.x, levels = levels_yes_no),
    .names = "{col}_4cat_f"
    )
  )
```

```{r}
self_report <- self_report %>%
  mutate(
    across(
      .cols = starts_with("physical") & ends_with("last_time"),
      .fns  = ~ case_when(
        .x == "Less than 1 month ago"                       ~ 1,
        .x == "Between 1 month and less than 3 months ago"  ~ 2,
        .x == "Between 3 months and less than 6 months ago" ~ 3,
        .x == "Between 6 months and less than 1 year ago"   ~ 4,
        .x == "Between 1 year and less than 3 years ago"    ~ 5,
        .x == "3 or more years ago"                         ~ 6, 
        .x == "Don't know"                                  ~ 7,
        .x == "Refused"                                     ~ 9
      ),
      .names = "{col}_8cat"
    ),
    across(
      .cols  = starts_with("physical") & ends_with("last_time"),
      .fns   = ~ factor(.x, levels = levels_last_time),
      .names =  "{col}_8cat_f"
    )
  )
```

```{r}
self_report <- self_report %>%
  mutate(
    across(
      .cols = starts_with("physical") & ends_with("times") & 
              !ends_with("times_times"),
      .fns = ~ case_when(
        .x == "1 or 2 times"                      ~ 1, 
        .x == "Between 3 and less than 5 times"   ~ 2,
        .x == "Between 5 and less than 10 times"  ~ 3, 
        .x == "Between 10 and less than 20 times" ~ 4, 
        .x == "20 or more times"                  ~ 5,
        .x == "Don't know"                        ~ 7, 
        .x == "Refused"                           ~ 9),
      .names = "{col}_7cat"
    ),
    across(
      .cols  = starts_with("physical") & ends_with("times") & 
              !ends_with("times_times"),
      .fns   = ~ factor(.x, levels = levels_times),
      .names = "{col}_7cat_f"
    )
  )
```
  
```{r}
self_report <- self_report %>%
  mutate(
    physical_person_friends_6cat = case_when(
      physical_person_friends == "None"           ~ 0, 
      physical_person_friends == "Very few (1-3)" ~ 1, 
      physical_person_friends == "Some (4-6)"     ~ 2, 
      physical_person_friends == "A lot (7+)"     ~ 3,
      physical_person_friends == "Don't know"     ~ 7, 
      physical_person_friends == "Refused"        ~ 9
    ),
    physical_person_friends_6cat_f = factor(
      physical_person_friends,
      levels = levels_friends
    )
  )
```
  

```{r}
self_report <- self_report %>%
  mutate(
    physical_incident_person_v2_12cat = case_when(
      physical_incident_person_v2 == "A stranger"              ~ 1,
      physical_incident_person_v2 == "A spouse or partner"     ~ 2, 
      physical_incident_person_v2 == "An ex spouse or partner" ~ 3, 
      physical_incident_person_v2 == "A parent or step-parent" ~ 4, 
      physical_incident_person_v2 == "A brother or sister"     ~ 5, 
      physical_incident_person_v2 == "A son or daughter"       ~ 6, 
      physical_incident_person_v2 == "Another relative"        ~ 7, 
      physical_incident_person_v2 == "A coworker"              ~ 8, 
      physical_incident_person_v2 == "A neighbor"              ~ 9, 
      physical_incident_person_v2 == "A friend"                ~ 10, 
      physical_incident_person_v2 == "Some other non-relative" ~ 11,
      physical_incident_person_v2 == "Don't know"              ~ 77, 
      physical_incident_person_v2 == "Refused"                 ~ 99
    ),
    physical_incident_person_v2_12cat_f = factor(
      physical_incident_person_v2,
      levels = levels_person_v2
    )
  )
```

```{r}
self_report <- self_report %>%
  mutate(
    physical_person_12cat = case_when(
      physical_person == "A stranger"              ~ 1,
      physical_person == "A spouse or partner"     ~ 2, 
      physical_person == "An ex spouse or partner" ~ 3, 
      physical_person == "A parent or step-parent" ~ 4, 
      physical_person == "A brother or sister"     ~ 5, 
      physical_person == "A son or daughter"       ~ 6, 
      physical_person == "Another relative"        ~ 7, 
      physical_person == "A coworker"              ~ 8, 
      physical_person == "A neighbor"              ~ 9, 
      physical_person == "A friend"                ~ 10, 
      physical_person == "Some other non-relative" ~ 11,
      physical_person == "Don't know"              ~ 77, 
      physical_person == "Refused"                 ~ 99
    ),
    physical_person_12cat_f = factor(
      physical_person,
      levels = levels_person_v2
    )
  )
```
  
# Sexual mistreatment variables

Recode categorical variables to factor variables

```{r}
self_report <- self_report %>%
  mutate(
    across(
      .cols = starts_with("sexual") & !ends_with("years") &
        !ends_with("times") &  !ends_with("age") &
        !ends_with("last_time") & !ends_with("friends") &
        !ends_with("person_v2"),
      .fns  = ~ case_when(
        .x == "Yes"        ~ 1,
        .x == "No"         ~ 2,
        .x == "Don't know" ~ 7,
        .x == "Refused"    ~ 9 
      ),
      .names = "{col}_4cat"
    ),
    across(
      .cols = starts_with("sexual") & !ends_with("years") &
        !ends_with("times") &  !ends_with("age") &
        !ends_with("last_time") & !ends_with("friends") & !ends_with("4cat") &
        !ends_with("person_v2"),
      .fns  = ~ factor(.x, levels = levels_yes_no),
      .names = "{col}_4cat_f"
    )
  )
```
  
```{r}
self_report <- self_report %>%
  mutate(
    across(
      .cols = starts_with("sexual") & ends_with("last_time"),
      .fns  = ~ case_when(
        .x == "Less than 1 month ago"                       ~ 1,
        .x == "Between 1 month and less than 3 months ago"  ~ 2,
        .x == "Between 3 months and less than 6 months ago" ~ 3,
        .x == "Between 6 months and less than 1 year ago"   ~ 4,
        .x == "Between 1 year and less than 3 years ago"    ~ 5,
        .x == "3 or more years ago"                         ~ 6, 
        .x == "Don't know"                                  ~ 7,
        .x == "Refused"                                     ~ 9
      ),
      .names = "{col}_8cat"
    ),
    across(
      .cols  = starts_with("sexual") & ends_with("last_time"),
      .fns   = ~ factor(.x, levels = levels_last_time),
      .names =  "{col}_8cat_f"
    )
  )
```
  
```{r}
self_report <- self_report %>%
  mutate(
    across(
      .cols = starts_with("sexual") & ends_with("times") & 
              !ends_with("times_times"),
      .fns = ~ case_when(
        .x == "1 or 2 times"                      ~ 1, 
        .x == "Between 3 and less than 5 times"   ~ 2,
        .x == "Between 5 and less than 10 times"  ~ 3, 
        .x == "Between 10 and less than 20 times" ~ 4, 
        .x == "20 or more times"                  ~ 5,
        .x == "Don't know"                        ~ 7, 
        .x == "Refused"                           ~ 9
      ),
      .names = "{col}_7cat"
    ),
    across(
      .cols  = starts_with("sexual") & ends_with("times") & 
              !ends_with("times_times"),
      .fns   = ~ factor(.x, levels = levels_times),
      .names = "{col}_7cat_f"
    )
  )
    
```
  
```{r}
self_report <- self_report %>%
  mutate(
    sexual_person_friends_6cat = case_when(
      sexual_person_friends == "None"           ~ 0, 
      sexual_person_friends == "Very few (1-3)" ~ 1, 
      sexual_person_friends == "Some (4-6)"     ~ 2, 
      sexual_person_friends == "A lot (7+)"     ~ 3,
      sexual_person_friends == "Don't know"     ~ 7, 
      sexual_person_friends == "Refused"        ~ 9
    ),
    sexual_person_friends_6cat_f = factor(
      sexual_person_friends,
      levels = levels_friends
    )
  )
```
  
```{r}
self_report <- self_report %>%
  mutate(
    sexual_incident_person_v2_12cat = case_when(
      sexual_incident_person_v2 == "A stranger"              ~ 1,
      sexual_incident_person_v2 == "A spouse or partner"     ~ 2, 
      sexual_incident_person_v2 == "An ex spouse or partner" ~ 3, 
      sexual_incident_person_v2 == "A parent or step-parent" ~ 4, 
      sexual_incident_person_v2 == "A brother or sister"     ~ 5, 
      sexual_incident_person_v2 == "A son or daughter"       ~ 6, 
      sexual_incident_person_v2 == "Another relative"        ~ 7, 
      sexual_incident_person_v2 == "A coworker"              ~ 8, 
      sexual_incident_person_v2 == "A neighbor"              ~ 9, 
      sexual_incident_person_v2 == "A friend"                ~ 10, 
      sexual_incident_person_v2 == "Some other non-relative" ~ 11,
      sexual_incident_person_v2 == "Don't know"              ~ 77, 
      sexual_incident_person_v2 == "Refused"                 ~ 99
    ),
    sexual_incident_person_v2_12cat_f = factor(
      sexual_incident_person_v2,
      levels = levels_person_v2
    )
  )
```
  
```{r}
self_report <- self_report %>%
  mutate(
    sexual_person_12cat = case_when(
      sexual_person == "A stranger"              ~ 1,
      sexual_person == "A spouse or partner"     ~ 2, 
      sexual_person == "An ex spouse or partner" ~ 3, 
      sexual_person == "A parent or step-parent" ~ 4, 
      sexual_person == "A brother or sister"     ~ 5, 
      sexual_person == "A son or daughter"       ~ 6, 
      sexual_person == "Another relative"        ~ 7, 
      sexual_person == "A coworker"              ~ 8, 
      sexual_person == "A neighbor"              ~ 9, 
      sexual_person == "A friend"                ~ 10, 
      sexual_person == "Some other non-relative" ~ 11,
      sexual_person == "Don't know"              ~ 77, 
      sexual_person == "Refused"                 ~ 99
    ),
    sexual_person_12cat_f = factor(
      sexual_person,
      levels = levels_person_v2
    )
  )
```

# Fears, wants, needs variables

Recode categorical variables to factor variables

```{r}
self_report <- self_report %>%
  mutate(
    across(
      .cols = starts_with("fear") & !ends_with("response"),
      .fns  = ~ case_when(
        .x == "Don't know" ~ 7,
        .x == "Refused" ~ 9
      ),
      .names = "{col}_2cat"
    ),
    across(
      .cols  = starts_with("fear") & !ends_with("response") &
        !ends_with("2cat"),
      .fns   = ~ factor(.x, levels = c("Don't know", "Refused")),
      .names = "{col}_2cat_f"
    )
  )

```


# Environment Variables

Recode categorical variables to factor variables

```{r}
self_report <- self_report %>%
  mutate(
    report_private_5cat = case_when(
      report_private == "Yes, for the entire time"                     ~ 1,
      report_private == "Yes, for part of the time"                    ~ 2,
      report_private == "No, but they were still close enough to hear" ~ 3,
      report_private == "No"                                           ~ 4,
      report_private == "Don't know"                                   ~ 7
    ),
    report_private_5cat_f = factor(
      report_private,
      levels = c("Yes, for the entire time", "Yes, for part of the time",
                "No, but they were still close enough to hear", "No",
                "Don't know")),
    report_influence_4cat = case_when(
      report_influence == "Yes"        ~ 1,
      report_influence == "No"         ~ 2,
      report_influence == "Don't know" ~ 7,
      report_influence == "Refused"    ~ 9
    ),
    report_influence_4cat_f = factor(
      report_influence,
      levels = levels_yes_no
    )
  )
```


```{r}
dim(self_report) # 598 491
```



#### Write to CSV

```{r}
write_csv(self_report, "../data/self_report_factor.csv")
```

