---
title: "socdem_recode_factor"
output: html_notebook
author: "Marissa Gough"
date: "May 5, 2022"
---

# Load packages

```{r, message= FALSE}
library(dplyr, warn.conflicts = FALSE)
library(readr)
library(purrr)
library(stringr)
```

# Load data

Load the data tables into the global environment as data frames.We will create factor variables for all categorical variables in the data frames and save them to a new CSV file. 

```{r load data, messages = FALSE}
socdem <- read_csv("../data/raw/Sociodemographic Information.csv") # 600 31
```

# Data cleaning

Here we will convert all variable names to snake case so that everything is uniform.

```{r}
# Convert all variable names to snake case
walk(
  # Grab the names of all data frames in the global environment
  .x = ls()[map_lgl(ls(), ~ is.data.frame(get(.)))],
  .f = function(x) {
    # Grab individual df from environment
    df <- get(x)
    # Grab the variables names
    var_names <- names(df)
    # Convert variable names to snake case
    var_names <- str_replace_all(var_names, '(\\B)([A-Z])', '_\\2')
    # Convert variable names to lower case
    var_names <- str_to_lower(var_names)
    # Fix medstar_id
    var_names[var_names == "medstar_i_d"] <- "medstar_id"
    # assign back to the dataframe
    names(df) <- var_names
    # Replace df with new names in global environment
    assign(x, df, envir = .GlobalEnv)
  }
)
```

Replace "<92>" and "\x92" with an apostrophe so that values read "Don't know".

```{r}
socdem <- socdem %>% 
  mutate(
    across(
      everything(),
      function(x) {
        x <- str_replace(x, "<92>", "'")
        x <- str_replace(x, "\x92", "'")
        x
      }
    )
  )
```

## Coerce categorical variables to factor variables

Create factor variables and match levels to codebook for all categorical variables except race and sode_race. The codebook does not include "Hispanic or Latino" for the race variable, but it is included in this data. For sode_race, several participants have multiple values. During analysis, the researchers may want to collapse some categories of race/ethnicity, so it can be coded correctly at that time. 

```{r}
socdem <- socdem %>%
  mutate(
    sode_marital_8cat = case_when(
      sode_marital == "Married"                                     ~ 1,
      sode_marital == "Living as an unmarried or common law couple" ~ 2,
      sode_marital == "Separated"                                   ~ 3,
      sode_marital == "Divorced"                                    ~ 4,
      sode_marital == "Widowed"                                     ~ 5,
      sode_marital == "Single, or never married"                    ~ 6,
      sode_marital == "Don't know"                                  ~ 7,
      sode_marital == "Refused"                                     ~ 9
    ),
    sode_marital_8cat_f = factor(
      sode_marital,
      levels = c(
        "Married", "Living as an unmarried or common law couple",
        "Separated", "Divorced", "Widowed", "Single, or never married", 
        "Don’t know", "Refused"
      )
    )
  )
```

```{r}
socdem <- socdem %>%
  mutate(
    sogi_identity_5cat = case_when(
      sogi_identity == "Male"       ~ 1,
      sogi_identity == "Female"     ~ 2,
      sogi_identity == "Other"      ~ 3,
      sogi_identity == "Don't Know" ~ 7,
      sogi_identity == "Refused"    ~ 9
    ),
    sogi_identity_5cat_f = factor(
      sogi_identity, 
      levels = c("Male", "Female", "Other", "Don't know", "Refused")
    )
  )
```

```{r}
socdem <- socdem %>%
  mutate(
    sogi_orientation_8cat = case_when(
      sogi_orientation == "Straight/heterosexual" ~ 1,
      sogi_orientation == "Gay man"               ~ 2,
      sogi_orientation == "Lesbian/gay woman"     ~ 3,
      sogi_orientation == "Bisexual"              ~ 4,
      sogi_orientation == "Queer"                 ~ 5,
      sogi_orientation == "Don't know"            ~ 7,
      sogi_orientation == "Refused"               ~ 9
    ),
    sogi_orientation_8cat_f = factor(
      sogi_orientation,
      levels = c(
        "Straight/heterosexual", "Gay man", "Lesbian/gay woman",
        "Bisexual", "Queer", "Other", "Don't know", "Refused"
      )
    )
  )
```

```{r}
socdem <- socdem %>%
  mutate(
    sode_age_4cat = case_when(
      sode_age == "Age 65 to 100+" ~ 1,
      sode_age == "Don't know"     ~ 7,
      sode_age == "Refused"        ~ 9
    ),
    sode_age_4cat_f = factor(
      sode_age,
      levels = c("Age 65 to 100+", "Don't know", "Refused")
    )
  )
```

```{r}
socdem <- socdem %>%
  mutate(
    sode_hispanic_4cat = case_when(
      sode_hispanic == "Yes"         ~ 1,
      sode_hispanic == "No"          ~ 2,
      sode_hispanic == "Don't know"  ~ 7,
      sode_hispanic == "Refused"     ~ 9
    ),
    sode_hispanic_4cat_f = factor(
      sode_hispanic,
      levels = c("Yes", "No", "Don't know", "Refused")
    )
  )
```

```{r}
socdem <- socdem %>%
  mutate(
    sode_school_9cat = case_when(
      sode_school == "Did not complete high school or GED"               ~ 1,
      sode_school == "High school graduate or GED"                       ~ 2,
      sode_school == "Some college (no degree)"                          ~ 3,
      sode_school == "Associate's degree"                                ~ 4,
      sode_school == "Bachelor's degree (BA, AB, BS, etc.)"              ~ 5,
      sode_school == "Some graduate or professional school (no degree)"  ~ 6,
      sode_school == 
        "Graduate or professional school degree (MS, MA, MD, PhD, etc.)" ~ 7,
      sode_school == "Don't know"                                        ~ 77,
      sode_school == "Refused"                                           ~ 99
    ),
    sode_school_9cat_f = factor(
      sode_school,
      levels = c(
        "Did not complete high school or GED", 
        "High school graduate or GED", 
        "Some college (no degree)",
        "Associate's degree",
        "Bachelor's degree (BA, AB, BS, etc.)",
        "Some graduate or professional school (no degree)",
        "Graduate or professional school degree (MS, MA, MD, PhD, etc.)",  "Don't know", "Refused"
      )
    )
  )
```

```{r}
socdem <- socdem %>%
  mutate(
    sode_employed_11cat = case_when(
      sode_employed == "Employed full time"         ~ 1,
      sode_employed == "Employed part time"         ~ 2,
      sode_employed == "In the military"            ~ 3,
      sode_employed == "Unemployed"                 ~ 4,
      sode_employed == "Retired"                    ~ 5,
      sode_employed == "A student"                  ~ 6,
      sode_employed == "A homemaker"                ~ 7,
      sode_employed == "Disabled or unable to work" ~ 8,
      sode_employed == "Something else"             ~ 9,
      sode_employed == "Don't know"                 ~ 77,
      sode_employed == "Refused"                    ~ 99
    ),
    sode_employed_11cat_f = factor(
      sode_employed,
      levels = c(
        "Employed full time", "Employed part time", "In the military",
        "Unemployed", "Retired", "A student", "A homemaker", 
        "Disabled or unable to work", "Something else", "Don't know",
        "Refused"
      )
    )
  )
```

```{r}
socdem <- socdem %>%
  mutate(
    sode_income_9cat = case_when(
      sode_income == "$10,000 or less"              ~ 1,
      sode_income == "Between $10,001 and $20,000"  ~ 2,
      sode_income == "Between $20,001 and $35,000"  ~ 3,
      sode_income == "Between $35,001 and $50,000" ~ 4,
      sode_income == "Between $50,001 and $75,000"  ~ 5,
      sode_income == "Between $75,001 and $100,000" ~ 6,
      sode_income == "More than $100,000"           ~ 7,
      sode_income == "Don't know"                   ~ 77,
      sode_income == "Refused"                      ~ 99
    ),
    sode_income_9cat_f = factor(
      sode_income,
      levels = c("$10,000 or less", "Between $10,001 and $20,000", 
      "Between $20,001 and $35,000", "Between $35,001 and $50,000",
      "Between $50,001 and $75,000", "Between $75,001 and $100,000", 
      "More than $100,000", "Don't know", "Refused"
      )
    )
  )
```

```{r}
socdem <- socdem %>%
  mutate(
    sode_military_4cat = case_when(
      sode_military == "Yes"        ~ 1,
      sode_military == "No"         ~ 2,
      sode_military == "Don't know" ~ 7,
      sode_military == "Refused"    ~ 9
    ),
    sode_military_4cat_f = factor(
      sode_military,
      levels = c("Yes", "No", "Don't know", "Refused")
    )
  )
```

```{r}
socdem <- socdem %>%
  mutate(
    sode_unwanted_4cat = case_when(
      sode_unwanted == "Yes"        ~ 1,
      sode_unwanted == "No"         ~ 2,
      sode_unwanted == "Don't know" ~ 7,
      sode_unwanted == "Refused"    ~ 9
    ),
    sode_unwanted_4cat_f = factor(
      sode_unwanted,
      levels = c("Yes", "No", "Don't know", "Refused")
    )
  )
```

```{r}
socdem <- socdem %>%
  mutate(
    sode_sexual_4cat = case_when(
      sode_sexual == "Yes"        ~ 1,
      sode_sexual == "No"         ~ 2,
      sode_sexual == "Don't know" ~ 7,
      sode_sexual == "Refused"    ~ 9
    ),
    sode_sexual_4cat_f = factor(
      sode_sexual,
      levels = c("Yes", "No", "Don't know", "Refused")
    )
  )
```

```{r}
socdem <- socdem %>%
  mutate(
    hsi_contact_4cat = case_when(
      hsi_contact == "Yes"        ~ 1,
      hsi_contact == "No"         ~ 2,
      hsi_contact == "Don't know" ~ 7,
      hsi_contact == "Refused"    ~ 9
    ),
    hsi_contact_4cat_f = factor(
      hsi_contact,
      levels = c("Yes", "No", "Don't know", "Refused")
    )
  )
```

```{r}
dim(socdem) # 600  55
```

# Write to CSV
```{r}
write_csv(socdem, "../data/socdem_factor.csv")
```
