

# Load packages

```{r, warning=FALSE, echo=FALSE, output = FALSE}
library(flextable)
library(table1)
library(dplyr)
library(tibble)
library(officer)
library(tidyverse)
library(here)
library(purrr, include.only = "reduce")
library(ggplot2)
library(mice)
library(reshape2, include.only = "melt")
```


# Load cleaned data and custom functions

Load the general health and participant datasets

```{r}
#| warning: false
general_health <- readRDS(
  here("data", "cleaned_rds_files", "general_health_import.rds"))

participant <- readRDS(
  here("data", "unique_id_creation", "participant_unique_id.rds"))

soc_dem <- readRDS(
  here("data", "cleaned_rds_files", "sociodemographic_information_import.rds"))  

self_report <- readRDS(
  here("data", "cleaned_rds_files", "self_report_import.rds")) 

sr_aggregate <- readRDS(
  here::here("data", "self_report_aggregate_data.rds"))

aps <- readRDS(
  here("data", "cleaned_rds_files", "aps_investigations_import.rds"))   

lpa <- readRDS(
  here("data", "cleaned_rds_files", "lead_panel_assessment_import.rds")) 

# Function for analyzing LEAD Panel Assessment data
source(here::here("r","lead_positive_votes_analysis.R"))

# Functions for summarizing missingness patterns
source(here::here("r", "missingness_pattern.R"))
source(here::here("r", "missingness_summary.R"))
```


```{r}
# Variable labels
all_labels <- read.csv(
  here::here("exploratory", "ucla_loneliness_scale", "ucla_variable_labels.csv"))
```


# Data Preparation

Select the relevant data and convert it to an analysis-ready format.

## Participant

  - The unique ID variable is useful for identifying individual participants.
  - The sociodemographic data set has missing values for sex and age so the corresponding variables in the participant data set will be used instead.
  
```{r}
# Select ID variables from the participant unique id data set.
part_id <- participant %>% select(unique_id, medstar_id)

# Select age and sex variables from the dataset
part_age_sex <- participant %>% select(medstar_id, sex_2cat_f, age)
```

## General Health
 
### UCLA 3-Item Loneliness Scale

#### Missingness Patterns

```{r}
# Create lists of loneliness scale variables
ls_vars <- c("ls_lack_companionship", "ls_feel_left_out", "ls_feel_isolated")

ls_vars_cat <- c("ls_lack_companionship_3cat", "ls_feel_left_out_3cat", 
             "ls_feel_isolated_3cat")

ls_vars_cat_f <- c("ls_lack_companionship_3cat_f", "ls_feel_left_out_3cat_f", 
             "ls_feel_isolated_3cat_f")
```

```{r}
ls <- general_health %>% 
  # Select loneliness scale factor variables and drop rows with missing values
  select(
    medstar_id, x_created_timestamp, starts_with("ls_")
  ) 
```

```{r}
ls_mp <- missing_pattern(ls, ls_vars_cat_f, all_labels)
ls_mp
```

```{r}
ls_ms <- missing_summary(ls, ls_vars_cat_f, all_labels)
ls_ms
```

#### Determine when we started collecting the loneliness scale data

Anything before this point is not actually missing.

```{r}
ls_start_df <- general_health %>% select(medstar_id, x_created_timestamp, 
                                         all_of(ls_vars_cat_f)) %>%
  arrange(x_created_timestamp) 

ls_start <- ls_start_df %>%
  summarise(
  medstar_id = medstar_id[min(which(if_all(
    .cols = all_of(ls_vars_cat_f),
    .fns = ~!is.na(.x)
  )))],
  ls_start = as.Date.POSIXct(x_created_timestamp)[min(which(if_all(
    .cols = all_of(ls_vars_cat_f),
    .fns = ~!is.na(.x)
  )))]
  )

ls_start_date <- ls_start[[2]]
ls_start_id <- ls_start[[1]]

cat("The first non-NA value for the loneliness scale variables was collected on:",
    as.character(ls_start_date), 
    "\nThe corresponding MedStar ID is:", ls_start_id)
```

Missingness pattern when all dates before start date are ignored

```{r}
ls_collected <- ls_start_df %>% filter(x_created_timestamp >= ls_start_date)
```

```{r}
ls_collected_mp <- missing_pattern(ls_collected, ls_vars_cat_f, all_labels)
ls_collected_mp
```

```{r}
ls_collected_ms <- missing_summary(ls_collected, ls_vars_cat_f, all_labels)
ls_collected_ms
```

```{r}
ls <- ls %>%
  # Drop rows where loneliness scale variable values are missing
  drop_na(all_of(ls_vars_cat_f)) %>%
  # Create total score and loneliness determination variables
  mutate(
    ls_total = ls_lack_companionship_3cat + ls_feel_left_out_3cat + 
                   ls_feel_isolated_3cat
  ) %>% select(-c(all_of(ls_vars_cat), all_of(ls_vars)))

# Merge the Unique ID variable to the UCLA variables
ls <- right_join(part_id, ls, by = "medstar_id") 
```

#### Unique people count

Create table with counts of unique names and number of names that occur once or more than once excluding rows with missing data.

```{r, warning = FALSE}
# Unique people count
unique_people <- ls %>%
  select(unique_id, medstar_id) %>%
  group_by(unique_id) %>%
  summarise( unique_id, medstar_id,
    count = n()) %>%
  ungroup() %>%
  select(-c(medstar_id)) %>% distinct()
  
# List of people whose names occur in only one row with complete ls scale data
ucs <- unique_people %>% filter(count == 1)

# People whose names occur in more than one row with complete ls scale data and 
# the number of occurrences
nucs <- unique_people %>% filter(count > 1)

# Unique MedStar IDs
unique_m_id <- ls %>% select(medstar_id) %>% unique()

# Table summarizing counts of unique names and number of names that occur once or more than once excluding rows with missing loneliness scale data

sum_table <- data.frame(
  Value = c("Unique people", "People with multiple MedStar IDs", 
            "People with only one MedStar ID", "Total unique MedStar IDs"),
  Count = c(nrow(unique_people), nrow(nucs), nrow(ucs), nrow(unique_m_id))
) %>%
  flextable()
# Set caption

sum_table <- set_caption(sum_table, "Unique and Non-unique Name Counts")
sum_table <- width(sum_table, j = c(1,2), width = c(3,1))

sum_table
```

#### Filter first assessment for each unique person rows

```{r}
first_ucla_unique_id <- ls %>% group_by(unique_id) %>%
  arrange(as.POSIXct(x_created_timestamp), .by_group = TRUE) %>%
  mutate(
    visit_no = row_number()
  ) %>% filter(visit_no == 1) %>%
  ungroup() %>%
  select(unique_id, medstar_id, all_of(ls_vars_cat_f), ls_total)

first_ucla <- first_ucla_unique_id %>% select(-c(unique_id))
```

#### Variable Selection and Calculation

```{r}
quintile_ls <- quantile(first_ucla$ls_total, prob=c(0.2,0.4,0.6,0.8, 1), type=1)

ls_plot <- ggplot(first_ucla, aes(ls_total)) +
  geom_histogram(binwidth = 1) +
  xlab("3-Item UCLA Loneliness Scale Score Total") +
  geom_vline(aes(xintercept = quintile_ls[4])) +
  geom_text(aes(x = quintile_ls[4], label = "\n4th quintile", y = 100), colour="blue", angle=90) +
  theme(legend.position="none")

ls_plot 
```

### PEG 3-Item Pain Assessment

```{r}
peg_vars <- c("peg_pain_11cat", "peg_enjoyment_11cat", "peg_activity_11cat")

peg <- general_health %>% 
  # Select relevant variables.
  select(medstar_id, all_of(peg_vars)) %>%
  mutate(
    peg_total = round((peg_pain_11cat + peg_enjoyment_11cat + 
                     peg_activity_11cat)/3, digits = 2)
  )
ls_peg <- first_ucla %>% left_join(peg, by = "medstar_id")
```

### Geriatric Depression Scale

Select geriatric depression scale variables and create a total score variable.
    
```{r}
gds <- general_health %>% 
  # Select relevant variables.
  select(c(medstar_id, starts_with("depres") & ends_with("_2cat"))) %>%
  mutate(
    across(
      .cols = c("depres_satisfied_2cat", "depres_spirits_2cat", 
                "depres_happy_2cat", "depres_alive_2cat", "depres_energy_2cat"),
      .fns = ~ ifelse(.x == 1, 0, 1)
    ),
    gds_total = depres_satisfied_2cat + depres_hopeless_2cat + 
      depres_better_2cat + depres_activities_2cat + depres_empty_2cat + 
      depres_bored_2cat + depres_spirits_2cat + depres_afraid_2cat + 
      depres_happy_2cat + depres_helpless_2cat + depres_home_2cat + 
      depres_memory_2cat + depres_alive_2cat + depres_worthless_2cat + 
      depres_energy_2cat
  )
             
                                          
ls_gds <- first_ucla %>% left_join(gds, by = "medstar_id")
```

### MO-11 to MO_16 of the medical outcomes study

Select the MO-11 to MO_16 of the medical outcomes study variables. 

```{r}
mos <- general_health %>% 
  # Select relevant variables.
  select(c(medstar_id, outcomes_month_social_5cat, 
           outcomes_month_nervous_5cat, outcomes_month_calm_5cat, 
           outcomes_month_blue_5cat, outcomes_month_happy_5cat, 
           outcomes_month_blue_5cat))

ls_mos <- first_ucla %>% left_join(mos, by = "medstar_id")
```

### 3-item AUDIT-C scale

Select the alcohol use disorders variables.

```{r}
aud_vars <- c("auditc_drink_5cat", "auditc_day_5cat", "auditc_five_5cat")

aud <- general_health %>% 
  # Select relevant variables.
  select(medstar_id, all_of(aud_vars)) %>%
  mutate(
    aud_total = auditc_drink_5cat + auditc_day_5cat + auditc_five_5cat
  )
ls_aud <- first_ucla %>% left_join(aud, by = "medstar_id")
```

### Past Year MedStar Visits

Visits that occurred during the  365 days prior to the first UCLA LS assessment

```{r}
py_ms_visits <- participant %>%
  # Select relevant variables
  select(unique_id, medstar_id, x_created_timestamp) %>% 
  # Filter to only people included in the UCLA LS analysis
  filter(unique_id %in% first_ucla_unique_id$unique_id) %>%
  # Filter to visits within a year prior to UCLA assessment
  mutate(
    # Indicate the visit with the first UCLA LS assessment for each person
    ucla_ls_visit = case_when(
        medstar_id %in% first_ucla_unique_id$medstar_id ~ 1,
      TRUE ~ 0
    )
  ) %>%
  # Create a column with the time stamp for the visit with the first UCLA LS assessment
  group_by(unique_id) %>%
  mutate(
    ucla_ls_timestamp = as.POSIXct(max(
      case_when(
        ucla_ls_visit == 1 ~ x_created_timestamp,
        TRUE ~ NA
        ),
      na.rm = TRUE
      )
      )
    ) %>% ungroup() %>%
  # Indicate past year visits for each person
  mutate(
    before_assessment = case_when(
      (as.Date(ucla_ls_timestamp) - as.Date(x_created_timestamp) < 365) &
      as.Date(ucla_ls_timestamp) - as.Date(x_created_timestamp) > 0 ~ 1,
      TRUE ~ 0
      )
    ) %>%
  group_by(unique_id) %>%
  mutate(
    total_py_visits = sum(before_assessment)
  ) %>% ungroup()
```

```{r}
py_ms_visits_count <- py_ms_visits %>% 
  filter(ucla_ls_visit == 1) %>%
  select(medstar_id, total_py_visits) 

ls_py_ms_visits <- first_ucla %>% left_join(py_ms_visits_count, 
                                            by = "medstar_id")
```

## Sociodemographic Information

sode_sexual and sode_uwanted were remove due to higher numbers of missing values.

```{r}
socio_dem <- soc_dem %>% select(medstar_id, sode_race_eth_4cat, 
                              sogi_orientation_6cat, sode_marital_6cat, 
                              sode_people_9cat, sode_school_7cat,
                              sode_employed_9cat, sode_income_7cat, 
                              sode_military_2cat) %>%
  # Take more complete sex and age variables from participant dataset
  left_join(part_age_sex, by = "medstar_id")

ls_sd <- first_ucla %>% left_join(socio_dem, by = "medstar_id")
```

## Self Report

```{r}
sr_ag <- sr_aggregate %>% select(-c(ends_with("_2cat_f"), unique_id))
ls_sr <- first_ucla %>% left_join(sr_ag, by = "medstar_id")
```


# Missing Data Summaries for Other Variables

## PEG 3-Item Pain Assessment

```{r}
peg_mp <- missing_pattern(ls_peg, peg_vars, all_labels)

peg_mp
```


```{r}
peg_ms <- missing_summary(ls_peg, peg_vars, all_labels)

peg_ms
```

## Geriatric depression scale

```{r}
gds_vars <- ls_gds %>% ungroup() %>% 
  select(starts_with("depres_") & ends_with("_2cat"), 
         gds_total) %>% names()

gds_mp <- missing_pattern(ls_gds, gds_vars, all_labels)
gds_mp
```

```{r}
gds_ms <- missing_summary(ls_gds, gds_vars, all_labels)
gds_ms
```

## MO-11 to MO_16 of the medical outcomes study

```{r}
mos_vars <- ls_mos %>% ungroup() %>% select(starts_with("outcomes_")) %>% names()

mos_mp <- missing_pattern(ls_mos, mos_vars, all_labels)
mos_mp
```

```{r}
mos_ms <- missing_summary(ls_mos, mos_vars, all_labels)
mos_ms
```

## Past Year MedStar Visits

```{r}
py_ms_visits_mp <- missing_pattern(ls_py_ms_visits, "total_py_visits", 
                                   all_labels)

py_ms_visits_mp
```

```{r}
py_ms_visits_ms <- missing_summary(ls_py_ms_visits, "total_py_visits", 
                                   all_labels)

py_ms_visits_ms
```


## 3-item AUDIT-C scale

```{r}
aud_vars <- ls_aud %>% ungroup() %>% select(starts_with("aud")) %>% names()

aud_mp <- missing_pattern(ls_aud, aud_vars, all_labels)
aud_mp
```

```{r}
aud_ms <- missing_summary(ls_aud, aud_vars, all_labels)
aud_ms
```

## Sociodemographic Information

```{r}
sd_vars <- ls_sd %>% ungroup() %>% select(starts_with("sode"), starts_with("sex"), 
                                       starts_with("age"), starts_with("sogi")
                                       ) %>% names()

sd_mp <- missing_pattern(ls_sd, sd_vars, all_labels)
sd_mp
```

```{r}
sd_ms <- missing_summary(ls_sd, sd_vars, all_labels)
sd_ms
```

## Self Report

```{r}
sr_vars <- ls_sr %>% ungroup() %>% 
  select(-c("medstar_id", starts_with("ls_"))) %>% 
  names()

sr_mp <- missing_pattern(ls_sr, sr_vars, all_labels)
sr_mp
```

```{r}
sr_ms <- missing_summary(ls_sr, sr_vars, all_labels)
sr_ms
```

## All Variables

```{r}
ls_peg_all <- ls_peg %>% select(medstar_id, peg_total)
ls_gds_all <- ls_gds %>% select(medstar_id, gds_total)
ls_mos_all <- ls_mos %>% select(medstar_id, starts_with("outcomes_"))
ls_aud_all <- ls_aud %>% select(medstar_id, aud_total)
ls_sd_all <- ls_sd %>% 
  select(-c(starts_with("ls_")))
ls_sr_all <- ls_sr %>% 
  select(-c(starts_with("ls_")))

all <- list(first_ucla, ls_peg_all, ls_gds_all, ls_mos_all, ls_aud_all, 
            ls_sd_all, ls_sr_all, py_ms_visits_count) %>% 
  reduce(left_join, by = "medstar_id")
```

```{r}
all_vars <- all %>% ungroup() %>% 
  select(-c(medstar_id)) %>% names()

all_mp <- missing_pattern(all, all_vars, all_labels)
all_mp
```

```{r}
all_ms <- missing_summary(all, all_vars, all_labels)
all_ms
```

Due to the large number of missing values (above 20% of total), the following variables will be dropped:
- AUDIT-C variables
- Any past month abuse

To prevent issues in missingness imputation arising from colinearity <https://stackoverflow.com/questions/58831710/mice-glm-fit-algorithm-did-not-converge>, the 
following self report variables will also be dropped

  - ever_phys_2cat             
  - ever_sex_2cat  
  - ever_emo_2cat              
  - ever_fin_2cat              
  - neglect_bills_pot_2cat     
  - neglect_clean_pot_2cat    
  - neglect_food_pot_2cat      
  - neglect_go_pot_2cat        
  - neglect_house_pot_2cat     
  - neglect_ready_pot_2cat 
  - any_pot_neglect_2cat       
  - over_65_phys_2cat          
  - over_65_sex_2cat           
  - over_65_emo_2cat  
  - over_65_fin_2cat           
  - pm_phys_2cat               
  - pm_sex_2cat                
  - pm_emo_2cat
  - pm_fin_2cat                
  - ever_abuse_any_2cat  
  
```{r}
all_new <- all %>% select(-c(aud_total, pm_abuse_any_2cat)) %>% 
  select(-c(ever_phys_2cat, ever_sex_2cat, ever_emo_2cat, ever_fin_2cat,
            neglect_bills_pot_2cat, neglect_clean_pot_2cat, 
            neglect_food_pot_2cat, neglect_go_pot_2cat, 
            neglect_house_pot_2cat, neglect_ready_pot_2cat, 
            any_pot_neglect_2cat, over_65_phys_2cat, over_65_sex_2cat,
            over_65_emo_2cat, over_65_fin_2cat, pm_phys_2cat, 
            pm_sex_2cat, pm_emo_2cat, pm_fin_2cat, ever_abuse_any_2cat))

all_vars <- all_new %>% ungroup() %>% 
  select(-c(medstar_id)) %>% names()

all_mp <- missing_pattern(all_new, all_vars, all_labels)
all_mp
```

```{r}
all_ms <- missing_summary(all_new, all_vars, all_labels)
all_ms
```


# Missingness Imputation

```{r}
mice_out <- mice(all_new, m = 5, seed = 11, maxit = 50)
```

```{r, eval =FALSE}
png(filename = here::here("exploratory", "ucla_loneliness_scale",
                          "mice_output_density_plot.png"), 
    type="cairo",
    units="in", 
    width=5, 
    height=4, 
    pointsize=12, 
    res=300)

mice::densityplot(mice_out)
dev.off()
```

# Save the data

## All predictor variables before mice

```{r}
saveRDS(all, here::here("data", "ucla_ls_scale_predictors.rds"))
```

## mice output

```{r}
path <- here::here("data", "ucla_ls_scale_mice_output.RData")
save(mice_out,
     file = path)
```


# Create Word Document

```{r, eval=FALSE}
# Open word file as an object
ucla_doc <- read_docx(here::here("exploratory", "officer_template.docx"))

ucla_doc <- ucla_doc %>%
  # Add UCLA ls
  body_add_par("UCLA Loneliness Scale Analysis", style = "Title") %>%
  body_add_par("UCLA 3-Item Loneliness Scale Data", style = "heading 1") %>%
  body_add_gg(ls_plot, height = 4.09, width = 4.91) %>%
  body_add_par("Missing Data Summary", style = "heading 2") %>%
  body_add_flextable(ls_ms, align = "left") %>%
  body_add_par(value = "") %>%
  body_add_par("Missing Data Summary Excluding Period before Loneliness Scale 
               Data was Collected", 
               style = "heading 2") %>%
  body_add_par("Loneliness Scale data was not collected from the beginning of the study. The first date when not all the loneliness scale variables were missing was 2022-01-17. The corresponding MedStar ID was 'f561525ec4f94a17af7ba3e2c12fee0f'. Data for dates prior to 2022-01-17 were filtered out.", 
               style = "Normal") %>%
  body_add_flextable(ls_collected_ms, align = "left") %>%
  body_add_par(value = "") %>%
  body_add_par("Unique Patient Counts Summary", style = "heading 2") %>%
  body_add_flextable(sum_table, align = "left") %>%
  body_add_par(value = "") %>%
  
  # Add other data variables
  body_add_par("Predictor variables", style = "heading 1") %>%
  
  # Sociodemographic Information
  body_add_par("Sociodemographic Information", style = "heading 2") %>%
  body_add_par("Missing Data Summary", style = "heading 3") %>%
  body_add_flextable(sd_ms, align = "left") %>%
  body_add_par(value = "") %>%
  
  # PEG 
  body_add_par("PEG 3-Item Pain Assessment", style = "heading 2") %>%
  body_add_par("Missing Data Summary", style = "heading 3") %>%
  body_add_flextable(peg_ms, align = "left") %>%
  body_add_par(value = "") %>%
  
  # GDS
  body_add_par("Geriatric Depression Scale", style = "heading 2") %>%
  body_add_par("Missing Data Summary", style = "heading 3") %>%
  body_add_flextable(gds_ms, align = "left") %>%
  body_add_par(value = "") %>%
  
  # MOS
  body_add_par("Medical Outcomes Study", style = "heading 2") %>%
  body_add_par("Missing Data Summary", style = "heading 3") %>%
  body_add_flextable(mos_ms, align = "left") %>% 
  body_add_par(value = "") %>%
  
  # AUDIT-C
  body_add_par("AUDIT-C Scale", style = "heading 2") %>%
  body_add_par("Missing Data Summary", style = "heading 3") %>%
  body_add_flextable(aud_ms, align = "left") %>%
  body_add_par(value = "") %>%
  
  # Self Report
  body_add_par("Self Report", style = "heading 2") %>%
  body_add_par("Missing Data Summary", style = "heading 3") %>%
  body_add_flextable(sr_ms, align = "left") %>%
  body_add_par(value = "") %>%

  # Model Variables
  body_add_par("All Variables", style = "heading 1") %>%
  body_add_flextable(all_ms, align = "left") %>%
  body_add_par(value = "") %>%
  
  # Mice output density plots
  body_add_par("MICE Package Missingness Imputation Output", 
               style = "heading 1") %>%
  body_add_par("Below are density plots for the output of the MICE missingness imputation. Variables with 1 or less missing values in the original data do not have density plots.", 
               style = "Normal")
  # body_add_img(src = here::here("exploratory", "mice_output_density_plot.png"),
  #              width = 5, height = 4)


# print the word document
print(ucla_doc, 
      target = here::here("exploratory", "ucla_loneliness_scale", 
                          "UCLA_loneliness_scale_missingness_summary.docx"))
```
