---
title: "Within-Set APS Chunk Cleaning"
html:
  embed-resources: true
format: html
---

# ⭐️ Overview

## APS Data Background

The APS records data set was divided into 5 separate, interconnected excel files. These files are documented in the [wiki](https://github.com/brad-cannell/detect_fu_interviews_public/wiki). The primary file of interest for subject-level linkage is the "Clients.xlsx" file. This file contained 568,562 observations of 11 variables, including 378,418 values for `client_id`. 

This APS data file was cleaned/prepped for processing prior to fuzzy-matching in [a separate Quarto file](https://github.com/brad-cannell/detect_fu_interviews_public/blob/main/data_management/unique_person_identification/data_unique_person_01_within_set_aps.qmd). Due to the significantly large size of the data (568,616 rows and 23 columns) the data had to be divided into 7 chunks for within-set fuzzy matching secondary to hardware limitations. This was performed in [a separate Quarto file](https://github.com/brad-cannell/detect_fu_interviews_public/blob/main/data_management/unique_person_identification/data_unique_person_01_aps_02_fl_chunk_generation.qmd).

## This File

This file performs the manual verification and cleaning of pairs generated within the individual chunks, in preparation for later iterative between-chunk matching and cleaning to re-unify and comprehensively assess/clean the data set for unique subject identification.

## Internal Files

This document was created as part of the DETECT project, specifically the merger of APS and MedStar data for analysis using the full follow-up period data. Internal documents relating to these files, which contain PHI, are securely stored on the research group's SharePoint in the [task notes folder](https://uthtmc.sharepoint.com/:f:/r/sites/SPHDETECT-RPC/Shared Documents/DETECT R01 2018/02 Shared Folders/DETECT Follow-up Interview Data Shared/data/notes_documents?csf=1&web=1&e=gLWUzJ). 

It is recommended that anyone orienting to the task start at the primary task notes document, which provides a high-level overview of the task data, parameters, and process: [notes_01_task_01_00_merging aps and medstar.docx](https://uthtmc.sharepoint.com/:w:/r/sites/SPHDETECT-RPC/Shared Documents/DETECT R01 2018/02 Shared Folders/DETECT Follow-up Interview Data Shared/data/notes_documents/notes_01_task_01_00_merging aps and medstar task.docx?d=w542529e69bd2411da7a2d7efe56269a5&csf=1&web=1&e=8ZF6Rg).

Notes for the APS data are located in the [notes_00_data_aps.docx](https://uthtmc.sharepoint.com/:w:/r/sites/SPHDETECT-RPC/Shared Documents/DETECT R01 2018/02 Shared Folders/DETECT Follow-up Interview Data Shared/data/notes_documents/notes_00_data_aps.docx?d=w854dec51d8b049bdab8b0018f3d4bfff&csf=1&web=1&e=DKCWsI) file. Notes relating to this specific step of processing are in the [notes_01_task_01_02_aps fuzzy matching task notes.docx](https://uthtmc.sharepoint.com/:w:/r/sites/SPHDETECT-RPC/Shared Documents/DETECT R01 2018/02 Shared Folders/DETECT Follow-up Interview Data Shared/data/notes_documents/notes_01_task_01_02_aps fuzzy matching task notes.docx?d=w81b2211a8d204ae5bc0021ac95c11c4e&csf=1&web=1&e=hgbwPk) file.

Please note: as these files contain PHI and proprietary information, they are not publicly available. Links are internal to the research team.

# Summary

-   Chunk 1 was formed from 167,916 rows (44.35%  of the APS data set). Processing created 164,291 unique subject IDs.

    -   60 of the 1,988 pairs (3.02%) in the posterior probability range of 0.20-0.70 were kept after review.
    
    -   49 of the 589 pairs (3.32%) in the posterior probability range of 0.70-0.90 were kept after review.
    
    -   3,750 of the 3,964 pairs (94.60%) in the posterior probability range of 0.90-1.00 were kept after review.
    
    -    95 APS rows, across 89 IDs, reflected APS rows in more than one ID value.
    
    -    59 IDs were dropped in consolidation. 1 ID was created.
    
-   Chunk 2 was formed from 167,827 rows (44.33%  of the APS data set). Processing created 164,495 unique subject IDs.

    -   59 of the 1,937 pairs (3.05%) in the posterior probability range of 0.20-0.70 were kept after review.
    
    -   56 of the 631 pairs (8.87%) in the posterior probability range of 0.70-0.90 were kept after review.
    
    -   3,368 of the 3,976 pairs (84.71%) in the posterior probability range of 0.90-1.00 were kept after review.
    
    -    38 APS rows, across 36 IDs, reflected APS rows in more than one ID value.
    
    -    25 IDs were dropped in consolidation. 
    
-   Chunk 3 was formed from 1,377 rows (0.36%  of the APS data set) which had missingness in name fields. Processing created 1,341 unique subject IDs.

    -   49 of the 400 non-self-to-self pairs (12.25%) were kept.
    
    -   No rows were in more than one ID value. All 62 rows, across 27 IDs, which were in IDs with more than one row were confirmed to be likely true matches after manual review. 
    
    -   1 ID was corrected for a `client_id`-based failed match.
    
-   Chunk 4 was formed from 12,359 rows (3.26%  of the APS data set) which had missingness in address fields. Processing created 12,136 unique subject IDs.

    -   245 of the 301 non-self-to-self pairs (81.67%) were kept.
    
    -   1 row was in more than 3 ID values, which was corrected. 
    
    -   All 37 rows across 11 IDs, which were in IDs with more than one `client_id` were confirmed to be likely true matches after manual review. All 420 rows across 202 ID values which represented ID values with more than one APS row were confirmed to be likely true matches after manual review.

-   Chunk 5 was formed from 28 rows (0.01%  of the APS data set) which had missingness in date of birth values. Processing created 28 unique subject IDs (all self-matches).

-   Chunk 6 was formed from 549 rows (0.15%  of the APS data set) which had missingness in more than one, but not all, identifier fields. Processing created 549 unique subject IDs (all self-matches).

-   As Chunk 7 consisted of rows without any identifier values, no processing was performed on these remaining rows.

## Assumptions and Considerations

-   Typographical errors may occur in any field, but are less likely to occur consistently

-   Common First and Last Names are more likely to result in accidental mismatches

    -   Hispanic naming conventions, which may include multiple family names and many relatively common names, may increase the probability these names are either mismatched or fail to match

-   Names

    -   First names may include nicknames or a middle name that the subject "goes by" in some observations, but their legal first name in others

        -   As twins are unlikely, individuals that identical other than First Name are likely to refer to the same person

    -   Individuals with hyphenated Last Names may go by either or both names

        -   More likely in Female patients, due to name change conventions around marriage in the U.S.A.

            -   The ability to keep a maiden name, hyphenate, or take a new last name [was not codified in the U.S.A until the 1980s](https://scholarship.law.wm.edu/wmjowl/vol17/iss1/6/), and as such is comparatively more common in younger women

            -   [Informal polls have found that today, approximately 10% of women chose to hyphenate and 20% keep their maiden name in full.](https://time.com/3939688/maiden-names-married-women-report/) These rates are likely lower in older populations.

        -   Men are both less likely to change their name at all based on name change conventions in the U.S.A, but also [face greater legal barriers in some states to obtaining name change on marriage](https://heinonline.org/HOL/LandingPage?handle=hein.journals/tclj24&div=10&id=&page=)

    -   Two individuals with the First and Last Name at the same Address, but with birth dates greater than 12 years apart may potentially be parent and child using a Junior/Senior naming conventionpe

        -   More likely in Male patients, due to naming conventions in the US

        -   Birth Date considerations relating to the possibility of JR/SR relationships or other familial pairing apply

-   Birth Dates

    -   Slight differences in any one Birth Date value is likely to be a data entry error if all other fields are either identical or significantly similar

    -   Month and Date values are most likely to be transposed in data entry errors

-   Address

    -   Address values may have been entered as a temporary location or the location where the reporter encountered the subject, rather than the subject's residential or mailing address

    -   There are multiple multi-residence facilities, such as apartment complexes and healthcare facilities represented in the data - these addresses should be weighed less heavily as identifiers for differentiation

    -   Individuals may move or be at a temporary location in an encounter

        -   Healthcare facilities, homeless shelters, and businesses should be considered indicators that the patient's address should be weighed less heavily as an identifier

        -   Multiple observations that appear to "alternate" between addresses are less likely to refer to the same individual

        -   Reported addresses may not be accurate, if the reporter was either misinformed, misremembered, or guessed at the subject's residential location - if addresses are within 0.5 miles of each other, or otherwise appear sufficiently close on a map that a GPS error may have occurred, consideration should be given that it was an error rather than a truly different value

-   Judgement should err on the side of separating observations if doubt exists that they refer to the same person

# 📦 Load Packages and Functions

## Library Imports

```{r, warning = FALSE}
suppressPackageStartupMessages({
  library(tidyverse)
  library(here)
  library(fastLink)
  library(janitor, include.only = "clean_names")
})
```

### Versioning

This file was created with:

-   R version 4.4.1 ("Race for Your Life").
-   tidyverse version 2.0.0, including all attached packages
-   here version 1.0.1
-   fastLink version 0.6.1
-   janitor version 2.2.0

## Functions

```{r}
# Function to reduce code repetition in informative imports of data
source(here::here("r", "informative_df_import.R"))

# Function that creates a modified version of table output, allowing
# simplified manual review of unique values in a given column or set of
# columns
source(here::here("r", "get_unique_value_summary.R"))

# Function that facilitates using fastlink to match a single data set
# without limiting the returned data
source(here::here("r", "single_df_fastlink.R"))
       
# Function that generates stacked pairs of the original data based on
# fastLink's probabilistic matching
source(here::here("r", "get_pair_data.R"))

# Function that adds a potential Unique Subject ID to pairs
source(here::here("r", "stack_ids.R"))
```

# 📥 Load Data

## APS Identifier Data for Chunking

APS client data was originally in XLSX format. It had been cleaned and exported to an RDS file with 568,616 rows and 23 columns. The data was further modified by reducing to 378,604 unique combinations and the addition of flags in the fastLink process.

```{r}
aps_path <- here::here(
  "data","cleaned_rds_files", "record_linkage", "aps", 
  "aps_01_prepped_for_fl.rds"
  )

informative_df_import(
    "aps", aps_path, overwrite = T
  )

 # 2025-01-08: APS data imported with 378,604 rows and 26 columns.
 # Data last modified on OneDrive: 2024-11-13 11:46:12  
```

## APS Chunk fastLink Outputs

Due to the size of the APS data, fastLink within-set fuzzy matching required "chunking" the data into 5 subsets. Observations within the APS data were randomly assigned a subset.

```{r, warning = F}
purrr::walk(
  .x = c(1:6),
  .f = function(x) {
    informative_df_import(
      paste0("aps_chunk_", x), 
      paste0(
        here::here("data","cleaned_rds_files", "record_linkage", "aps"), 
        "/aps_01_fl_chunk_",
        x, 
        ".rds"
        ), overwrite = T
      ) 
  }
)

 # 2025-01-08: APS CHUNK 1 data imported with NULL rows and NULL columns.
 # Data last modified on OneDrive: 2024-11-12 20:13:17 
 # 
 # 2025-01-08: APS CHUNK 2 data imported with NULL rows and NULL columns.
 # Data last modified on OneDrive: 2024-11-12 21:58:02 
 # 
 # 2025-01-08: APS CHUNK 3 data imported with NULL rows and NULL columns.
 # Data last modified on OneDrive: 2024-11-13 11:34:38 
 # 
 # 2025-01-08: APS CHUNK 4 data imported with NULL rows and NULL columns.
 # Data last modified on OneDrive: 2024-11-13 11:35:34 
 # 
 # 2025-01-08: APS CHUNK 5 data imported with NULL rows and NULL columns.
 # Data last modified on OneDrive: 2024-11-13 11:36:51 
 # 
 # 2025-01-08: APS CHUNK 6 data imported with NULL rows and NULL columns.
 # Data last modified on OneDrive: 2024-11-13 11:43:10 
```

# Constants

We named our constants: the variables utilized for fuzzy matching, the manual verification posterior probability range (0.20 - 0.70), the names of all gamma columns, and which variables we wished to include in our side-by-side pair data sets.

```{r}
## Fuzzy-Matching Variables
str_vars <- c(
  "client_first_name", "client_last_name", "client_street_address"
  )
num_vars <- c(
  "client_dob_year", "client_dob_month", "client_dob_day", "client_zip_code"
  )

match_vars <- c(str_vars, num_vars)

## Gamma column names
gamma_cols <- paste(match_vars, "gamma", sep = "_")

## Manual review posterior probability range
posteriors = c(0.20, 0.70)

## Defining Packed Identifiers to review for pairs
pack_id_vars <- c(
  'aps_row', match_vars, 'client_id', 'client_notes',
  'flag_unresolvable', 'flag_mult_clients', 'flag_issues'
  )

pack_id_vars <- c(pack_id_vars, setdiff(pack_id_vars, colnames(aps)))


rm(str_vars)
rm(num_vars)
```

# Cleaning of Chunks

## Chunk 1

We converted our first chunk into our desired stacked pair data.

```{r}
# Get APS subset for this chunk
subset <- aps |>
  dplyr::filter(chunks == 1)

subset_pack <- list()
subset_pack$df <- subset
subset_pack$suffix <- 'aps_1'
subset_pack$ids <- pack_id_vars

aps_chunk_1_pairs <- get_pair_data(
  subset_pack, subset_pack, match_vars, aps_chunk_1
  )

aps_chunk_1_ids <- stack_ids(subset_pack, subset_pack, aps_chunk_1_pairs)
```

### Review of Initial ID Assignments

There were 168,615 observations in the First APS Within-Set Matching Chunk ID set, generated from 167,916 APS observations. There were no pairs were missing values for `aps_row` variables. Additionally, there were no APS observations that were not found in the pair data, likely due to failure to find a match. There were 162,062 unique IDs (1 - 162,062) assigned in this preliminary processing, with no pairs missing an ID assignment.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

# How many observations in the ID set?
format(nrow(aps_chunk_1_ids), big.mark = ',')

# How many rows are in the subset used to generate this chunk?
format(nrow(subset), big.mark = ',')

# Are there any pairs missing a value for row?
format(sum(is.na(aps_chunk_1_ids$aps_row)), big.mark = ',')

# How many rows in the original APS data for this chunk are missing from the
# ID/Pair generated set (likely due to no matches)
format(length(setdiff(
  subset$aps_row, unique(aps_chunk_1_ids$aps_row)
  )), big.mark = ",")

# How many unique IDs were generated?
format(length(unique(aps_chunk_1_ids$id)), big.mark = ',')

# Are there any pairs missing an ID value?
format(sum(is.na(aps_chunk_1_ids$id)), big.mark = ',')

# [1] "168,615"
# [1] "167,916"
# [1] "0"
# [1] "0"
# [1] "162,062"
# [1] "0"
```

### Within Posterior Probability Range

We examined all pairs within the manual review posterior probability range of 0.20 - 0.70. This resulted in manual review of 1,988 pairs.

```{r}
checking <- aps_chunk_1_pairs |>
  dplyr::filter(
    dplyr::between(posterior_probability, posteriors[1], posteriors[2])
    )

format(nrow(checking), big.mark = ',')
# [1] "1,988"
```

We found no pairs within this range demonstrated identical values for `client_id`.

```{r}
format(nrow(
  checking |> 
    dplyr::filter(client_id_a == client_id_b)
  ),
  big.mark = ',')

# [1] "0"
```

In examining our gamma values for our matching variables, we found several trends:

-   The vast majority (1,764) failed to match at all on first name (gamma = 0)
-   The vast majority (1,473) failed to match on birth year (gamma = 0)
-   The vast majority (1,085) failed to match on birth day (gamma = 0)
-   The vast majority (1,389) significantly matched on last name (gamma = 2)
-   The vast majority (1,905) significantly matched on street address (gamma = 2)
-   The vast majority (1,986) significantly matched on zip code (gamma = 2)
-   The vast majority (1,487) significantly matched on birth month (gamma = 2)

```{r, warning = F}
get_unique_value_summary(
  checking |>
    dplyr::select(dplyr::all_of(gamma_cols))
  )
```

We initiated our list of pairs to drop, which we would build during our processing.

```{r}
drop_pairs_c1 <- c()
```


#### Address Failures

##### ZIP Code (Non-Matches)

We first examined pairs with non-matching ZIP Codes (Gamma == 0). The ZIP code values in the rows of these pairs appeared to only differ due to small typos.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- checking |>
  dplyr::filter(client_zip_code_gamma != 2)

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# [1] "2"
# [1] "Min: 0.26486; Max: 0.26486"
```

Both of these pairs were deemed valid. As such, we did not add their values to the drop list.


##### Street Address (Weak Matches)

We examined remaining pairs with weakly matching street address values (Gamma == 1). The street address values of rows in these pairs appeared to primarily consist of minor differences in house number, with the exception of two pairs that also had changes in a numeric street name.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- checking |>
  dplyr::filter(client_street_address_gamma == 1) |>
  # Omit previous check groups
  dplyr::filter(client_zip_code_gamma != 0 )

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# [1] "34"
# [1] "Min: 0.22983; Max: 0.63173"
```

None of the 34 pairs was found to be a true match. As such, we added these 34 pair ids to our drop list.

```{r}
drop_pairs_c1 <- unique(c(drop_pairs_c1, checking_cols$pair))

length(drop_pairs_c1)
# [1] 34
```

##### Street Address (Non-Matches)

We examined remaining pairs with non-matching street address values (Gamma == 0). Many of these pairs appeared to potentially reflect a single subject that had moved to a new location.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- checking |>
  dplyr::filter(client_street_address_gamma == 0) |>
  # Omit previous check groups
  dplyr::filter(client_zip_code_gamma != 0 )

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# [1] "49"
# [1] "Min: 0.57096; Max: 0.66833"
```

There were 27 of the 49 pairs found to be a true match. As such, we added the remaining 22 pair ids to our drop list.

```{r}
keep_pairs <- c(
  10017, 10682, 41833, 72698, 103411, 113730, 113744, 134052, 134950, 144283,
  144284, 134053, 10077, 10563, 20976, 21069, 21216, 31472, 53729, 62436, 
  93332, 93407, 113673, 113753, 134136, 144286, 165974
  )

drop_pairs_c1 <- unique(c(
  drop_pairs_c1, 
  setdiff(checking_cols$pair, keep_pairs)
  ))

length(drop_pairs_c1)
# [1] 56
```

#### Name Failures

##### Last Name (Weak Matches)

We examined remaining pairs with weakly matching last name values (Gamma == 1). Many of the last name values in the rows of pairs in this section appeared to differ primarily due to small typos.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- checking |>
  dplyr::filter(client_last_name_gamma == 1) |>
  # Omit previous check groups
  dplyr::filter(!(
    client_zip_code_gamma == 0 | client_street_address_gamma < 2
    ))

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# [1] "19"
# [1] "Min: 0.36699; Max: 0.56855"
```

There were 11 of the 19 pairs found to be a true match. As such, we added the remaining 8 pair ids to our drop list.

```{r}
keep_pairs <- c(
  41913, 21178, 21203, 24747, 41598, 41607, 52038, 93160, 134079, 137722, 
  144309 
  )

drop_pairs_c1 <- unique(c(
  drop_pairs_c1, 
  setdiff(checking_cols$pair, keep_pairs)
  ))

length(drop_pairs_c1)
# [1] 64
```

##### Last Name (Non Matches)

We examined remaining pairs with non-matching last name values (Gamma == 0). Many of the subjects in the pairs of this section had identical or highly similar addresses. Many were identified to be women who used more than one surname. Of note, there were also several pairs that were found to be valid but had first and last name transposed in data entry.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- checking |>
  dplyr::filter(client_last_name_gamma == 0) |>
  # Omit previous check groups
  dplyr::filter(!(
    client_zip_code_gamma == 0 | client_street_address_gamma < 2
    ))

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# [1] "557"
# [1] "Min: 0.22985; Max: 0.66238"
```

There were 16 of the 557 pairs found to be a true match. As such, we added the remaining 541 pair ids to our drop list.

```{r}
keep_pairs <- c(
  27697, 31443, 41682, 41735, 113771, 10348, 41814, 52015, 146007, 150879, 
  21117, 35818, 52093, 52144, 93149, 144316
  )

drop_pairs_c1 <- unique(c(
  drop_pairs_c1, 
  setdiff(checking_cols$pair, keep_pairs)
  ))

length(drop_pairs_c1)
# [1] 605
```

##### First Name (Weak Matches)

There were no remaining pairs with weak matching first name values (Gamma == 1).

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- checking |>
  dplyr::filter(client_first_name_gamma == 1) |>
  # Omit previous check groups
  dplyr::filter(!(
    client_zip_code_gamma == 0 | client_street_address_gamma < 2 | 
      client_last_name_gamma < 2
    ))

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# [1] "0"
```

##### First Name (Non-Matches)

We examined remaining pairs with non-matching first name values (Gamma == 0).

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- checking |>
  dplyr::filter(client_first_name_gamma == 0) |>
  # Omit previous check groups
  dplyr::filter(!(
    client_zip_code_gamma == 0 | client_street_address_gamma < 2 | 
      client_last_name_gamma < 2
    ))

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# [1] "1,327"
# [1] "Min: 0.45822; Max: 0.63838"
```

There were 4 of the 1,327 pairs found to be a true match. As such, we added the remaining 1,323 pair ids to our drop list.

```{r}
keep_pairs <- c(
  20912, 31233, 31533, 72886 
  )

drop_pairs_c1 <- unique(c(
  drop_pairs_c1, 
  setdiff(checking_cols$pair, keep_pairs)
  ))

format(length(drop_pairs_c1), big.mark = ',')
# [1] "1,928"
```

#### Remaining Pairs

There were no remaining pairs to examine.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- checking |>
  dplyr::filter(client_first_name_gamma == 0) |>
  # Omit previous check groups
  dplyr::filter(!(
    client_zip_code_gamma == 0 | client_street_address_gamma < 2 | 
      client_last_name_gamma < 2 | client_first_name_gamma < 2
    ))

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# [1] "0"
```

We verified that we had a total of 60 pairs kept from this subset.

```{r}
nrow(
  checking |>
    dplyr::filter(!(pair %in% drop_pairs_c1))
  ) == 60
# [1] TRUE
```

### Above posterior probability range

We examined pairs just above our posterior probability range, to ensure appropriate capture. All pairs within the posterior probability range of 0.70 - 0.90 were examined. This resulted in manual review of 589 pairs.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- aps_chunk_1_pairs |>
  dplyr::filter(
    dplyr::between(posterior_probability, posteriors[2], posteriors[2]+0.2)
    )

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# [1] "589"
# [1] "Min: 0.72774; Max: 0.85986"
```

We found no pairs within this range demonstrated identical values for `client_id`.

```{r}
format(nrow(
  checking_cols |> 
    dplyr::filter(client_id_a == client_id_b)
  ),
  big.mark = ',')

# [1] "0"
```

We identified that the majority of pairs above a probability of 0.80 appeared to be true matches, with few exceptions. We added these false matches to our drop list.

```{r}
drop_pairs_c1 <- c(
  drop_pairs_c1, 
  c(46014, 62387, 103513, 113683, 31495)
  )
```

Pairs between 0.70 and 0.80 were primarily false matches, specifically spousal/familial mismatches or subjects with highly similar common name values. We identified the true matches within this range, and added all other pairs to our list of exclusions.

```{r}
drop_pairs_c1 <- c(
  drop_pairs_c1, 
  dplyr::pull(
    checking_cols |>
      dplyr::filter(
        dplyr::between(posterior_probability, 0.70, 0.80)
        ) |>
      dplyr::filter(
        !(pair %in% c(
          10262, 10413, 10496, 10519, 10552, 10603, 10653, 10686, 15353, 
          20843, 20864, 21029, 31288, 31519, 31549, 34923,
          41742, 47321, 52099, 52133, 52154, 52183, 61383, 72596, 72732, 
          72753, 72793, 82999, 83006, 83115, 86981, 93369, 103571, 103589, 
          105844, 113699, 123900, 124000, 134176, 144296, 154376, 155215, 
          155216, 166703
          ))
      ) |>
      dplyr::select(pair)
    )
  )

```

We verified that we had a total of 2,468 pairs excluded from this chunk.

```{r}
nrow(
  aps_chunk_1_pairs |>
    dplyr::filter((pair %in% drop_pairs_c1))
  ) == 2468
# [1] TRUE
```

We lastly gave a cursory examination to pairs with a posterior probability above 0.90, where the pair did not represent a self-match.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- aps_chunk_1_pairs |>
  dplyr::filter(
    posterior_probability > 0.90
    ) |>
  dplyr::filter(aps_row_a != aps_row_b)

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# [1] "3,964"
# [1] "Min: 0.91854; Max: 1"
```

We identified several human-recognizable likely mismatches. We excluded these pairs.

```{r}
drop_pairs_c1 <- c(drop_pairs_c1, c(
  21163, 83003, 10178, 113793, 154411, 97387, 70565, 52251, 56203, 113654, 
  20995, 83043, 21076, 83393, 21155, 31372, 82950, 134041, 144303, 31494, 
  62421, 68914, 21204, 41747, 41929, 52261, 62388, 93289, 103406, 103414, 
  125518, 144205, 144265, 154332, 10003, 10145, 20876, 20940, 21072, 21130, 
  21175, 23019, 31306, 40484, 51455, 62519, 67514, 72771, 78715, 82965, 
  90818, 93296, 93344, 124912, 134073, 153423, 169087, 17291, 95872, 109796,
  123941, 151339, 877, 10119, 10360, 10410, 10578, 10649, 11377, 20878, 
  38612, 41639, 42087, 52066, 52205, 52206, 54657, 62456, 62547, 67460, 
  72966, 73058, 73657, 76911, 77007, 77637, 79346, 82990, 93192, 100835, 
  103422, 103436, 103494, 110053, 113721, 113811, 121201, 123849, 123940, 
  123993, 125964, 126426, 134042, 144247, 144287, 153488, 154746, 171691, 
  172682, 173129, 35897, 62380, 134981, 113667, 48579, 144271, 10337, 20750, 
  20898, 41595, 123914, 62338, 10623, 21109, 134036, 72718, 41594, 41775, 
  93232, 113777, 134116, 164436, 30176, 63087, 113647, 92873, 153943,
  93364, 134898, 72745, 72746, 93208, 32664, 167921, 7463,9024, 10651, 13452, 
  31392, 31595, 144226, 154354, 154355, 2956, 41797, 41839, 51985, 75848, 
  117197, 16889, 93210, 134056, 4369, 10165, 11362, 17907, 19790, 
  20333, 20778, 20996, 31500, 39160, 52568, 60780, 67517, 71539, 72683, 93476,
  103217, 104046, 110631, 118170, 122995, 127618, 138379, 144207, 149352, 
  149364, 157524, 157704, 164081, 164428, 166123, 167516, 169923, 20741, 
  20879, 48158, 52208, 68593, 85225, 103897, 113092, 161571, 38802, 
  134039, 62526, 84856, 72614, 57566, 62308, 10242, 10148, 134132
  ))
```


### Regenerating ID Assignments

We reduced our Chunk 1 pairs, excluding all pairs in the manual verification range that we determined were false matches. We used this reduced set to re-generate ID assignments.

```{r}
aps_chunk_1_pairs <- aps_chunk_1_pairs |>
  dplyr::filter(!(pair %in% drop_pairs_c1))

aps_chunk_1_ids <- stack_ids(subset_pack, subset_pack, aps_chunk_1_pairs)
```

There were 168,049 observations in the First APS Within-Set Matching Chunk ID set, generated from 167,916 APS observations. There were no pairs were missing values for `aps_row` variables. Additionally, there were no APS observations that were not found in the pair data, likely due to failure to find a match. There were 164,340 unique IDs (1 - 164,340) assigned in this preliminary processing, with no pairs missing an ID assignment.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

# How many observations in the ID set?
format(nrow(aps_chunk_1_ids), big.mark = ',')

# How many rows are in the subset used to generate this chunk?
format(nrow(subset), big.mark = ',')

# Are there any pairs missing a value for row?
format(sum(is.na(aps_chunk_1_ids$aps_row)), big.mark = ',')

# How many rows in the original APS data for this chunk are missing from the
# ID/Pair generated set (likely due to no matches)
format(length(setdiff(
  subset$aps_row, unique(aps_chunk_1_ids$aps_row)
  )), big.mark = ",")

# How many unique IDs were generated?
format(length(unique(aps_chunk_1_ids$id)), big.mark = ',')

# Are there any pairs missing an ID value?
format(sum(is.na(aps_chunk_1_ids$id)), big.mark = ',')

# [1] "168,049"
# [1] "167,916"
# [1] "0"
# [1] "0"
# [1] "164,340"
# [1] "0"
```

### Cleaning IDs

#### Row in more than one ID

We identified 95 rows which were paired in more than one ID value.

```{r}
multi_id_rows <- dplyr::pull(
  aps_chunk_1_ids |>
    dplyr::filter(duplicated(aps_row) | duplicated(aps_row, fromLast = T)
    ) |>
    dplyr::select(aps_row) |>
    dplyr::distinct()
)

format(length(unique((multi_id_rows))), big.mark = ',')
# [1] "95"
```

We isolated the 95 rows that were associated with more than one ID assignment, as well as rows associated with one of the 89 ID assignments that included one of these rows. This left us with 228 observations to manually review.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

multi_id_row_ids <- dplyr::pull(
    aps_chunk_1_ids |>
    dplyr::filter(
      aps_row %in% multi_id_rows
      ) |>
    dplyr::select(id)
  )

checking <- aps_chunk_1_ids |>
  dplyr::filter(
    id %in% multi_id_row_ids | aps_row %in% multi_id_rows
    )

# Number of unique rows with more than one ID (same output as last chunk)
format(length(unique(multi_id_rows)), big.mark = ',')

# Number of unique IDs associated with a row that appears in more than one ID
format(length(unique(multi_id_row_ids)), big.mark = ',')

# Number of observations pulled for checking (either a row that appears in
# more than one ID, or a row associated with one of those IDs)
format(nrow(checking), big.mark = ',')
# [1] "95"
# [1] "89"
# [1] "228"
```

After manual review, we identified 59 IDs that could be dropped. One group (419) required manual creation to consolidate two observations together that were not otherwise in an existing ID.

```{r}
dropping_ids <- c(
  419, 50284, 1483, 19612, 2142, 9744, 9854, 29375, 27909, 3917, 33345, 
  6114, 9849, 102605, 106784, 15411, 106925, 52729, 68517, 25566, 
  25567, 39743, 47931, 45749, 145218, 47173, 79569, 48838, 86168, 57625, 
  57628, 63150, 97131, 63901, 63902, 68402, 68403, 107466, 107911, 94413, 
  113822, 94711, 135642, 103612, 135641, 109999, 116416, 114511, 116417, 
  130152, 143104, 5040, 72631, 73973, 92051, 91026, 91027, 95436, 97129
  )

# Drop the listed IDs, and remove the list of rows in the ID
aps_chunk_1_ids <- aps_chunk_1_ids |>
  dplyr::filter(!(id %in% dropping_ids)) |>
  dplyr::select(-match_rows)

# Subset rows that were not previously assigned an ID value
unassigned_rows <- subset_pack$df |>
  dplyr::filter(!(aps_row %in% aps_chunk_1_ids$aps_row))

# Assign from the dropped ID values. Reserve 419 for the manually created
# pair ID
unassigned_rows <- unassigned_rows |>
  dplyr::mutate(
    id = setdiff(
      seq(1,164340),
      c(aps_chunk_1_ids$id, 419)
      )[1:nrow(unassigned_rows)]
  ) |>
  dplyr::mutate(
    id = ifelse(aps_row %in% c(221077, 254321), 419, id)
  )

# Combine the chunk back together
aps_chunk_1_ids <- dplyr::bind_rows(
  aps_chunk_1_ids, unassigned_rows
  )
```

#### Flagged Rows

We identified 204 rows which were flagged for any reason, which included 203 ID values. In total, we isolated 293 observations for manual review.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

flagged_rows <- dplyr::pull(
  aps_chunk_1_ids |>
    dplyr::filter(flag_issues | flag_unresolvable | flag_mult_clients) |>
    dplyr::select(aps_row)
  )

flagged_ids <- dplyr::pull(
  aps_chunk_1_ids |>
    dplyr::filter(
      flag_issues | flag_unresolvable | flag_mult_clients | 
        (aps_row %in% flagged_rows)
      ) |>
    dplyr::select(id)
  )

checking <- aps_chunk_1_ids |>
  dplyr::filter(id %in% flagged_ids)

# Number of flagged rows?
format(length(unique((flagged_rows))), big.mark = ',')

# Number of impacted IDs?
format(length(unique((flagged_ids))), big.mark = ',')

# Total observations to review?
format(nrow(checking), big.mark = ',')

# [1] "204"
# [1] "203"
# [1] "293"
```

No necessary changes were identified from the review. We further checked that our ID assignment did not create more than one ID for a given `client_id`, which would have indicated failed matches. We found none.

```{r}
# No duplicated CLIENTID values?
nrow(
  aps_chunk_1_ids |>
    dplyr::group_by(client_id) |>
    dplyr::summarise(n_ids = dplyr::n_distinct(id)) |>
    dplyr::filter(n_ids > 1)
  ) == 0
# [1] TRUE
```

This concluded the cleaning and examination of Chunk 1.

### 💾 Save and Export Data

We exported this subset of our data.

```{r, eval = F}
saveRDS(
  aps_chunk_1_ids,
  here::here(
    "data", "cleaned_rds_files", "record_linkage", "aps", 
    "aps_02_ids_chunk_1.rds"
    )
)
```

### 🧹 Clean up

```{r}
rm(aps_chunk_1_ids)
rm(aps_chunk_1_pairs)
rm(aps_chunk_1)
rm(drop_pairs_c1)
```

## Chunk 2

We converted our second chunk into our desired stacked pair data.

```{r}
# Get APS subset for this chunk
subset <- aps |>
  dplyr::filter(chunks == 2)

subset_pack <- list()
subset_pack$df <- subset
subset_pack$suffix <- 'aps_2'
subset_pack$ids <- pack_id_vars

aps_chunk_2_pairs <- get_pair_data(
  subset_pack, subset_pack, match_vars, aps_chunk_2
  )

aps_chunk_2_ids <- stack_ids(subset_pack, subset_pack, aps_chunk_2_pairs)
```

### Review of Initial ID Assignments

There were 168,525 observations in the second APS Within-Set Matching Chunk ID set, generated from 167,827 APS observations. There were no pairs were missing values for `aps_row` variables. Additionally, there were no APS observations that were not found in the pair data, likely due to failure to find a match. There were 161,909 unique IDs (1 - 161,909) assigned in this preliminary processing, with no pairs missing an ID assignment.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

# How many observations in the ID set?
format(nrow(aps_chunk_2_ids), big.mark = ',')

# How many rows are in the subset used to generate this chunk?
format(nrow(subset), big.mark = ',')

# Are there any pairs missing a value for row?
format(sum(is.na(aps_chunk_2_ids$aps_row)), big.mark = ',')

# How many rows in the original APS data for this chunk are missing from the
# ID/Pair generated set (likely due to no matches)
format(length(setdiff(
  subset$aps_row, unique(aps_chunk_2_ids$aps_row)
  )), big.mark = ",")

# How many unique IDs were generated?
format(length(unique(aps_chunk_2_ids$id)), big.mark = ',')

# Are there any pairs missing an ID value?
format(sum(is.na(aps_chunk_2_ids$id)), big.mark = ',')

# [1] "168,525"
# [1] "167,827"
# [1] "0"
# [1] "0"
# [1] "161,909"
# [1] "0"
```

### Within Posterior Probability Range

We examined all pairs within the manual review posterior probability range of 0.20 - 0.70. This resulted in manual review of 1,937 pairs.

```{r}
checking <- aps_chunk_2_pairs |>
  dplyr::filter(
    dplyr::between(posterior_probability, posteriors[1], posteriors[2])
    )

format(nrow(checking), big.mark = ',')
# [1] "1,937"
```

We found no pairs within this range demonstrated identical values for `client_id`.

```{r}
format(nrow(
  checking |> 
    dplyr::filter(client_id_a == client_id_b)
  ),
  big.mark = ',')

# [1] "0"
```

In examining our gamma values for our matching variables, we found several trends:

-   The vast majority (1,728) failed to match at all on first name (gamma = 0)
-   The vast majority (1,447) failed to match on birth year (gamma = 0)
-   The vast majority (1,061) failed to match on birth day (gamma = 0)
-   The vast majority (1,371) significantly matched on last name (gamma = 2)
-   The vast majority (1,864) significantly matched on street address (gamma = 2)
-   The vast majority (1,936) significantly matched on zip code (gamma = 2)
-   The vast majority (1,428) significantly matched on birth month (gamma = 2)

```{r, warning = F}
get_unique_value_summary(
  checking |>
    dplyr::select(dplyr::all_of(gamma_cols))
  )
```

We initiated our list of pairs to drop, which we would build during our processing.

```{r}
drop_pairs_c2 <- c()
```


#### Address Failures

##### ZIP Code (Non-Matches)

We first examined pair with non-matching ZIP Codes (Gamma == 0). The ZIP code values in the rows of these pairs appeared to only differ due to small typos.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- checking |>
  dplyr::filter(client_zip_code_gamma != 2)

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# [1] "1"
# [1] "Min: 0.47959; Max: 0.47959"
```

This pair was deemed valid. As such, we did not add its value to the drop list.

##### Street Address (Weak Matches)

We examined remaining pairs with weakly matching street address values (Gamma == 1). The street address values of rows in these pairs appeared to primarily consist of minor differences in house number.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- checking |>
  dplyr::filter(client_street_address_gamma == 1) |>
  # Omit previous check groups
  dplyr::filter(client_zip_code_gamma != 0 )

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# [1] "46"
# [1] "Min: 0.28981; Max: 0.56301"
```

4 of the 46 pairs was found to be a true match. As such, we added 42 to our drop list.

```{r}
keep_pairs <- c(49677, 20839, 62424, 123819)

drop_pairs_c2 <- unique(c(
  drop_pairs_c2, 
  setdiff(checking_cols$pair, keep_pairs)
  ))

length(drop_pairs_c2)
# [1] 42
```

##### Street Address (Non-Matches)

We examined remaining pairs with non-matching street address values (Gamma == 0). The street address values of rows in these pairs appeared to primarily consist of minor differences in house number.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- checking |>
  dplyr::filter(client_street_address_gamma == 0) |>
  # Omit previous check groups
  dplyr::filter(client_zip_code_gamma != 0 )

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# [1] "27"
# [1] "Min: 0.65266; Max: 0.65266"
```

11 of the 27 pairs was found to be a true match. As such, we added 16 to our drop list.

```{r}
keep_pairs <- c(
  21000, 52252, 52353, 72640, 72696, 78907, 87877, 93649, 103611, 133965, 
  154262
  )

drop_pairs_c2 <- unique(c(
  drop_pairs_c2, 
  setdiff(checking_cols$pair, keep_pairs)
  ))

length(drop_pairs_c2)
# [1] 58
```

#### Name Failures

##### Last Name (Weak Matches)

We examined remaining pairs with weakly matching last name values (Gamma == 1). Many of the last name values in the rows of pairs in this section appeared to differ primarily due to small typos.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- checking |>
  dplyr::filter(client_last_name_gamma == 1) |>
  # Omit previous check groups
  dplyr::filter(!(
    client_zip_code_gamma == 0 | client_street_address_gamma < 2
    ))

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# [1] "10"
# [1] "Min: 0.43836; Max: 0.6431"
```

5 of the 10 pairs found to be a true match. As such, we added the remaining 5 pair ids to our drop list.

```{r}
keep_pairs <- c(144223, 10648, 22605, 41775, 72675)

drop_pairs_c2 <- unique(c(
  drop_pairs_c2, 
  setdiff(checking_cols$pair, keep_pairs)
  ))

length(drop_pairs_c2)
# [1] 63
```

##### Last Name (Non Matches)

We examined remaining pairs with non-matching last name values (Gamma == 0). Many of the subjects in the pairs of this section had identical or highly similar addresses. Many were identified to be women who used more than one surname. Of note, there were also several pairs that were found to be valid but had first and last name transposed in data entry.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- checking |>
  dplyr::filter(client_last_name_gamma == 0) |>
  # Omit previous check groups
  dplyr::filter(!(
    client_zip_code_gamma == 0 | client_street_address_gamma < 2
    ))

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# [1] "547"
# [1] "Min: 0.25968; Max: 0.69851"
```

There were 27 of the 547 pairs found to be a true match. As such, we added the remaining 520 pair ids to our drop list.

```{r}
keep_pairs <- c(
  10191, 10372, 31473, 31504, 31595, 41804, 52049, 52342, 72779, 82908, 82947, 
  113800, 148983, 113790, 52087, 52358, 62366, 62502, 72720, 82982, 82999, 
  103429, 113700, 123978, 164367, 93316, 129771
  )

drop_pairs_c2 <- unique(c(
  drop_pairs_c2, 
  setdiff(checking_cols$pair, keep_pairs)
  ))

length(drop_pairs_c2)
# 583
```

##### First Name (Weak Matches)

There were no remaining pairs with weak matching first name values (Gamma == 1).

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- checking |>
  dplyr::filter(client_first_name_gamma == 1) |>
  # Omit previous check groups
  dplyr::filter(!(
    client_zip_code_gamma == 0 | client_street_address_gamma < 2 | 
      client_last_name_gamma < 2
    ))

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# [1] "0"
```

##### First Name (Non-Matches)

We examined remaining pairs with non-matching first name values (Gamma == 0). The vast majority appeared to be familial pairs.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- checking |>
  dplyr::filter(client_first_name_gamma == 0) |>
  # Omit previous check groups
  dplyr::filter(!(
    client_zip_code_gamma == 0 | client_street_address_gamma < 2 | 
      client_last_name_gamma < 2
    ))

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# [1] "1,306"
# [1] "Min: 0.52549; Max: 0.69701"
```

There were 11 of the 1,306 pairs found to be a true match. As such, we added the remaining 1,295 pair ids to our drop list.

```{r}
keep_pairs <- c(
  10333, 20874, 31448, 52020, 82942, 95042, 104966, 113767, 31640, 103493, 
  113653
  )

drop_pairs_c2 <- unique(c(
  drop_pairs_c2, 
  setdiff(checking_cols$pair, keep_pairs)
  ))

format(length(drop_pairs_c2), big.mark = ',')
# [1] "1,878"
```

#### Remaining Pairs

There were no remaining pairs to examine.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- checking |>
  dplyr::filter(client_first_name_gamma == 0) |>
  # Omit previous check groups
  dplyr::filter(!(
    client_zip_code_gamma == 0 | client_street_address_gamma < 2 | 
      client_last_name_gamma < 2 | client_first_name_gamma < 2
    ))

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# [1] "0"
```

We verified that we had a total of 59 pairs kept from this subset.

```{r}
nrow(
  checking |>
    dplyr::filter(!(pair %in% drop_pairs_c2))
  ) == 59
# [1] TRUE
```

### Above posterior probability range

We examined pairs just above our posterior probability range, to ensure appropriate capture. All pairs within the posterior probability range of 0.70 - 0.90 were examined. This resulted in manual review of 631 pairs.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- aps_chunk_2_pairs |>
  dplyr::filter(
    dplyr::between(posterior_probability, posteriors[2], posteriors[2]+0.2)
    )

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# [1] "631"
# [1] "Min: 0.71946; Max: 0.89622"
```

We found no pairs within this range demonstrated identical values for `client_id`.

```{r}
format(nrow(
  checking_cols |> 
    dplyr::filter(client_id_a == client_id_b)
  ),
  big.mark = ',')

# [1] "0"
```

We identified that the majority of pairs above a probability between 0.70 and 0.80 appeared to be true matches, with few exceptions. We added these false matches to our drop list.

```{r}
drop_pairs_c2 <- c(
  drop_pairs_c2, 
  c(144203, 10521, 25650, 31296, 31377, 52320)
  )
```

Pairs between 0.80 and 0.90 were primarily false matches, specifically spousal/familial mismatches or subjects with highly similar common name values. We identified the true matches within this range, and added all other pairs to our list of exclusions.

```{r}
drop_pairs_c2 <- c(
  drop_pairs_c2, 
  dplyr::pull(
    checking_cols |>
      dplyr::filter(
        dplyr::between(posterior_probability, 0.80, 0.90)
        ) |>
      dplyr::filter(
        !(pair %in% c(
          134099, 134134, 20811, 42006, 44424, 52034, 52301, 52359, 93219,
          154317, 10239, 20670, 31333, 31477, 31495, 31572, 31610, 41636,
          41967, 52099, 52201, 62498, 62577, 64210, 66271, 72650, 72800,
          103504, 103547, 103583, 103636, 113688, 154298, 31236, 72848, 
          83036, 83048, 123930, 123938, 62429, 62473, 62572, 93300
          ))
      ) |>
      dplyr::select(pair)
    )
  )

```

We verified that we had a total of 2453 pairs excluded from this chunk.

```{r}
nrow(
  aps_chunk_2_pairs |>
    dplyr::filter((pair %in% drop_pairs_c2))
  ) == 2453
# [1] TRUE
```

We lastly gave a cursory examination to pairs with a posterior probability above 0.90, where the pair did not represent a self-match.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking_cols <- aps_chunk_2_pairs |>
  dplyr::filter(
    posterior_probability > 0.90
    ) |>
  dplyr::filter(aps_row_a != aps_row_b)

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# [1] "3,976"
# [1] "Min: 0.93825; Max: 1"
```

We identified several human-recognizable likely mismatches. We excluded these pairs.

```{r}
drop_pairs_c2 <- c(drop_pairs_c2, c(
  21166, 52224, 62380, 83084, 93366, 93388, 93393, 134093, 10287, 10653, 
  21071, 21186, 52369, 62540, 72797, 113749, 134087, 134127, 135982, 144238,
  164334, 31535, 113785, 52269, 113629, 41790, 22731, 72738, 93327, 103541,
  52272, 83058, 72814, 1898, 3091, 3288, 5272, 10124, 10395, 10430, 14773,
  17743, 17854, 19761, 20729, 20806, 20813, 20884, 22099, 24451, 25262, 26849,
  26962, 28329, 31270, 31284, 31376, 31425, 34000, 35505, 37483, 40106, 40420,
  41736, 41829, 46773, 47194, 51010, 55452, 57874, 62403, 63645, 63653, 70054,
  70584, 72837, 74481, 77405, 82048, 82494, 82857, 83429, 83967, 84368, 85877,
  92962, 93250, 93260, 93361, 95720, 95919, 100269, 103574, 103623, 106865,
  111545, 112576, 113658, 114698, 115241, 123848, 124540, 128843, 130183,
  132080, 133395, 134067, 134069, 135033, 138908, 139434, 144135, 144199,
  145867, 147719, 149079, 151653, 154266, 156848, 158041, 161467, 163765,
  164450, 167190, 167539, 168666, 168824, 172054, 172256, 1816, 1848, 2710,
  4328, 5581, 7011, 10060, 10073, 10128, 10231, 10273, 10289, 10396, 10612,
  10629, 10669, 12362, 12581, 13564, 15433, 17421, 18176, 18383, 20305, 20719,
  20794, 20946, 21204, 21208, 21553, 23123, 23849, 23991, 24473, 24494, 24684,
  25143, 25472, 27425, 30608, 31265, 32534, 33636, 34633, 38522, 39706, 40065,
  40269, 41719, 41733, 41799, 41878, 41912, 42743, 45227, 45669, 48048, 51375,
  52009, 52307, 52896, 55994, 56317, 62470, 62563, 65359, 65638, 67263, 68751,
  69177, 71796, 72692, 72853, 72894, 73057, 74332, 79943, 80258, 82973, 83010,
  85234, 86895, 87811, 88575, 89916, 91375, 91905, 92290, 93034, 93192, 
  93226, 93230, 93234, 93364, 94870, 98321, 99854, 100937, 101879, 103546,
  103594, 103609, 103621, 103629, 106235, 112038, 113631, 113695, 117895,
  118682, 119963, 121259, 121594, 123082, 123799, 123940, 123955, 125300,
  125985, 126066, 128067, 129698, 133964, 134074, 135624, 135800, 138352,
  140875, 141358, 142732, 142951, 143076, 144142, 144209, 144220, 146886,
  148071, 150389, 150715, 154258, 154263, 154285, 155394, 159630, 160116,
  161505, 163614, 164509, 165919, 166578, 168251, 169539, 169581, 171011,
  172843, 10503, 110540, 122862, 132768, 156644, 3895, 10400, 21238, 31603,
  55395, 100978, 104101, 105583, 20814, 63996, 68496, 75469, 91566, 123841,
  144191, 165331, 20711, 77604, 93367, 123864, 133994, 83043, 88169, 115403,
  10425, 159216, 10130, 62355, 52108, 72732, 103531, 120643, 123871, 154337,
  72795, 132305, 74303, 38552, 41758, 113642, 113801, 62414, 72782, 20797,
  62437, 83044, 92692, 20867, 103521, 83051, 91699, 10546, 62627, 10563, 
  20706, 149953, 62624, 93351, 26413, 52328, 80767, 82918, 123969, 37, 21047,
  72778, 31592, 8511, 10254, 10351, 154615, 36924, 40538, 61041, 
  113670, 113826, 138495, 154279, 145913, 31625, 10638, 62557, 41992, 9976,
  1811, 9984, 9988, 10134, 10222, 10232, 10297, 10319, 10398, 10438, 10484,
  10633, 20836, 20926, 31423, 31528, 41771, 41870, 52102, 52162, 52190, 83156,
  83179, 93297, 93406, 103426, 123826, 123962, 135008, 154291, 93418, 23263,
  52061, 62487, 123934, 41888, 20977, 83053, 10381, 10649, 65283, 31369,
  120802, 10234, 93257, 94602, 95004, 113771, 144186, 31613, 35931, 103554,
  161264, 87181, 113708, 10077, 10561, 33901, 133776, 134103, 21196, 103443,
  132791, 148868, 164339, 10476, 10539, 67943, 123875, 10576, 41913, 62533,
  124191, 62591, 103441, 109160, 20773, 62550, 123843, 143879, 31282, 31304,
  197, 10579, 83173, 115203, 79933, 62554, 62636, 72667, 6949, 41826, 12514,
  88430, 128614, 47904, 4560, 72845, 82972, 98465, 130361, 20970, 21009, 
  31295, 62390, 93294, 151178, 154319, 20821, 20783, 29899, 34890, 44411,
  46877, 80351, 91234, 100123, 101745, 121357, 122079, 129575, 134470,
  147093, 150186, 151518, 152552, 152586, 161510, 164863, 20737, 22944, 93229,
  107607, 112887, 113757, 119221, 133969, 135098, 156300, 64279, 123827, 
  20697, 20714, 21136, 27200, 30317, 31349, 31543, 31561, 58147, 62579, 82976,
  110946, 153274, 153513, 162523, 23602, 63880, 75075, 80412, 114343, 124792,
  127525, 163707, 8807, 33903, 66508, 79305, 89146, 93525, 98658, 101802,
  118567, 139940, 143516, 155635, 158781, 164941, 54546, 66058, 106460, 
  125176, 129263, 135990, 140393, 144849, 147786, 157496, 60747, 89817, 
  120251, 133943, 143781, 150778, 161282, 54834, 114209, 168988, 31342, 
  100067, 158827, 168499, 172352, 41752, 62398, 65784, 110123, 155761, 10368,
  20934, 52146, 160350, 76815, 41672, 47731, 62453, 81631, 114907, 167940,
  22078, 103024, 73339, 120135, 108524, 101783, 154242, 103627, 129153, 1960,
  45633, 166099, 51123, 41654, 63881, 134125	
  ))
```

### Regenerating ID Assignments

We reduced our Chunk 2 pairs, excluding all pairs in the manual verification range that we determined were false matches. We used this reduced set to re-generate ID assignments.

```{r}
aps_chunk_2_pairs <- aps_chunk_2_pairs |>
  dplyr::filter(!(pair %in% drop_pairs_c2))

aps_chunk_2_ids <- stack_ids(subset_pack, subset_pack, aps_chunk_2_pairs)
```

There were 167,877 observations in the Second APS Within-Set Matching Chunk ID set, generated from 167,827 APS observations. There were no pairs were missing values for `aps_row` variables. Additionally, there were no APS observations that were not found in the pair data, likely due to failure to find a match. There were 164,516 unique IDs (1 - 164,516) assigned in this preliminary processing, with no pairs missing an ID assignment.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

# How many observations in the ID set?
format(nrow(aps_chunk_2_ids), big.mark = ',')

# How many rows are in the subset used to generate this chunk?
format(nrow(subset), big.mark = ',')

# Are there any pairs missing a value for row?
format(sum(is.na(aps_chunk_2_ids$aps_row)), big.mark = ',')

# How many rows in the original APS data for this chunk are missing from the
# ID/Pair generated set (likely due to no matches)
format(length(setdiff(
  subset$aps_row, unique(aps_chunk_2_ids$aps_row)
  )), big.mark = ",")

# How many unique IDs were generated?
format(length(unique(aps_chunk_2_ids$id)), big.mark = ',')

# Are there any pairs missing an ID value?
format(sum(is.na(aps_chunk_2_ids$id)), big.mark = ',')

# [1] "167,877"
# [1] "167,827"
# [1] "0"
# [1] "0"
# [1] "164,516"
# [1] "2"
```

### Cleaning IDs

#### Row in more than one ID

We identified 38 rows which were paired in more than one ID value.

```{r}
multi_id_rows <- dplyr::pull(
  aps_chunk_2_ids |>
    dplyr::filter(duplicated(aps_row) | duplicated(aps_row, fromLast = T)
    ) |>
    dplyr::select(aps_row) |>
    dplyr::distinct()
)

format(length(unique((multi_id_rows))), big.mark = ',')
# [1] "38"
```

We isolated the 38 rows that were associated with more than one ID assignment, as well as rows associated with one of the 36 ID assignments impacted by one of these rows for manual review. This left us with 88 observations to manually review.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

multi_id_row_ids <- dplyr::pull(
    aps_chunk_2_ids |>
    dplyr::filter(
      aps_row %in% multi_id_rows
      ) |>
    dplyr::select(id)
  )

checking <- aps_chunk_2_ids |>
  dplyr::filter(
    id %in% multi_id_row_ids | aps_row %in% multi_id_rows
    )

# Number of unique rows with more than one ID (same output as last chunk)
format(length(unique(multi_id_rows)), big.mark = ',')

# Number of unique IDs associated with a row that appears in more than one ID
format(length(unique(multi_id_row_ids)), big.mark = ',')

# Number of observations pulled for checking (either a row that appears in
# more than one ID, or a row associated with one of those IDs)
format(nrow(checking), big.mark = ',')
# [1] "38"
# [1] "36"
# [1] "88"
```

After manual review, we identified 25 IDs that could be dropped. No groups required manual creation to consolidate two observations together that were not otherwise in an existing ID.

```{r}
dropping_ids <- c(
  19517, 60082, 19631, 30758, 39163, 62349, 31844, 145343, 136075, 143203, 
  33097, 69068, 34631, 68244, 40975, 87589, 48872, 107662, 95127, 97216, 
  71923, 71524, 77919, 113550, 126246
  )

# Drop the listed IDs, and remove the list of rows in the ID
aps_chunk_2_ids <- aps_chunk_2_ids |>
  dplyr::filter(!(id %in% dropping_ids)) |>
  dplyr::select(-match_rows)

# Subset rows that were not previously assigned an ID value
unassigned_rows <- subset_pack$df |>
  dplyr::filter(!(aps_row %in% aps_chunk_2_ids$aps_row))

# Assign from the dropped ID values. Reserve 2 for the manually created
# pair IDs
unassigned_rows <- unassigned_rows |>
  dplyr::mutate(
    id = setdiff(
      seq(1,164516),
      aps_chunk_2_ids$id
      )[1:nrow(unassigned_rows)]
  )

# Combine the chunk back together
aps_chunk_2_ids <- dplyr::bind_rows(
  aps_chunk_2_ids, unassigned_rows
  )
```

#### Flagged Rows

We identified 204 rows which were flagged for any reason, which included 202 ID values. In total, we isolated 290 observations for manual review.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

flagged_rows <- dplyr::pull(
  aps_chunk_2_ids |>
    dplyr::filter(flag_issues | flag_unresolvable | flag_mult_clients) |>
    dplyr::select(aps_row)
  )

flagged_ids <- dplyr::pull(
  aps_chunk_2_ids |>
    dplyr::filter(
      flag_issues | flag_unresolvable | flag_mult_clients | 
        (aps_row %in% flagged_rows)
      ) |>
    dplyr::select(id)
  )

checking <- aps_chunk_2_ids |>
  dplyr::filter(id %in% flagged_ids)

# Number of flagged rows?
format(length(unique((flagged_rows))), big.mark = ',')

# Number of impacted IDs?
format(length(unique((flagged_ids))), big.mark = ',')

# Total observations to review?
format(nrow(checking), big.mark = ',')

# [1] "204"
# [1] "202"
# [1] "290"
```

No necessary changes were identified from the review. We further checked that our ID assignment did not create more than one ID for a given `client_id`, which would have indicated failed matches. We found none.

```{r}
# No duplicated CLIENTID values?
nrow(
  aps_chunk_2_ids |>
    dplyr::group_by(client_id) |>
    dplyr::summarise(n_ids = dplyr::n_distinct(id)) |>
    dplyr::filter(n_ids > 1)
) == 0

# [1] TRUE
```

This concluded the cleaning and examination of Chunk 2.

### 💾 Save and Export Data

We exported this subset of our data.

```{r}
saveRDS(
  aps_chunk_2_ids,
  here::here(
    "data", "cleaned_rds_files", "record_linkage", "aps", 
    "aps_02_ids_chunk_2.rds"
    )
)
```

### 🧹 Clean up

```{r}
rm(aps_chunk_2_ids)
rm(aps_chunk_2_pairs)
rm(aps_chunk_2)
rm(drop_pairs_c2)
```

## Chunk 3

We converted our third chunk into our desired stacked pair data. As this
chunk omitted name matching due to patterns of missingness in the data, we
omitted the name variables from our match variables in pair generation.

```{r}
# Get APS subset for this chunk
subset <- aps |>
  dplyr::filter(chunks == 3)

subset_pack <- list()
subset_pack$df <- subset
subset_pack$suffix <- 'aps_3'
subset_pack$ids <- pack_id_vars

aps_chunk_3_pairs <- get_pair_data(
  subset_pack, subset_pack, 
  setdiff(match_vars, c("client_first_name", "client_last_name")), 
  aps_chunk_3
  )

aps_chunk_3_ids <- stack_ids(subset_pack, subset_pack, aps_chunk_3_pairs)
```

### Review of Initial ID Assignments

There were 1,391 observations in the third APS Within-Set Matching Chunk ID set, generated from 1,377 APS observations. There were no pairs were missing values for `aps_row` variables. Additionally, there were no APS observations that were not found in the pair data, likely due to failure to find a match. There were 1,138 unique IDs (1 - 1,138) assigned in this preliminary processing, with no pairs missing an ID assignment.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

# How many observations in the ID set?
format(nrow(aps_chunk_3_ids), big.mark = ',')

# How many rows are in the subset used to generate this chunk?
format(nrow(subset), big.mark = ',')

# Are there any pairs missing a value for row?
format(sum(is.na(aps_chunk_3_ids$aps_row)), big.mark = ',')

# How many rows in the original APS data for this chunk are missing from the
# ID/Pair generated set (likely due to no matches)
format(length(setdiff(
  subset$aps_row, unique(aps_chunk_3_ids$aps_row)
  )), big.mark = ",")

# How many unique IDs were generated?
format(length(unique(aps_chunk_3_ids$id)), big.mark = ',')

# Are there any pairs missing an ID value?
format(sum(is.na(aps_chunk_3_ids$id)), big.mark = ',')
```

### Within Posterior Probability Range

We examined all pairs within the manual review posterior probability range of 0.20 - 0.70. This resulted in manual review of 25 pairs with a posterior probability of 0.34119. There were 1,752 pairs with a greater posterior probability than our established threshold for manual verification.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking <- aps_chunk_3_pairs 

checking_cols <- checking |>
  dplyr::filter(
    dplyr::between(posterior_probability, posteriors[1], posteriors[2])
    )

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# Number of rows with a greater posterior probability than the threshold
format(nrow(
  aps_chunk_3_pairs |>
  dplyr::filter(
    posterior_probability > posteriors[2])
    ),
  big.mark = ','
  )

# [1] "25"
# [1] "Min: 0.34119; Max: 0.34119"
# [1] "1,752"
```

We found no pairs within this range demonstrated identical values for `client_id`.

```{r}
format(nrow(
  checking |> 
    dplyr::filter(client_id_a == client_id_b)
  ),
  big.mark = ',')

# [1] "0"
```

In examining our gamma values for our matching variables, we found several trends. All pairs matched on ZIP Code. None matched on date of birth values. Street Addresses were all weak matches.

```{r, warning = F}
get_unique_value_summary(
  checking |>
    dplyr::select(dplyr::all_of(
      setdiff(
        gamma_cols, c("client_first_name_gamma", "client_last_name_gamma")
        )
      ))
  )
```

#### Manual Review

We manually examined all pairs within this chunk. Pairs with no names, but identical DOB and address values confirmed to belong to single-family homes were kept. An additional 4 pairs were kept after manual review determined reasonably high probability of a true match. Additionally, pairs that were self-matched were kept. All other pairs were excluded.

```{r}
kept_pairs <- dplyr::pull(
  aps_chunk_3_pairs |>
    dplyr::filter(aps_row_a == aps_row_b) |>
    dplyr::select(pair) |>
    dplyr::distinct()
  )

kept_pairs <- c(
  kept_pairs, 
  12, 70, 108, 109, 111, 121, 166, 262, 341, 418, 555, 556, 560, 731, 809, 
  825, 1097, 1098, 1099, 1100, 1101, 1103, 1104, 1105, 1106, 1108, 1109, 
  1110, 1112, 1113, 1115, 1208, 1209, 1211, 1243, 1244, 1246, 1348, 1377, 
  1390, 1403, 1486, 1615, 1655, 1711, 1595, 1628, 963, 616
  )
```

#### Regenerating ID Assignments

We reduced our Chunk 3 pairs, excluding all pairs except for those we deemed acceptable. We used this reduced set to re-generate ID assignments.

```{r}
aps_chunk_3_pairs <- aps_chunk_3_pairs |>
  dplyr::filter((pair %in% kept_pairs))

aps_chunk_3_ids <- stack_ids(subset_pack, subset_pack, aps_chunk_3_pairs)
```

There were 1,377 observations in the third APS Within-Set Matching Chunk ID set, generated from 1,377 APS observations. There were no pairs were missing values for `aps_row` variables. Additionally, there were no APS observations that were not found in the pair data, likely due to failure to find a match. There were 1,342 unique IDs (1 - 1,342) assigned in this preliminary processing, with no pairs missing an ID assignment.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

# How many observations in the ID set?
format(nrow(aps_chunk_3_ids), big.mark = ',')

# How many rows are in the subset used to generate this chunk?
format(nrow(subset), big.mark = ',')

# Are there any pairs missing a value for row?
format(sum(is.na(aps_chunk_3_ids$aps_row)), big.mark = ',')

# How many rows in the original APS data for this chunk are missing from the
# ID/Pair generated set (likely due to no matches)
format(length(setdiff(
  subset$aps_row, unique(aps_chunk_3_ids$aps_row)
  )), big.mark = ",")

# How many unique IDs were generated?
format(length(unique(aps_chunk_3_ids$id)), big.mark = ',')

# Are there any pairs missing an ID value?
format(sum(is.na(aps_chunk_3_ids$id)), big.mark = ',')
```

### Cleaning IDs

#### Row in more than one ID

We identified 0 rows which were paired in more than one ID value.

```{r}
multi_id_rows <- dplyr::pull(
  aps_chunk_3_ids |>
    dplyr::filter(duplicated(aps_row) | duplicated(aps_row, fromLast = T)
    ) |>
    dplyr::select(aps_row) |>
    dplyr::distinct()
)

format(length(unique((multi_id_rows))), big.mark = ',')
# [1] "0"
```

We isolated the 62 rows that were associated with one of the 27 ID values that included more than one row for manual review. This left us with 62 observations to manually review.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

multi_id_row_ids <- dplyr::pull(
    aps_chunk_3_ids |>
      dplyr::filter(stringr::str_detect(match_rows, ",")) |>
      dplyr::select(id) |>
      dplyr::distinct()
  )

multi_id_rows <- dplyr::pull(
  aps_chunk_3_ids |>
      dplyr::filter(id %in% multi_id_row_ids) |>
      dplyr::select(aps_row) |>
      dplyr::distinct()
)

checking <- aps_chunk_3_ids |>
  dplyr::filter(
    id %in% multi_id_row_ids | aps_row %in% multi_id_rows
    )

# Number of unique IDs associated with more than one row
format(length(unique(multi_id_row_ids)), big.mark = ',')

# Number of unique rows associated with these IDs
format(length(unique(multi_id_rows)), big.mark = ',')

# Number of observations pulled for checking (either an ID that includes
# more than one row, or a row associated with one of those IDs)
format(nrow(checking), big.mark = ',')
# [1] "27"
# [1] "62"
# [1] "62"
```

After manual review, we identified no IDs that should be dropped. No groups required manual creation to consolidate two observations together that were not otherwise in an existing ID.

#### Flagged Rows

We identified 1 row which were flagged for any reason other than missingness, which included 1 ID value. We isolated this observation for manual review.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

flagged_rows <- dplyr::pull(
  aps_chunk_3_ids |>
    dplyr::filter(flag_unresolvable | flag_mult_clients) |>
    dplyr::select(aps_row)
  )

flagged_ids <- dplyr::pull(
  aps_chunk_3_ids |>
    dplyr::filter(
      flag_unresolvable | flag_mult_clients | 
        (aps_row %in% flagged_rows)
      ) |>
    dplyr::select(id)
  )

checking <- aps_chunk_3_ids |>
  dplyr::filter(id %in% flagged_ids)

# Number of flagged rows?
format(length(unique((flagged_rows))), big.mark = ',')

# Number of impacted IDs?
format(length(unique((flagged_ids))), big.mark = ',')

# Total observations to review?
format(nrow(checking), big.mark = ',')

# [1] "1"
# [1] "1"
# [1] "1"
```

No necessary changes were identified from the review. 

We further checked that our ID assignment did not create more than one ID for a given `client_id`. We identified a single `client_id` value which appeared in more than one ID, the result of address variants.

```{r}
# Duplicated CLIENTID values?
dup_clients <- unique(pull(
  aps_chunk_3_ids |>
    dplyr::group_by(client_id) |>
    dplyr::summarise(n_ids = dplyr::n_distinct(id)) |>
    dplyr::filter(n_ids > 1) |>
    dplyr::select(client_id)
  ))

length(dup_clients)
# [1] 1
```

On review, we identified that this `client_id` value failed to match due to addressing variants, created during cleaning of unusual address format which included multiple addresses. We consolidated these groups.

```{r}
aps_chunk_3_ids <- aps_chunk_3_ids |>
  dplyr::mutate(
    id = ifelse(
      aps_row %in% c(378600, 351122), 1211, id
    )
  )
```

We verified that this resolved the `client_id` to `id` discrepancy, which it did.

```{r}
# No duplicated CLIENTID values?
nrow(
  aps_chunk_3_ids |>
    dplyr::group_by(client_id) |>
    dplyr::summarise(n_ids = dplyr::n_distinct(id)) |>
    dplyr::filter(n_ids > 1)
) == 0

# [1] TRUE
```

This concluded the cleaning and examination of Chunk 3.

### 💾 Save and Export Data

We exported this subset of our data.

```{r}
saveRDS(
  aps_chunk_3_ids,
  here::here(
    "data", "cleaned_rds_files", "record_linkage", "aps", 
    "aps_02_ids_chunk_3.rds"
    )
)
```

### 🧹 Clean up

```{r}
rm(aps_chunk_3_ids)
rm(aps_chunk_3_pairs)
rm(aps_chunk_3)
```

## Chunk 4

We converted our fourth chunk into our desired stacked pair data. As this
chunk omitted address matching due to patterns of missingness in the data, we
omitted the address variables from our match variables in pair generation.

```{r}
# Get APS subset for this chunk
subset <- aps |>
  dplyr::filter(chunks == 4)

subset_pack <- list()
subset_pack$df <- subset
subset_pack$suffix <- 'aps_4'
subset_pack$ids <- pack_id_vars

aps_chunk_4_pairs <- get_pair_data(
  subset_pack, subset_pack, 
  setdiff(match_vars, c("client_street_address", "client_zip_code")), 
  aps_chunk_4
  )

aps_chunk_4_ids <- stack_ids(subset_pack, subset_pack, aps_chunk_4_pairs)
```

### Review of Initial ID Assignments

There were 12,359 observations in the fourth APS Within-Set Matching Chunk ID set, generated from 12,359 APS observations. There were no pairs were missing values for `aps_row` variables. Additionally, there were no APS observations that were not found in the pair data, likely due to failure to find a match. There were 12,084 unique IDs (1 - 12,084) assigned in this preliminary processing, with no pairs missing an ID assignment.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

# How many observations in the ID set?
format(nrow(aps_chunk_4_ids), big.mark = ',')

# How many rows are in the subset used to generate this chunk?
format(nrow(subset), big.mark = ',')

# Are there any pairs missing a value for row?
format(sum(is.na(aps_chunk_4_ids$aps_row)), big.mark = ',')

# How many rows in the original APS data for this chunk are missing from the
# ID/Pair generated set (likely due to no matches)
format(length(setdiff(
  subset$aps_row, unique(aps_chunk_4_ids$aps_row)
  )), big.mark = ",")

# How many unique IDs were generated?
format(length(unique(aps_chunk_4_ids$id)), big.mark = ',')

# Are there any pairs missing an ID value?
format(sum(is.na(aps_chunk_4_ids$id)), big.mark = ',')
```

### Within Posterior Probability Range

There were no pairs within the manual review posterior probability range of 0.20 - 0.70. There were 12,660 pairs with a greater posterior probability than our established threshold for manual verification.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking <- aps_chunk_4_pairs 

checking_cols <- checking |>
  dplyr::filter(
    dplyr::between(posterior_probability, posteriors[1], posteriors[2])
    )

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Number of rows with a greater posterior probability than the threshold
format(nrow(
  aps_chunk_4_pairs |>
  dplyr::filter(
    posterior_probability > posteriors[2])
    ),
  big.mark = ','
  )

# [1] "0"
# [1] "12,660"
```

We found 12,363 pairs within this range demonstrated identical values for `client_id`.

```{r}
format(nrow(
  checking |> 
    dplyr::filter(client_id_a == client_id_b)
  ),
  big.mark = ',')

# [1] "12,363"
```

In examining our gamma values for our matching variables, we found several trends. Few pairs were less than a strong match for name values.

```{r, warning = F}
get_unique_value_summary(
  checking |>
    dplyr::select(dplyr::all_of(
      setdiff(
        gamma_cols, c("client_street_address_gamma", "client_zip_code_gamma")
        )
      ))
  )
```

#### Manual Review

We manually examined all pairs within this chunk. We identified 56 pairs to drop, primarily due to common name values and poor information to support a match.

```{r}
kept_pairs <- dplyr::pull(
  aps_chunk_4_pairs |>
    dplyr::filter(aps_row_a == aps_row_b) |>
    dplyr::select(pair) |>
    dplyr::distinct()
  )

kept_pairs <- c(
  kept_pairs, 
  setdiff(setdiff(aps_chunk_4_pairs$pair, kept_pairs),
          c(
            1486, 6096, 8446, 225, 3298, 4445, 4745, 7123, 7693, 4452, 5172, 
            3467, 11941, 4242, 5830, 8816, 10930, 4441, 4718, 1279, 1784, 
            4490, 1783, 10011, 6066, 899, 3581, 6543, 955, 4281, 1905, 2554, 
            365, 4446, 6966, 9455, 313, 407, 2518, 4332, 5562, 320, 540, 677, 
            717, 3435, 4101, 4299, 4347, 7154, 7155, 8299, 8798, 10488, 10527, 
            10863
             ))
  
  )
```

#### Regenerating ID Assignments

We reduced our Chunk 4 pairs, excluding all pairs except for those we deemed acceptable. We used this reduced set to re-generate ID assignments.

```{r}
aps_chunk_4_pairs <- aps_chunk_4_pairs |>
  dplyr::filter((pair %in% kept_pairs))

aps_chunk_4_ids <- stack_ids(subset_pack, subset_pack, aps_chunk_4_pairs)
```

There were 12,363 observations in the fourth APS Within-Set Matching Chunk ID set, generated from 12,359 APS observations. There were no pairs were missing values for `aps_row` variables. Additionally, there were no APS observations that were not found in the pair data, likely due to failure to find a match. There were 12,138 unique IDs (1 - 12,138) assigned in this preliminary processing, with no pairs missing an ID assignment.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

# How many observations in the ID set?
format(nrow(aps_chunk_4_ids), big.mark = ',')

# How many rows are in the subset used to generate this chunk?
format(nrow(subset), big.mark = ',')

# Are there any pairs missing a value for row?
format(sum(is.na(aps_chunk_4_ids$aps_row)), big.mark = ',')

# How many rows in the original APS data for this chunk are missing from the
# ID/Pair generated set (likely due to no matches)
format(length(setdiff(
  subset$aps_row, unique(aps_chunk_4_ids$aps_row)
  )), big.mark = ",")

# How many unique IDs were generated?
format(length(unique(aps_chunk_4_ids$id)), big.mark = ',')

# Are there any pairs missing an ID value?
format(sum(is.na(aps_chunk_4_ids$id)), big.mark = ',')

# [1] "12,363"
# [1] "12,359"
# [1] "0"
# [1] "0"
# [1] "12,138"
# [1] "0"
```

### Cleaning IDs

#### Row in more than one ID

We identified 3 rows which were paired in more than one ID value.

```{r}
multi_id_rows <- dplyr::pull(
  aps_chunk_4_ids |>
    dplyr::filter(duplicated(aps_row) | duplicated(aps_row, fromLast = T)
    ) |>
    dplyr::select(aps_row) |>
    dplyr::distinct()
)

format(length(unique((multi_id_rows))), big.mark = ',')
# [1] "3"
```

We isolated the 3 rows that were associated with more than one ID assignment, as well as rows associated with one of the 3 ID assignments impacted by one of these rows for manual review. This left us with 7 observations to manually review.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

multi_id_row_ids <- dplyr::pull(
    aps_chunk_4_ids |>
    dplyr::filter(
      aps_row %in% multi_id_rows
      ) |>
    dplyr::select(id)
  )

checking <- aps_chunk_4_ids |>
  dplyr::filter(
    id %in% multi_id_row_ids | aps_row %in% multi_id_rows
    )

# Number of unique rows with more than one ID (same output as last chunk)
format(length(unique(multi_id_rows)), big.mark = ',')

# Number of unique IDs associated with a row that appears in more than one ID
format(length(unique(multi_id_row_ids)), big.mark = ',')

# Number of observations pulled for checking (either a row that appears in
# more than one ID, or a row associated with one of those IDs)
format(nrow(checking), big.mark = ',')
# [1] "3"
# [1] "3"
# [1] "7"
```

We identified that the groups could be consolidated. We dropped the ID values that reflected partial groupings.

```{r}
dropping_ids <- c(7965, 9110)

# Drop the listed IDs, and remove the list of rows in the ID
aps_chunk_4_ids <- aps_chunk_4_ids |>
  dplyr::filter(!(id %in% dropping_ids))
```

We isolated the 420 rows that were associated with one of the 202 ID values (excluding our previously verified IDs) that included more than one row for manual review, and had more than one `client_id` value (were not already matched). This left us with 420 observations to manually review.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

multi_id_row_ids <- dplyr::pull(
    aps_chunk_4_ids |>
      dplyr::filter(stringr::str_detect(match_rows, ",")) |>
      dplyr::filter(!(id %in% c(7965, 9109, 9110))) |>
      dplyr::group_by(id) |>
      dplyr::mutate(n_clients = dplyr::n_distinct(client_id)) |>
      dplyr::ungroup() |>
      dplyr::filter(n_clients > 1) |>
      dplyr::select(id) |>
      dplyr::distinct()
  )
  

multi_id_rows <- dplyr::pull(
  aps_chunk_4_ids |>
      dplyr::filter(id %in% multi_id_row_ids) |>
      dplyr::select(aps_row) |>
      dplyr::distinct()
)

checking <- aps_chunk_4_ids |>
  dplyr::filter(
    id %in% multi_id_row_ids | aps_row %in% multi_id_rows
    )

# Number of unique IDs associated with more than one row
format(length(unique(multi_id_row_ids)), big.mark = ',')

# Number of unique rows associated with these IDs
format(length(unique(multi_id_rows)), big.mark = ',')

# Number of observations pulled for checking (either an ID that includes
# more than one row, or a row associated with one of those IDs)
format(nrow(checking), big.mark = ',')

# [1] "202"
# [1] "420"
# [1] "420"
```

After manual review, we identified no IDs that should be dropped. No groups required manual creation to consolidate two observations together that were not otherwise in an existing ID.

#### Flagged Rows

We identified 159 row which were flagged for any reason other than missingness, which included 156 ID value. We isolated the 170 related observations for manual review.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

flagged_rows <- dplyr::pull(
  aps_chunk_4_ids |>
    dplyr::filter(flag_unresolvable | flag_mult_clients) |>
    dplyr::select(aps_row)
  )

flagged_ids <- dplyr::pull(
  aps_chunk_4_ids |>
    dplyr::filter(
      flag_unresolvable | flag_mult_clients | 
        (aps_row %in% flagged_rows)
      ) |>
    dplyr::select(id)
  )

checking <- aps_chunk_4_ids |>
  dplyr::filter(id %in% flagged_ids)

# Number of flagged rows?
format(length(unique((flagged_rows))), big.mark = ',')

# Number of impacted IDs?
format(length(unique((flagged_ids))), big.mark = ',')

# Total observations to review?
format(nrow(checking), big.mark = ',')

# [1] "159"
# [1] "156"
# [1] "170"
```

No necessary changes were identified from the review. We further checked that our ID assignment did not create more than one ID for a given `client_id`, which would have indicated failed matches. We found none.

```{r}
# No duplicated CLIENTID values?
nrow(
  aps_chunk_4_ids |>
    dplyr::group_by(client_id) |>
    dplyr::summarise(n_ids = dplyr::n_distinct(id)) |>
    dplyr::filter(n_ids > 1)
) == 0

# [1] TRUE
```

This concluded the cleaning and examination of Chunk 4.

### 💾 Save and Export Data

We exported this subset of our data.

```{r}
saveRDS(
  aps_chunk_4_ids,
  here::here(
    "data", "cleaned_rds_files", "record_linkage", "aps", 
    "aps_02_ids_chunk_4.rds"
    )
)
```

### 🧹 Clean up

```{r}
rm(aps_chunk_4_ids)
rm(aps_chunk_4_pairs)
rm(aps_chunk_4)
```

## Chunk 5

We converted our fifth chunk into our desired stacked pair data. As this
chunk omitted DOB matching due to patterns of missingness in the data, we
omitted the DOB variables from our match variables in pair generation.

```{r}
# Get APS subset for this chunk
subset <- aps |>
  dplyr::filter(chunks == 5)

subset_pack <- list()
subset_pack$df <- subset
subset_pack$suffix <- 'aps_5'
subset_pack$ids <- pack_id_vars

aps_chunk_5_pairs <- get_pair_data(
  subset_pack, subset_pack, 
  setdiff(match_vars, 
          c("client_dob_year", "client_dob_month", "client_dob_day")
          ), 
  aps_chunk_5
  )

aps_chunk_5_ids <- stack_ids(subset_pack, subset_pack, aps_chunk_5_pairs)
```

### Review of Initial ID Assignments

There were 28 observations in the fifth APS Within-Set Matching Chunk ID set, generated from 28 APS observations. There were no pairs were missing values for `aps_row` variables. Additionally, there were no APS observations that were not found in the pair data, likely due to failure to find a match. There were 28 unique IDs (1 - 28) assigned in this preliminary processing, with no pairs missing an ID assignment.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

# How many observations in the ID set?
format(nrow(aps_chunk_5_ids), big.mark = ',')

# How many rows are in the subset used to generate this chunk?
format(nrow(subset), big.mark = ',')

# Are there any pairs missing a value for row?
format(sum(is.na(aps_chunk_5_ids$aps_row)), big.mark = ',')

# How many rows in the original APS data for this chunk are missing from the
# ID/Pair generated set (likely due to no matches)
format(length(setdiff(
  subset$aps_row, unique(aps_chunk_5_ids$aps_row)
  )), big.mark = ",")

# How many unique IDs were generated?
format(length(unique(aps_chunk_5_ids$id)), big.mark = ',')

# Are there any pairs missing an ID value?
format(sum(is.na(aps_chunk_5_ids$id)), big.mark = ',')

# [1] "28"
# [1] "28"
# [1] "0"
# [1] "0"
# [1] "28"
# [1] "0"
```

### Within Posterior Probability Range

There were no pairs within the manual review posterior probability range of 0.20 - 0.70. There were 28 observations in pairs with a greater posterior probability than our established threshold for manual verification.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking <- aps_chunk_5_pairs 

checking_cols <- checking |>
  dplyr::filter(
    dplyr::between(posterior_probability, posteriors[1], posteriors[2])
    )

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Number of rows with a greater posterior probability than the threshold
format(nrow(
  aps_chunk_5_pairs |>
  dplyr::filter(
    posterior_probability > posteriors[2])
    ),
  big.mark = ','
  )

# [1] "0"
# [1] "28"
```

All 28 pairs within this range demonstrated identical values for `client_id`.

```{r}
format(nrow(
  checking |> 
    dplyr::filter(client_id_a == client_id_b)
  ),
  big.mark = ',')

# [1] "28"
```

In examining our gamma values for our matching variables, we found that our pairs were all considered "perfect matches".

```{r, warning = F}
get_unique_value_summary(
  checking |>
    dplyr::select(dplyr::all_of(
      setdiff(
        gamma_cols, c(
          "client_dob_year_gamma", "client_dob_month_gamma", 
          "client_dob_day_gamma"
          )
        )
      ))
  )
```

#### Manual Review

We manually examined all pairs within this chunk. All pairs were found to be individual (i.e., self-to-self). Manual review of all observations in this subset found no failed matches. As there were no modifications to pairs or ID assignments, this concluded the cleaning and examination of Chunk 5.

### 💾 Save and Export Data

We exported this subset of our data.

```{r}
saveRDS(
  aps_chunk_5_ids,
  here::here(
    "data", "cleaned_rds_files", "record_linkage", "aps", 
    "aps_02_ids_chunk_5.rds"
    )
)
```

### 🧹 Clean up

```{r}
rm(aps_chunk_5_ids)
rm(aps_chunk_5_pairs)
rm(aps_chunk_5)
```

## Chunk 6

We converted our sixth chunk into our desired stacked pair data. This chunk utilized all possible variables for matching.

```{r}
# Get APS subset for this chunk
subset <- aps |>
  dplyr::filter(chunks == 6)

subset_pack <- list()
subset_pack$df <- subset
subset_pack$suffix <- 'aps_6'
subset_pack$ids <- pack_id_vars

aps_chunk_6_pairs <- get_pair_data(
  subset_pack, subset_pack, match_vars, aps_chunk_6
  )

aps_chunk_6_ids <- stack_ids(subset_pack, subset_pack, aps_chunk_6_pairs)
```

### Review of Initial ID Assignments

There were 963 observations in the sixth APS Within-Set Matching Chunk ID set, generated from 549 APS observations. There were no pairs were missing values for `aps_row` variables. Additionally, there were no APS observations that were not found in the pair data, likely due to failure to find a match. There were 505 unique IDs (1 - 505) assigned in this preliminary processing, with no pairs missing an ID assignment.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

# How many observations in the ID set?
format(nrow(aps_chunk_6_ids), big.mark = ',')

# How many rows are in the subset used to generate this chunk?
format(nrow(subset), big.mark = ',')

# Are there any pairs missing a value for row?
format(sum(is.na(aps_chunk_6_ids$aps_row)), big.mark = ',')

# How many rows in the original APS data for this chunk are missing from the
# ID/Pair generated set (likely due to no matches)
format(length(setdiff(
  subset$aps_row, unique(aps_chunk_6_ids$aps_row)
  )), big.mark = ",")

# How many unique IDs were generated?
format(length(unique(aps_chunk_6_ids$id)), big.mark = ',')

# Are there any pairs missing an ID value?
format(sum(is.na(aps_chunk_6_ids$id)), big.mark = ',')

# [1] "963"
# [1] "549"
# [1] "0"
# [1] "0"
# [1] "505"
# [1] "0"
```

### Manual Review

We isolated 494 pairs within the manual review posterior probability range of 0.20 - 0.70, with posterior probabilities ranging from 0.29877 to 0.63256. There were an additional 298 pairs with a greater posterior probability than our established threshold for manual verification.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

checking <- aps_chunk_6_pairs 

checking_cols <- checking |>
  dplyr::filter(
    dplyr::between(posterior_probability, posteriors[1], posteriors[2])
    )

# Number of rows in this subset
format(nrow(checking_cols), big.mark = ',')

# Posterior probability range in this subset
paste0(
  "Min: ",
  format(min(checking_cols$posterior_probability), digits = 5),
  "; Max: ",
  format(max(checking_cols$posterior_probability), digits = 5)
  )

# Number of rows with a greater posterior probability than the threshold
format(nrow(
  aps_chunk_6_pairs |>
  dplyr::filter(
    posterior_probability > posteriors[2])
    ),
  big.mark = ','
  )

# [1] "494"
# [1] "Min: 0.29877; Max: 0.63256"
# [1] "298"
```

There were 549 pairs within this chunk that demonstrated identical values for `client_id`.

```{r}
format(nrow(
  checking |> 
    dplyr::filter(client_id_a == client_id_b)
  ),
  big.mark = ',')

# [1] "549"
```

In examining our gamma values for our matching variables, we identified several trends. The vast majority of observations were considered strong matches, only failing or partially matching on First Name, Date of Birth (Year), or due to missingness.

```{r, warning = F}
get_unique_value_summary(
  checking |>
    dplyr::select(dplyr::all_of(gamma_cols))
  )
```

We manually examined all pairs within this chunk. Only pairs with identical `client_id` values were considered valid, as others only matched on partial information or referred to large areas; these pairs were self-to-self matches, not true outside matches. Manual review of all observations in this subset found no failed matches. 

### Regenerating ID Assignments

We reduced our Chunk 6 pairs, excluding all pairs except for those we deemed acceptable. We used this reduced set to re-generate ID assignments.

```{r}
aps_chunk_6_pairs <- aps_chunk_6_pairs |>
  dplyr::filter(client_id_a == client_id_b)

aps_chunk_6_ids <- stack_ids(subset_pack, subset_pack, aps_chunk_6_pairs)
```

There were 549 observations in the sixth APS Within-Set Matching Chunk ID set, generated from 549 APS observations. There were no pairs were missing values for `aps_row` variables. Additionally, there were no APS observations that were not found in the pair data, likely due to failure to find a match. There were 549 unique IDs (1 - 549) assigned in this preliminary processing, with no pairs missing an ID assignment.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

# How many observations in the ID set?
format(nrow(aps_chunk_6_ids), big.mark = ',')

# How many rows are in the subset used to generate this chunk?
format(nrow(subset), big.mark = ',')

# Are there any pairs missing a value for row?
format(sum(is.na(aps_chunk_6_ids$aps_row)), big.mark = ',')

# How many rows in the original APS data for this chunk are missing from the
# ID/Pair generated set (likely due to no matches)
format(length(setdiff(
  subset$aps_row, unique(aps_chunk_6_ids$aps_row)
  )), big.mark = ",")

# How many unique IDs were generated?
format(length(unique(aps_chunk_6_ids$id)), big.mark = ',')

# Are there any pairs missing an ID value?
format(sum(is.na(aps_chunk_6_ids$id)), big.mark = ',')

# [1] "549"
# [1] "549"
# [1] "0"
# [1] "0"
# [1] "549"
# [1] "0"
```

### Cleaning IDs

#### Row in more than one ID

We identified 0 rows which were paired in more than one ID value, and 0 IDs with more than one row.

```{r}
## ==========================================================================
## This chunk is meant to have multiple outputs, used by a human using the
## file to perform a standardized set of data checks in one block.
## ==========================================================================

multi_id_rows <- dplyr::pull(
  aps_chunk_6_ids |>
    dplyr::filter(duplicated(aps_row) | duplicated(aps_row, fromLast = T)
    ) |>
    dplyr::select(aps_row) |>
    dplyr::distinct()
)


multi_id_row_ids <- dplyr::pull(
    aps_chunk_6_ids |>
      dplyr::filter(stringr::str_detect(match_rows, ",")) |>
      dplyr::select(id) |>
      dplyr::distinct()
  )

# Rows in more than one ID
format(length(unique((multi_id_rows))), big.mark = ',')

# IDs with more than one row
format(length(unique((multi_id_row_ids))), big.mark = ',')
# [1] "0"
# [1] "0"
```

No necessary changes were identified from the review. We further checked that our ID assignment did not create more than one ID for a given `client_id`, which would have indicated failed matches. We found none.

```{r}
# No duplicated CLIENTID values?
nrow(
  aps_chunk_6_ids |>
    dplyr::group_by(client_id) |>
    dplyr::summarise(n_ids = dplyr::n_distinct(id)) |>
    dplyr::filter(n_ids > 1)
) == 0

# [1] TRUE
```

This concluded the cleaning and examination of Chunk 6.

### 💾 Save and Export Data

We exported this subset of our data.

```{r}
saveRDS(
  aps_chunk_6_ids,
  here::here(
    "data", "cleaned_rds_files", "record_linkage", "aps", 
    "aps_02_ids_chunk_6.rds"
    )
)
```

# 🧹 Clean up

```{r}
rm(list=ls())
```

