---
title: "Unique ID Creation"
format: html
---


# Load Packages

```{r, warning = FALSE}
library(dplyr)
library(readr)
library(tidyverse)
library(fastLink)
library(stringdist)
library(purrr)
library(stringr)
library(igraph)
library(here)
```


# Load the participant dataset and the fastlink output

```{r}
flo <- read_rds(here::here("data", "unique_id_creation", "fast_link_output.rds"))
par <- read_rds(here::here("data", "cleaned_rds_files", "participant_import.rds"))
```


# Group exact matches to reduce the number of stacked pair matches

```{r}
par_exact_id <- par %>%
  group_by(name_first, name_last, dob, sex_2cat_f, address) %>%
  mutate(
    # Column that shows the frequency of each unique observation
    count               = n(),
    # Column that assigns an ID to each unique observation based on exact matching
    exact_match_id = cur_group_id()
  ) %>%
  group_by(x_created_timestamp) %>%
  arrange() %>%
  ungroup() %>%
  group_by(name_first, name_last, dob, sex_2cat_f, address) %>%
  mutate(
    # Column that gives each visit a number that represents the chronological order
    visit_no = row_number()
  ) %>%
  ungroup() 
  
```

```{r}
# Filter out only the first visit for each exact id to reduce the number of matches. 
par_exact_id_1 <- par_exact_id %>%
  select(medstar_id, name_first, name_middle_initial, name_last, dob, sex_2cat_f, 
         address, phone, exact_match_id, visit_no, x_created_timestamp) %>%
  filter(visit_no == 1) %>%
  
  ## Split the single date of birth variable into 3 variables - month, day and year
  mutate_at(vars(dob), list(birth_year = year, birth_month = month, 
                            birth_day = day)) %>%
  mutate(
    birth_day = as.numeric(birth_day)
  ) 

```

### Match Check

A function was written by Dr. Cannell to permit examination of potential matches with posterior probabilities.

```{r}
fmr_fastlink_stack_matches <- function(.x, df) {
  
  # ===========================================================================
  # Error checks
  # ===========================================================================
  if (!("fastLink" %in% class(.x))) {
    stop('.x must be of class "fastLink"')
  }
  
  
  # ===========================================================================
  # Create data frame of potential matches to compare
  # ===========================================================================
  potential_matches <- tibble::tibble(
    row = .x$matches$inds.b,
    matching_row = .x$matches$inds.a,
    posterior_probability = .x$posterior
  )
  
  # Keep only unique combinations of rows (e.g., not 1-3 and 3-1)
  potential_matches <- potential_matches %>%
    dplyr::mutate(
      combo = purrr::map2_chr(
        .x = row,
        .y = matching_row,
        .f = function(x, y) {
          min <- min(x, y)
          max <- max(x, y)
          out <- paste(min, max, sep = "_")
          out
        }
      ),
      dup = duplicated(combo)
    ) %>%
    dplyr::filter(!dup) %>%
    dplyr::select(-combo, -dup)
  
  
  # ===========================================================================
  # Manipulate the potential matches data frame
  # Stack row and matching row on top of each other
  # Add a pair number to each row and matching row
  # ===========================================================================
  stacked_potential_matches <- tibble::tibble(
    row = c(rbind(potential_matches[["row"]], potential_matches[["matching_row"]])),
    pair = rep(seq(1, length(row) / 2), each = 2),
    posterior_probability = rep(potential_matches[["posterior_probability"]], 
                                each = 2)
  )
  
  
  # ===========================================================================
  # Add substantive variables of interest to matched pairs for review
  # ===========================================================================
  out <- stacked_potential_matches %>% 
    dplyr::left_join(
      df %>% 
        dplyr::mutate(row = dplyr::row_number()),
      by = "row"
    )
  
  
  # ===========================================================================
  # Return data frame of potential matches to compare
  # ===========================================================================
  out
}

```

```{r}
stacked_out <- fmr_fastlink_stack_matches(flo, par_exact_id_1) %>%
  relocate(exact_match_id, .after = "row")
```

```{r}
a <- par %>% select(medstar_id) %>% unique() %>% nrow()
b <- par_exact_id %>% select(exact_match_id) %>% unique() %>% nrow()
c <- par_exact_id %>% filter((is.na(name_first) == T) & (is.na(name_last) == T)) %>%
  select(exact_match_id) %>% unique() %>% nrow()
d <- stacked_out %>% select(medstar_id) %>% unique() %>% nrow()
```

```{r}
cat("The total number of unique medstar IDs in the original participant data set is", a)
```

```{r}
cat("The total number of unique person IDs based on exact matching in the original participant data set is", b)
```

```{r}
cat("The total number of medstar IDs with missing names which are needed to create fastLink matches is", c)
```

```{r}
cat("The total number of medstar IDs in the stacked matched pairs is", d)
```


# Review the Potential Matches

## Assumptions
The following assumptions were made while reviewing the potential matches:
Name

The first and last name were taken into consideration in every case. Since the majority of middle initials were missing, they were only considered if they were present. There were names with typographical errors and sometimes nicknames not very similar to their full versions were used e.g Betsy vs Elizabeth or Bill vs William. People with hyphenated last names or last names with multiple parts sometimes included only one part or the other. Some names are more rare and more weight was given to the name if it was rare.

DOB

The presence of typos was assumed in cases were all other values were the same but the dob differed by a few months a year or a few days. If only one digit was different, the presence of a typo was also assumed. In cases were the dob was the same but only the first name was different, the possibility of the observations being for twins was considered. Related people with the same name could live in the same house and this was also taken into consideration.


Address

Addresses were not always uniformly formatted e.g "St" could be used in place of "Street". People could have also moved houses as a result of the incident that led to the 911 call. Some addresses were for group homes rather than single family homes so unrelated people could have the same address. There were also typos.

Phone number

There were typos present in many of the phone numbers but many were similar enough and when other factors were considered, a determination was made.

Time stamp

In cases where the address was missing, if the other values were the same, it was assumed that such observations were for the same person if they had a time stamp that fell within the same day.

## Create a flag column to determine whether or not the stacked pairs need to be manually reviewed

```{r}
stacked_out_review <- stacked_out %>%
  # Create indices for each pair
  group_by(pair) %>% 
  mutate(pair_index = row_number()) %>%
  relocate(pair_index, .after = "pair") %>%
  
  # Create a column that indicates whether the pairs have the same exact_match_id or not
  mutate(same = +(n_distinct(exact_match_id) == 1)) %>% 
  ungroup %>%
  
  # Convert 999-999-9999 phone number to NA
  mutate(
    phone = case_when(
      phone == "999-999-9999" ~ NA,
      TRUE                    ~ phone
    )
  ) %>%

  # Create a column that indicates whether or not the phone number is missing
  group_by(pair) %>%
  mutate(
    phone_na = case_when(
      any(is.na(phone)) ~ 1,
      TRUE              ~ 0
      )
  ) %>%
  
  # Create a column that indicates the level of similarity of the phone numbers
    mutate(
      phone          = as.character(phone),
      phone_sim_dist = stringsim(phone[pair_index == 1], phone[pair_index == 2], 
                                  method = c("osa", "lv", "dl", "hamming", "lcs", 
                                             "qgram", "cosine", "jaccard", "jw",
                                              "soundex")),
      phone_sim = case_when(
        phone_sim_dist == 1                         ~ "same",
        phone_sim_dist < 1 & phone_sim_dist >= 0.83 ~ "similar",
        phone_sim_dist < 0.83                       ~ "different"
      )
    ) %>%
  ungroup() %>%
  
  # Create columns that indicates whether or not the names are similar
  unite(name_full, c(name_first, name_last), sep = " ", remove = FALSE) %>%
  group_by(pair) %>%
  mutate(
    name_full_sim_dist = stringsim(name_full[pair_index == 1], 
                                   name_full[pair_index == 2], 
                               method = c("osa", "lv", "dl", "hamming", "lcs", 
                                          "qgram", "cosine", "jaccard", "jw",
           "soundex")),
    name_full_sim = case_when(
      name_full_sim_dist >= 0.65                            ~ "Highly likely",
      name_full_sim_dist >= 0.4 & name_full_sim_dist < 0.65 ~ "Possibly",
      name_full_sim_dist < 0.4                              ~ "Not likely"
      
    )
  )%>% 
  ungroup %>%

  # Create a column that indicates whether or not the initials are the same 
  mutate(
    across(
      .cols  = c(name_first, name_last),
      .fns   = ~ map_chr(str_extract(.x, "[A-Z]+"), ~ str_c(.x, collapse=" ")),
      .names = "{col}_initial"
    )
) %>%
  unite(name_initials, c(name_first_initial, name_last_initial), sep = " ", 
        remove = TRUE) %>%
  group_by(pair) %>%
  mutate(same_initials = +(n_distinct(name_initials) == 1)) %>% 
  ungroup %>%
  
  # Create a column that indicates whether or not the initials are the same if 
  # the last name has two parts
  mutate(
    name_first_initial = map_chr(str_extract(name_first, "[A-Z]+"), ~ 
                                   str_c(.x, collapse=" ")),
    name_last_initial = map_chr(str_extract(name_last, "(?<=( |-))[A-Z]+"), ~ 
                                  str_c(.x, collapse=" "))
  ) %>%
  unite(name_initials_alt, c(name_first_initial, name_last_initial), sep = " ", 
        remove = TRUE) %>%
  group_by(pair) %>%
  mutate(
    same_initials_alt = case_when(
      name_initials[pair_index == 1] == name_initials_alt[pair_index == 2]  ~ 1,
      name_initials[pair_index == 2] == name_initials_alt[pair_index == 1]  ~ 1,
      TRUE                                                                  ~ 0
    ) 
    )%>%
  
  # Create a column that indicates the similarity of the dobs
  group_by(pair) %>%
  mutate(dob_similarity = stringsim(dob[pair_index == 1], dob[pair_index == 2],
                                    method = c("jw"))
    
  ) %>%
  mutate(
    same_dob = case_when(
      dob_similarity == 1                         ~ "same",
      dob_similarity < 1 & dob_similarity >= 0.83 ~ "similar",
      dob_similarity < 0.83                       ~ "different",
    ),
  # Create a column that indicates the same birth year
    same_birth_year = +(n_distinct(birth_year) == 1)
           ) %>% 
  ungroup %>%
  
  # Create a column that indicates whether or not the sex is the same  
  group_by(pair) %>%
  mutate(same_sex = +(n_distinct(sex_2cat_f) == 1)) %>% 
  ungroup %>%
  
 # Create a column that indicates whether or not the address is the same  
  group_by(pair) %>%
    mutate(
      address_sim_dist = stringsim(address[pair_index == 1], 
                                   address[pair_index == 2], 
                                  method = c("osa", "lv", "dl", "hamming", 
                                             "lcs", "qgram", "cosine", "jaccard", 
                                             "jw", "soundex")),
      address_sim = case_when(
        address_sim_dist >= 0.63                            ~ "Highly likely",
        address_sim_dist >= 0.4 & address_sim_dist < 0.63   ~ "Possibly",
        address_sim_dist < 0.4                              ~ "Not likely"
      )
    ) %>% 
  ungroup() %>%
  
  # Create a column that indicates whether or not one but not both of the values 
  # or a column are missing in a pair 
  # dob
  group_by(pair) %>%
  mutate(
    one_na_dob = case_when(
      !all(is.na(dob)) & any(is.na(dob))  ~ 1,
      TRUE                                ~ 0
    )
  ) %>%
  ungroup() %>%
  
  # address
  group_by(pair) %>%
  mutate(
    one_na_address = case_when(
      !all(is.na(address)) & any(is.na(address))  ~ 1,
      TRUE                                        ~ 0
    )
  ) %>%
  ungroup() %>%
  
  # sex
  group_by(pair) %>%
  mutate(
    one_na_sex = case_when(
      !all(is.na(sex_2cat_f)) & any(is.na(sex_2cat_f))  ~ 1,
      TRUE                                              ~ 0
    )
  ) %>%
  ungroup() %>%
  
  # Create date column from x_created_timestamp
  mutate(
    x_created_timestamp_date = as.Date(x_created_timestamp)
  ) %>%
  # Create column to show if the timestamp is the same or different
  group_by(pair) %>%
  mutate(
    same_timestamp = +(n_distinct(x_created_timestamp_date) == 1)
  ) %>%
  ungroup() %>%
  
  # Create a column that flags which columns need manual review
  mutate(
    flag = case_when(
      same == 1 ~ "exact match",
      (same == 0 & name_full_sim == "Highly likely" & same_dob == "same" & 
        same_sex == 1 & address_sim == "Highly likely") |
        (same == 0 & name_full_sim == "Possibly" & (same_initials == 1 | 
        same_initials_alt == 1) & same_sex == 1 & same_dob == "same" & 
        address_sim == "Highly likely") | 
        (same == 0 & name_full_sim == "Highly likely" & same_dob == "same" & 
        same_timestamp == 1) |
        (same == 0 & name_full_sim == "Highly likely" & same_dob == "same" & 
           phone_sim == "same")|
        (same == 0 & (name_full_sim == "Highly likely" | same_initials == 1 | 
                        same_initials_alt == 1) & address_sim == "Highly likely" & 
           ((phone_na == 0 & phone_sim == "same") | same_timestamp == 1)) | 
           (same == 0 & name_full_sim == "Highly likely" & same_timestamp == 1 & 
              same_dob == "same") ~ "Likely same",
      same == 0 & name_full_sim == "Highly likely"  & same_dob != "different" & 
        same_sex == 1 & address_sim != "Highly likely" & phone_sim == "same" & 
        phone_na == 0 ~ "Likely same, diff address",
      same == 0 & name_full_sim == "Highly likely" & same_dob == "same" & 
        same_sex == 0 & address_sim == "Highly likely" ~ "Likely same, diff sex",
      same == 0 & name_full_sim == "Highly likely" & (same_dob == "similar" | 
        same_birth_year == 1) & address_sim == "Highly likely" 
      ~ "Likely same, similar dob",
      (same == 0 & (name_first == "Jane" | name_first == "John") & 
         name_last == "Doe" &
        (is.na(dob) == T |  same_dob != "same" | 
           address_sim != "Highly likely")) |
        (same == 0 & same_dob != "same" & address_sim == "Not likely" & 
           phone_sim != "same") ~ "Likely not the same",
      (same == 0 & one_na_address == 1 & phone_na == 1) |
        (same == 0 & one_na_dob == 1) ~ "Cannot be determined",
      TRUE ~ "Needs Manual Review"
)
  ) %>%
  mutate(
    flag = factor(flag,
         levels = c("exact match", "Likely same", "Likely same, diff address", 
                    "Likely same, diff sex", "Likely same, similar dob", 
                    "Needs Manual Review", "Likely not the same", 
                    "Cannot be determined"))
  ) 

```

Note: Very few with the same initials or alternate initials had very different first names.

## Filter rows for manual review

```{r}
manual_review <- stacked_out_review %>% 
  filter(flag == "Needs Manual Review" & posterior_probability > 0.7 & 
           (same_initials == 1 | same_initials_alt == 1 | 
              name_full_sim == "Highly likely") & dob_similarity > 0.7 & 
           address_sim != "Not likely") %>% 
  select(pair, name_full, address, dob, sex_2cat_f, phone, phone_sim, 
         posterior_probability, x_created_timestamp)
```

The following pairs flagged as needing manual review were determined to be the 
same after review:

Same name + same address + slightly different dob / dob difference around a year
1318, 5010, 6304, 11903, 17227, 17420, 19107, 23090, 28676, 28781, 34312, 34701, 
34772, 42813, 50551, 50814, 50840, 50992

Same name + same dob + slightly different address
4583, 4660, 5029, 5137, 10865, 11341, 11370, 11467, 11620, 11661, 12032, 17082, 
17137, 17331,  17383, 17481, 17846, 17965, 20457, 23524, 23851, 34313, 34551, 
34882, 40223, 40280, 40421, 50862, 50993, 55575


Same name + same dob + slightly different phone (typo) 
4845, 5461, 11443, 17996, 50650

Same uncommon name + same dob
5441, 28747, 29582, 34728, 34817, 40232

Slightly different name + same dob + same address
23915, 29578, 30883, 34332, 34881, 35079, 50729,  52243

Slightly different name + slightly different dob
39997, 50682

Pairs with names that were not detected as being similar but have the same or 
similar addresses and dobs 

```{r}
manual_review <- stacked_out_review %>% 
  filter(same_dob != "different" & address_sim == "Highly likely" & 
           name_full_sim != "Highly likely" & flag == "Needs Manual Review") %>% 
  select(pair, name_full, name_middle_initial, posterior_probability)
```

Likely nickname or shortened form of name
654, 4586, 4612, 4823, 4880, 5110, 5146, 5460, 5522, 10841, 10898, 11322, 11442, 
11890, 16819, 17406, 22654, 22681, 22881, 23240, 23569, 23778, 28565, 28732, 
29274, 29516, 34154, 34175, 34363, 34447, 34656, 36119, 38732, 39070, 39919, 
40520, 41064, 45812, 45850, 50673, 55703

Uncommon first name + different last name/ typo likely
4605, 6035, 17922, 17973, 34413, 42867, 47979

Based on other pairs last, first and middle names likely swapped around
19368, 19369

Same first name + phone number and/ or middle initial that corresponds to one of 
the first names in the pair
7772, 11572, 12044, 17413, 17550, 20857, 23397, 23403, 29512, 30134, 34148, 
34623, 37779, 37918, 41203, 43675, 45935, 49810, 50955, 55781, 57194

Pairs with the same name, the same dob but different addresses and similar but 
not the same phone numbers.

```{r}
manual_review <- stacked_out_review %>% 
  filter(name_full_sim == "Highly likely" & same_dob == "same" & 
           address_sim != "Highly likely" & 
           phone_sim == "similar" & posterior_probability > 0.7 & 
           flag == "Needs Manual Review") %>%
  select(pair, name_full, name_middle_initial, dob, address, phone, 
         posterior_probability)
```

Same_name + same dob + similar phone number (could be a typo) or uncommon name

4604, 4748, 4845, 4990, 5116, 5142, 5248, 5418, 5448, 5461, 5513, 5837, 5838, 
5980, 6274, 10862, 11111, 11226, 11231, 11323, 11443, 11455, 11467, 11490, 
11676, 11823, 11902, 11911, 16910,  17011, 17095, 17114, 17137, 17293, 17588, 
17663, 17723, 17996, 18051, 22682, 23134, 23272, 23717, 23808, 25329, 28515, 
28927, 29090, 29163, 29191, 29265, 34337, 34747, 34972, 35108, 35304, 39903, 
40090, 40136, 40280, 40281, 40365, 40437, 40608, 45453, 45498, 45590,  45661,  
50549, 50650, 50812

## Change the flags for the manually reviewed pairs that were determined to be incorrect

```{r}
pair_list <- c(1318, 5010, 6304, 11903, 17227, 17420, 19107, 23090, 28676, 28781, 
               34312, 34701, 34772, 42813, 50551, 50814, 50840, 50992, 4583, 
               4660, 5029, 5137, 10865, 11341, 11370, 11467, 11620, 11661, 12032, 
               17082, 17137, 17331, 17383, 17481, 17846, 17965, 20457, 23524, 
               23851, 34313, 34551, 34882, 40223, 40280, 40421, 50862, 50993, 
               55575, 4845, 5461, 11443, 17996, 50650, 5441, 28747, 29582, 34728, 
               34817, 40232, 23915, 29578, 30883, 34332, 34881, 35079, 50729,  
               52243, 39997, 50682, 654, 4586, 4612, 4823, 4880, 5110, 5146, 
               5460, 5522, 10841, 10898, 11322, 11442, 11890, 16819, 17406, 
               22654, 22681, 22881, 23240, 23569, 23778, 28565, 28732, 29274, 
               29516, 34154, 34175, 34363, 34447, 34656, 36119, 38732, 39070, 
               39919, 40520, 41064, 45812, 45850, 50673, 55703, 4605, 6035, 
               17922, 17973, 34413, 42867, 47979, 19368, 19369, 7772, 11572, 
               12044, 17413, 17550, 20857, 23397, 23403, 29512, 30134, 34148, 
               34623, 37779, 37918, 41203, 43675, 45935, 49810, 50955, 55781, 
               57194, 4604, 4748, 4845, 4990, 5116, 5142, 5248, 5418, 5448, 
               5461, 5513, 5837, 5838, 5980, 6274, 10862, 11111, 11226, 11231, 
               11323, 11443, 11455, 11467, 11490, 11676, 11823, 11902, 11911, 
               16910,  17011, 17095, 17114, 17137, 17293, 17588, 17663, 17723, 
               17996, 18051, 22682, 23134, 23272, 23717, 23808, 25329, 28515, 
               28927, 29090, 29163, 29191, 29265, 34337, 34747, 34972, 35108, 
               35304, 39903, 40090, 40136, 40280, 40281, 40365, 40437, 40608, 
               45453, 45498, 45590,  45661,  50549, 50650, 50812
)  

stacked_out_review <- stacked_out_review %>% 
  mutate(
    new_flag = case_when(
      pair %in% pair_list ~ "Likely same",
      TRUE                ~ flag
    )
  )
```

```{r}
table(stacked_out_review$new_flag)
```


# Assign the same unique ID to verified matches

```{r}
# Create a dichotomous variable for verified matches
stacked_out_review <- stacked_out_review %>% 
  mutate(
    v_match = case_when(
      new_flag != "Cannot be determined" & new_flag != "Needs Manual Review" & 
        new_flag != "Likely not the same" ~ 1,
      TRUE  ~ 0
    )
  )
```

```{r}
# Filter out the verified matches and group them by pair
veri_matches <- stacked_out_review %>% filter(v_match == 1) %>% 
  select(pair_index, pair, exact_match_id) %>% distinct() %>% group_by(pair) 
```

```{r}
# Widen the data by separating each pair into two columns
veri_match_wide <- veri_matches %>% 
  pivot_wider(names_from = pair_index, values_from = exact_match_id) %>% 
  rename(
  pair_index_1 = "1",
  pair_index_2 = "2"
  ) %>%
  ungroup() %>%
  right_join(veri_matches, by = "pair") 
```


```{r}
# Use functions in the igraph package to cluster ids with overlapping pair 
# groups together

# Create a graph from the widened data frame
graph_test <- veri_match_wide %>% 
  select(pair_index_1, pair_index_2) %>% 
  graph_from_data_frame()

# Use components() instead of clusters()
component_results <- components(graph_test)

# Create a data frame from the results of the igraph functions
group_id <- data.frame(
  V = names(component_results$membership),
  cluster = component_results$membership,
  stringsAsFactors = FALSE
)
group_id <- group_id %>% 
  mutate(
    V = as.numeric(V)
  )

# Join the created ids back to the data frame with the exact match
# ids and filter unique rows for each exact_match_id
unique_id <- left_join(veri_match_wide, group_id, 
                       by = c("pair_index_2" = "V")) %>% 
  group_by(exact_match_id) %>%
  slice(1) %>% 
  rename(
    unique_id = "cluster"
  )
```

## Add the new unique id column to the participant data frame

```{r}
# Manually assign unique ids to the 4 rows in the participant data frame that 
# were not in the stacked pairs since their names and dobs are missing
excluded_rows <- par_exact_id %>% 
  filter(!(exact_match_id %in% unique_id$exact_match_id)) %>% 
  select(exact_match_id) %>% arrange(exact_match_id)

excluded_rows["unique_id"] <- c(42201, 42202, 42203, 42204)

unique_id <- bind_rows(unique_id, excluded_rows)
```

```{r}
# Add the unique id column to the par data set
par_unique_id <- unique_id %>% select(exact_match_id, unique_id) %>% 
  right_join(par_exact_id, by = "exact_match_id") %>% 
  select(-c("visit_no", "count")) %>%
  ungroup()

par_unique_id %>% select(medstar_id) %>% unique() %>% nrow()
```


```{r}
e <- par_unique_id %>% select(exact_match_id) %>% unique() %>% nrow()

f <- par_unique_id %>% select(unique_id) %>% unique() %>% nrow()

cat("The mumber of IDs assigned using exact matching is", e, 
    "while the number assignmed using probabilistic matching is", f)
```


# Save the RDS file

```{r}
saveRDS(par_unique_id, 
        here::here("data", "unique_id_creation", "participant_unique_id.rds"))
```

