---
title: "Preliminary DETECT R01 analysis"
---

# Overview

In this file, we analyse the DETECT R01 main outcomes.

```{r, message= FALSE}
# Load all necessary libraries
library(readr)
library(table1)
library(flextable)
library(tidyverse)
library(officer)
library(expss) # add variable labels

# Create confusion matrix for each abuse type 
source("../r/lead_determination_vs_detect_tool_confusion_matrix_by_abuse_type.R")

# Create confusion matrix for each DETECT tool item 
source("../r/lead_determination_vs_detect_tool_item_confusion_matrix.R")

# Extract each df from the merged df
source("../r/extract_df_from_merged_detect.R")

# Function for analyzing LEAD Panel Assessment data
source("../R/lead_positive_votes_analysis.R")
```


# Load data
```{r}
# Import the merged data frame.
detect_fu_merge  <- readRDS("../data/cleaned_rds_files/detect_fu_data_merged.rds")
```

# Overall confusion matrix using LEAD as the gold standard

```{r}
#| echo: false
# Extract lead Panel data from merged data frame
lpa <- filter_merged_df(detect_fu_merge, "_lpa")

# Extract participant data frame from merged dataframe
par <- filter_merged_df(detect_fu_merge, "_par") 

# Extract detect tool variables from participant data frame and recode variables to convert all responses besides "Yes" and "No" to NA.
detect_tool <- par %>% select(c(medstar_id, ends_with("_5cat_f"))) %>%
  mutate(
    across(
      .cols = ends_with("_5cat_f"),
      .fns = ~ case_when(
        .x == "Yes" ~ "Yes",
        .x == "No"  ~ "No",
        TRUE        ~ NA
      )
    ),
    across(
      .cols = ends_with("_5cat_f"),
      .fns = ~ factor(.x, levels = c("Yes", "No"))
    )
  )
```

```{r}
#| echo: false
# Generate positive vote summary columns for each Medstar ID
lead_sum <- pos_votes(lpa)

# Separate rows in final determination data frame from the rest
final_det <- lead_sum %>% filter(final_determination == 1)
lead_pos_votes <- lead_sum %>% filter(final_determination == 0)
```

The DETECT tool determination was counted as positive if the value of any of the detect tool variables was 'Yes' while the LEAD Panel Assessment was counted as positive if the final determination value was 'Yes' for any of the abuse types.

```{r}
conf_mat <- compare_det(final_det, detect_tool, abuse_any)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

```{r}
# Check data frame used to create confusion matrix
conf_mat_df <- conf_mat[[3]]
```


# Create confusion matrices for each abuse type using LEAD as the gold standard.

## Physical Abuse

```{r}
conf_mat <- compare_det(final_det, detect_tool, physical_abuse_det)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

## Sexual abuse

```{r}
conf_mat <- compare_det(final_det, detect_tool, sexual_abuse_det)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

## Emotional - Psychological Abuse

```{r}
conf_mat <- compare_det(final_det, detect_tool, emotional_psycho_abuse_det)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

## Neglect

```{r}
conf_mat <- compare_det(final_det, detect_tool, neglect_det)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

## Self Neglect

```{r}
conf_mat <- compare_det(final_det, detect_tool, self_neglect_det)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

## Financial Exploitation

```{r}
conf_mat <- compare_det(final_det, detect_tool, financial_exploitation_det)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```


## Abandonment

```{r}
conf_mat <- compare_det(final_det, detect_tool, abandonment_det)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

# Create confusion matrices using LEAD as the gold standard and each DETECT screening item as the exposure.
## Unusual odor 
```{r}
conf_mat <- compare_det_item(final_det, detect_tool, x_unusual_odor_5cat_f)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

```{r}
# Check df used to create confusion matrix
df <- conf_mat[[3]]
```

## Unmet needs

```{r}
conf_mat <- compare_det_item(final_det, detect_tool, x_unmet_needs_5cat_f)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

## Difficulty medications

```{r}
conf_mat <- compare_det_item(final_det, detect_tool, x_difficulty_medications_5cat_f)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

## Hoarding medications

```{r}
conf_mat <- compare_det_item(final_det, detect_tool, x_hoarding_medications_5cat_f)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

## Disarray hoarding

```{r}
conf_mat <- compare_det_item(final_det, detect_tool, x_disarray_hoarding_5cat_f)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

## Health safety concern

```{r}
conf_mat <- compare_det_item(final_det, detect_tool, x_health_safety_concern_5cat_f)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

## Caregiver lack knowledge

```{r}
conf_mat <- compare_det_item(final_det, detect_tool, x_caregiver_lack_knowledge_5cat_f)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

## Caregiver unengaged

```{r}
conf_mat <- compare_det_item(final_det, detect_tool, x_caregiver_unengaged_5cat_f)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

## Caregiver frustrated

```{r}
conf_mat <- compare_det_item(final_det, detect_tool, x_caregiver_frustrated_5cat_f)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

## Caregiver anxious

```{r}
conf_mat <- compare_det_item(final_det, detect_tool, x_caregiver_anxious_5cat_f)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

## Isolated home

```{r}
conf_mat <- compare_det_item(final_det, detect_tool, x_isolated_home_5cat_f)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

## Depressed

```{r}
conf_mat <- compare_det_item(final_det, detect_tool, x_depressed_5cat_f)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

## Poor personal hygeine

```{r}
conf_mat <- compare_det_item(final_det, detect_tool, x_poor_personal_hygiene_5cat_f)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

## Inadequately clothed

```{r}
conf_mat <- compare_det_item(final_det, detect_tool, x_inadequately_clothed_5cat_f)
```

```{r}
conf_mat[[1]]
```

```{r}
conf_mat[[2]]
```

# Create Table 1

```{r}
# Extract sociodemographic data from merged data frame (include only rows with non-missing data for abuse determination)
soc <- filter_merged_df(detect_fu_merge, "_soc") %>% filter(medstar_id %in% conf_mat_df$medstar_id)
```

```{r}
table1_vars <- soc %>% 
  mutate(
    # Create new categorical age variable with 4 age groups
    age_4cat_f = case_when(
      sode_age_years >= 65 & sode_age_years < 75 ~ "65-74",
      sode_age_years >= 75 & sode_age_years < 85 ~ "75-84",
      sode_age_years >= 85 & sode_age_years < 95 ~ "85-94",
      sode_age_years >= 95                       ~ "95+"
    ),
    age_4cat_f = factor(age_4cat_f, 
                        levels = c("65-74", "75-84", "85-94", "95+")
                        ),
    # Create new household size variable with 9 levels
    sode_people_9cat_f = factor(sode_people)
  )

# merge sex variable from participant dataset
table1_vars <- par %>% select(medstar_id, sex_3cat_f) %>% right_join(table1_vars, by = "medstar_id") 
```


```{r}
# Replace "Don't know" and "Refused" values with NA
table1_vars <- table1_vars %>% mutate(
  across(
    .cols = matches("_[0-9]+cat_f"),
    .fns = ~ case_when(
      .x == "Refused" | .x == "Don’t know" | .x == "Don't know" ~ NA,
      TRUE                                                      ~ .x
    )
  )
) %>% droplevels()

```

```{r}
# add variable labels
table1_vars <- apply_labels(table1_vars,
  age_4cat_f = "Age", 
  sex_3cat_f = "Sex",
  sode_race_eth_6cat_f = "Race/ ethnicity",
  sogi_orientation_8cat_f = "Sexual orientation",
  sode_marital_8cat_f = "Marital status", 
  sode_people_9cat_f = "Household size", 
  sode_employed_11cat_f = "Employment status",
  sode_income_9cat_f = "Household income",
  sode_military_4cat_f = "Military service", 
  sode_unwanted_4cat_f = "Unwanted sexual attention", 
  sode_sexual_4cat_f = "Sexual coersion"
  
)

```

```{r}
# Select variables to include in Table 1

table1_vars %>% select(matches("_[0-9]+cat_f")) %>% select(-c(sode_age_4cat_f, hsi_contact_4cat_f, sode_race_8cat_f, sode_hispanic_4cat_f)) %>% names()
```

```{r}
# Create caption/ title
cap <- "Table 1: Table of study population characteristics"


tabele1_tab <- table1(~ age_4cat_f + sex_3cat_f + sode_race_eth_6cat_f + sogi_orientation_8cat_f + sode_marital_8cat_f + sode_people_9cat_f + sode_employed_11cat_f +
                        sode_income_9cat_f + sode_military_4cat_f + sode_unwanted_4cat_f + sode_sexual_4cat_f,
  data = table1_vars,
  caption = cap
)
tabele1_tab <- t1flex(tabele1_tab, tablefn = c("qflextable", "flextable", "regulartable"))
tabele1_tab
```





