---
title: "Preliminary analysis of the self-reported EM section of the follow-up interviews"
---

# Overview

In this file, we conduct a preliminary analysis of the self-reported EM section of the DETECT follow-up interviews to understand what people self-reported in more detail.

```{r, message= FALSE}
# Load all necessary libraries
library(readr)
library(dplyr)
library(flextable)
library(officer)
source("../r/extract_df_from_merged_detect.R")
source("../r/n_percent_ci.R")
```


# Load data

Load the merged detect data frame into the environment and extract the self-report data.

```{r}
detect_fu_merge  <- readRDS("../data/cleaned_rds_files/detect_fu_data_merged.rds")
sr <- filter_merged_df(detect_fu_merge, "_sfr")
```

# Recode missing data

Replace "Don't know" and "Refused" values with NA
```{r}
sr <- sr %>% mutate(
  across(
    .cols = matches("_[0-9]+cat_f"),
    .fns = ~ case_when(
      .x == "Refused" | .x == "Don’t know" | .x == "Don't know" ~ NA,
      TRUE                                                      ~ .x
    )
  )
)
```

# Create an aggregate variable of any self-reported abuse
For each type of abuse, create a binary variable with yes/ no categories for: 
- Ever abuse
- Abuse over age 65
- Abuse in the past year

## Ever abuse
The category will be "yes" if the value is "yes" for any of the variables related to ever abuse.

```{r}
# Create empty data frame for aggregate variables
sr_aggr <- sr %>% select(medstar_id, unique_id_par) %>% data.frame()

# Function for creating aggregate columns
aggr <- function(abuse_cols, cat_name, f_name){
  aggr_vars <- sr %>%
    mutate(
      # Create a column that has a value of 1 if at least one of the ever physical abuse variables have a value of "yes".
      cat_name = case_when(
        if_any(all_of(abuse_cols), ~. == "Yes")  ~ 1,
        if_all(all_of(abuse_cols), ~. == "No")   ~ 0,
        TRUE                                     ~ NA
      ),
      # Create a factor variable
      f_name = factor(cat_name, 
                      levels = c(1, 0),
                      labels = c("Yes", "No"))
    ) %>% select(c(medstar_id, cat_name, f_name)) %>%
    rename(
      {{cat_name}} := cat_name,
      {{f_name}} := f_name
    )
  # Merge with data frame of aggregate variables
  sr_aggr <- sr_aggr %>% left_join(., aggr_vars, by = "medstar_id")
}
```

### Physical abuse
```{r}
# Create list of columns that the aggregate variable will be determined by
ever_phys_cols <- sr %>% select(physical_hit_4cat_f, physical_hurt_4cat_f, physical_restrain_4cat_f) %>% names()

# Apply function
sr_aggr <- aggr(ever_phys_cols, ever_phys_2cat, ever_phys_2cat_f)
```

### Sexual abuse
```{r}
# Create list of columns that the aggregate variable will be determined by
ever_sex_cols <- sr %>% select(sexual_harm_4cat_f, sexual_touched_4cat_f, sexual_forced_4cat_f, sexual_picture_4cat_f) %>% names()

# Apply function
sr_aggr <- aggr(ever_sex_cols, ever_sex_2cat, ever_sex_2cat_f)
```

### Emotional abuse
```{r}
# Create list of columns that the aggregate variable will be determined by
ever_emo_cols <- sr %>% select(emotional_yelled_4cat_f, emotional_embarrassed_4cat_f, emotional_harassed_4cat_f,
                               emotional_refused_4cat_f) %>% 
  names()

# Apply function
sr_aggr <- aggr(ever_emo_cols, ever_emo_2cat, ever_emo_2cat_f)
```

### Financial exploitation

```{r}
# Create lists of financial abuse columns that will result in the aggregate column variable being "No" if all are "No".
fin_person_cols <- sr %>% select(finance_person_forged_4cat_f, finance_person_tricked_4cat_f,
                               finance_person_stolen_4cat_f) %>% 
  names()
fin_stranger_cols <- sr %>% select(finance_stranger_permission_4cat_f, finance_stranger_forged_4cat_f,
                               finance_stranger_tricked_4cat_f) %>%
  names()


sr <- sr %>%
  mutate(
    # The values for columns used to calculate ever abuse involving a non-stranger will be "No" and not NA if the finance_help value is "No".
    across(
      .cols = all_of(fin_person_cols),
      .fns = ~ case_when(
        finance_help_4cat_f == "No" & is.na(.x)                                ~ "No",
        TRUE                                                                   ~ .x
      ),
      .names = "{col}_r"
    ),
    # Re-code finance_person_permission column similarly considering the finance_help variable. 
    finance_person_permission_4cat_f_r = case_when(
      finance_help_4cat_f == "No" & is.na(finance_person_permission_4cat_f) ~ "Yes",
      TRUE                                                                  ~ finance_person_permission_4cat_f
    ),
    # Additionally, Since the question is whether or not permission was asked rather than whether or not a form of abuse was experienced, values of "Yes" will be re-coded as "No" and vice versa.
    finance_person_permission_4cat_f_r = case_when(
      finance_person_permission_4cat_f_r == "No"  ~ "Yes",
      finance_person_permission_4cat_f_r == "Yes" ~ "No",
      TRUE                                        ~ NA
    )    
  )


aggr_vars <- sr %>%
  mutate(
   # Determine the aggregate "ever financial abuse" values
   ever_fin_2cat = case_when(
     if_any(all_of(fin_stranger_cols), ~. == "Yes") | if_any(ends_with("_r"), ~. == "Yes") ~ 1,
     if_all(all_of(fin_stranger_cols), ~. == "No") & if_all(ends_with("_r"), ~. == "No")   ~ 0,
     TRUE                                                                                       ~ NA
   ),
   # Create factor variable for "ever financial abuse"
   ever_fin_2cat_f = factor(ever_fin_2cat,
                            levels = c(1, 0),
                            labels = c("Yes", "No"))
  ) %>% select(ever_fin_2cat, ever_fin_2cat_f, medstar_id)

# Add variables to aggregate variable dataframe
sr_aggr <- sr_aggr %>% left_join(., aggr_vars, by = "medstar_id")

sr_aggr %>% freqtables::freq_table(ever_fin_2cat_f)
```

### Potential Neglect

Neglect potential will have a value of "Yes" when:
  - Neglect "have help" variable has a value of "No" when the "need help" value is "Yes"
  - Neglect variable with suffix "reliable" has value of "Not at all reliable" 
  - Neglect variable with suffix "reliable" has value of "Somewhat reliable" (this will be looked at later but not included for now)
  
And "No" when:
  - Neglect "need help variable" has value of "No"
  - Neglect variable with suffix "reliable" has any other value besides "Not at all reliable" and is not missing.
  
It will be missing when:
  - Neglect "need help variable" has a missing value. 
  - Neglect "need help variable" has a value of "Yes" and any of the other variables have missing values.

```{r}
# Create a nested list of the names of the variables used to determine potential abuse
neg_cols <- sr %>% select(starts_with("neglect") & matches("_[0-9]+cat_f") & !matches("neglect_person")) %>% names() %>% sort() %>% cbind() %>% 
  split(., cut(seq_along(.), 6, labels = FALSE))
neg_cols
```

```{r}
for(i in 1:6){
  pot_neg <- sr %>% 
    mutate(
      "{neg_cols[[i]][[1]]}_pot" := case_when(
        # Potential neglect
        sr[neg_cols[[i]][[1]]] == "Yes" & sr[neg_cols[[i]][[2]]] == "No" ~ 1, # Need help but don't have it
        sr[neg_cols[[i]][[3]]] == "Not at all reliable"                  ~ 1, # Helper is not at all reliable
        
        # No potential neglect
        sr[neg_cols[[i]][[1]]] == "No"                                   ~ 0, # Don't need help
        sr[neg_cols[[i]][[3]]] != "Not at all reliable" & 
          !is.na(sr[neg_cols[[i]][[3]]])                                 ~ 0, # Helper is at least somewhat reliable
        
        # Missing
        sr[neg_cols[[i]][[1]]] == NA                                     ~ NA, # Need help value is missing
        sr[neg_cols[[i]][[1]]] == "Yes" & 
          (sr[neg_cols[[i]][[2]]] == NA | sr[neg_cols[[i]][[3]]] == NA)  ~ NA  # Need help value is yes but any of the other variables have missing values
      )
    ) %>% 
    rename_with(
      .cols   = ends_with("_pot"),
      .fn     = ~ gsub("4cat_f_pot", "pot_2cat", .x)
    ) %>% select(medstar_id, matches("_pot"))
  # Merge with data frame of aggregate variables
  sr_aggr <- sr_aggr %>% left_join(., pot_neg, by = "medstar_id")
  
}

sr_aggr <- sr_aggr %>% 
  mutate(
    across(
      .cols = ends_with("pot_2cat"),
      .fns = ~ factor(.x,
                    levels = c(1, 0),
                    labels = c("Yes", "No")
      ),
      .names = "{col}_f"
    )
  )
  
  
sr_aggr %>% freqtables::freq_table(neglect_go_pot_2cat_f)
```

#### Any potential negelct
```{r}
sr_aggr <- sr_aggr %>%
  mutate(
     any_pot_neglect_2cat = case_when(
      if_any(ends_with("pot_2cat"), ~. == 1)  ~ 1,
      if_all(ends_with("pot_2cat"), ~. == 0)  ~ 0,
      TRUE                                    ~ NA
    ),
    # Create a factor variable
    any_pot_neglect_2cat_f = factor(any_pot_neglect_2cat, 
                    levels = c(1, 0),
                    labels = c("Yes", "No"))   
  )
```


## Recode 65 and last time variables

If the value is "No" for any of the variables used in the ever variable determination, the values for the corresponding over 65 variable will be "No" and that of the last time variables will be "Never experienced" and not NA.
```{r}
# Create a nested list of the names of the variables used to determine ever, last time and 65 aggregate variables

# Select finance_stranger ever columns and the recoded finance_person columns for use in analyseis of last time and over 65 variables
ever_fin_cols <-sr %>% select(c(finance_stranger_permission_4cat_f, finance_stranger_forged_4cat_f, finance_stranger_tricked_4cat_f, ends_with("_r"))) %>% names() %>% cbind()

last_time_65_cols <- sr %>% select(matches("_65_[0-9]+cat_f"), matches("_last_time_[0-9]+cat_f")) %>% names()

col_names <- c(ever_emo_cols, ever_fin_cols, ever_phys_cols, ever_sex_cols, last_time_65_cols) %>% sort() %>% cbind() %>% 
  split(., cut(seq_along(.), 18, labels = FALSE))

head(col_names)
```

```{r}
for(i in 1:18){
  sr <- sr %>% 
    mutate(
      # 65
      "{col_names[[i]][[2]]}_rc" := case_when(
        sr[col_names[[i]][[1]]] == "No" ~ "No",
        TRUE                            ~ sr[[col_names[[i]][[2]]]]
        ),
      # last_time
      "{col_names[[i]][[3]]}_rc" := case_when(
        sr[col_names[[i]][[1]]] == "No" ~ "Never experienced",
        TRUE                            ~ sr[[col_names[[i]][[3]]]]
        )
    )   
}
```

## Abuse over 65

### Physical abuse
```{r}
# Create list of columns that the aggregate variable will be determined by
over_65_phys_cols <- sr %>% select(starts_with("physical") & matches("65_[0-9]+cat_f_rc$")) %>% names()

# Apply function
sr_aggr <- aggr(over_65_phys_cols, over_65_phys_2cat, over_65_phys_2cat_f)
```

### Sexual abuse
```{r}
# Create list of columns that the aggregate variable will be determined by
over_65_sex_cols <- sr %>% select(starts_with("sexual") & matches("65_[0-9]+cat_f_rc$")) %>% names()

# Apply function
sr_aggr <- aggr(over_65_sex_cols, over_65_sex_2cat, over_65_sex_2cat_f)
```

### Emotional abuse
```{r}
# Create list of columns that the aggregate variable will be determined by
over_65_emo_cols <- sr %>% select(starts_with("emotional") & matches("65_[0-9]+cat_f_rc$")) %>% names()

# Apply function
sr_aggr <- aggr(over_65_emo_cols, over_65_emo_2cat, over_65_emo_2cat_f)
```

### Financial exploitation
```{r}
# Create list of columns that the aggregate variable will be determined by
over_65_fin_cols <- sr %>% select(starts_with("finance") & matches("65_[0-9]+cat_f_rc$")) %>% names()

# Apply function
sr_aggr <- aggr(over_65_fin_cols, over_65_fin_2cat, over_65_fin_2cat_f)
```

## Abuse in the past month
The category will be "yes" if the value is:
  - Less than 1 month ago
  
And "no" if the value is:
  - Between 1 month and less than 3 months ago
  - Between 3 months and less than 6 months ago
  - Between 6 months and less than 1 year ago
  - Between 1 year and less than 3 years ago
  - 3 or more years ago

for any of the variables related to ever abuse.

```{r}
# create past month variables
sr <- sr %>% 
  mutate(
    across(
      .cols = matches("last_time_[0-9]+cat_f_rc$"),
      .fns  = ~ case_when(
        .x == "Less than 1 month ago"                             ~ "Yes",
        .x == "Never experienced" | 
          (.x != "Less than 1 month ago" & !is.na(.x))            ~ "No",
        TRUE                                                      ~ NA
      ),
      .names = "{col}_pm"
    )
  ) %>%
  # rename the new columns
  rename_with(
    .cols   = ends_with("_pm"),
    .fn     = ~ gsub("_[0-9]+cat_f_rc_pm", "_pm", .x)
  )

```

### Physical abuse
```{r}
# Create list of columns that the aggregate variable will be determined by
pm_phys_cols <- sr %>% select(starts_with("physical") & ends_with("_pm")) %>% names()

# Apply function
sr_aggr <- aggr(pm_phys_cols, pm_phys_2cat, pm_phys_2cat_f)
```

### Sexual abuse
```{r}
# Create list of columns that the aggregate variable will be determined by
pm_sex_cols <- sr %>% select(starts_with("sexual") & ends_with("_pm")) %>% names()

# Apply function
sr_aggr <- aggr(pm_sex_cols, pm_sex_2cat, pm_sex_2cat_f)
```

### Emotional abuse
```{r}
# Create list of columns that the aggregate variable will be determined by
pm_emo_cols <- sr %>% select(starts_with("emotional") & ends_with("_pm")) %>% 
  names()

# Apply function
sr_aggr <- aggr(pm_emo_cols, pm_emo_2cat, pm_emo_2cat_f)
```

### Financial exploitation
```{r}
# Create list of columns that the aggregate variable will be determined by
pm_fin_cols <- sr %>% select(starts_with("finance") & ends_with("_pm")) %>% 
  names()

# Apply function
sr_aggr <- aggr(pm_fin_cols, pm_fin_2cat, pm_fin_2cat_f)
```

### Any abuse
```{r}
sr_aggr <- sr_aggr %>%
  mutate(
    # Create a column that has a value of 1 if at least one of the ever physical abuse variables have a value of "yes".
    ever_abuse_any_2cat = case_when(
      if_any((starts_with("ever") & ends_with("2cat")), ~. == 1) ~ 1,
      if_all((starts_with("ever") & ends_with("2cat")), ~. == 0) ~ 0,
      TRUE                                     ~ NA
    ),
    # Create a factor variable
    ever_abuse_any_2cat_f = factor(ever_abuse_any_2cat, 
                    levels = c(1, 0),
                    labels = c("Yes", "No")),
    # Create a column that has a value of 1 if at least one of the ever physical abuse variables have a value of "yes".
    over_65_abuse_any_2cat = case_when(
      if_any((starts_with("over_65") & ends_with("2cat")), ~. == 1)  ~ 1,
      if_all((starts_with("over_65") & ends_with("2cat")), ~. == 0)  ~ 0,
      TRUE                                     ~ NA
    ),
    # Create a factor variable
    over_65_abuse_any_2cat_f = factor(over_65_abuse_any_2cat, 
                    levels = c(1, 0),
                    labels = c("Yes", "No")),
    # Create a column that has a value of 1 if at least one of the ever physical abuse variables have a value of "yes".
    pm_abuse_any_2cat = case_when(
      if_any((starts_with("pm") & ends_with("2cat")), ~. == 1)  ~ 1,
      if_all((starts_with("pm") & ends_with("2cat")), ~. == 0)  ~ 0,
      TRUE                                                      ~ NA
    ),
    # Create a factor variable
    pm_abuse_any_2cat_f = factor(pm_abuse_any_2cat, 
                    levels = c(1, 0),
                    labels = c("Yes", "No")),
  )
```


# Create summary flextable

## Descriptions
```{r}
aggr_cols <- sr_aggr %>% select(ends_with("cat_f") & !starts_with("neglect_")) %>% names()

descriptions <- c(
 "Ever experienced physical mistreatment.",
 "Ever experienced sexual mistreatment.",
 "Ever experienced emotional mistreatment.",
 "Ever experienced financial exploitation.",
 "Potentially experienced any type of neglect",
 "Experienced physical mistreatment at age 65 or older.",
 "Experienced sexual mistreatment at age 65 or older.",
 "Experienced emotional mistreatment at age 65 or older.",
 "Experienced financial exploitation at age 65 or older.",
 "Experienced physical mistreatment in the past year.",
 "Experienced sexual mistreatment in the past year.",
 "Experienced emotional mistreatment in the past year.",
 "Experienced financial exploitation in the past year.",
 "Ever experienced any type of abuse.",
 "Experienced any type of abuse at age 65 or older.",
 "Experienced any type of abuse in the past year."
)

var <- aggr_cols

aggr_desc <- data.frame(var, descriptions)
```



```{r}
sum_aggr_list <- aggr_cols |>
  rlang::set_names(aggr_cols) |> 
  purrr::map(~ n_percent_ci(sr_aggr, !! rlang::sym(.x), 1))
```

```{r}
sum_aggr_table <- purrr::map_dfr(
  # Bind rows together
  .x = aggr_cols,
  .f = ~ dplyr::bind_rows(sum_aggr_list[[.x]])
)

# Reorder the columns so that `cat` comes after `var`
sum_aggr_table <- sum_aggr_table |> 
  dplyr::select(var, cat, everything())


# Add description column 
sum_aggr_table <- sum_aggr_table %>%
  left_join(., aggr_desc, by = c("var"))

```

```{r}
#| echo: false
# Split data frame into list of data frames by variable
sum_aggr_table_list <- split(sum_aggr_table, sum_aggr_table$var)

```

```{r, include = FALSE}
# Create flextable
cat_flextable <- function(var_name, table_list) {
  # Extract each variable data frame from list 
  df <- data.frame(table_list[[var_name]])
  
  # Set up table header line text including variable name and description
  title_cap <- as_paragraph(var_name)
  desc_cap <- df %>% select(descriptions) %>% unique() %>% toString() %>% as_paragraph()
  format_border <- fp_border(color = "black")
    
    # Create flextable
    flex_tab <- flextable(df, col_keys = c("var", "cat", "n", "formatted_stats")) %>%
      # Rename columns
      set_header_labels(
        var = "Variable", 
        cat = "Category", 
        "n" = "N",
        "formatted_stats" = "Percent of N (95% CI)") %>%
      
      # Shade alternating rows
      bg(i = ~ cat == "No", 
         bg = ("transparent"), 
         part = "body") %>%
      bg(i = ~ cat == "Yes", 
         bg = ("#f1f1f1"), 
         part = "body") %>%
      
      # Format Header lines
      add_header_lines(desc_cap) %>%
      add_header_lines(title_cap) %>%
      bg(bg = "transparent", part = "header", i = c(1,2)) %>%
      bold(i = 1, bold = TRUE, part = "header") %>%
      align(align = "left", part = "header") %>%
      # Add border lines to header
      border_remove() %>%
       surround(i = c(2,3), part = "header", border.bottom = format_border) %>%
      
      # Set width and alignment
      width(width = 4.8, unit = "in") %>%
      align(align = "left") %>%
      # add space for website view
      add_footer_lines("")
    
    flex_tab
}
```

```{r, results ='asis', echo=FALSE}
sum_aggr_flex <- lapply(aggr_cols, cat_flextable, table_list = sum_aggr_table_list)
sum_aggr_flex
```

# Print Word File
```{r}
title_style <- fp_text_lite(font.size = 18, bold = TRUE)

#  Create an empty Word document
aggr_doc <- read_docx()

aggr_doc <- aggr_doc %>%
  
  # Add Heading
  body_add_fpar(fpar(ftext("Self Report Aggregate Variable Tables", prop = title_style))) %>%
  body_add_par("")
  

for(var_name in aggr_cols) {
 aggr_flex <- cat_flextable(var_name, sum_aggr_table_list)
  # Set width of tables
  aggr_flex <- aggr_flex %>% width(j = c(1,2,3,4), width = c(2.3, 1.4, 1.4, 1.7), unit = "in") %>%
    # Remove space for document view
    delete_part(part = "footer") %>%
    # Prevent table breaking up into different pages.
    paginate(init = TRUE, hdr_ftr = TRUE)
  
  # Align tables and add a separating empty line between each table    
  aggr_doc <- aggr_doc %>%
    body_add_flextable(aggr_flex, align = "left") %>%
    body_add_par("")
}  

  

# print the word document
print(aggr_doc, target = "./self_report_aggregate.docx")
```

