---
title: "DETECT Data Descriptive Tables"
format: html
---

# Load packages
```{r, warning=FALSE, echo=FALSE, output = FALSE}
library(flextable)
library(table1)
library(dplyr)
library(tibble)
library(misty)
library(mice)
library(officer)
library(tidyverse)
```

## Load cleaned data

Load the general health and participant datasets

```{r}
#| warning: false
general_health <- readRDS("../data/cleaned_rds_files/general_health_import.rds")

participant <- readRDS("../data/cleaned_rds_files/participant.rds")

soc_dem <- readRDS("../data/cleaned_rds_files/sociodemographic_information_import.rds")

self_report <- readRDS("../data/cleaned_rds_files/self_report_import.rds")

aps <- readRDS("../data/cleaned_rds_files/aps_investigations_import.rds")
```

#UCLA loneliness scale

## Missing data summary

Create table that summarizes missing data using the md.pattern function 

```{r, fig.width = 12}
ls_m <- general_health %>%
  select(
    starts_with("ls") & ends_with("4cat_f")
  ) %>%
  md.pattern(., plot = F, rotate.names = T)

ls_m <- ls_m %>%
  as.data.frame() %>%
  rownames_to_column() %>%
  rename(
    No_of_rows = rowname,
    ls_lack_companionship = ls_lack_companionship_4cat_f,
    ls_feel_left_out = ls_feel_left_out_4cat_f,
    ls_feel_isolated = ls_feel_isolated_4cat_f,
    No_missing_per_row = V4
  ) %>%
  flextable()

ls_m <- add_footer_row(ls_m,
  values = c("A matrix with ncol(x)+1 columns, in which each row corresponds to a missing data pattern (1 = observed, 0 = missing). Rows and columns are sorted in increasing amounts of missing information. The last column and row contain row and column counts, respectively."),
  colwidths = c(5), top = TRUE
)

ls_m <- align(ls_m, align = "left", part = "all")

ls_m <- bold(ls_m, bold = TRUE, i = 5, part = "body")
ls_m <- bold(ls_m, bold = TRUE, j = 1, part = "body")
ls_m <- bold(ls_m, bold = TRUE, j = 5, part = "body")
ls_m <- set_caption(ls_m, "Missing Data Patterns")
ls_m <- width(ls_m, width = 1)

ls_m
```

## Unique people count

Table that summarizes counts of unique people that completed the UCLA loneliness scale

### Prepare data 

Merge relevant variables from the participant and general health datasets into one dataset and separate certain variables for the unique value summary excluding missing rows

```{r}
part_id <- participant %>%
  select(medstar_id, name_first, name_middle_initial, name_last, dob, sex_3cat_f, x_address_original)

# merge name columns into new full name column
part_id <- part_id %>%
  unite("name_full", "name_first":"name_last", sep = " ", na.rm = TRUE, remove = F) %>%
  relocate(name_full, .after = name_last)

ls <- general_health %>%
  select(
    medstar_id, x_record_month, x_record_year,
    starts_with("ls") & ends_with("4cat_f")
  ) %>%
  drop_na(c("ls_lack_companionship_4cat_f", "ls_feel_left_out_4cat_f", "ls_feel_isolated_4cat_f"))

gen_part <- left_join(ls, part_id)
gen_part <- gen_part %>% separate(x_address_original, into = c("house_number", "street_name"), sep = "^\\S*\\K\\s+")
```
### Create table
Table with counts of unique names and number of names that occur once or more than once excluding rows with missing data.

```{r, warning = FALSE}
# Unique people count

unique_people <- gen_part %>%
  select(name_first, name_last, dob, sex_3cat_f, house_number) %>%
  group_by_all() %>%
  summarise(count = n()) %>%
  unique()

# List of people whose names occur in only one row with complete ls scale data

ucs <- unique_people %>% filter(count == 1)

# People whose names occur in more than one row with complete ls scale data with the number of occurrences

nucs <- unique_people %>% filter(count > 1)

# Filtered dataset that includes only people that occur more than once

nucs_df <- filter(gen_part, name_full %in% nucs$Name)

# Table summarizing counts of unique names and number of names that occur once or more than once excluding rows with missing loneliness scale data

sum_table <- data.frame(
  Value = c("Unique people", "Occur multiple times", "Occur only once", "Total number of rows"),
  Count = c(nrow(unique_people), nrow(nucs), nrow(ucs), nrow(gen_part))
) %>%
  flextable()
# Set caption

sum_table <- set_caption(sum_table, "Unique and Non-unique Name Counts")
sum_table <- width(sum_table, width = 2)

sum_table
```

## Create descriptive tables

### Prepare data

Create a data subset that includes the loneliness scale data and excludes missing and 'refused' responses

```{r}
#| echo: false
#| eval: true
lsd <- general_health %>%
  select(
    medstar_id,
    starts_with("ls") & ends_with(c("4cat_f", "4cat"))
  ) %>%
  na.omit() %>%
  filter(
    if_all(
      everything(), ~ !grepl(paste("Refused", collapse = "|"), .)
    )
  ) %>%
  droplevels()
```

### Create descriptive table for categorical data

```{r}
# Create labels
label(lsd$ls_lack_companionship_4cat_f) <- "feel a lack of companionship"
label(lsd$ls_feel_left_out_4cat_f) <- "feel left out"
label(lsd$ls_feel_isolated_4cat_f) <- "feel isolated"
label(lsd$ls_lack_companionship_4cat) <- "feel a lack of companionship"
label(lsd$ls_feel_left_out_4cat) <- "feel left out"
label(lsd$ls_feel_isolated_4cat) <- "feel isolated"


cap_c <- "Basic Stats for UCLA Loneliness Scale"


ls_c <- table1(~ ls_lack_companionship_4cat_f + ls_feel_left_out_4cat_f + ls_feel_isolated_4cat_f, data = lsd, caption = cap_c)
ls_c <- t1flex(ls_c, tablefn = c("qflextable", "flextable", "regulartable"))
ls_c <- width(ls_c, width = 3)

ls_c
```

### Create descriptive table for scores (Calculating the UCLA scale scores individually)

```{r}
cap_s <- "Basic Stats for UCLA Loneliness Scale Numeric Scores (Individual)"


ls_s <- table1(~ ls_lack_companionship_4cat + ls_feel_left_out_4cat + ls_feel_isolated_4cat, data = lsd, caption = cap_s)
ls_s <- t1flex(ls_s, tablefn = c("qflextable", "flextable", "regulartable"))

ls_s <- width(ls_s, width = 3)

ls_s
```

### Create descriptive table for scores (Calculating the UCLA scale total score with SD)

```{r}
# Create column with total scores
lsd <- lsd %>% mutate(total_score = rowSums(.[2:4]))

# Create label
label(lsd$total_score) <- "total score"

# Create descriptive table
cap_t <- "Basic Stats for UCLA Loneliness Scale Numeric Scores (Total)"

ls_t <- table1(~total_score, data = lsd, caption = cap_t)
ls_t <- t1flex(ls_t, tablefn = c("qflextable", "flextable", "regulartable"))
ls_t <- width(ls_t, width = 3)

ls_t
```

# Sociodemographic Information

## Prepare data
Create data frame that includes requested socio-demographic information for rows that do not have any missing values or 'Refused' or 'Don't know responses for loneliness scale data. 

```{r}
# Select socio-demographic information variables
sdf <- soc_dem %>%
  select(c(8, 10:12, 17:42))

# Combine ls and sociodemographic data
soc_dem_ls <- left_join(lsd, sdf)

# Exclude 'Refused' and 'Don't know' responses for all variables
pat <- c("Don't know", "Refused")
soc_dem_ls_n <- soc_dem_ls %>%
  filter(
    if_all(
      everything(), ~ !grepl(paste(pat, collapse = "|"), .)
    )
  ) %>%
  droplevels() %>%
  mutate(
    sode_age_years = as.numeric(sode_age_years), sode_people = as.numeric(sode_people)
  )
```
## Create descriptive tables

### Categorical data

```{r}
# Create caption/ title
cap_soc <- "Basic Stats for Sociodemographic Information (Frequency)"


sdls_tab <- table1(~ sode_people_3cat_f + sode_race + sode_marital_8cat_f + sode_age_4cat_f + sode_hispanic_4cat_f + sode_school_9cat_f + sode_employed_11cat_f + sode_income_9cat_f + sode_military_4cat_f + sode_unwanted_4cat_f + sode_sexual_4cat_f + sogi_identity_5cat_f + sogi_orientation_8cat_f + hsi_contact_4cat_f,
  data = soc_dem_ls,
  caption = cap_soc
)
sdls_tab <- t1flex(sdls_tab, tablefn = c("qflextable", "flextable", "regulartable"))
sdls_tab <- width(sdls_tab, width = 3)
sdls_tab
```
### Numerically coded data


```{r}
cap_soc_n <- "Basic Stats for Sociodemographic Information (Central tendency)"


sdls_tab_n <- table1(~ sode_age_years + sode_age_4cat + sode_people + sode_marital_8cat + sode_hispanic_4cat + sode_school_9cat + sode_employed_11cat + sode_income_9cat + sode_military_4cat + sode_unwanted_4cat + sode_sexual_4cat + sogi_identity_5cat + sogi_orientation_8cat + hsi_contact_4cat,
  data = soc_dem_ls_n,
  caption = cap_soc_n
)
sdls_tab_n <- t1flex(sdls_tab_n, tablefn = c("qflextable", "flextable", "regulartable"))
sdls_tab_n <- width(sdls_tab_n, width = 3)

sdls_tab_n
```

# General Health
## Prepare the data

Filter out columns with unneeded variables and exclude rows that have any missing values or 'Refused' or 'Don't know responses for loneliness scale data. Create total scale score for PEG and depression variables.

```{r}
# Filter out columns with unneeded variables and exclude rows that have any missing values or 'Refused' or 'Don't know responses for loneliness scale data.
gh_ls <- general_health %>%
  select(-c(starts_with("outcomes_tf") | starts_with("nesarc"))) %>%
  drop_na(c("ls_lack_companionship_4cat_f", "ls_feel_left_out_4cat_f", "ls_feel_isolated_4cat_f")) %>%
  filter(
    if_all(
      c("ls_lack_companionship_4cat_f", "ls_feel_left_out_4cat_f", "ls_feel_isolated_4cat_f"),
      ~ !grepl(paste("Refused", collapse = "|"), .)
    )
  ) %>%
  droplevels()

# Create total score columns for PEG and depression variables.
gh_ls <- gh_ls %>% mutate(
  PEG_total = rowSums(.[14:16]),
  depres_total = rowSums(
    select(., (starts_with("depres") & ends_with("cat")))
  )
)

# Exclude 'Refused' and 'Don't know' responses for all variables
pat <- c("Don't know", "Refused")
gh_ls_n <- gh_ls %>%
  filter(
    if_all(
      everything(), ~ !grepl(paste(pat, collapse = "|"), .)
    )
  ) %>%
  droplevels()
```

## Create descriptive table

### Categorical Data

```{r}
cap_g <- "Basic Stats for General Health Data (Categories)"

gh_ls_tab <- table1(~ outcomes_health_vigorous_5cat_f + outcomes_health_moderate_5cat_f + outcomes_health_uphill_5cat_f + outcomes_health_bend_5cat_f + outcomes_health_block_5cat_f + outcomes_health_bathe_5cat_f + outcomes4_weeks_pain_8cat_f + outcomes_month_social_7cat_f + outcomes_month_nervous_7cat_f + outcomes_month_calm_7cat_f + outcomes_month_blue_7cat_f + outcomes_month_happy_7cat_f + outcomes_month_dumps_7cat_f + auditc_drink_7cat_f + auditc_day_7cat_f + auditc_five_7cat_f,
  data = gh_ls,
  caption = cap_g
)

gh_ls_tab <- t1flex(gh_ls_tab, tablefn = c("qflextable", "flextable", "regulartable"))
gh_ls_tab <- width(gh_ls_tab, width = 3)

gh_ls_tab
```

### Numerically coded data

```{r}
cap_g_n <- "Basic Stats for General Health Data"

gh_ls_n_tab <- table1(~ PEG_total + depres_total + outcomes_health_vigorous_5cat + outcomes_health_moderate_5cat + outcomes_health_uphill_5cat + outcomes_health_bend_5cat + outcomes_health_block_5cat + outcomes_health_bathe_5cat + outcomes4_weeks_pain_8cat + outcomes_month_social_7cat + outcomes_month_nervous_7cat + outcomes_month_calm_7cat + outcomes_month_blue_7cat + outcomes_month_happy_7cat + outcomes_month_dumps_7cat + auditc_drink_7cat + auditc_day_7cat + auditc_five_7cat,
  data = gh_ls_n,
  caption = cap_g_n
)

gh_ls_n_tab <- t1flex(gh_ls_n_tab, tablefn = c("qflextable", "flextable", "regulartable"))
gh_ls_n_tab <- width(gh_ls_n_tab, width = 3)

gh_ls_n_tab
```

# Self Report
## Prepare the data

Filter out columns with unneeded variables and exclude rows that have any missing values or 'Refused' or 'Don't know responses for loneliness scale data. 

```{r}
# Select relevant variables
sr_ls <- self_report %>%
  select(
    neglect_go_4cat, neglect_food_4cat, neglect_house_4cat, neglect_clean_4cat, neglect_ready_4cat,
    neglect_bills_4cat, neglect_go_help_5cat, neglect_food_help_5cat, neglect_house_help_5cat,
    neglect_clean_help_5cat, neglect_ready_help_5cat, neglect_bills_help_5cat, neglect_go_reliable_6cat,
    neglect_food_reliable_6cat, neglect_house_reliable_6cat, neglect_clean_reliable_6cat,
    neglect_ready_reliable_6cat, neglect_bills_reliable_6cat, neglect_person_12cat, finance_help_4cat,
    finance_person_permission_4cat, finance_person_decisions_4cat, finance_copies_4cat,
    finance_person_forged_4cat, finance_person_tricked_4cat, finance_person_stolen_4cat,
    finance_stranger_permission_4cat, finance_stranger_forged_4cat, finance_stranger_tricked_4cat,
    finance_person_permission65_4cat, finance_person_forged65_4cat, finance_person_tricked65_4cat,
    finance_person_stolen65_4cat, finance_stranger_permission65_4cat, finance_stranger_forged65_4cat,
    finance_stranger_tricked65_4cat, finance_person_12cat, finance_person_permission_last_time_8cat,
    finance_person_forged_last_time_8cat, finance_person_tricked_last_time_8cat,
    finance_person_stolen_last_time_8cat, finance_stranger_permission_last_time_8cat,
    finance_stranger_forged_last_time_8cat, finance_stranger_tricked_last_time_8cat,
    emotional_yelled_4cat, emotional_embarrassed_4cat, emotional_harassed_4cat, emotional_refused_4cat,
    emotional_incident_reported_4cat, emotional_person_help_4cat, emotional_person_no_live_4cat,
    emotional_yelled65_4cat, emotional_embarrassed65_4cat, emotional_harassed65_4cat,
    emotional_refused65_4cat, emotional_incident_reported_v2_4cat, emotional_person_live_then_4cat,
    emotional_person_live_now_4cat, emotional_incident_person_12cat, emotional_yelled_last_time_8cat,
    emotional_embarrassed_last_time_8cat, emotional_harassed_last_time_8cat,
    emotional_refused_last_time_8cat, emotional_yelled_times_7cat, emotional_embarrassed_times_7cat,
    emotional_harassed_times_7cat, emotional_refused_times_7cat, physical_hit_4cat,
    physical_restrain_4cat, physical_hurt_4cat, physical_incident_reported_4cat,
    physical_incident_person_4cat, physical_person_4cat, physical_person_help_4cat,
    physical_person_no_live_4cat, physical_hit65_4cat, physical_restrain65_4cat, physical_hurt65_4cat,
    physical_incident_reported_v2_4cat, physical_person_live_then_4cat, physical_person_live_now_4cat,
    emotional_incident_person_v2_12cat, physical_hit_last_time_8cat, physical_restrain_last_time_8cat,
    physical_hurt_last_time_8cat, physical_hit_times_7cat, physical_restrain_times_7cat,
    physical_hurt_times_7cat, physical_incident_person_v2_12cat, physical_person_12cat,
    sexual_harm_4cat, sexual_touched_4cat, sexual_forced_4cat, sexual_picture_4cat,
    sexual_incident_reported_4cat, sexual_incident_person_4cat, sexual_person_4cat,
    sexual_person_help_4cat, sexual_person_no_live_4cat, sexual_harm65_4cat, sexual_touched65_4cat,
    sexual_forced65_4cat, sexual_picture65_4cat, sexual_incident_reported_v2_4cat,
    sexual_person_live_then_4cat, sexual_person_live_now_4cat, sexual_harm_last_time_8cat,
    sexual_touched_last_time_8cat, sexual_forced_last_time_8cat, sexual_picture_last_time_8cat,
    sexual_harm_times_7cat, sexual_touched_times_7cat, sexual_forced_times_7cat,
    sexual_picture_times_7cat, sexual_incident_person_v2_12cat, neglect_go_4cat_f, neglect_food_4cat_f,
    neglect_house_4cat_f, neglect_clean_4cat_f, neglect_ready_4cat_f, neglect_bills_4cat_f,
    neglect_go_help_5cat_f, neglect_food_help_5cat_f, neglect_house_help_5cat_f,
    neglect_clean_help_5cat_f, neglect_ready_help_5cat_f, neglect_bills_help_5cat_f,
    neglect_go_reliable_6cat_f, neglect_food_reliable_6cat_f, neglect_house_reliable_6cat_f,
    neglect_clean_reliable_6cat_f, neglect_ready_reliable_6cat_f, neglect_bills_reliable_6cat_f,
    neglect_person_12cat_f, finance_help_4cat_f, finance_person_permission_4cat_f,
    finance_person_decisions_4cat_f, finance_copies_4cat_f, finance_person_forged_4cat_f,
    finance_person_tricked_4cat_f, finance_person_stolen_4cat_f, finance_stranger_permission_4cat_f,
    finance_stranger_forged_4cat_f, finance_stranger_tricked_4cat_f, finance_person_permission65_4cat_f,
    finance_person_forged65_4cat_f, finance_person_tricked65_4cat_f, finance_person_stolen65_4cat_f,
    finance_stranger_permission65_4cat_f, finance_stranger_forged65_4cat_f,
    finance_stranger_tricked65_4cat_f, finance_person_12cat_f,
    finance_person_permission_last_time_8cat_f, finance_person_forged_last_time_8cat_f,
    finance_person_tricked_last_time_8cat_f, finance_person_stolen_last_time_8cat_f,
    finance_stranger_permission_last_time_8cat_f, finance_stranger_forged_last_time_8cat_f,
    finance_stranger_tricked_last_time_8cat_f, emotional_yelled_4cat_f, emotional_embarrassed_4cat_f,
    emotional_harassed_4cat_f, emotional_refused_4cat_f, emotional_incident_reported_4cat_f,
    emotional_person_help_4cat_f, emotional_person_no_live_4cat_f, emotional_yelled65_4cat_f,
    emotional_embarrassed65_4cat_f, emotional_harassed65_4cat_f, emotional_refused65_4cat_f,
    emotional_incident_reported_v2_4cat_f, emotional_person_live_then_4cat_f,
    emotional_person_live_now_4cat_f, emotional_incident_person_12cat_f,
    emotional_yelled_last_time_8cat_f, emotional_embarrassed_last_time_8cat_f,
    emotional_harassed_last_time_8cat_f, emotional_refused_last_time_8cat_f,
    emotional_yelled_times_7cat_f, emotional_embarrassed_times_7cat_f, emotional_harassed_times_7cat_f,
    emotional_refused_times_7cat_f, emotional_incident_person_v2_12cat_f, physical_hit_4cat_f,
    physical_restrain_4cat_f, physical_hurt_4cat_f, physical_incident_reported_4cat_f,
    physical_incident_person_4cat_f, physical_person_4cat_f, physical_person_help_4cat_f,
    physical_person_no_live_4cat_f, physical_hit65_4cat_f, physical_restrain65_4cat_f,
    physical_hurt65_4cat_f, physical_incident_reported_v2_4cat_f, physical_person_live_then_4cat_f,
    physical_person_live_now_4cat_f, physical_hit_last_time_8cat_f, physical_restrain_last_time_8cat_f,
    physical_hurt_last_time_8cat_f, physical_hit_times_7cat_f, physical_restrain_times_7cat_f,
    physical_hurt_times_7cat_f, physical_incident_person_v2_12cat_f, physical_person_12cat_f,
    sexual_harm_4cat_f, sexual_touched_4cat_f, sexual_forced_4cat_f, sexual_picture_4cat_f,
    sexual_incident_reported_4cat_f, sexual_incident_person_4cat_f, sexual_person_4cat_f,
    sexual_person_help_4cat_f, sexual_person_no_live_4cat_f, sexual_harm65_4cat_f,
    sexual_touched65_4cat_f, sexual_forced65_4cat_f, sexual_picture65_4cat_f,
    sexual_incident_reported_v2_4cat_f, sexual_person_live_then_4cat_f, sexual_person_live_now_4cat_f,
    sexual_harm_last_time_8cat_f, sexual_touched_last_time_8cat_f, sexual_forced_last_time_8cat_f,
    sexual_picture_last_time_8cat_f, sexual_harm_times_7cat_f, sexual_touched_times_7cat_f,
    sexual_forced_times_7cat_f, sexual_picture_times_7cat_f, sexual_incident_person_v2_12cat_f,
    medstar_id
  )
# Merge filtered UCLA ls data with self report data
sr_ls <- left_join(lsd, sr_ls)

# Exclude 'Refused' and 'Don't know' responses for all variables
sr_ls_n <- sr_ls %>%
  filter(
    if_all(
      everything(), ~ !grepl(paste(pat, collapse = "|"), .)
    )
  ) %>%
  droplevels()
```

## Create descriptive table

### Categorical Data

```{r}
cap_sr <- "Basic Stats for Self Report Data (Categories)"

sr_ls_tab <- table1(~ neglect_go_4cat_f + neglect_food_4cat_f + neglect_house_4cat_f + neglect_clean_4cat_f + neglect_ready_4cat_f + neglect_bills_4cat_f + neglect_go_help_5cat_f + neglect_food_help_5cat_f + neglect_house_help_5cat_f + neglect_clean_help_5cat_f + neglect_ready_help_5cat_f + neglect_bills_help_5cat_f + neglect_go_reliable_6cat_f + neglect_food_reliable_6cat_f + neglect_house_reliable_6cat_f + neglect_clean_reliable_6cat_f + neglect_ready_reliable_6cat_f + neglect_bills_reliable_6cat_f + neglect_person_12cat_f + finance_help_4cat_f + finance_person_permission_4cat_f + finance_person_decisions_4cat_f + finance_copies_4cat_f + finance_person_forged_4cat_f + finance_person_tricked_4cat_f + finance_person_stolen_4cat_f + finance_stranger_permission_4cat_f + finance_stranger_forged_4cat_f + finance_stranger_tricked_4cat_f + finance_person_permission65_4cat_f + finance_person_forged65_4cat_f + finance_person_tricked65_4cat_f + finance_person_stolen65_4cat_f + finance_stranger_permission65_4cat_f + finance_stranger_forged65_4cat_f + finance_stranger_tricked65_4cat_f + finance_person_12cat_f + finance_person_permission_last_time_8cat_f + finance_person_forged_last_time_8cat_f + finance_person_tricked_last_time_8cat_f + finance_person_stolen_last_time_8cat_f + finance_stranger_permission_last_time_8cat_f + finance_stranger_forged_last_time_8cat_f + finance_stranger_tricked_last_time_8cat_f + emotional_yelled_4cat_f + emotional_embarrassed_4cat_f + emotional_harassed_4cat_f + emotional_refused_4cat_f + emotional_incident_reported_4cat_f + emotional_person_help_4cat_f + emotional_person_no_live_4cat_f + emotional_yelled65_4cat_f + emotional_embarrassed65_4cat_f + emotional_harassed65_4cat_f + emotional_refused65_4cat_f + emotional_incident_reported_v2_4cat_f + emotional_person_live_then_4cat_f + emotional_person_live_now_4cat_f + emotional_incident_person_12cat_f + emotional_yelled_last_time_8cat_f + emotional_embarrassed_last_time_8cat_f + emotional_harassed_last_time_8cat_f + emotional_refused_last_time_8cat_f + emotional_yelled_times_7cat_f + emotional_embarrassed_times_7cat_f + emotional_harassed_times_7cat_f + emotional_refused_times_7cat_f + emotional_incident_person_v2_12cat_f + physical_hit_4cat_f + physical_restrain_4cat_f + physical_hurt_4cat_f + physical_incident_reported_4cat_f + physical_incident_person_4cat_f + physical_person_4cat_f + physical_person_help_4cat_f + physical_person_no_live_4cat_f + physical_hit65_4cat_f + physical_restrain65_4cat_f + physical_hurt65_4cat_f + physical_incident_reported_v2_4cat_f + physical_person_live_then_4cat_f + physical_person_live_now_4cat_f + physical_hit_last_time_8cat_f + physical_restrain_last_time_8cat_f + physical_hurt_last_time_8cat_f + physical_hit_times_7cat_f + physical_restrain_times_7cat_f + physical_hurt_times_7cat_f + physical_incident_person_v2_12cat_f + physical_person_12cat_f + sexual_harm_4cat_f + sexual_touched_4cat_f + sexual_forced_4cat_f + sexual_picture_4cat_f + sexual_incident_reported_4cat_f + sexual_incident_person_4cat_f + sexual_person_4cat_f + sexual_person_help_4cat_f + sexual_person_no_live_4cat_f + sexual_harm65_4cat_f + sexual_touched65_4cat_f + sexual_forced65_4cat_f + sexual_picture65_4cat_f + sexual_incident_reported_v2_4cat_f + sexual_person_live_then_4cat_f + sexual_person_live_now_4cat_f + sexual_harm_last_time_8cat_f + sexual_touched_last_time_8cat_f + sexual_forced_last_time_8cat_f + sexual_picture_last_time_8cat_f + sexual_harm_times_7cat_f + sexual_touched_times_7cat_f + sexual_forced_times_7cat_f + sexual_picture_times_7cat_f + sexual_incident_person_v2_12cat_f,
  data = sr_ls,
  caption = cap_sr
)

sr_ls_tab <- t1flex(sr_ls_tab, tablefn = c("qflextable", "flextable", "regulartable"))
sr_ls_tab <- width(sr_ls_tab, width = 3)

sr_ls_tab
```

### Numerically coded data

```{r}
cap_sr_n <- "Basic Stats for Self Report Data"

sr_ls_n_tab <- table1(~ neglect_go_4cat + neglect_food_4cat + neglect_house_4cat + neglect_clean_4cat + neglect_ready_4cat + neglect_bills_4cat + neglect_go_help_5cat + neglect_food_help_5cat + neglect_house_help_5cat + neglect_clean_help_5cat + neglect_ready_help_5cat + neglect_bills_help_5cat + neglect_go_reliable_6cat + neglect_food_reliable_6cat + neglect_house_reliable_6cat + neglect_clean_reliable_6cat + neglect_ready_reliable_6cat + neglect_bills_reliable_6cat + neglect_person_12cat + finance_help_4cat + finance_person_permission_4cat + finance_person_decisions_4cat + finance_copies_4cat + finance_person_forged_4cat + finance_person_tricked_4cat + finance_person_stolen_4cat + finance_stranger_permission_4cat + finance_stranger_forged_4cat + finance_stranger_tricked_4cat + finance_person_permission65_4cat + finance_person_forged65_4cat + finance_person_tricked65_4cat + finance_person_stolen65_4cat + finance_stranger_permission65_4cat + finance_stranger_forged65_4cat + finance_stranger_tricked65_4cat + finance_person_12cat + finance_person_permission_last_time_8cat + finance_person_forged_last_time_8cat + finance_person_tricked_last_time_8cat + finance_person_stolen_last_time_8cat + finance_stranger_permission_last_time_8cat + finance_stranger_forged_last_time_8cat + finance_stranger_tricked_last_time_8cat + emotional_yelled_4cat + emotional_embarrassed_4cat + emotional_harassed_4cat + emotional_refused_4cat + emotional_incident_reported_4cat + emotional_person_help_4cat + emotional_person_no_live_4cat + emotional_yelled65_4cat + emotional_embarrassed65_4cat + emotional_harassed65_4cat + emotional_refused65_4cat + emotional_incident_reported_v2_4cat + emotional_person_live_then_4cat + emotional_person_live_now_4cat + emotional_incident_person_12cat + emotional_yelled_last_time_8cat + emotional_embarrassed_last_time_8cat + emotional_harassed_last_time_8cat + emotional_refused_last_time_8cat + emotional_yelled_times_7cat + emotional_embarrassed_times_7cat + emotional_harassed_times_7cat + emotional_refused_times_7cat + physical_hit_4cat + physical_restrain_4cat + physical_hurt_4cat + physical_incident_reported_4cat + physical_incident_person_4cat + physical_person_4cat + physical_person_help_4cat + physical_person_no_live_4cat + physical_hit65_4cat + physical_restrain65_4cat + physical_hurt65_4cat + physical_incident_reported_v2_4cat + physical_person_live_then_4cat + physical_person_live_now_4cat + emotional_incident_person_v2_12cat + physical_hit_last_time_8cat + physical_restrain_last_time_8cat + physical_hurt_last_time_8cat + physical_hit_times_7cat + physical_restrain_times_7cat + physical_hurt_times_7cat + physical_incident_person_v2_12cat + physical_person_12cat + sexual_harm_4cat + sexual_touched_4cat + sexual_forced_4cat + sexual_picture_4cat + sexual_incident_reported_4cat + sexual_incident_person_4cat + sexual_person_4cat + sexual_person_help_4cat + sexual_person_no_live_4cat + sexual_harm65_4cat + sexual_touched65_4cat + sexual_forced65_4cat + sexual_picture65_4cat + sexual_incident_reported_v2_4cat + sexual_person_live_then_4cat + sexual_person_live_now_4cat + sexual_harm_last_time_8cat + sexual_touched_last_time_8cat + sexual_forced_last_time_8cat + sexual_picture_last_time_8cat + sexual_harm_times_7cat + sexual_touched_times_7cat + sexual_forced_times_7cat + sexual_picture_times_7cat + sexual_incident_person_v2_12cat,
  data = sr_ls_n,
  caption = cap_sr_n
)

sr_ls_n_tab <- t1flex(sr_ls_n_tab, tablefn = c("qflextable", "flextable", "regulartable"))
sr_ls_n_tab <- width(sr_ls_n_tab, width = 3)

sr_ls_n_tab
```

# APS Investigations
## Prepare the data

Filter out columns with unneeded variables and exclude rows that have any missing values or 'Refused' or 'Don't know responses for loneliness scale data.

```{r}
# Select relevant variables
aps_ls <- aps %>%
  select(c(8, 15:22))

# Merge filtered UCLA ls data with self report data
aps_ls <- left_join(lsd, aps_ls)

# Exclude 'Refused' and 'Don't know' responses for all variables
aps_ls_n <- aps_ls %>%
  filter(
    if_all(
      everything(), ~ !grepl(paste(pat, collapse = "|"), .)
    )
  ) %>%
  droplevels()
```

## Create descriptive table

### Categorical Data

```{r}
cap_aps <- "Basic Stats for Self Report Data (Categories)"

aps_ls_tab <- table1(~ aps_report_4cat_f + aps_times_5cat_f + aps_first_8cat_f + aps_recent_8cat_f,
  data = aps_ls,
  caption = cap_aps
)

aps_ls_tab <- t1flex(aps_ls_tab, tablefn = c("qflextable", "flextable", "regulartable"))
aps_ls_tab <- width(aps_ls_tab, width = 3)

aps_ls_tab
```

### Numerically coded data

```{r}
cap_aps_n <- "Basic Stats for Self Report Data"

aps_ls_n_tab <- table1(~ aps_report_4cat + aps_times_5cat + aps_first_8cat + aps_recent_8cat,
  data = aps_ls_n,
  caption = cap_aps_n
)

aps_ls_n_tab <- t1flex(aps_ls_n_tab, tablefn = c("qflextable", "flextable", "regulartable"))
aps_ls_n_tab <- width(aps_ls_n_tab, width = 3)

aps_ls_n_tab
```

# Create Word Document

```{r, echo = FALSE}
# create Word file and object
detect_doc <- read_docx()

# Add title
text_style <- fp_text(font.size = 28)
par_style <- fp_par(text.align = "center")

detect_doc <- body_add_fpar(detect_doc, fpar(ftext("DETECT Data Summary", prop = text_style),
  fp_p = par_style
))
# Add UCLA ls tables
detect_doc <- detect_doc %>%
  body_add_par("UCLA Loneliness Scale Data", style = "heading 1") %>%
  body_add_par("There are 376 rows with completed UCLA loneliness scale data and 563 rows with at least one item missing.") %>%
  body_add_par(value = "") %>%
  body_add_flextable(ls_m, align = "left") %>%
  body_add_par(value = "") %>%
  body_add_par("The table shows the counts for unique people while excluding rows with at least one missing UCLA scale item.") %>%
  body_add_par(value = "") %>%
  body_add_flextable(sum_table, align = "left") %>%
  body_add_par(value = "") %>%
  body_add_par("The tables show the summary statistics for the UCLA three item scale while excluding rows with at least one missing UCLA scale item as well as rows where response to any item question was refused.") %>%
  body_add_par(value = "") %>%
  body_add_flextable(ls_c, align = "left") %>%
  body_add_par(value = "") %>%
  body_add_flextable(ls_s, align = "left") %>%
  body_add_par(value = "") %>%
  body_add_flextable(ls_t, align = "left") %>%
  body_add_par(value = "")

# Add Sociodemographic Information tables
detect_doc <- detect_doc %>%
  body_add_par("Sociodemographic Information Data", style = "heading 1") %>%
  body_add_par("The table below shows the frequencies for categorical variables in the sociodemographic Information dataset while excluding rows where items in the UCLA loneliness scale were either missing or had a response of 'Refused'.") %>%
  body_add_par(value = "") %>%
  body_add_flextable(sdls_tab, align = "left") %>%
  body_add_par(value = "") %>%
  body_add_par("The table below shows the central tendency and variation measures for some numerically coded sociodemographic information variables while excluding rows where items in the UCLA loneliness scale were either missing or had a response of 'Refused'. Additionally, rows that had 'Refused' and 'Don't know' responses for the sociodemographic information variables were filtered out.") %>%
  body_add_par(value = "") %>%
  body_add_flextable(sdls_tab_n, align = "left")

# Add General Health Data tables
detect_doc <- detect_doc %>%
  body_add_par("General Health Data", style = "heading 1") %>%
  body_add_par("The table below shows the frequencies for categorical variables in the general health dataset while excluding rows where items in the UCLA loneliness scale were either missing or had a response of 'Refused'.") %>%
  body_add_par(value = "") %>%
  body_add_flextable(gh_ls_tab, align = "left") %>%
  body_add_par(value = "") %>%
  body_add_par("The table below shows the central tendency and variation measures for some numerically coded general health variables while excluding rows where items in the UCLA loneliness scale were either missing or had a response of 'Refused'. Additionally, rows that had 'Refused' and 'Don't know' responses for the general health variables were filtered out.") %>%
  body_add_par(value = "") %>%
  body_add_flextable(gh_ls_n_tab, align = "left")

# Add Self Report Data tables
detect_doc <- detect_doc %>%
  body_add_par("Self Report Data", style = "heading 1") %>%
  body_add_par("The table below shows the frequencies for categorical variables in the self report dataset while excluding rows where items in the UCLA loneliness scale were either missing or had a response of 'Refused'.") %>%
  body_add_par(value = "") %>%
  body_add_flextable(sr_ls_tab, align = "left") %>%
  body_add_par(value = "") %>%
  body_add_par("The table below shows the central tendency and variation measures for some numerically coded self report variables while excluding rows where items in the UCLA loneliness scale were either missing or had a response of 'Refused'. Additionally, rows that had 'Refused' and 'Don't know' responses for the self report variables were filtered out.") %>%
  body_add_par(value = "") %>%
  body_add_flextable(sr_ls_n_tab, align = "left")

# Add APS Investigations Data tables
detect_doc <- detect_doc %>%
  body_add_par("APS Investigations Data", style = "heading 1") %>%
  body_add_par("The table below shows the frequencies for categorical variables in the APS Investigations dataset while excluding rows where items in the UCLA loneliness scale were either missing or had a response of 'Refused'.") %>%
  body_add_par(value = "") %>%
  body_add_flextable(aps_ls_tab, align = "left") %>%
  body_add_par(value = "") %>%
  body_add_par("The table below shows the central tendency and variation measures for some numerically coded APS Investigations variables while excluding rows where items in the UCLA loneliness scale were either missing or had a response of 'Refused'. Additionally, rows that had 'Refused' and 'Don't know' responses for the APS Investigations variables were filtered out.") %>%
  body_add_par(value = "") %>%
  body_add_flextable(aps_ls_n_tab, align = "left")

# print the word document
print(detect_doc, target = "UCLA_loneliness_scale_descriptive_summary.docx")
```
